### 2020-02-04 analysis/step1_get_drawings/THU_Drawings/1_checksubjects/subID_check.Rmd
port experiments & analyses for photodraw from kiddraw to new repo

---
title: "tsinghua-subids"
author: "Bria Long"
date: "1/16/2020"
output: html_document
---

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

```{r}
is_test = c('Ipad5',
'P0000',
'Test',
'Test4',
'Test5','Ipad2_tes3','Ipad1','ipad4_Test1','ipad4_Test1')

# ids in database
IDs_DB <- read_csv('subject_logs/subIDs_afterNov15.csv') %>%
  rowwise() %>%
  mutate(is_test = str_detect(subID,'test')) %>%
  filter(is_test==FALSE) %>%
  mutate(ID_Database = str_replace_all(subID,' ','')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
  mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
  mutate(ID_Database = str_to_upper(ID_Database))  %>%
  mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2])

# ids in subject log
IDs_SL <- read_csv('subject_logs/KIDDRW_THU_cleaned.csv') %>%
  select(age, gender, ID_age, CB, ID, note,db_mismatch) %>%
  rowwise() %>%
  mutate(ID_SubjectLog = str_replace_all(ID,' ','')) %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'-','_'))  %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'__','_')) %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'I','i'))  %>%
  mutate(ID_SubjectLog = str_to_upper(ID_SubjectLog))  %>%
  mutate(iPad_Used = str_split(ID_SubjectLog,"[_]")[[1]][1],Short_SubID = str_split(ID_SubjectLog,"[_]")[[1]][2])

merged <- IDs_SL %>%
  left_join(IDs_DB, by=c("iPad_Used","Short_SubID"))

mismatch <- merged %>%
  filter(is.na(ID_Database)) %>%
  select(-db_mismatch, -subID, -is_test, -note)

db_only <- IDs_DB %>%
  left_join(IDs_SL, by=c("iPad_Used","Short_SubID")) %>%
  filter(is.na(ID_SubjectLog))

write_csv(db_only,'db_only_IDs.csv')
write_csv(mismatch,'no_db_entry.csv')

```

```{r}

# no_ipad_assigned = c("IPA2_THU9F41"  , "IPAD_THU5F6"  , "IPAD_THU6F13" ,  "IPAD_THU7M12"  , "IPAD_THU8M21" )
# 
# #mismatch candidates
# 
# mismatch_maybes <- c('IPAD1_1THU6F30',

match_count=0
subid_count=0
sorted_DB_Ids=array()
reported_IDS <- unique(reported_IDS)
db_IDS <- IDs$ID_Database
for (this_subid in reported_IDS){
  subid_count = subid_count +1
  match = !is.na(str_detect(this_subid, db_IDS))

  # if any matches
  if (sum(match)>0){
  match_count = match_count +1
  match_ind = which(!is.na(str_locate(this_subid, db_IDS)))[1]

  sorted_DB_Ids[subid_count] = db_IDS[match_ind]
  }
  else{
  sorted_DB_Ids[subid_count] = 'NA'
  }

}
```

```{r}
# ID_matches = bind_cols(data.frame(reported_IDS), data.frame(sorted_DB_Ids))
# num_matches = sum(!is.na(ID_matches$sorted_DB_Ids))
# need_matches = ID_matches$reported_IDS[is.na(ID_matches$sorted_DB_Ids)]

```

```{r}
db_sorted = sort(IDs$ID_Database)
not_matched_db <- as_tibble(db_sorted) %>%
  filter(!is.na(value)) %>%
  filter(!value %in% sorted_DB_Ids) %>%
  rowwise() %>%
  mutate(iPad_Used = str_split(value,"[_]")[[1]][1],SubID = str_split(value,"[_]")[[1]][2]) %>%
  mutate(age = str_split_fixed(SubID,'THU',2)[,2])

need_matches <- as_tibble(need_matches) %>%
  rowwise() %>%
  mutate(iPad_Used = str_split(value,"[_]")[[1]][1],SubID = str_split(value,"[_]")[[1]][2]) %>%
  mutate(maybe_match = SubID %in% not_matched_db$SubID)

super_confused <- need_matches %>%
  filter(maybe_match==FALSE)

## typo
IPAD1_1THU6F30 = IPAD1_THU6F30

# 
# write_csv(not_matched_db, "non-matched-db.csv")
# write_csv(as_tibble(need_matches), "Tsinghua_DB_need_matches.csv")
# db_sorted = sort(IDs$ID_Database)

```

### 2020-02-04 analysis/step2_get_features_and_classifications/1_extract_features/embedding.py

@@ -1,0 +1,287 @@
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+import copy
+import numpy as np
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from PIL import Image
+
+## feature dimensions by layer_ind
+## 0: [64, 112, 112] = 802,816
+## 1: [128, 56, 56] = 401,408
+## 2: [256, 28, 28] = 200,704
+## 3: [512, 14, 14] = 100,352
+## 4: [512, 7, 7] = 50,176
+## 5: [1, 4096]
+## 6: [1, 4096]
+
+use_cuda = torch.cuda.is_available()
+
+class VGG19Embeddings(nn.Module):
+    """Splits vgg19 into separate sections so that we can get
+    feature embeddings from each section.
+
+    :param vgg19: traditional vgg19 model
+    """
+    def __init__(self, vgg19, layer_index=-1, spatial_avg=True):
+        super(VGG19Embeddings, self).__init__()
+        self.conv1 = nn.Sequential(*(list(vgg19.features.children())[slice(0, 5)]))
+        self.conv2 = nn.Sequential(*(list(vgg19.features.children())[slice(5, 10)]))
+        self.conv3 = nn.Sequential(*(list(vgg19.features.children())[slice(10, 19)]))
+        self.conv4 = nn.Sequential(*(list(vgg19.features.children())[slice(19, 28)]))
+        self.conv5 = nn.Sequential(*(list(vgg19.features.children())[slice(28, 37)]))
+        self.linear1 = nn.Sequential(*(list(vgg19.classifier.children())[slice(0, 2)]))
+        self.linear2 = nn.Sequential(*(list(vgg19.classifier.children())[slice(3, 5)]))
+        self.linear3 = nn.Sequential(list(vgg19.classifier.children())[-1])
+        layer_index = int(float(layer_index)) # bll 
+        assert layer_index >= -1 and layer_index < 8
+        self.layer_index = layer_index
+        self.spatial_avg = spatial_avg
+
+    def _flatten(self, x):
+        if (self.spatial_avg==True) & (self.layer_index<5):
+            x = x.mean(3).mean(2)
+        return x.view(x.size(0), -1)   
+
+    def forward(self, x):
+        # build in this ugly way so we don't have to evaluate things we don't need to.
[…]

### 2020-02-04 analysis/step2_get_features_and_classifications/1_extract_features/extract_all_images.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+python extract_features.py --data='/data3/bria/kiddraw_datasets/photodraw2_020519/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw2_020519'
+
+python extract_features.py --data='/data3/bria/kiddraw_datasets/photodraw2_030719/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw2_030719'

### 2020-02-04 analysis/step2_get_features_and_classifications/1_extract_features/extract_features.py

@@ -1,0 +1,144 @@
+from __future__ import division
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from glob import glob
+import os
+
+import numpy as np
+import pandas as pd
+import json
+import re
+
+from PIL import Image
+import base64
+
+from embedding import *
+
+# retrieve sketch paths
+def list_files(path, ext='png'):
+    result = [y for x in os.walk(path) for y in glob(os.path.join(x[0], '*.%s' % ext))]
+    return result
+
+def check_invalid_sketch(filenames,invalids_path='images_to_exclude.txt'):    
+    if not os.path.exists(invalids_path):
+        print('No file containing invalid paths at {}'.format(invalids_path))
+        invalids = []        
+    else:
+        print('found invalids file...')
+        x = pd.read_csv(invalids_path, header=None)
+        x.columns = ['filenames']
+        invalids = list(x.filenames.values)
+    valids = []   
+    basenames = [f.split('/')[-1] for f in filenames]
+    for i,f in enumerate(basenames):
+        if f not in invalids:
+            valids.append(filenames[i])
+    return valids
+
+def make_dataframe(Labels,Ages,Sessions):    
+    Y = pd.DataFrame([Labels,Ages,Sessions])
+    Y = Y.transpose()
+    Y.columns = ['label','age','session']   
+    return Y
+
+def make_dataframe_photodraw(Labels,Ages,Sessions,Conditions):    
+    Y = pd.DataFrame([Labels,Ages,Sessions,Conditions])
+    Y = Y.transpose()
+    Y.columns = ['label','age','session','condition']   
+    return Y
+
+def normalize(X):
+    X = X - X.mean(0)
+    X = X / np.maximum(X.std(0), 1e-5)
+    return X
+
+def preprocess_features(Features, Y):
+    _Y = Y.sort_values(['label','age','session'])
+    inds = np.array(_Y.index)
+    _Features = normalize(Features[inds])
+    _Y = _Y.reset_index(drop=True) # reset pandas dataframe index
+    return _Features, _Y
+
+def save_features(Features, Y, layer_num, cohort,spatial_avg,dataset):
+    if not os.path.exists('./features'):
+        os.makedirs('./features')
+    layers = ['P1','P2','P3','P4','P5','FC6','FC7']
[…]

### 2020-02-04 analysis/step2_get_features_and_classifications/2_run_classsificatinos/run_classification_multiprocess.py

@@ -1,0 +1,147 @@
+# libraries
+from __future__ import division
+
+import time
+import pandas as pd
+import numpy as np
+import os
+import thread
+import subprocess
+import urllib, cStringIO
+import scipy.stats as stats
+import multiprocessing
+import subprocess
+from multiprocessing.dummy import Pool as ThreadPool 
+
+
+## scikit learn
+import sklearn
+from sklearn.model_selection import train_test_split, cross_val_score
+from sklearn import svm
+from sklearn import linear_model, datasets, neighbors
+from sklearn import metrics
+from sklearn.model_selection import LeaveOneOut
+
+## for rebalancing datasetes
+from imblearn.under_sampling import RandomUnderSampler
+
+'''
+This script run_classification_jobs.py is a wrapper around the main function get_classifications.
+to generate csv files that summarize key statistics of interest (e.g., classificaiton scores and probabilitioes)
+from model predictions, for each model and data split.
+
+It will spawn several threads to get predictions from all splits and models.
+'''
+
+################################################################################################################################
+
+def load_features(cohort, layer_num):
+    layers = ['P1','P2','P3','P4','P5','FC6','FC7']    
+    F = np.load('/data5/bria/kiddraw_datasets/{}/features/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
+    M = pd.read_csv('/data5/bria/kiddraw_datasets/{}/features/METADATA_{}.csv'.format(DATASET, cohort)) 
+    #  F = np.load('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
+    # M = pd.read_csv('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/METADATA_{}.csv'.format(DATASET, cohort)) 
+    M = M[['label','age','session']]
+    return F, M
+
+def balance_dataset(KF, KM):
+    rus = RandomUnderSampler(random_state=0) ## always have same random under sampling
+    KF_downsampled, class_labels_downsampled = rus.fit_resample(KF, KM['label'].values)
+    new_samples_ind = rus.sample_indices_
+    KM_downsampled = KM.loc[new_samples_ind]
+    X = KF_downsampled
+    Y = class_labels_downsampled
+    return(X,Y,KM_downsampled)
+
[…]

### 2020-02-04 analysis/z_photodraw_pilot/python/embedding.py

@@ -1,0 +1,263 @@
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+import copy
+import numpy as np
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from PIL import Image
+
+## feature dimensions by layer_ind
+## 0: [64, 112, 112] = 802,816
+## 1: [128, 56, 56] = 401,408
+## 2: [256, 28, 28] = 200,704
+## 3: [512, 14, 14] = 100,352
+## 4: [512, 7, 7] = 50,176
+## 5: [1, 4096]
+## 6: [1, 4096]
+
+use_cuda = torch.cuda.is_available()
+
+class VGG19Embeddings(nn.Module):
+    """Splits vgg19 into separate sections so that we can get
+    feature embeddings from each section.
+
+    :param vgg19: traditional vgg19 model
+    """
+    def __init__(self, vgg19, layer_index=-1, spatial_avg=True):
+        super(VGG19Embeddings, self).__init__()
+        self.conv1 = nn.Sequential(*(list(vgg19.features.children())[slice(0, 5)]))
+        self.conv2 = nn.Sequential(*(list(vgg19.features.children())[slice(5, 10)]))
+        self.conv3 = nn.Sequential(*(list(vgg19.features.children())[slice(10, 19)]))
+        self.conv4 = nn.Sequential(*(list(vgg19.features.children())[slice(19, 28)]))
+        self.conv5 = nn.Sequential(*(list(vgg19.features.children())[slice(28, 37)]))
+        self.linear1 = nn.Sequential(*(list(vgg19.classifier.children())[slice(0, 2)]))
+        self.linear2 = nn.Sequential(*(list(vgg19.classifier.children())[slice(3, 5)]))
+        self.linear3 = nn.Sequential(list(vgg19.classifier.children())[-1])
+        layer_index = int(float(layer_index)) # bll 
+        assert layer_index >= -1 and layer_index < 8
+        self.layer_index = layer_index
+        self.spatial_avg = spatial_avg
+
+    def _flatten(self, x):
+        if (self.spatial_avg==True) & (self.layer_index<5):
+            x = x.mean(3).mean(2)
+        return x.view(x.size(0), -1)   
+
+    def forward(self, x):
+        # build in this ugly way so we don't have to evaluate things we don't need to.
[…]

### 2020-02-04 analysis/z_photodraw_pilot/python/extract_all_images.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+for i in {0..6}
+    do
+	echo 'extracting image features from layer ' $i
+	python extract_features.py --data='/data2/jefan/imagenet_kiddraw' --layer_ind=$i --cohort='images' --ext="jpg" --spatial_avg=False
+    done
+
+
+
+python extract_features.py --data='/home/bria/kiddraw/data/photodraw_sketches/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True

### 2020-02-04 analysis/z_photodraw_pilot/python/extract_features.py

@@ -1,0 +1,129 @@
+from __future__ import division
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from glob import glob
+import os
+
+import numpy as np
+import pandas as pd
+import json
+import re
+
+from PIL import Image
+import base64
+
+from embedding import *
+
+# retrieve sketch paths
+def list_files(path, ext='png'):
+    result = [y for x in os.walk(path) for y in glob(os.path.join(x[0], '*.%s' % ext))]
+    return result
+
+def check_invalid_sketch(filenames,invalids_path='images_to_exclude.txt'):    
+    if not os.path.exists(invalids_path):
+        print('No file containing invalid paths at {}'.format(invalids_path))
+        invalids = []        
+    else:
+        print('found invalids file...')
+        x = pd.read_csv(invalids_path, header=None)
+        x.columns = ['filenames']
+        invalids = list(x.filenames.values)
+    valids = []   
+    basenames = [f.split('/')[-1] for f in filenames]
+    for i,f in enumerate(basenames):
+        if f not in invalids:
+            valids.append(filenames[i])
+    return valids
+
+def make_dataframe(Labels,Ages,Sessions,Conditions):    
+    Y = pd.DataFrame([Labels,Ages,Sessions,Conditions])
+    Y = Y.transpose()
+    Y.columns = ['label','age','session','condition']   
+    return Y
+
+def normalize(X):
+    X = X - X.mean(0)
+    X = X / np.maximum(X.std(0), 1e-5)
+    return X
+
+def preprocess_features(Features, Y):
+    _Y = Y.sort_values(['label','age','session'])
+    inds = np.array(_Y.index)
+    _Features = normalize(Features[inds])
+    _Y = _Y.reset_index(drop=True) # reset pandas dataframe index
+    return _Features, _Y
+
+def save_features(Features, Y, layer_num, cohort,spatial_avg):
+    if not os.path.exists('./features'):
+        os.makedirs('./features')
+    layers = ['P1','P2','P3','P4','P5','FC6','FC7']
+    np.save('/home/bria/kiddraw/data/photodraw_features/FEATURES_{}_{}_Spatial_{}.npy'.format(layers[int(layer_num)], cohort,spatial_avg), Features)
+    Y.to_csv('/home/bria/kiddraw/data/photodraw_features/METADATA_{}.csv'.format(cohort))
[…]

### 2020-02-04 experiments/0_photodraw_pilot/recognition_ratings/batch1/experiment/sketchRecognize.js

@@ -1,0 +1,222 @@
+// ############################ Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) 
+{ 
+    var o = [];
+    
+    for (var i=0; i < a.length; i++) {
+	o[i] = a[i];
+    }
+    
+    for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+    return o;
+}
+
+// ######################## Experiment specific functinons ############################
+
+$(document).ready(function() {
+
+
+$.ajax({
+    type: "GET",
+    url: "sketchNames_batch1_balanced.csv",
+    dataType: "text",
+    success: function(data) {
+            results = Papa.parse(data); // parse csv file
+
+            //set up image names
+            imgArray = new Array();
+            for (i = 1; i < results.data.length; i++) {
+                var session_id= results.data[i][0]; //starts i at 1 to get rid of header
+                var category = results.data[i][4];
+                var age = results.data[i][1];
+                var condition = results.data[i][3];
+                var imageSet = results.data[i][5];
+                imgArray[i] = new Image();
+                imgArray[i].src = ['sketches_by_condition_only/' + condition + '/' +  category + '_sketch_' + session_id + '_' + condition + '_age' + age + '.png'];
+                imgArray[i].category = category;
+                imgArray[i].age = age;
[…]

### 2020-02-04 experiments/0_photodraw_pilot/recognition_ratings/batch2/experiment/sketchRecognize.js

@@ -1,0 +1,222 @@
+// ############################ Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) 
+{ 
+    var o = [];
+    
+    for (var i=0; i < a.length; i++) {
+	o[i] = a[i];
+    }
+    
+    for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+    return o;
+}
+
+// ######################## Experiment specific functinons ############################
+
+$(document).ready(function() {
+
+
+$.ajax({
+    type: "GET",
+    url: "sketchNames_batch2_balanced.csv",
+    dataType: "text",
+    success: function(data) {
+            results = Papa.parse(data); // parse csv file
+
+            //set up image names
+            imgArray = new Array();
+            for (i = 1; i < results.data.length; i++) {
+                var session_id= results.data[i][0]; //starts i at 1 to get rid of header
+                var category = results.data[i][4];
+                var age = results.data[i][1];
+                var condition = results.data[i][3];
+                var imageSet = results.data[i][5];
+                imgArray[i] = new Image();
+                imgArray[i].src = ['sketches_by_condition_only/' + condition + '/' +  category + '_sketch_' + session_id + '_' + condition + '_age' + age + '.png'];
+                imgArray[i].category = category;
+                imgArray[i].age = age;
[…]

### 2020-02-04 experiments/photodraw2/code/trial-sequence.js

@@ -1,0 +1,803 @@
+/* 
+
+Handles dynamic elements of standard kidddraw task
+Oct 9 2018 photodraw2 updates
+
+*/
+// General to-do
+// 1. Record new audio (watch, triangle, rectangle)
+// 2. Make atypical triangle and rectangle images (ask Renata maybe how she did this?)
+// 3. Finish stimuli selection, resizing, renaming to .jpg, put in file folder.
+
+// 6. Change DB name for pilot and then for run time
+// 7. Check CB entering on splash page is intuitive
+
+// 4. Double check stroke saving timestamps here (done)
+// 5. Port over simplified stroke saving framework from new museumstation (done)
+
+paper.install(window);
+socket = io.connect();
+
+// Set global variables
+var curTrial=0 // global variable, trial counter
+var clickedSubmit=0; // whether an image is submitted or not
+var tracing = true; //whether the user is in tracing trials or not
+var maxTraceTrial = 2; //the max number of tracing trials
+var numPracticeTrials = maxTraceTrial + 1; // number of tracing trials
+var timeLimit=30;
+var disableDrawing = false; //whether touch drawing is disabled or not
+var language = "English";
+
+// current mode and session info
+var mode = "CDM";
+var version =mode + "_photodraw" + "_e2"; // set experiment name
+var sessionId=version + Date.now().toString();
+
+var consentPage = '#consentBing';
+var thanksPage = "#thanksBing";
+var maxTrials;
+var stimList = [];
+var subID = $('#subID').val();
+
+var strokeThresh = 3; // each stroke needs to be at least this many pixels long to be sent
+
+var stimLang = {
+    "square": "square",
+    "triangle": "triangle",
+    "rectangle": "rectangle",
+    "airplane": "an airplane",
+    "bike": "a bike",
+    "bird": "a bird",
+    "car": "a car",
+    "cat": "a cat",
+    "chair": "a chair",
+    "cup": "a cup",
+    "hat": "a hat",
+    "house": "a house",
+    "rabbit": "a rabbit",
+    "tree": "a tree",
+    "watch": "a watch", 
+}
+
+
+
+
+
+// HELPER FUNCTIONS - GENERAL
+function getRandomInt(min, max) {
+    return Math.floor(Math.random() * (max - min + 1)) + min;
+}
+
+// shuffle the order of drawing trials
+function shuffle (a)
+{
+    var o = [];
[…]

### 2020-02-04 experiments/photodraw2/recognition_ratings_setup/0-experiment/sketchRecognize_chunk3.js

@@ -1,0 +1,342 @@
+// ############################ Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+    $('#recognitionInput').focus();
+}
+
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) 
+{ 
+    var o = [];
+    
+    for (var i=0; i < a.length; i++) {
+	o[i] = a[i];
+    }
+    
+    for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+    return o;
+}
+
+// ######################## Experiment specific functinons ############################
+
+$(document).ready(function() {
+
+$.ajax({
+    type: "GET",
+    url: "recognition_rating_chunks/chunk_" + 3 + "photodraw2_srcd_recognition.csv",
+    dataType: "text",
+    success: function(data) {
+
+            results = Papa.parse(data); // parse csv file
+
+            //set up image arrays for both practice/catch trials 
+            pracArray = new Array();
+            chunk = 3;
+            
+            prac_categories = ['bird','dog','fish','rabbit'] 
+            index=0
+            for (i = 0; i < 3; i++){ // 3 exemplars for 4 categories = 12 validation trials
+
+                for(j = 0; j < (prac_categories.length); j++){
+                    this_prac_category = prac_categories[j]
+                    var session_id= 'null'
+                    var age = 'photo'
[…]

### 2020-09-03 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
preprocessing code to make filtered dataset

---
title: "preprocess_sketches"
author: "Bria Long"
date: "9/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(here)
library(lubridate)
```

```{r}
final_subject_info = here::here('data/THU/demographics/final_subject_info.csv')
demo = read_csv(final_subject_info)
```

```{r}
drawing_path = here::here('data/THU/drawings/full_set/')
filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
dir.create(filtered_dataset_path)
```

```{r}
all_drawings = list.files(path=drawing_path, pattern = ".png$", recursive = TRUE) %>%
    as_tibble()  %>%
    rename(fullPath = value)

drawing_info = all_drawings %>%
    mutate(fileNameShort = str_split_fixed(fullPath,"/",2)[,2]) %>%
    mutate(condition = str_split_fixed(fileNameShort,"_",2)[,1]) %>%
    mutate(category = str_split_fixed(fileNameShort,"_",3)[,2]) %>%
    mutate(raw_db_id = str_split_fixed(fileNameShort,"_",4)[,4]) %>%
    mutate(raw_db_id = str_split_fixed(raw_db_id,"_20",2)[,1]) %>%
    mutate(ID_Database = str_replace_all(raw_db_id,' ','')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
    mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
    mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
    mutate(ID_Database = str_to_upper(ID_Database))  %>%
    mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2]) %>%
   select(ID_Database, better_filename, fileNameShort, fullPath, category, condition)

```

```{r}
drawings_to_include <- drawing_info %>%
  left_join(demo, by=c('ID_Database')) %>%
  filter(!is.na(Age)) %>%
  mutate(age_group = floor(Age)) %>%
  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))

```

# copy included drawings and rename
```{r}
file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))
```

```{r}

drawings_by_category <- drawings_to_include %>%
  group_by(category, condition) %>%
  summarize(num_drawings = length(fileNameShort))

```

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/extract_features.py
change path for saving feature outputs

@@ -69,8 +69,8 @@ def save_features(Features, Y, layer_num, cohort,spatial_avg,dataset):
     if not os.path.exists('./features'):
         os.makedirs('./features')
     layers = ['P1','P2','P3','P4','P5','FC6','FC7']
-    np.save('/data5/bria/kiddraw_datasets/{}/features/FEATURES_{}_{}_Spatial_{}.npy'.format(dataset,layers[int(layer_num)], cohort,spatial_avg), Features)
-    Y.to_csv('/data5/bria/kiddraw_datasets/{}/features/METADATA_{}.csv'.format(dataset,cohort))
+    np.save('/devphotodraw/data/{}/features/FEATURES_{}_{}_Spatial_{}.npy'.format(dataset,layers[int(layer_num)], cohort,spatial_avg), Features)
+    Y.to_csv('/devphotodraw/data/{}/features/METADATA_{}.csv'.format(dataset,cohort))
     return layers[int(layer_num)]
 
 def convert_age(Ages):

### 2020-09-03 analysis/step1_get_drawings/CDM_Drawings/photodraw2/1_render_all_sketches_photodraw.py
update rendering code for new server

@@ -32,12 +32,12 @@ exclude_ids = ['102618_3',
 # set path to database connectinos 
 auth = pd.read_csv('auth.txt', header = None) 
 pswd = auth.values[0][0]
-user = 'sketchloop'
-host = 'rxdhawkins.me' ## cocolab ip address
+user = 'stanford'
+host = 'stanford-cogsci.org' ## cocolab ip address
 
 ## use pymongo for database
 import pymongo as pm
-conn = pm.MongoClient('mongodb://sketchloop:' + pswd + '@127.0.0.1')
+conn = pm.MongoClient('mongodb://stanford:' + pswd + '@127.0.0.1')
 db = conn['kiddraw']
 photodraw_e2 = db['CDM_photodraw_e2']
 
@@ -231,4 +231,4 @@ for s in subIDS_to_render:
 X_out = pd.DataFrame([session_id,trial_num,category,age,submit_time,submit_date,num_strokes,draw_duration_old,draw_duration_new,trial_duration, mean_intensity, bounding_box, filename,condition, CB, subID, image_name])
 X_out = X_out.transpose()
 X_out.columns = ['session_id','trial_num','category','age','submit_time','submit_date','num_strokes','draw_duration_old','draw_duration_new','trial_duration','mean_intensity','bounding_box','filename','condition','CB','subID','image_name']
-X_out.to_csv(os.path.join(output_dir,'MuseumStation_AllDescriptives_{}_images_final_{}.csv'.format(writeImageCount,which_run)))   
+X_out.to_csv(os.path.join(output_dir,'Photodraw2_CDM_AllDescriptives_{}_images_final_{}.csv'.format(writeImageCount,which_run)))   

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/extract_all_images.sh
update paths for features/classifications

@@ -2,4 +2,4 @@
 
 python extract_features.py --data='/data3/bria/kiddraw_datasets/photodraw2_020519/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw2_020519'
 
-python extract_features.py --data='/data3/bria/kiddraw_datasets/photodraw2_030719/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw2_030719'
+python extract_features.py --data='/home/bria/devphotodraw/data/object_drawings/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='compiled'

### 2020-09-03 analysis/step2_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py

@@ -37,8 +37,8 @@ It will spawn several threads to get predictions from all splits and models.
 
 def load_features(cohort, layer_num):
     layers = ['P1','P2','P3','P4','P5','FC6','FC7']    
-    F = np.load('/data3/bria/kiddraw_datasets/{}/features/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
-    M = pd.read_csv('/data3/bria/kiddraw_datasets/{}/features/METADATA_{}.csv'.format(DATASET, cohort)) 
+    F = np.load('/home/bria/devphotodraw/data/{}/features/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
+    M = pd.read_csv('/home/bria/devphotodraw/data/{}/features/METADATA_{}.csv'.format(DATASET, cohort)) 
     #  F = np.load('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
     # M = pd.read_csv('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/METADATA_{}.csv'.format(DATASET, cohort)) 
     M = M[['label','age','session']]
@@ -94,21 +94,21 @@ def get_classifications(test_index):
     print 'finished and saving!'
     if not os.path.exists(out_path_specific):
         os.makedirs(out_path_specific)
-    out.to_csv(os.path.join(out_path_specific,'photodraw2_subset_classification_ind_{}.csv'.format(test_index_numeric)))
+    out.to_csv(os.path.join(out_path_specific,'devphotodraw_all_classification_ind_{}.csv'.format(test_index_numeric)))
 
 ################################################################################################################################
 
 #### SPECIFY PARAMETERS
-DATASET = 'photodraw2_030719' ## no features yet
+DATASET = 'compiled' ## no features yet
 LAYER_IND = 6
-OUT_PATH = 'classification-outputs-030719'
+OUT_PATH = 'classification-outputs-092020'
 REGULARIZE_PARAM = .1
 
 # start clock
 start_time = time.time()
 
-start_ind=10
-end_ind=100
+start_ind=0
+end_ind=1000
 
 for this_ind in range(start_ind, end_ind):
 	print 'getting classifications for index {}'.format(this_ind)

### 2020-09-03 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
code to get filtered, object drawings for features/classifications

@@
 ---
-title: "preprocess_sketches"
+title: "preprocess_sketches THU"
 author: "Bria Long"
@@
 drawing_path = here::here('data/THU/drawings/full_set/')
-filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
-dir.create(filtered_dataset_path)
+# filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
+# filtered_dataset_path =  here::here('data/THU/drawings/object_drawings')
+compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
+# dir.create(filtered_dataset_path)
+dir.create(compiled_dataset_path)
 ```
@@
     mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2]) %>%
-   select(ID_Database, better_filename, fileNameShort, fullPath, category, condition)
+   select(ID_Database, fileNameShort, fullPath, category, condition)
 
@@
 ```{r}
+practice_categories = c('triangle','this shape','this square','rectangle')
+
 drawings_to_include <- drawing_info %>%
@@
   mutate(age_group = floor(Age)) %>%
-  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))
+  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))  %>%
+  filter(!category %in% practice_categories)
 
@@
 ```{r}
-file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))
+# file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))
+
+file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
 ```

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/extract_features.py
fix path typo

@@ -69,8 +69,8 @@ def save_features(Features, Y, layer_num, cohort,spatial_avg,dataset):
     if not os.path.exists('./features'):
         os.makedirs('./features')
     layers = ['P1','P2','P3','P4','P5','FC6','FC7']
-    np.save('/devphotodraw/data/{}/features/FEATURES_{}_{}_Spatial_{}.npy'.format(dataset,layers[int(layer_num)], cohort,spatial_avg), Features)
-    Y.to_csv('/devphotodraw/data/{}/features/METADATA_{}.csv'.format(dataset,cohort))
+    np.save('/home/bria/devphotodraw/data/{}/features/FEATURES_{}_{}_Spatial_{}.npy'.format(dataset,layers[int(layer_num)], cohort,spatial_avg), Features)
+    Y.to_csv('/home/bria/devphotodraw/data/{}/features/METADATA_{}.csv'.format(dataset,cohort))
     return layers[int(layer_num)]
 
 def convert_age(Ages):

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/embedding.py
change extract features for photodraw metadata

@@ -166,7 +166,7 @@ class FeatureExtractor():
 
             if self.dataset=='rendered_111918':
                 label = path.split('/')[-1].split('_')[0]
-            elif self.dataset=='photodraw2_030719':
+            elif self.dataset=='photodraw_compiled':
                 label = path.split('/')[-1].split('_')[1]   
                 condition = path.split('/')[-1].split('_')[0]
             else:
@@ -186,7 +186,7 @@ class FeatureExtractor():
                 print('Need to specify a cohort: "kid" or "adult"!')
                 age = 'unknown'
                 session = 'unknown'
-            if self.dataset=='photodraw2_030719':
+            if self.dataset=='photodraw_compiled':
                 return label, age, session, condition        
             else:
                 return label, age, session
@@ -194,7 +194,7 @@ class FeatureExtractor():
         def generator(paths, imsize=self.imsize, use_cuda=use_cuda, dataset=self.dataset):
             for path in paths:
                 image = load_image(path)
-                if self.dataset=='photodraw2_030719':
+                if self.dataset=='photodraw_compiled':
                     label, age, session, condition = get_metadata_from_path(path,dataset)
                     yield (image, label, age, session,condition)        
                 else:
@@ -233,7 +233,7 @@ class FeatureExtractor():
                     print('Batch {}'.format(n + 1))            
                 for b in range(batch_size):
                     try:
-                        if self.dataset=='photodraw2_030719':
+                        if self.dataset=='photodraw_compiled':
                             sketch, label, age, session, condition = generator.next()
                             sketch_batch[b] = sketch 
                             label_batch.append(label)
@@ -279,7 +279,7 @@ class FeatureExtractor():
         Ages = np.array([item for sublist in Ages for item in sublist])
         Sessions = np.array([item for sublist in Sessions for item in sublist])
 
-        if self.dataset=='photodraw2_030719':
+        if self.dataset=='photodraw_compiled':
             Conditions = np.array([item for sublist in Conditions for item in sublist])
             return Features, Labels, Ages, Sessions, Conditions
         else:

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/extract_all_images.sh

@@ -2,4 +2,4 @@
 
 python extract_features.py --data='/data3/bria/kiddraw_datasets/photodraw2_020519/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw2_020519'
 
-python extract_features.py --data='/home/bria/devphotodraw/data/object_drawings/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='compiled'
+python extract_features.py --data='/home/bria/devphotodraw/data/object_drawings/' --layer_ind=6 --cohort='kid' --ext="png" --spatial_avg=True --dataset='photodraw_compiled'

### 2020-09-03 analysis/step2_get_features_and_classifications/1_extract_features/extract_features.py

@@ -118,7 +118,7 @@ if __name__ == "__main__":
     layers = ['P1','P2','P3','P4','P5','FC6','FC7']
     extractor = FeatureExtractor(sketch_paths,layer=args.layer_ind,cohort=args.cohort,spatial_avg=args.spatial_avg, dataset=args.dataset)
     
-    if args.dataset=='photodraw2_030719':
+    if args.dataset=='photodraw_compiled':
         Features, Labels, Ages, Sessions, Conditions = extractor.extract_feature_matrix()
     else:
         Features, Labels, Ages, Sessions = extractor.extract_feature_matrix()
@@ -129,7 +129,7 @@ if __name__ == "__main__":
         Ages = convert_age(Ages)       
         
     # organize metadata into dataframe
-    if args.dataset=='photodraw2_030719':
+    if args.dataset=='photodraw_compiled':
         Y = make_dataframe_photodraw(Labels,Ages,Sessions,Conditions)
     else:
         Y = make_dataframe(Labels,Ages,Sessions)

### 2020-09-03 analysis/step2_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
reorg classification folder; change names

@@ -99,7 +99,7 @@ def get_classifications(test_index):
 ################################################################################################################################
 
 #### SPECIFY PARAMETERS
-DATASET = 'compiled' ## no features yet
+DATASET = 'photodraw_compiled' ## no features yet
 LAYER_IND = 6
 OUT_PATH = 'classification-outputs-092020'
 REGULARIZE_PARAM = .1

### 2021-04-28 analysis/step1_get_drawings/THU_Drawings/1_download_sketches/render_metadata_and_sketches.py
script to render THU metadata from couchdb

@@ -1,0 +1,173 @@
+### Set up libraries
+from __future__ import division
+
+import os
+import urllib, cStringIO
+
+import numpy as np
+import scipy.stats as stats
+import pandas as pd
+import json
+import re
+
+from PIL import Image
+import base64
+import datetime
+import time
+import couchdb
+
+auth = pd.read_csv('auth.txt', header = None) 
+server_address_input = auth.values[0][0]
+couch = couchdb.Server(server_address_input)
+db = couch['tsinghua-draw'] 
+db.info()
+
+sketch_dir='THU_sketches_and_metadata'
+if not os.path.exists(sketch_dir):
+    os.makedirs(sketch_dir)
+
+
+def load_image_data(imgData,imsize):
+    filestr = base64.b64decode(imgData)
+    fname = os.path.join('sketch.png')
+    with open(fname, "wb") as fh:
+        fh.write(imgData.decode('base64'))
+    im = Image.open(fname).resize((imsize,imsize))
+    _im = np.array(im)
+    return(_im)
+
+def get_mean_intensity(img,imsize):
+    thresh = 250
+    numpix = imsize**2
+    mean_intensity = len(np.where(img[:,:,3].flatten()>thresh)[0])/numpix
+    return mean_intensity
+    
+def get_bounding_box(img):
+    rows = np.any(img, axis=1)
+    cols = np.any(img, axis=0)
+    rmin, rmax = np.where(rows)[0][[0, -1]]
+    cmin, cmax = np.where(cols)[0][[0, -1]]
+    bounding_box = tuple((rmin, rmax, cmin, cmax))
+    return bounding_box
+
+
+## img writing parameters
+imsize = 224
+
+## desired output: a dataframe that has trials on the rows, and the following columns:
+## category, age, number of strokes, mean_pixel_intensity, bounding_box_coordinates_LTRB, list of strokes, 
+## PNG string, submission_time, submission_date
+## to be saved out as a nice tidy CSV
+session_id = []
+subid=[]
+trial_num = []
+category = []
+num_strokes = []
+mean_intensity = []
+bounding_box = []
+svg = []
+_svg_start_times = []
+_svg_end_times = []
+png = []
+submit_time = []
+submit_date = []
+draw_duration = []
+draw_duration_strokes = []
+filename = []
+age=[]
+condition=[]
+readadble_date = []
+imsize = 224 ## img writing size, optimized for CNN
+
+
[…]

### 2021-04-28 analysis/step1_get_drawings/THU_Drawings/2_subject_log_checks/Step1_subid_clean_and_check.Rmd
scripts to automatically merge subject logs and resave darwings

---
title: "tsinghua-subids"
author: "Bria Long"
date: "1/16/2020"
output: html_document
---

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
library(here)
theme_set(theme_few())
```

## Read in manually matched IDs
```{r}
IDs_match <- read_csv('subject_logs/correct_matches.csv') %>%
  rename(ID_SubjectLog = ID_SubjectLog_cleaned) %>%
  filter(!is.na(ID_Database_raw)) %>% # 3 subjects for whom we don't have matches at all
  mutate(ID_Database = str_replace_all(ID_Database_raw,' ','')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
  mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
  mutate(ID_Database = str_to_upper(ID_Database))  %>%
  rowwise() %>%
  mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2])

```

## Read in Ids from  database

```{r}
### test ids
is_test = c('Ipad5',
'P0000',
'Test',
'Test4',
'Test5','Ipad2_tes3','Ipad1','ipad4_Test1','ipad4_Test1')
```

```{r}
IDs_DB <- read_csv('subject_logs/subIDs_afterNov15.csv') %>%
  rowwise() %>%
  mutate(is_test = str_detect(subID,'test')) %>%
  filter(is_test==FALSE) %>%
  mutate(ID_Database = str_replace_all(subID,' ','')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'-','_'))  %>%
  mutate(ID_Database = str_replace_all(ID_Database,'__','_')) %>%
  mutate(ID_Database = str_replace_all(ID_Database,'I','i'))  %>%
  mutate(ID_Database = str_to_upper(ID_Database))  %>%
  mutate(iPad_Used = str_split(ID_Database,"[_]")[[1]][1],Short_SubID = str_split(ID_Database,"[_]")[[1]][2]) %>%
  rename(ID_Database_raw = subID)
```

### Read in IDs from subject log
```{r}
# ids in subject log
IDs_SL <- read_csv('subject_logs/subject_log_sept2020.csv') %>%
  select(Age, Sex, ID, CB, note,Date) %>%
  rowwise() %>%
  mutate(ID_SubjectLog = str_replace_all(ID,' ','')) %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'-','_'))  %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'__','_')) %>%
  mutate(ID_SubjectLog = str_replace_all(ID_SubjectLog,'I','i'))  %>%
  mutate(ID_SubjectLog = str_to_upper(ID_SubjectLog))  %>%
  mutate(iPad_Used = str_split(ID_SubjectLog,"[_]")[[1]][1],Short_SubID = str_split(ID_SubjectLog,"[_]")[[1]][2]) 
```

```{r}

# need to use specdal spreadsheet for these subjects
to_fix <- IDs_SL %>% # get ids from subject log
  filter(ID_SubjectLog %in% IDs_match$ID_SubjectLog) %>% # get set of subjects in subject log that we had to manually match 
  left_join(IDs_match %>% select(ID_SubjectLog, ID_Database_raw, ID_Database))  
```
```{r}
# can merge with subject log here
merged <- IDs_SL %>%
  filter(!ID_SubjectLog %in% IDs_match$ID_SubjectLog) %>%
  left_join(IDs_DB, by=c("iPad_Used","Short_SubID")) %>%
  full_join(to_fix)

## assumption is didn't record these due to technical eerrors
mismatch <- merged %>%
  filter(is.na(ID_Database)) %>%
  select(-is_test, -note)

write_csv(mismatch,'no_db_entry_sept2020_tech_errors.csv')
```

## Save out information
```{r}
final_subject_info <-  merged %>%
  filter(!is.na(ID_Database))

write_csv(final_subject_info,here::here('data/THU/demographics/final_subject_info.csv'))
```

```{r}
subs_by_age <- final_subject_info %>%
  mutate(age_group = floor(Age)) %>%
  group_by(age_group) %>%
  summarize(count_subs = length(unique(ID_Database)))
```

### 2021-04-28 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
scripts to automatically merge subject logs and resave darwings

@@
 
+# demographics information for subjects
 ```{r}
@@
 
+# paths to drawings and where they should be copied
 ```{r}
 drawing_path = here::here('data/THU/drawings/full_set/')
+# these will contain tracings/drawings from all THU/CDM sessions
+compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
+compiled_tracing_dataset_path = here::here('data/compiled/drawings/tracings')
+dir.create(compiled_dataset_path)
+dir.create(compiled_tracing_dataset_path)
+
+# old structure
 # filtered_dataset_path =  here::here('data/THU/drawings/filtered_dataset')
 # filtered_dataset_path =  here::here('data/THU/drawings/object_drawings')
-compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
 # dir.create(filtered_dataset_path)
-dir.create(compiled_dataset_path)
 ```
 
+# grab pngs of rendered drawings
 ```{r}
@@
 
+# copy tracings/drawings into separate folderes
 ```{r}
@@
   mutate(age_group = floor(Age)) %>%
-  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))  %>%
+  mutate(better_filename = paste0(condition, '_',category, '_sketch_age',age_group, '_', ID_Database,'.png'))
+
+object_drawings <- drawings_to_include %>%
   filter(!category %in% practice_categories)
 
+tracings_to_include <- drawings_to_include %>%
+  filter(category %in% practice_categories)
 ```
 
-# copy included drawings and rename
+# summarize number of drawings/tracings that we had
 ```{r}
-# file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(filtered_dataset_path, drawings_to_include$better_filename))
+drawings_by_category <- object_drawings %>%
+  group_by(category, condition) %>%
+  summarize(num_drawings = length(fileNameShort))
 
+tracings_by_category <- tracings_to_include %>%
+  group_by(category) %>% 
+  summarize(num_drawings = length(fileNameShort))
+```
+
+# copy included drawings/tracings and rename
+```{r}
 file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
@@
 ```{r}
-
-drawings_by_category <- drawings_to_include %>%
-  group_by(category, condition) %>%
-  summarize(num_drawings = length(fileNameShort))
-
+file.copy(fs::path(drawing_path, tracings_to_include$fullPath), fs::path(compiled_tracing_dataset_path, tracings_to_include$better_filename))
 ```

### 2021-04-28 analysis/step2_get_features_and_classifications/2_run_classsificatinos/count_classification_outputs.Rmd
update classification count script

---
title: "Count and compile classifications"
output: html_notebook
---

## Check we have values for all images
```{r}
library(tidyverse)
current_dir <- "classification-outputs-092020_C_0.1"
files <- dir(current_dir)
indexes = array()
count=0
for (f in files){
  count = count +1
  this_csv = read.csv(paste0(current_dir,'/',f)) 
  indexes[count] = this_csv$index
}
```

```{r}
index_full_array = seq.int(0,max(indexes),1)
index_full_array = as.tibble(index_full_array)

indexes_missing <- index_full_array %>%
  filter(! value %in% indexes)
```

## Make joined CSV
```{r}

files <- dir(current_dir) 
indexes = array()
options(warn=-1) # lots of warningss for full_join over and over even though it's fine

count=0
for (f in files){
  count = count +1
  this_csv = read.csv(paste0(current_dir,'/',f)) 
  if (count==1){
    all_data = this_csv
  }
  all_data <- all_data %>%
    full_join(this_csv)
}
```

```{r}
write.csv(all_data, paste0('compiled_classifications/Classification_Outputs',count,'.csv'))

```

### 2021-04-28 analysis/step4_main_analyses_both_sites/main_analysis.Rmd
remove old files

---
title: "Examine_classifications"
author: "Bria Long"
date: "4/9/2021"
output: html_document
---

```{r, libraries}
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(langcog)
library(forcats)
library(egg)
library(gridExtra)
library(reticulate)
library(readr)
library(ggplot2)
library(reshape2)
library(lme4)
library(stringr)
library(viridis)
library(MuMIn)
library(here)
theme_set(theme_few())
```

## Load compiled classification data
```{r load-classifications}
classification_data <- read.csv('compiled_classifications/Classification_Outputs2832.csv') %>%
  as.tibble() %>%
  # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site))
```

## Need to rewrite some code to get meta-data for couchdb/mongodb dumps
```{r}
## Load in meta data from mongo-db database dumps
# metadata_photodraw <- read.csv('mongodb-output/Photodraw2_AllDescriptives_1475_images_final_CDM_photodraw_e2_no_blanks.csv') %>%
#   as.tibble() %>%
#   mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
#   mutate(session_id = as.factor(session_id)) %>%
#   mutate(draw_duration_new = replace(draw_duration_new, draw_duration_new > 30,30))
# 
# ## join with classification data
# d <- classification_data %>%
#   left_join(metadata_photodraw) %>%
#   mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2]))
```

## Read in meta data fed to classifications
```{r}
meta <- read_csv(here('data/compiled/meta/METADATA_kid.csv'))
```

## Compile some sanity checks on counts of draiwngs per site/condition/etc
```{r}
sanity_counts <- classification_data %>%
  left_join(meta, by=c('session_id' = 'session', 'category' = 'label')) %>%
  filter(age_numeric < 10) %>%
  group_by(condition,age_numeric, site) %>%
  summarize(num_drawings = n()) %>%
  kable()
```

```{r}
participant_counts <- d %>%
  group_by(age_numeric, site) %>%
  summarize(num_participants = length(unique(session_id)))

count_by_site <- d %>%
  group_by(site) %>%
  summarize(num_participants = length(unique(session_id)))

count_by_category <- d %>%
  group_by(category) %>%
  summarize(num_drawings = length(unique(session_id)), what = length(unique(index)))

what <- d %>%
  group_by(index) %>%
  summarize(num_ids = length(session_id)) %>%
  filter(num_ids >1)

count_by_id <- d %>%
  group_by(session_id) %>%
  summarize(num_drawings = length(unique(category))) 
```

265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum & Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children aged 4-9 years of age after exclusions (i.e. 20 4-year-olds, 20 5-year-olds). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, leading to a final sample of `r count_by_site$num_participants[1]` children. In the China based sample, 140 children participated; (10) participants were tested but their data was not recorded due to a technical error with the remote database, leading to a final sample of `r count_by_site$num_participants[2]`. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification. On average, each child contributed `r mean(count_by_id$num_drawings)` to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`) with leaving 232-234 drawings per category.

# Descriptive anlayses
```{r descriptives-across-age}
### How do our covariates change with age? Compute means and CIs; Group by age/category
## first join  data  
d <- classification_data %>% 
  left_join(meta, by=c('session_id' = 'session', 'category' = 'label'))

```

```{r}
cor_by_age <- d %>%  
  group_by(session_id,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(cor_by_age, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) + 
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~site)
```

### Correlation of item effects across sites
```{r}
item_effects <- d %>%
  group_by(session_id,age_numeric,category, site) %>%
  summarize(avg_sub_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,category, site) %>%
  summarize(avg_cor = mean(avg_sub_cor)) %>%
  spread(key=site, value=avg_cor)

ggplot(item_effects, aes(x=CDM, y=THU, color=age_numeric)) +
  # geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.5)) + 
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  # labs(x='Age', y='Classification accuracy') +
  # scale_color_viridis(option="D") + 
  # theme(legend.position = "none") + 
  # geom_smooth(col='grey',span=10, alpha=smooth_alpha) +
  ylim(0,1) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_wrap(~category)
```

```{r}
item_effects_no_age <- d %>%
  group_by(session_id,category, site) %>%
  summarize(avg_sub_cor = mean(correct_or_not)) %>%
  group_by(category, site) %>%
  summarize(avg_cor = mean(avg_sub_cor)) %>%
  spread(key=site, value=avg_cor)

ggplot(item_effects_no_age, aes(x=CDM, y=THU, color=category)) +
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  geom_abline(intercept = 0, slope=1)
```

# Inferential stats
```{r}
full_model <- glmer(correct_or_not ~ condition*age_numeric+ site +
                        (1|session_id) +
                        (1|category),
      data = d, family="binomial")

summary(full_model)

```

# Witheffort covariates (not ready yet)
```{r}
draw_duration <- d %>%
  group_by(session_id,condition,age_numeric) %>%
  summarize(avg_draw_duration = mean(draw_duration_new)) %>%
  group_by(age_numeric,condition) %>%
  multi_boot_standard(col = "avg_draw_duration")

num_strokes <- d %>%
  group_by(session_id,condition,age_numeric) %>%
  summarize(avg_num_strokes = mean(num_strokes)) %>%
  group_by(age_numeric,condition) %>%
  multi_boot_standard(col = "avg_num_strokes")

avg_intensity <- d %>%
  group_by(session_id,condition,age_numeric) %>%
  summarize(avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric,condition) %>%
  multi_boot_standard(col = "avg_intensity")

```

```{r plot-descriptives-across-age}
## Make compiled plot of descriptives
base_size_chosen=18 # size of text in plots
smooth_alpha=.2

cor_by_age_plot_A = ggplot(cor_by_age, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) + 
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  # scale_color_viridis(option="D") + 
  theme(legend.position = "none") +
  # geom_smooth(col='grey',span=10, alpha=smooth_alpha) +
  # ggtitle('A') + 
  ylim(0,.75) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey")

p1=ggplot(draw_duration, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Draw duration (s)') +
  # scale_color_viridis(option="D") +
  theme(legend.position = "none") + 
  ylim(0,20) 
  # geom_smooth(col='grey', span = 10) +
  # ggtitle('B')

p2=ggplot(avg_intensity, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Ink used (mean intensity)') +
  # scale_color_viridis(option="D") +
  theme(legend.position = "none") + 
  ylim(.02,.08) 
  # geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  # ggtitle('C')

p3=ggplot(num_strokes, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Number of strokes') +
  # scale_color_viridis(option="D") +
  theme(legend.position = "right") +
  ylim(0,15) 
  # geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  # ggtitle('D')

# p4=ggplot(tracing_scores, aes(age_numeric,mean, color=age_numeric)) +
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   theme_few(base_size = base_size_chosen) +
#   labs(x='Age', y='Normalized tracing score') +
#   # scale_color_viridis(option="D") +
#   theme(legend.position = "none") + 
#   geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
#   ggtitle('E')
```

### 2021-04-28 analysis/step1b_get_cumulative_drawings/svg_helpers.py
remove older files to old directory

@@ -1,142 +1,0 @@
-def polyline_pathmaker(lines):
-    x = []
-    y = []
-
-    codes = [Path.MOVETO] # start with moveto command always
-    for i,l in enumerate(lines):
-        for _i,_l in enumerate(l):
-            x.append(_l[0])
-            y.append(_l[1])
-            if _i<len(l)-1:
-                codes.append(Path.LINETO) # keep pen on page
-            else:
-                if i != len(lines)-1: # final vertex
-                    codes.append(Path.MOVETO)
-    verts = zip(x,y) 
-    return verts, codes
-
-def path_renderer(verts, codes):
-    fig = plt.figure(figsize=(6,6))
-    ax = fig.add_subplot(111)
-    if len(verts)>0:
-        path = Path(verts, codes)
-        patch = patches.PathPatch(path, facecolor='none', lw=2)
-        ax.add_patch(patch)
-        ax.set_xlim(0,1638)
-        ax.set_ylim(0,1638) 
-        ax.axis('off')
-        plt.gca().invert_yaxis() # y values increase as you go down in image
-        plt.show()
-    else:
-        ax.set_xlim(0,1638)
-        ax.set_ylim(0,1638)        
-        ax.axis('off')
-        plt.show()
-    plt.savefig()
-    plt.close()
-    
-def flatten(x):
-    return [val for sublist in x for val in sublist]
-
-    def get_verts_and_codes(svg_list):
-    '''
-    parse into x,y coordinates and output list of lists of coordinates
-    
-    '''    
-    lines = []
-    Verts = []
-    Codes = []
-    for stroke_ind,stroke in enumerate(svg_list):
-        x = []
-        y = []
-        parsed = parse_path(stroke)
-        for i,p in enumerate(parsed):
-            if i!=len(parsed)-1: # last line segment
-                x.append(p.start.real)
-                y.append(p.start.imag)    
-            else:
-                x.append(p.start.real)
-                y.append(p.start.imag)     
-                x.append(p.end.real)
-                y.append(p.end.imag)
-        lines.append(zip(x,y))
-        verts, codes = polyline_pathmaker(lines)
-        Verts.append(verts)
-        Codes.append(codes) 
-    return Verts, Codes
-    
-def make_svg_list(stroke_recs):
-    '''
-    grab sample drawing's strokes and make a list of svg strings from it
-    '''
-    svg_list = []
-    for single_stroke in stroke_recs:
-        svg_string = single_stroke['svg']
-        svg_list.append(svg_string)  
-        
[…]

### 2021-04-28 analysis/step2_clean_metadata/merge_and_clean_datasets.Rmd
new folder for cleaning metadata in analysis pipeline

---
title: "Examine_photodraw_classifications"
author: "Bria Long"
date: "4/2021"
output: html_document
---

```{r, libraries}
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(langcog)
library(stringr)
library(here)
theme_set(theme_few())
```

# CDM cleaning
## Get drawing-specific metadata for CDM
```{r}
## Load in meta data from mongo-db database dumps
CDM_metadata <- read.csv(here::here('data/CDM/drawing_metadata/Photodraw2_CDM_AllDescriptives_1922_images_final_CDM_photodraw_e2.csv')) %>%
  as_tibble() %>%
  mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
  mutate(session_id = as.factor(session_id)) %>%
  mutate(draw_duration = replace(draw_duration_new, draw_duration_new > 30,30)) %>%
  rowwise() %>%
  mutate(filename = str_split_fixed(filename, 'photodraw2_all_sketches/',2)[,2]) %>%
  mutate(filename = str_split_fixed(filename, '/',2)[,2])  %>%
  select(subID, session_id, condition, category, num_strokes, draw_duration, mean_intensity, age,filename) %>%
  mutate(age_numeric =as.numeric(str_split_fixed(age,'age',2)[,2]))

```

## Clean up any subid issues from CDM dataset
```{r}
# exclude any subjects that have duplicate IDs
prac_trials = c('this square','this shape','triangle','rectangle')
double_sessions <- CDM_metadata %>%
  distinct(subID,session_id) %>%
  group_by(subID) %>%
  summarize(num_sessions = n()) %>%
  filter(num_sessions > 1)

drawings_by_doubles <-  CDM_metadata %>%
  filter(subID %in% double_sessions$subID) %>%
  filter(!category %in% prac_trials) %>%
  group_by(subID,category) %>%
  summarize(num_drawings = n()) %>%
  filter(num_drawings >1)

# one duplicate ID
duplicate_sub_id = unique(drawings_by_doubles$subID)
to_fix <- CDM_metadata %>%
  filter(subID == duplicate_sub_id)

unique(to_fix$age) ## two ages here -- age 5 and 7 with the same subID

# To match run sheet: 111418_6 & age7 stays as ID 111418_6
# To match run sheet: 111418_6 & age5 should instead be 111418_5
assert_that(sum(CDM_metadata$session_id=="111418_5")==0) # isn't it the database yet, so that's the error

## FIX IT : change subid to character so can replace value; change back to factor to keep tidy
CDM_metadata <- CDM_metadata %>%
  mutate(subID = as.character(subID)) %>%
  mutate(subID=replace(subID, subID=="111418_6" & age=="age5","111418_5")) %>%
  mutate(subID = as.factor(subID))
```

## Exclude first sessions from duplicate sessions
```{r}
# one subject who had two sessions for the same subid -- exclude the first session
# this is just a practice trial
session_to_exclude <- CDM_metadata %>%
  group_by(subID) %>%
  mutate(count_sessions = length(unique(session_id))) %>%
  filter(count_sessions>1) %>%
  mutate(timestamp = as.numeric(str_split_fixed(session_id, 'photodraw_e2',2)[,2])) %>%
  mutate(max_timestamp = max(timestamp)) %>%
  filter(timestamp <  max_timestamp)

# filter this out
CDM_metadata <- CDM_metadata %>%
  filter(!session_id %in% session_to_exclude$session_id)  %>%
  mutate(site = 'CDM')

```

# THU cleaning
## Now load and clean up THU metadata 
```{r}
#Serious headache with extra spaces in database IDs vs subject log IDs (see anlaysis > step1_getdrawings for most of the legwork here)

# from subject logs
THU_final_subject_info = read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
  as_tibble() %>%
  select(ID_Database_raw, ID_Database, Age) %>%
  mutate(age_numeric = floor(Age)) %>%
  select(-Age) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(ID_Database_raw, fixed(" "), "")) %>%
  mutate(ID_Database_raw = as.factor(ID_Database_raw)) 
  # rename(session_id = ID_Database) #session_id = cleaned ID_Database anme for merging with CDM data

# metadata for each drawing
all_THU_metadata<- read.csv(here::here('data/THU/drawing_metadata/THU_Drawings_AllDescriptives_april2021_all.csv')) %>%
  select(subid, session_id, condition, category, num_strokes, draw_duration, mean_intensity, filename) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(subid, fixed(" "), "")) %>% #subid = ID_Database_raw in this spreadsheet, I know, sorry
  mutate(ID_Database_raw = as.factor(ID_Database_raw))

# joint drawing metadata with subject info
THU_metadata <-  THU_final_subject_info %>%
  left_join(all_THU_metadata, by=c("ID_Database_raw")) %>%
  select(-ID_Database_raw, -subid, - filename) %>%
  mutate(filename = paste0(condition, '_',category, '_sketch_age',age_numeric, '_', ID_Database,'.png'))   # used to re-save sketches, so should match but can sanity check

# check nothing went wrong with merging....spaces were causing issues
assert_that(sum(is.na(THU_metadata$num_strokes))==0)

```

## Check for duplicate session_ids in THU_metadata
```{r}
thu_session_to_exclude <- THU_metadata %>%
  group_by(ID_Database) %>%
  mutate(count_sessions = length(unique(session_id))) %>%
  filter(count_sessions>1) %>%
  mutate(timestamp = as.numeric(str_split_fixed(session_id, 'Tsinghua_photodraw_production',2)[,2])) %>%
  mutate(max_timestamp = max(timestamp)) %>%
  filter(timestamp <  max_timestamp)

# exclude first sessions, only one with category drawings...assuming that's a real participant, but can't link to subject log so taking second participant
THU_metadata <- THU_metadata %>%
  filter(!session_id %in% thu_session_to_exclude$session_id) %>%
  mutate(site = 'THU')

```

# Join both sets of metadata together
```{r}
all_meta <- CDM_metadata %>%
  full_join(THU_metadata %>% rename(subID = ID_Database)) %>%
  mutate(age_numeric = replace(age_numeric,age_numeric==10, 9))

# remove some duplicate rows -- had same session, etc. so not worried
# repeats <- all_meta %>%
#   group_by(filename) %>%
#   mutate(count_repeats = n()) %>%
#   filter(count_repeats>1) %>%
#   filter(category=='chair') %>%
#   mutate(same_session = length(unique(session_id)))

all_meta <- unique(all_meta)

```

## And save
```{r}
write_csv(all_meta,here::here('data/compiled/metadata/final_merged_metadata.csv'))
```

### 2021-04-28 analysis/step2_clean_metadata/save_batches_for_recognition.Rmd
new folder for cleaning metadata in analysis pipeline

---
title: "Photodraw2-Descriptives"
author: "Bria Long"
date: "2/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(assertthat)
library(here)
```

## Do you really want to rerun this?
```{r}
## Generally you don't -- this does a lot of copying and filtering based on the dataset preprocessing stage...
rerun=FALSE
```
## Import metadata
```{r}
all_meta <- read.csv(file = here::here('data/compiled/metadata/final_merged_metadata.csv')) %>%
  as_tibble() 
```

## looked at differences between full set of rendered drawings and cleaned metadata; removed excluded drawings
```{r}

if (rerun=TRUE){
  compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')

  all_rendered_drawings = list.files(path=compiled_dataset_path, pattern = ".png$", recursive = TRUE) %>%
      as_tibble()  %>%
      rename(fullPath = value)

  prac_trials = c('this square','this shape','triangle','rectangle')
  object_drawings <- all_meta %>%
    filter(!category %in% prac_trials)

  # either duplicate sessions or no stroke data, see merge_and_clean_datasets.
  drawings_excluded <- all_drawings %>%
    filter(!fullPath %in% object_drawings$filename)

  ## DO ONCE
  file.remove(fs::path(compiled_dataset_path, drawings_excluded$fullPath))

  # should be none
  drawings_not_rendered <- object_drawings %>%
    filter(!filename %in% all_drawings$fullPath)

  assert_that(length(drawings_not_rendered$subID)==0)
  length(object_drawings$filename)
  length(all_drawings$fullPath)
}
```

# copy tracings from included THU children
```{r}
if (rerun==TRUE){
  compiled_tracings_path = here::here('data/compiled/drawings/tracings')
  tracings_THU = here::here('data/THU/drawings/tracings/')

  tracings_to_include_THU <- all_meta %>%
    filter(category %in% c('this square','this shape')) %>%
    filter(site == "THU")

  file.copy(fs::path(tracings_THU, tracings_to_include_THU$filename), fs::path(compiled_tracings_path, tracings_to_include_THU$filename))
}
```

# copy tracings from included CDM children
```{r}
if (rerun==TRUE){
compiled_tracings_path = here::here('data/compiled/drawings/tracings')
tracings_CDM = here::here('data/CDM/drawings/tracings/')

tracings_to_include_CDM <- all_meta %>%
  filter(category %in% c('this square','this shape')) %>%
  filter(site == "CDM")

file.copy(fs::path(tracings_CDM, tracings_to_include_CDM$filename), fs::path(compiled_tracings_path, tracings_to_include_CDM$filename))
}
```

# Randomly sample from groups of categories / ages / sites into subsets for different participants
```{r}
if (rerun==TRUE){
sample_set <- object_drawings
##
max_iter=21 
for (iteration in 1:max_iter) {
    if (iteration==max_iter){
      # whatever we have left if on last iteration
      print('last iteration...')
      print (length(sample_set$filename))
      write_csv(sample_set,here::here('data/compiled/recognition_rating_chunks/',paste0('chunk_',iteration,'_compiled_dataset.csv')))
    }
    # for all the other iterations
    else if (iteration<max_iter){

    this_chunk <- sample_set %>%
      group_by(age_numeric,category, site) %>%
      slice_sample(n=1, replace=FALSE)

    assert_that(length(unique(this_chunk$category))==12)
    assert_that(length(unique(this_chunk$age_numeric))==6)
    assert_that(length(unique(this_chunk$site))==2)

    print (length(this_chunk$filename))
    write_csv(this_chunk,here::here('data/compiled/recognition_rating_chunks/',paste0('chunk_',iteration,'_compiled_dataset.csv')))

    sample_set <- sample_set %>%
      filter(!filename %in% this_chunk$filename)

    # print (length(sample_set$filename))
    }
}
}

```

### 2021-04-28 analysis/step4_main_analyses/examine_photodraw_classifications.Rmd
move starter analysis scripts to new folder

--- 2021-04-28 analysis/step4_main_analyses_both_sites/main_analysis.Rmd
@@
 ---
-title: "Examine_classifications"
+title: "Examine_photodraw_classifications"
 author: "Bria Long"
-date: "4/9/2021"
+date: "4/2021"
 output: html_document
@@
 ```{r load-classifications}
-classification_data <- read.csv('compiled_classifications/Classification_Outputs2832.csv') %>%
-  as.tibble() %>%
+classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2832.csv')) %>%
+  as_tibble() %>%
   # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
@@
   # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
-  select(-X) %>%
+  select(-X, -X.1, -index) %>%
   mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
@@
 
-## Need to rewrite some code to get meta-data for couchdb/mongodb dumps
+## Get drawing-specific metadata and join with main dataset
 ```{r}
 ## Load in meta data from mongo-db database dumps
-# metadata_photodraw <- read.csv('mongodb-output/Photodraw2_AllDescriptives_1475_images_final_CDM_photodraw_e2_no_blanks.csv') %>%
-#   as.tibble() %>%
-#   mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
-#   mutate(session_id = as.factor(session_id)) %>%
-#   mutate(draw_duration_new = replace(draw_duration_new, draw_duration_new > 30,30))
-# 
-# ## join with classification data
-# d <- classification_data %>%
-#   left_join(metadata_photodraw) %>%
-#   mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2]))
+CDM_metadata <- read.csv(here::here('data/CDM/drawing_metadata/Photodraw2_CDM_AllDescriptives_1922_images_final_CDM_photodraw_e2.csv')) %>%
+  as_tibble() %>%
+  mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
+  mutate(session_id = as.factor(session_id)) %>%
+  mutate(draw_duration = replace(draw_duration_new, draw_duration_new > 30,30)) %>%
+  select(session_id, condition, category, num_strokes, draw_duration, mean_intensity)
+
 ```
 
-## Read in meta data fed to classifications
+# for THU
 ```{r}
-meta <- read_csv(here('data/compiled/meta/METADATA_kid.csv'))
+THU_final_subject_info = read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
+  as_tibble() %>%
+  select(ID_Database_raw, ID_Database) %>%
+  rowwise() %>%
+  mutate(ID_Database_raw = str_replace_all(ID_Database_raw, fixed(" "), "")) %>%
+  mutate(ID_Database_raw = as.factor(ID_Database_raw)) %>%
+  rename(session_id = ID_Database) #session_id = cleaned ID_Database anme for merging with CDM data
+
+all_THU_metadata<- read.csv(here::here('data/THU/drawing_metadata/THU_Drawings_AllDescriptives_april2021_all.csv')) %>%
+  select(subid, condition, category, num_strokes, draw_duration, mean_intensity, filename) %>%
+  rowwise() %>%
+  mutate(ID_Database_raw = str_replace_all(subid, fixed(" "), "")) %>% #subid = ID_Database_raw in this spreadsheet, I know, sorry
+  mutate(ID_Database_raw = as.factor(ID_Database_raw))
+
+# joint drawing metadata with subject info
+THU_metadata <-  THU_final_subject_info %>%
+  left_join(all_THU_metadata, by=c("ID_Database_raw")) %>%
+  select(-ID_Database_raw, -subid, - filename)
+
+# check nothing went wrong with merging
+assert_that(sum(is.na(THU_metadata$num_strokes))==0)
+
+```
+
+### join both sets of metadata together
+```{r}
+all_meta <- CDM_metadata %>%
+  full_join(THU_metadata)
+```
+
+### join with classification data -- which has age embedded
+```{r}
+d <- classification_data %>%
+  left_join(all_meta, by=c('category','session_id'))  %>%
+  mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2])) %>%
+  mutate(age_numeric = replace(age_numeric, age_numeric==10,9)) # two THU participants who are just barely 10-years old, including in 9-year-old group
+
+# subids in d should be a superset of those in classification_data
+check_ids <- classification_data %>%
+  filter(!session_id %in% unique(all_meta$session_id))
+assert_that(length(check_ids$age)==0) # all match up
+
+```
+
+### get rid of tech error drawings (see note)
+```{r}
+# bizarrely, there are 24 drawing for which stroke data didn't save -- technical error.
+# this was checked directly in mongodb database -- no idea why, assuming bad internet.
+tech_error_drawings <- d %>%
+  filter(is.na(num_strokes))
+# filter out terch error drawings from dataset (24)
+d <- d %>%
+  filter(!is.na(num_strokes)) 
+```
+
+```{r}
+# only did one practice trial, not in subject log or classification data because no category level trials
+missing_id <- CDM_metadata %>%
+  filter(!session_id %in% d$session_id)
 ```
@@
 ```{r}
-sanity_counts <- classification_data %>%
-  left_join(meta, by=c('session_id' = 'session', 'category' = 'label')) %>%
-  filter(age_numeric < 10) %>%
+sanity_counts <- d %>%
   group_by(condition,age_numeric, site) %>%
@@
   group_by(category) %>%
-  summarize(num_drawings = length(unique(session_id)), what = length(unique(index)))
-
-what <- d %>%
-  group_by(index) %>%
-  summarize(num_ids = length(session_id)) %>%
-  filter(num_ids >1)
+  summarize(num_drawings = length(unique(session_id)))
 
@@
 
-265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum & Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
-We aimed to recruit approximately 120 children aged 4-9 years of age after exclusions (i.e.
-20 4-year-olds, 20 5-year-olds).
-In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, leading to a final sample of `r count_by_site$num_participants[1]` children.
-In the China based sample, 140 children participated; (10) participants were tested but their data was not recorded due to a technical error with the remote database, leading to a final sample of `r count_by_site$num_participants[2]`.
+265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e.
+20 4-year-olds, 20 5-year-olds, etc.).
+In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children.
+In the China based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
 A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.
@@
 ### How do our covariates change with age? Compute means and CIs; Group by age/category
-## first join  data  
-d <- classification_data %>% 
-  left_join(meta, by=c('session_id' = 'session', 'category' = 'label'))
-
-```
-
-```{r}
 cor_by_age <- d %>%  

### 2021-04-28 analysis/step4_main_analyses/main_analysis_for_prereg.Rmd
move starter analysis scripts to new folder

--- 2021-04-28 analysis/step4_main_analyses/examine_photodraw_classifications.Rmd
@@
 ---
-title: "Examine_photodraw_classifications"
+title: "main_analyses_prereg"
 author: "Bria Long"
-date: "4/2021"
+date: "4/28/2021"
 output: html_document
@@
 
-```{r, libraries}
-library(knitr)
-library(tidyverse)
-library(assertthat)
-library(ggthemes)
-library(langcog)
-library(forcats)
-library(egg)
-library(gridExtra)
-library(reticulate)
-library(readr)
-library(ggplot2)
-library(reshape2)
-library(lme4)
-library(stringr)
-library(viridis)
-library(MuMIn)
-library(here)
-theme_set(theme_few())
-```
+## Load compiled classification data
 
-## Load compiled classification data
 ```{r load-classifications}
@@
   mutate(site = as.factor(site))
-```
-
-## Get drawing-specific metadata and join with main dataset
-```{r}
-## Load in meta data from mongo-db database dumps
-CDM_metadata <- read.csv(here::here('data/CDM/drawing_metadata/Photodraw2_CDM_AllDescriptives_1922_images_final_CDM_photodraw_e2.csv')) %>%
-  as_tibble() %>%
-  mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
-  mutate(session_id = as.factor(session_id)) %>%
-  mutate(draw_duration = replace(draw_duration_new, draw_duration_new > 30,30)) %>%
-  select(session_id, condition, category, num_strokes, draw_duration, mean_intensity)
-
-```
-
-# for THU
-```{r}
-THU_final_subject_info = read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
-  as_tibble() %>%
-  select(ID_Database_raw, ID_Database) %>%
-  rowwise() %>%
-  mutate(ID_Database_raw = str_replace_all(ID_Database_raw, fixed(" "), "")) %>%
-  mutate(ID_Database_raw = as.factor(ID_Database_raw)) %>%
-  rename(session_id = ID_Database) #session_id = cleaned ID_Database anme for merging with CDM data
-
-all_THU_metadata<- read.csv(here::here('data/THU/drawing_metadata/THU_Drawings_AllDescriptives_april2021_all.csv')) %>%
-  select(subid, condition, category, num_strokes, draw_duration, mean_intensity, filename) %>%
-  rowwise() %>%
-  mutate(ID_Database_raw = str_replace_all(subid, fixed(" "), "")) %>% #subid = ID_Database_raw in this spreadsheet, I know, sorry
-  mutate(ID_Database_raw = as.factor(ID_Database_raw))
-
-# joint drawing metadata with subject info
-THU_metadata <-  THU_final_subject_info %>%
-  left_join(all_THU_metadata, by=c("ID_Database_raw")) %>%
-  select(-ID_Database_raw, -subid, - filename)
-
-# check nothing went wrong with merging
-assert_that(sum(is.na(THU_metadata$num_strokes))==0)
-
-```
-
-### join both sets of metadata together
-```{r}
-all_meta <- CDM_metadata %>%
-  full_join(THU_metadata)
 ```

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
add recognition ratings experiment

@@ -1,0 +1,249 @@
+// ############################ Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) 
+{ 
+    var o = [];
+    
+    for (var i=0; i < a.length; i++) {
+	o[i] = a[i];
+    }
+    
+    for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+    return o;
+}
+
+function shuffle_mult() {
+    var length0 = 0,
+        length = arguments.length,
+        i,
+        j,
+        rnd,
+        tmp;
+
+    for (i = 0; i < length; i += 1) {
+        if ({}.toString.call(arguments[i]) !== "[object Array]") {
+            throw new TypeError("Argument is not an array.");
+        }
+
+        if (i === 0) {
+            length0 = arguments[0].length;
+        }
+
+        if (length0 !== arguments[i].length) {
+            throw new RangeError("Array lengths do not match.");
+        }
+    }
+
+
+    for (i = 0; i < length0; i += 1) {
+        rnd = Math.floor(Math.random() * i);
+        for (j = 0; j < length; j += 1) {
+            tmp = arguments[j][i];
+            arguments[j][i] = arguments[j][rnd];
+            arguments[j][rnd] = tmp;
+        }
+    }
+}
+
[…]

### 2021-04-28 experiments/Recognition_ratings/experiment/store.js
change port

@@ -11,7 +11,7 @@ const colors = require('colors/safe');
 
 const app = express();
 const MongoClient = mongodb.MongoClient;
-const port = 4000;
+const port = 4040;
 const mongoCreds = require('./auth.json');
 const mongoURL = `mongodb://${mongoCreds.user}:${mongoCreds.password}@localhost:27017/`;
 const handlers = {};

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
remove old dependencies, add comments

@@ -8,7 +8,6 @@ function showSlide(id) {
 	$("#"+id).show();
 }
 
-
 // Get random integers.
 // When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
 function random(a,b) {
@@ -152,7 +151,7 @@ showSlide("instructions"); // Show the instructions slide -- this is what we wan
 // ############################## The main event ##############################
 var experiment = {
 
-	// The object to be submitted.
+	// The object to be submitted; needs to have all columns in it.
 	data: {
         sub_id: [],
         guessed_category: [],
@@ -189,7 +188,7 @@ var experiment = {
                 dataType: 'recognition_rating',
                 dbname:'devphotodraw_recognition',
                 colname: 'batched_12afc', 
-                guessed_category: response,
+                guessed_category: response, 
                 imageCategory: document.getElementById("imagePlaceholder").name,
                 imageName: document.getElementById("imagePlaceholder").src,
             }

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
fix tupo

@@ -155,11 +155,12 @@ var experiment = {
 	data: {
         sub_id: [],
         guessed_category: [],
-        dbname:'devphotodraw_recognition',
+        dbname: 'devphotodraw_recognition',
         colname: 'batched_12afc', 
-        trial_type: [].
+        trial_type: [],
 		comments: [],
 	},
+
 	// end the experiment
 	end: function() {
 		showSlide("finished");

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
try getting socket.io to work..

@@ -76,7 +76,7 @@ function shuffle_mult() {
 // ######################## Configuration settings ############################
 
 // connect to node.js
-socket = io.connect();
+socket = io.connect('http://localhost:4040');
 
 //set up trials from csv
 $(document).ready(function() {

### 2021-04-28 experiments/Recognition_ratings/experiment/app.js
skip readers in image reading, try without specifying port

@@ -22,14 +22,14 @@ if(argv.gameport) {
     console.log('no gameport specified: using 8880\nUse the --gameport flag to change');
 }
 
-var mode;
-if(argv.mode) {
-    mode = argv.mode;
-    console.log('using mode ' + mode);
-} else {
-    mode = "CDM";
-    console.log('no mode specified: using CDM\nUse the --mode flag to change');
-}
+// var mode;
+// if(argv.mode) {
+//     mode = argv.mode;
+//     console.log('using mode ' + mode);
+// } else {
+//     mode = "CDM";
+//     console.log('no mode specified: using CDM\nUse the --mode flag to change');
+// }
 
 
 try {
@@ -69,27 +69,27 @@ io.on('connection', function (socket) {
 
 });
 
-var serveFile = function(req, res) {
-    var fileName = req.params[0];
+// var serveFile = function(req, res) {
+//     var fileName = req.params[0];
 
-    if (fileName == "send"){
-        console.log('sending the consent form to the parent email');
-        sendEmail(req,res);
+//     if (fileName == "send"){
+//         console.log('sending the consent form to the parent email');
+//         sendEmail(req,res);
 
-    }else if(fileName == "mode"){
-        console.log ("mode: " + mode);
-        res.send({'mode':mode});
+//     }else if(fileName == "mode"){
+//         console.log ("mode: " + mode);
+//         res.send({'mode':mode});
 
-    }else{
-        console.log('\t :: Express :: file requested: ' + fileName);
-        return res.sendFile(fileName, {root: __dirname});
-    }
+//     }else{
+//         console.log('\t :: Express :: file requested: ' + fileName);
+//         return res.sendFile(fileName, {root: __dirname});
+//     }
 
-};
+// };
 
 var writeDataToMongo = function(data) {
     sendPostRequest(
-        'http://localhost:4000/db/insert',
+        'http://localhost:4040/db/insert',
         { json: data },
         (error, res, body) => {
         if (!error && res.statusCode === 200) {

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js

@@ -76,7 +76,7 @@ function shuffle_mult() {
 // ######################## Configuration settings ############################
 
 // connect to node.js
-socket = io.connect('http://localhost:4040');
+socket = io.connect();
 
 //set up trials from csv
 $(document).ready(function() {
@@ -87,10 +87,10 @@ $.ajax({
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
-            
             imgArray = new Array();
             //set up image names
-            for (i = 0; i < results.data.length; i++) {
+            // skip row 0 = headers
+            for (i = 1; i < results.data.length; i++) { 
                 var imageName= results.data[i][8]; //starts i at 1 to get rid of header
                 var imageCategory=results.data[i][3]
                 imgArray[i] = new Image();

### 2021-04-28 experiments/Recognition_ratings/experiment/app.js
revert change to app.js

@@ -69,23 +69,23 @@ io.on('connection', function (socket) {
 
 });
 
-// var serveFile = function(req, res) {
-//     var fileName = req.params[0];
+var serveFile = function(req, res) {
+    var fileName = req.params[0];
 
-//     if (fileName == "send"){
-//         console.log('sending the consent form to the parent email');
-//         sendEmail(req,res);
+    if (fileName == "send"){
+        console.log('sending the consent form to the parent email');
+        sendEmail(req,res);
 
-//     }else if(fileName == "mode"){
-//         console.log ("mode: " + mode);
-//         res.send({'mode':mode});
+    }else if(fileName == "mode"){
+        console.log ("mode: " + mode);
+        res.send({'mode':mode});
 
-//     }else{
-//         console.log('\t :: Express :: file requested: ' + fileName);
-//         return res.sendFile(fileName, {root: __dirname});
-//     }
+    }else{
+        console.log('\t :: Express :: file requested: ' + fileName);
+        return res.sendFile(fileName, {root: __dirname});
+    }
 
-// };
+};
 
 var writeDataToMongo = function(data) {
     sendPostRequest(

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
debugging image reading

@@ -90,11 +90,11 @@ $.ajax({
             imgArray = new Array();
             //set up image names
             // skip row 0 = headers
-            for (i = 1; i < results.data.length; i++) { 
+            for (i = 1; i < results.data.length-1; i++) { 
                 var imageName= results.data[i][8]; //starts i at 1 to get rid of header
                 var imageCategory=results.data[i][3]
                 imgArray[i] = new Image();
-                imgArray[i].src = ['object_drawings/' + imageName ];
+                imgArray[i].src = ['object_drawings/' + imageName];
                 imgArray[i].name = imageCategory;
             }                 
                

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
debugging image loading

@@ -90,12 +90,12 @@ $.ajax({
             imgArray = new Array();
             //set up image names
             // skip row 0 = headers
-            for (i = 1; i < results.data.length-1; i++) { 
+            for (i = 1; i < results.data.length; i++) { 
                 var imageName= results.data[i][8]; //starts i at 1 to get rid of header
                 var imageCategory=results.data[i][3]
-                imgArray[i] = new Image();
-                imgArray[i].src = ['object_drawings/' + imageName];
-                imgArray[i].name = imageCategory;
+                imgArray[i-1] = new Image();
+                imgArray[i-1].src = ['object_drawings/' + imageName];
+                imgArray[i-1].name = imageCategory;
             }                 
                
         

### 2021-04-28 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
clear response before next trial, add image name to db

@@ -157,6 +157,7 @@ var experiment = {
         guessed_category: [],
         dbname: 'devphotodraw_recognition',
         colname: 'batched_12afc', 
+        imageName: [],
         trial_type: [],
 		comments: [],
 	},
@@ -194,9 +195,10 @@ var experiment = {
                 imageName: document.getElementById("imagePlaceholder").src,
             }
 
+            $("#recognitionInput").val(""); // clear value
             socket.emit('current_data', trial_data);
             experiment.next();
-            $("#recognitionInput").val(""); // clear value
+        
             
         } else {
             $("#testMessage_att").html('<font color="red">' + 

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
adapt ajax loop for specific csvs

@@ -89,14 +89,13 @@ $.ajax({
             results = Papa.parse(data);
             imgArray = new Array();
             //set up image names
-            // skip row 0 = headers
-            for (i = 1; i < results.data.length; i++) { 
-                var imageName= results.data[i][8]; //starts i at 1 to get rid of header
+            for (i = 1; i < results.data.length-1; i++) {  // start at 1 get rid of header, end one row early to avoid empty last row (speciifc to these csvs?)
+                var imageName= results.data[i][8]; 
                 var imageCategory=results.data[i][3]
-                imgArray[i-1] = new Image();
-                imgArray[i-1].src = ['object_drawings/' + imageName];
-                imgArray[i-1].name = imageCategory;
-            }                 
+                imgArray[i] = new Image();
+                imgArray[i].src = ['object_drawings/' + imageName];
+                imgArray[i].name = imageCategory;
+            }                       
                
         
     trials = []

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
fix index

@@ -92,9 +92,9 @@ $.ajax({
             for (i = 1; i < results.data.length-1; i++) {  // start at 1 get rid of header, end one row early to avoid empty last row (speciifc to these csvs?)
                 var imageName= results.data[i][8]; 
                 var imageCategory=results.data[i][3]
-                imgArray[i] = new Image();
-                imgArray[i].src = ['object_drawings/' + imageName];
-                imgArray[i].name = imageCategory;
+                imgArray[i-1] = new Image();
+                imgArray[i-1].src = ['object_drawings/' + imageName];
+                imgArray[i-1].name = imageCategory;
             }                       
                
         

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
add prolific redirect

@@ -166,7 +166,7 @@ var experiment = {
 		showSlide("finished");
 		setTimeout(function() {
             socket.emit('current_data', experiment.data);
-            window.location.href="https://app.prolific.co/submissions/complete?cc=3769E361"
+            window.location.href="https://app.prolific.co/submissions/complete?cc=731A3666"
 		}, 1500);
 	},
 

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
add testing check

@@ -177,6 +177,7 @@ var experiment = {
         var response_logged = false;
         var input = document.getElementById("recognitionInput");
         var response = input.value;
+        var testing = true
 
         // if there is something in the response, log it
         if (input && response) {
@@ -199,7 +200,12 @@ var experiment = {
             experiment.next();
         
             
-        } else {
+        } else if (testing) {
+            $("#recognitionInput").val(""); // clear value
+            socket.emit('testing')
+            experiment.next();
+        }
+        else{
             $("#testMessage_att").html('<font color="red">' + 
             'Please make a response!' + 
              '</font>');   

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
no longer testing

@@ -177,7 +177,7 @@ var experiment = {
         var response_logged = false;
         var input = document.getElementById("recognitionInput");
         var response = input.value;
-        var testing = true
+        var testing = false
 
         // if there is something in the response, log it
         if (input && response) {

### 2021-04-29 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
add column for production

@@ -186,6 +186,7 @@ var experiment = {
             readable_date = new Date();
             trial_data =  {
                 date: readable_date,
+                version: 'production_batch1',
                 sub_id: trials[0].sub_id,
                 dataType: 'recognition_rating',
                 dbname:'devphotodraw_recognition',

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
fix subid issue

@@ -103,17 +103,18 @@ $.ajax({
 
     try{
         url = window.location.href
-        var this_sub_id = url.substring(url.lastIndexOf('PROLIFIC_PID')+13, url.lastIndexOf('PROLIFIC_PID') + 36);
+        this_sub_id = url.substring(url.lastIndexOf('PROLIFIC_PID')+13, url.lastIndexOf('PROLIFIC_PID') + 36);
         console.log(this_sub_id)
     }
     catch(err){
-        var this_sub_id = random(10000000000)
+        this_sub_id = random(10000000000)
         console.log(this_sub_id)
     }
     
     for (i = 0; i < numTrialsExperiment; i++) {
         trial = {
             thisImageName: imgArray[i].src,
+            thisImageCategory: imgArray[i].name,
             slide: "recognitionRatings",
             sub_id: this_sub_id,
         }
@@ -187,7 +188,7 @@ var experiment = {
             trial_data =  {
                 date: readable_date,
                 version: 'production_batch1',
-                sub_id: trials[0].sub_id,
+                sub_id: this_sub_id,
                 dataType: 'recognition_rating',
                 dbname:'devphotodraw_recognition',
                 colname: 'batched_12afc', 
@@ -235,9 +236,10 @@ var experiment = {
 			}
             // check which trial type you're in and display correct slide
             if (trial_info.slide == "recognitionRatings") {
+                document.getElementById("imagePlaceholder").name = trial_info.thisImageCategory;
                 document.getElementById("imagePlaceholder").src = trial_info.thisImageName;
                 showSlide("recognitionRatings"); //display slide
-                experiment.data.imageName.push(trial_info.thisImageName);
+                
                 }
         experiment.data.trial_type.push(trial_info.slide);
 		}

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
10 trials for testing

@@ -111,7 +111,7 @@ $.ajax({
         console.log(this_sub_id)
     }
     
-    for (i = 0; i < numTrialsExperiment; i++) {
+    for (i = 0; i < 10; i++) {
         trial = {
             thisImageName: imgArray[i].src,
             thisImageCategory: imgArray[i].name,

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
redo comments submission

@@ -97,7 +97,10 @@ $.ajax({
                 imgArray[i-1].name = imageCategory;
             }                       
                
-        
+    
+    //global variable 
+    this_version = 'testing_version2'
+    //
     trials = []
     numTrialsExperiment = imgArray.length;    
 
@@ -111,7 +114,7 @@ $.ajax({
         console.log(this_sub_id)
     }
     
-    for (i = 0; i < 10; i++) {
+    for (i = 0; i < 2; i++) {
         trial = {
             thisImageName: imgArray[i].src,
             thisImageCategory: imgArray[i].name,
@@ -187,7 +190,7 @@ var experiment = {
             readable_date = new Date();
             trial_data =  {
                 date: readable_date,
-                version: 'production_batch1',
+                version: this_version,
                 sub_id: this_sub_id,
                 dataType: 'recognition_rating',
                 dbname:'devphotodraw_recognition',
@@ -252,7 +255,17 @@ var experiment = {
 
 // submitcomments function
     submit_comments: function() {
-        experiment.data.comments.push(document.getElementById("comments").value);
+        trial_data =  {
+                date: readable_date,
+                version: this_version,
+                sub_id: this_sub_id,
+                dataType: 'comments',
+                dbname:'devphotodraw_recognition',
+                colname: 'batched_12afc', 
+                comments:  document.getElementById("comments").value,
+            }
+
+        socket.emit('final_comments', trial_data);
         experiment.end();
     }
 }

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
clean up old data structures

@@ -169,8 +169,7 @@ var experiment = {
 	end: function() {
 		showSlide("finished");
 		setTimeout(function() {
-            socket.emit('current_data', experiment.data);
-            window.location.href="https://app.prolific.co/submissions/complete?cc=731A3666"
+ex            window.location.href="https://app.prolific.co/submissions/complete?cc=731A3666"
 		}, 1500);
 	},
 
@@ -244,7 +243,6 @@ var experiment = {
                 showSlide("recognitionRatings"); //display slide
                 
                 }
-        experiment.data.trial_type.push(trial_info.slide);
 		}
 	},
 
@@ -255,7 +253,7 @@ var experiment = {
 
 // submitcomments function
     submit_comments: function() {
-        trial_data =  {
+        comments_data =  {
                 date: readable_date,
                 version: this_version,
                 sub_id: this_sub_id,
@@ -265,7 +263,7 @@ var experiment = {
                 comments:  document.getElementById("comments").value,
             }
 
-        socket.emit('final_comments', trial_data);
+        socket.emit('final_comments', comments_data);
         experiment.end();
     }
 }

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
typo

@@ -169,7 +169,7 @@ var experiment = {
 	end: function() {
 		showSlide("finished");
 		setTimeout(function() {
-ex            window.location.href="https://app.prolific.co/submissions/complete?cc=731A3666"
+            window.location.href="https://app.prolific.co/submissions/complete?cc=731A3666"
 		}, 1500);
 	},
 

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
socket.emit command change

@@ -263,7 +263,7 @@ var experiment = {
                 comments:  document.getElementById("comments").value,
             }
 
-        socket.emit('final_comments', comments_data);
+        socket.emit('current_data', comments_data);
         experiment.end();
     }
 }

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
switch to production

@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'testing_version2'
+    this_version = 'batch1_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    
@@ -114,7 +114,7 @@ $.ajax({
         console.log(this_sub_id)
     }
     
-    for (i = 0; i < 2; i++) {
+    for (i = 0; i < numTrialsExperiment; i++) {
         trial = {
             thisImageName: imgArray[i].src,
             thisImageCategory: imgArray[i].name,

### 2021-06-14 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
batch 2 production

---
title: "preprocess_human_recognition"
author: "Bria Long"
date: "6/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
d <- read.csv("csv_out/Devphotodraw_recognition_pilot.csv") %>%
  as.tibble() %>%
  mutate(image_name_short = str_split_fixed(imageName,'object_drawings/',2)[,2]) %>%
  mutate(age_temp = str_split_fixed(image_name_short,'age',2)[,2]) %>%
  mutate(age = as.numeric(str_split_fixed(age_temp,'_',2)[,1]))
```

# filter out participants who don't finish
```{r}
included_subs <- d %>%
  group_by(subID) %>%
  summarize(num_drawings = length(unique(image_name_short))) %>%
  filter(num_drawings > 140)

used_all_options <- d %>%
  group_by(subID) %>%
  summarize(num_labels = length(unique(guessed_category)))

d <- d %>%
  filter(subID %in% included_subs$subID)
```

# quick check by age
```{r}
check_by_age <- d %>%
  group_by(age) %>%
  summarize(mean(guessed_category == drawn_category))
```

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_1_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_2_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch1_production_june2021'
+    this_version = 'batch2_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-14 analysis/step5_tracing_evaluation/step2_evaluate_tracings/model_pred.Rmd
add tracing rendering and analysis scripts, update gitignore

---
title: "Model Prediction"
output: html_document
---

```{r}
library(tidyverse)
library(lme4)
library(groupdata2)
library(dplyr)
library(knitr) 
library(broom) 
library(hydroGOF)
library(MASS)
library(DescTools)
library(broom)
library(brms)
library(reshape2)
library(caret)
```

```{r}
load("vm_model.rda")
```

```{r}
# read the orig files
data_dir = here::here('data')
# filename = 'kiddraw_tracing_cdm_run_v4.csv'

files = dir(data_dir)
```

```{r}

count_files = 0
for (f in files) {
  count_files = count_files + 1 
  new_data <- read.csv(fs::path(data_dir,f))
      # select(-X)

  if (count_files == 1) {
    all_data <- new_data  
  }

  if (count_files > 1) {
  all_data <- all_data %>%
    full_join(new_data) 
  }
}
```

```{r}
length(unique(all_data$session_id))

```

```{r}
# predict on new data
ord.pred = predict(ord_wid, all_data, re_formula = NA)
ord.pred = data.frame(ord.pred)
all_data$rating = round(ord.pred$P.Y...1*1 + ord.pred$P.Y...2*2 + ord.pred$P.Y...3*3 + ord.pred$P.Y...4*4)
write.csv(all_data, paste0("rated_", "all_museumstation_filtered.csv"))
```

### 2021-06-14 analysis/step5_tracing_evaluation/step1_render_highres_tracings/svg_render_helpers.py

@@ -1,0 +1,155 @@
+from __future__ import division
+import os
+import urllib, cStringIO
+import pymongo as pm ## first establish ssh tunnel to server where database is running
+import base64
+import numpy as np
+from numpy import *
+import PIL
+from PIL import Image
+import base64
+import matplotlib
+from matplotlib import pylab, mlab, pyplot
+from IPython.core.pylabtools import figsize, getfigs
+plt = pyplot
+import seaborn as sns
+sns.set_context('poster')
+sns.set_style('white')
+from matplotlib.path import Path
+import matplotlib.patches as patches
+
+import pandas as pd
+from svgpathtools import parse_path
+
+
+def get_verts_and_codes(svg_list):
+    '''
+    parse into x,y coordinates and output list of lists of coordinates
+
+    '''
+    lines = []
+    Verts = []
+    Codes = []
+    for stroke_ind, stroke in enumerate(svg_list):
+        x = []
+        y = []
+        parsed = parse_path(stroke)
+        for i, p in enumerate(parsed):
+            if i != len(parsed) - 1:  # last line segment
+                x.append(p.start.real)
+                y.append(p.start.imag)
+            else:
+                x.append(p.start.real)
+                y.append(p.start.imag)
+                x.append(p.end.real)
+                y.append(p.end.imag)
+        lines.append(zip(x, y))
+        verts, codes = polyline_pathmaker(lines)
+        Verts.append(verts)
+        Codes.append(codes)
+    return Verts, Codes
+
+
+def make_svg_list(stroke_recs):
+    '''
+    grab sample drawing's strokes and make a list of svg strings from it
+    '''
+    svg_list = []
+    for strec in stroke_recs:   
+        svg_string = strec['svg']       
+        svg_list.append(svg_string)
+    return svg_list
+
+
+def render_and_save(Verts,
+                    Codes,
+                    outpath,
+                    line_width=5,
+                    imsize=3,
+                    canvas_size=809):
+    '''
+    input:
+        line_width: how wide of strokes do we want? (int)
+        imsize: how big of a picture do we want? (setting the size of the figure)
+        canvas_size: original canvas size on tablet?
+        out_path: where do you want to save your images? currently hardcoded below.
+    output:
[…]

### 2021-06-14 analysis/step5_tracing_evaluation/step2_evaluate_tracings/evaluation.py

@@ -1,0 +1,124 @@
+# Copyright 2018 University of Basel, Center for medical Image Analysis and Navigation
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     http://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+import SimpleITK as sitk
+import torch as th
+
+import matplotlib.pyplot as plt
+import time
+import numpy as np
+import cv2
+import sys
+import os
+
+sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))))
+
+import airlab as al
+
+
+def affine_reg(img_draw, img_ref, output_path, lr=0.01, iter=200):
+    # set the used data type
+    dtype = th.float32
+    # set the device for the computaion to CPU
+    device = th.device("cpu")
+
+    # In order to use a GPU uncomment the following line. The number is the device index of the used GPU
+    # Here, the GPU with the index 0 is used.
+    # device = th.device("cuda:0")
+
+    # load the image data and normalize to [0, 1]
+    itkImg = sitk.ReadImage(img_ref, sitk.sitkFloat32)
+    itkImg = sitk.RescaleIntensity(itkImg, 0, 1)
+    fixed_image = al.create_tensor_image_from_itk_image(itkImg, dtype=dtype, device=device)
+    fsize = fixed_image.numpy().flatten().size
+
+    itkImg = sitk.ReadImage(img_draw, sitk.sitkFloat32)
+    itkImg = sitk.RescaleIntensity(itkImg, 0, 1)
+    moving_image = al.create_tensor_image_from_itk_image(itkImg, dtype=dtype, device=device)
+
+
+    # create pairwise registration object
+    registration = al.PairwiseRegistration(dtype=dtype, device=device)
+
+    # choose the affine transformation model
+    transformation = al.transformation.pairwise.RigidTransformation(moving_image.size, dtype=dtype, device=device)
[…]

### 2021-06-14 analysis/step4_get_features_and_classifications/1_extract_features/embedding.py
get site from path

@@ -167,8 +167,13 @@ class FeatureExtractor():
             if self.dataset=='rendered_111918':
                 label = path.split('/')[-1].split('_')[0]
             elif self.dataset=='photodraw_compiled':
-                label = path.split('/')[-1].split('_')[1]   
-                condition = path.split('/')[-1].split('_')[0]
+                label = path.split('/')[-1].split('_')[1]
+                if path.find('CDM')!=-1:
+                    site = 'CDM'
+                else:
+                    site = 'THU'   
+                # condition = path.split('/')[-1].split('_')[0]
+                condition = site
             else:
                 label = path.split('/')[-2]   
 

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 3 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_2_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_3_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch2_production_june2021'
+    this_version = 'batch3_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-14 analysis/step4_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
update to balance by both site and label

@@ -41,12 +41,13 @@ def load_features(cohort, layer_num):
     M = pd.read_csv('/home/bria/devphotodraw/data/{}/features/METADATA_{}.csv'.format(DATASET, cohort)) 
     #  F = np.load('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
     # M = pd.read_csv('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/METADATA_{}.csv'.format(DATASET, cohort)) 
-    M = M[['label','age','session']]
+    M['joint_site_label'] = M['label'] + M['session']
+    M = M[['label','age','joint_site_label']]
     return F, M
 
 def balance_dataset(KF, KM):
     rus = RandomUnderSampler(random_state=0) ## always have same random under sampling
-    KF_downsampled, class_labels_downsampled = rus.fit_resample(KF, KM['label'].values)
+    KF_downsampled, class_labels_downsampled = rus.fit_resample(KF, KM['joint_site_label'].values) # balance by category (label) and site (condition)
     new_samples_ind = rus.sample_indices_
     KM_downsampled = KM.loc[new_samples_ind]
     X = KF_downsampled

### 2021-06-14 analysis/step4_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
update condition typo / out paths

@@ -41,7 +41,7 @@ def load_features(cohort, layer_num):
     M = pd.read_csv('/home/bria/devphotodraw/data/{}/features/METADATA_{}.csv'.format(DATASET, cohort)) 
     #  F = np.load('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
     # M = pd.read_csv('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/METADATA_{}.csv'.format(DATASET, cohort)) 
-    M['joint_site_label'] = M['label'] + M['session']
+    M['joint_site_label'] = M['label'] + M['condition']
     M = M[['label','age','joint_site_label']]
     return F, M
 
@@ -102,7 +102,7 @@ def get_classifications(test_index):
 #### SPECIFY PARAMETERS
 DATASET = 'photodraw_compiled' ## no features yet
 LAYER_IND = 6
-OUT_PATH = 'classification-outputs-092020'
+OUT_PATH = 'classification-outputs-062021'
 REGULARIZE_PARAM = .1
 
 # start clock

### 2021-06-14 analysis/step4_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
fix typo

@@ -42,7 +42,7 @@ def load_features(cohort, layer_num):
     #  F = np.load('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/FEATURES_{}_{}_Spatial_True.npy'.format(DATASET,layers[layer_num],cohort))
     # M = pd.read_csv('/Users/brialong/Documents/GitHub/kiddraw/analysis/museumstation/feature_space_analyses/features/{}/METADATA_{}.csv'.format(DATASET, cohort)) 
     M['joint_site_label'] = M['label'] + M['condition']
-    M = M[['label','age','joint_site_label']]
+    M = M[['label','age','session','joint_site_label']]
     return F, M
 
 def balance_dataset(KF, KM):

### 2021-06-14 analysis/step4_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
fix to classify by label instead of joint label/site

@@ -62,11 +62,12 @@ def get_classifications(test_index):
     out_path_specific = OUT_PATH + "_C_" + str(REGULARIZE_PARAM)
     ### Load features, balance dataset
     KF, KM = load_features('kid',LAYER_IND)
-    X, y, KM_downsampled = balance_dataset(KF,KM)
+    X, y_balanced, KM_downsampled = balance_dataset(KF,KM)
     ## delete test index from test index array from 
     train_indexes = np.asarray(range(0,np.shape(X)[0]))
     train_indexes = np.delete(train_indexes,test_index)
-    ## get train/test indexes    
+    ## get train/test indexes
+    y = np.asarray(KM_downsampled['label'])    
     X_train, X_test = X[train_indexes], X[test_index]
     y_train, y_test = y[train_indexes], y[test_index]
     # run model
@@ -95,7 +96,6 @@ def get_classifications(test_index):
     print 'finished and saving!'
     if not os.path.exists(out_path_specific):
         os.makedirs(out_path_specific)
-    out.to_csv(os.path.join(out_path_specific,'devphotodraw_all_classification_ind_{}.csv'.format(test_index_numeric)))
 
 ################################################################################################################################
 

### 2021-06-14 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
scripts to preprocesss recognition data

@@
 
+# compile all output csvs
 ```{r}
-d <- read.csv("csv_out/Devphotodraw_recognition_pilot.csv") %>%
-  as.tibble() %>%
+all_data=as_tibble()
+for (batch in range(1,2)){
+  this_batch = read.csv(paste0("csv_out/Devphotodraw_recognition_batch",batch,".csv")) %>% as_tibble() 
+  all_data <- rbind(all_data, this_batch)
+}
+
+```
+
+# preprocess image name / age
+```{r}
+d <- all_data %>%
   mutate(image_name_short = str_split_fixed(imageName,'object_drawings/',2)[,2]) %>%

### 2021-06-14 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 4 productino

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_3_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_4_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch3_production_june2021'
+    this_version = 'batch4_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-14 analysis/step5_tracing_evaluation/step2_evaluate_tracings/model_pred.Rmd
update .rmd to make predictions on devphotodrawdata

@@
 ---
-title: "Model Prediction"
+title: "Use previously fit model to predict tracing scores"
 output: html_document
@@
 library(caret)
+library(here)
 ```
 
+# Load model
 ```{r}
@@
 
+# Read in tracing scores from airlab
 ```{r}
 # read the orig files
-data_dir = here::here('data')
-# filename = 'kiddraw_tracing_cdm_run_v4.csv'
-
-files = dir(data_dir)
-```
-
-```{r}
-
-count_files = 0
-for (f in files) {
-  count_files = count_files + 1 
-  new_data <- read.csv(fs::path(data_dir,f))
-      # select(-X)
-
-  if (count_files == 1) {
-    all_data <- new_data  
-  }
-
-  if (count_files > 1) {
-  all_data <- all_data %>%
-    full_join(new_data) 
-  }
-}
+all_data = read.csv(here::here('data/compiled/tracing_outputs/devphotodraw_tracing_all_tracings.csv')) %>%
+  as_tibble() %>%
+  mutate(site = str_split_fixed(filename,'_',4)[,1]) %>%
+  mutate(session_id = str_split_fixed(filename,'_',4)[,3])
 ```
@@
 length(unique(all_data$session_id))
-
 ```
@@
 all_data$rating = round(ord.pred$P.Y...1*1 + ord.pred$P.Y...2*2 + ord.pred$P.Y...3*3 + ord.pred$P.Y...4*4)
-write.csv(all_data, paste0("rated_", "all_museumstation_filtered.csv"))
+write.csv(all_data, here::here('data/compiled/tracing_outputs/transformed_tracings.csv')) 
 ```

### 2021-06-15 analysis/step4_get_features_and_classifications/2_run_classsificatinos/run_classification_loop.py
update saving on loop

@@ -96,6 +96,7 @@ def get_classifications(test_index):
     print 'finished and saving!'
     if not os.path.exists(out_path_specific):
         os.makedirs(out_path_specific)
+    out.to_csv(os.path.join(out_path_specific,'devphotodraw_classification_ind_{}.csv'.format(test_index_numeric)))
 
 ################################################################################################################################
 

### 2021-06-16 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
add free response catch trial

@@ -234,19 +234,22 @@ var experiment = {
 			//If the current trial is undefined, call the end function.
 
 			if (typeof trial_info == "undefined") {
-				return experiment.debriefing();
+				return experiment.catch();
 			}
             // check which trial type you're in and display correct slide
             if (trial_info.slide == "recognitionRatings") {
                 document.getElementById("imagePlaceholder").name = trial_info.thisImageCategory;
                 document.getElementById("imagePlaceholder").src = trial_info.thisImageName;
                 showSlide("recognitionRatings"); //display slide
-                
                 }
 		}
 	},
 
 	//	go to debriefing slide
+    catch: function() {
+        showSlide("catch_trial");
+    },
+
     debriefing: function() {
         showSlide("debriefing");
     },
@@ -265,6 +268,31 @@ var experiment = {
 
         socket.emit('current_data', comments_data);
         experiment.end();
+    }
+
+    submit_catch: function(){
+        var input = document.getElementById("catch");
+        var response = input.value;
+
+        // if there is something in the response, log it
+        if (input && response) {
+
+            catch_data =  {
+                date: readable_date,
+                version: this_version,
+                sub_id: this_sub_id,
+                dataType: 'catch_trial',
+                dbname:'devphotodraw_recognition',
+                colname: 'batched_12afc', 
+                catch:  response,
+            }
+
+        socket.emit('current_data', catch_data);
+        experiment.debriefing();
+        }
+        else {
+        $("#testMessage_att").html('<font color="red">' + 'Please make a response!' + '</font>');      
+        }
     }
 }
 

### 2021-06-16 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
shorter for testing

@@ -114,7 +114,7 @@ $.ajax({
         console.log(this_sub_id)
     }
     
-    for (i = 0; i < numTrialsExperiment; i++) {
+    for (i = 0; i < 3; i++) {
         trial = {
             thisImageName: imgArray[i].src,
             thisImageCategory: imgArray[i].name,
@@ -268,9 +268,9 @@ var experiment = {
 
         socket.emit('current_data', comments_data);
         experiment.end();
-    }
+    },
 
-    submit_catch: function(){
+    submit_catch: function() {
         var input = document.getElementById("catch");
         var response = input.value;
 
@@ -291,7 +291,7 @@ var experiment = {
         experiment.debriefing();
         }
         else {
-        $("#testMessage_att").html('<font color="red">' + 'Please make a response!' + '</font>');      
+            $("#testMessage_att").html('<font color="red">' + 'Please make a response!' + '</font>');      
         }
     }
 }

### 2021-06-16 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
change to batch 5 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_4_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_5_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch4_production_june2021'
+    this_version = 'batch5_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    
@@ -114,7 +114,7 @@ $.ajax({
         console.log(this_sub_id)
     }
     
-    for (i = 0; i < 3; i++) {
+    for (i = 0; i < numTrialsExperiment; i++) {
         trial = {
             thisImageName: imgArray[i].src,
             thisImageCategory: imgArray[i].name,

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 6 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_5_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_6_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch5_production_june2021'
+    this_version = 'batch6_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
Revert "batch 6 production"
This reverts commit 0dccd919871999c2e817e3b12bfa30d1e32477dc.

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_6_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_5_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch6_production_june2021'
+    this_version = 'batch5_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 7 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_6_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_7_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch6_production_june2021'
+    this_version = 'batch7_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 analysis/step4_get_features_and_classifications/2_run_classsificatinos/count_classification_outputs.Rmd
for merging individual machine classifications

--- 2021-04-28 analysis/step2_get_features_and_classifications/2_run_classsificatinos/count_classification_outputs.Rmd
@@
 library(tidyverse)
-current_dir <- "classification-outputs-092020_C_0.1"
-files <- dir(current_dir)
+library(here)
+
+```
+
+```{r}
+current_dir <- here::here("data/compiled/classification-outputs-062021_C_0.1/")
+
+files = dir(current_dir)
 indexes = array()
@@
 ```{r}
-write.csv(all_data, paste0('compiled_classifications/Classification_Outputs',count,'.csv'))
+write.csv(all_data, here::here("data/compiled/", paste0('compiled_classifications/Classification_Outputs',count,'.csv')))
 

### 2021-06-17 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
for merging individual machine classifications

---
title: "Devphotodraw_main_anlayses"
author: "Bria Long"
date: "6/16/2021"
output: html_document
---
# Preprocessing
## Load libraries
```{r}
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

## Load data
### Compiled classification data
```{r load-classifications}
classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
  as_tibble() %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  dplyr::select(-X, -X.1, -index) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site)) 
```

### Load metadata
```{r}
# load and clean up "category" for tracing trials
all_meta <- read.csv(here::here('data/compiled/metadata/final_merged_metadata.csv')) %>%
    mutate(category = as.character(category)) %>%
    mutate(category = case_when(category == 'this square' ~ 'square',
                                category == 'this shape' ~ 'shape',                                
                                TRUE ~ as.character(category)))

# subIDs are unique identifier in recognition data for THU, session_ids in CDM data
meta_thu <- all_meta %>%
  filter(site=='THU') %>%
  mutate(unique_ids = subID) %>%
  mutate(draw_duration = draw_duration / 1000) # in ms for thu, whoops

meta_cdm <- all_meta %>%
  filter(site=='CDM') %>%
  mutate(unique_ids = session_id)

## unique IDs are now the identifier which will be used to join with machine/human recognition data
all_meta_cleaned <- meta_cdm %>%
  full_join(meta_thu) 
```

### Load tracing data, clean, and avg across participants
```{r}
# import, standardized spliced session_ids, and join back together
# tracing IDs are read in by session_ids, so need these to join with metadata
tracing_thu <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  mutate(session_id =  paste0('Tsinghua_photodraw_',session_id)) %>%
  filter(site=='Tsinghua') %>%
  left_join(meta_thu, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

tracing_cdm <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  filter(site=='CDM') %>%
  mutate(session_id = paste0('photodraw_',session_id)) %>%
  left_join(meta_cdm, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

# for modeling tracing scores for each shape (square/shape) separately for each participant
all_tracing <- tracing_thu %>%
  full_join(tracing_cdm)

# for per-subject tracing estimates
tracing_by_sub <- all_tracing %>%
  group_by(unique_ids) %>%
  summarize(avg_tracing_score = mean(rating))

```

### Join meta/tracing with classification data 
```{r}
d <- classification_data %>%
  mutate(unique_ids = session_id) %>%
  left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
  left_join(tracing_by_sub) %>%
  mutate(age_numeric = as.double(age_numeric)) %>%
  mutate(age_numeric = case_when(age_numeric == 10 ~ 9, # merge 2 10-year-olds into THU data for 9-year-olds
                                 TRUE ~ age_numeric))

```

### Load human classification data
```{r}
humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))

humans_merged <- humans %>%
  group_by(unique_ids, category) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) # join with classification data

```

### Clean up: Get rid of tech error drawings (see note)
```{r}
# bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
# this was checked directly in mongodb database -- no idea why, assuming bad internet.
tech_error_drawings <- d %>%
  filter(is.na(num_strokes))
# filter out tech error drawings from dataset (24)
d <- d %>%
  filter(!is.na(num_strokes)) 
```

```{r}
# this sub did one practice trial, not in subject log or classification data because no category level trials
# missing_id <- meta_cdm %>%
#   filter(!unique_ids %in% d$unique_ids)
```

### Sannity checks on counts of draiwngs per site/condition/etc
```{r}
sanity_counts <- d %>%
  group_by(condition,age_numeric, site) %>%
  summarize(num_drawings = n()) %>%
  kable()
```

```{r}
participant_counts <- d %>%
  group_by(age_numeric, site) %>%
  summarize(num_participants = length(unique(session_id)))

count_by_site <- d %>%
  group_by(site) %>%
  summarize(num_participants = length(unique(session_id)))

count_by_category <- d %>%
  group_by(category) %>%
  summarize(num_drawings = length(unique(session_id)))

count_by_id <- d %>%
  group_by(session_id) %>%
  summarize(num_drawings = length(unique(category))) 
```

265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e. 20 4-year-olds, 20 5-year-olds, etc.). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children. In the China based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database. Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification. On average, each child contributed `r mean(count_by_id$num_drawings)` to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).

# Descriptive anlayses
## Plot avg human vs. vgg classification
```{r}
ggplot(humans_merged, aes(x=correct_or_not, y=num_correct)) +
  geom_jitter(alpha=.2, width=.1, height=.1) +
  geom_smooth(method='lm') +
  ylab('human recognition') +
  xlab('model recognition')+
  theme_few()
```

### Correlates humans vs vgg classifications 
```{r}
cor.test(humans_merged$num_correct, humans_merged$target_label_prob)
cor.test(humans_merged$num_correct, humans_merged$correct_or_not)
```

## Main descriptive anlayses 
### Compute accuracy by age, condition, site 
```{r descriptives-across-age}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(session_id,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

### Plot accuracy by age, condition, site 
```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) + 
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~site)
```
### Compute effort/tracing by age, condition, site 
```{r}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

num_strokes <- d %>%
  group_by(unique_ids,condition,age_numeric,site) %>%
  summarize(avg_num_strokes = mean(num_strokes)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_num_strokes")

avg_intensity <- d %>%
  group_by(unique_ids,condition,age_numeric,site) %>%
  summarize(avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_intensity")

tracing_scores <- d %>%
  distinct(avg_tracing_score, unique_ids, site, age_numeric) %>%
  group_by(age_numeric, site) %>%
  multi_boot_standard(col = "avg_tracing_score")

```

### Plot effort/tracing by age, condition, site 
```{r plot-descriptives-across-age}
## Make compiled plot of descriptives
base_size_chosen=18 # size of text in plots
smooth_alpha=.2

p1=ggplot(draw_duration, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Draw duration (s)') +
  theme(legend.position = "right") + 
  ylim(0,30) +
  facet_grid(~site)

p2=ggplot(avg_intensity, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Ink used (mean intensity)') +
  theme(legend.position = "right") + 
  ylim(.02,.08) +
  facet_grid(~site)

p3=ggplot(num_strokes, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Number of strokes') +
  theme(legend.position = "right") +
  ylim(0,30) +
  facet_grid(~site)
```

### Plot effort covariates
Looks like THU kids spent more time on drawings, interesting; otherwise no big differences.

```{r}
p1
```

```{r}
p2
```

```{r}
p3
```

### Plot traing scores
```{r}
ggplot(tracing_scores, aes(age_numeric,mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none") +
  geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  facet_grid(~site) +
  ylim(0,4)
```

## Correlation of item effects across sites
Wow, cats are always badly classified.
```{r}
item_effects <- d %>%
  group_by(session_id,age_numeric,category, site) %>%
  summarize(avg_sub_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,category, site) %>%
  summarize(avg_cor = mean(avg_sub_cor)) %>%
  spread(key=site, value=avg_cor)

ggplot(item_effects, aes(x=CDM, y=THU, color=age_numeric)) +
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  ylim(0,1) + 
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_wrap(~category)
```

```{r}
item_effects_no_age <- d %>%
  group_by(session_id,category, site) %>%
  summarize(avg_sub_cor = mean(correct_or_not)) %>%
  group_by(category, site) %>%
  summarize(avg_cor = mean(avg_sub_cor)) %>%
  spread(key=site, value=avg_cor)

ggplot(item_effects_no_age, aes(x=CDM, y=THU, color=category)) +
  geom_point() + 
  theme_few(base_size = base_size_chosen) + 
  geom_abline(intercept = 0, slope=1)
```

# Inferential stats
## Try maximumal model first
Singular boundary fits when including (condition | subject) random slopes
Won't converge with random slopes for condition x age xs ite on each category
```{r}
full_model <- glmer(correct_or_not ~ condition*scale(age_numeric)*site +
                        (1 | unique_ids) +
                        (condition*scale(age_numeric) | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

summary(full_model)
```

## Remove 3-way interaction
No interactions with site are significant, removing from main effects structure
When 3 way interaction is removed, still can't add back more random slopes.
```{r}

full_model_no_int <- glmer(correct_or_not ~ condition*scale(age_numeric)+site +
                        (1 | unique_ids) +
                        (condition*scale(age_numeric) | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

summary(full_model_no_int)

```

ANOVA suggests that these two models -- with/without 3-way int -- explain equal variance.
```{r}
anova(full_model, full_model_no_int)
```

```{r}
summary(full_model_no_int)
```

## Add in effort/tracing covariates — does effort mediate any of the differences we're seeing? Not really. Still see same main effects structure.
```{r}
full_model_with_effort <- glmer(correct_or_not ~ condition*scale(age_numeric)+site +
                      scale(avg_tracing_score) +
                      scale(mean_intensity) +
                      scale(draw_duration) +
                      scale(num_strokes) + 
                      (1 | unique_ids) +
                      (condition*scale(age_numeric)  | category),
      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))

# frustratingly can't get anything with random slopes to converge!
summary(full_model_with_effort)

```

## No difference in tracing abilities across sites; only across age
```{r}
tracing_diff = lmer(rating ~ age_numeric + site + (1|unique_ids), data = all_tracing)
summary(tracing_diff)
```

### 2021-06-17 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
to download and preprocess recognition chunks

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
 library(tidyverse)
+library(here)
 ```
@@
 ```{r}
-all_data=as_tibble()
-for (batch in range(1,2)){
-  this_batch = read.csv(paste0("csv_out/Devphotodraw_recognition_batch",batch,".csv")) %>% as_tibble() 
-  all_data <- rbind(all_data, this_batch)
+for (batch in 1:4){
+  this_batch = read.csv(paste0("csv_out/",'batch',  batch, '_production_june2021.csv')) 
+  if (batch==1) {
+    all_data = this_batch
+  }
+  else {
+    all_data <- all_data %>%
+      full_join(this_batch)
+  }
 }
@@
 
-used_all_options <- d %>%
-  group_by(subID) %>%
-  summarize(num_labels = length(unique(guessed_category)))
+# used_all_options <- d %>%
+#   group_by(subID) %>%
+#   summarize(num_labels = length(unique(guessed_category))) %>%
+#   filter(num_labels==12)
 
@@
   filter(subID %in% included_subs$subID) 
+  # filter(subID %in% used_all_options$subID)
 ```
 
-# quick check by age
+# Preprocess recognition data for merging with classificatinos, etc
 ```{r}
-check_by_age <- d %>%
-  group_by(age) %>%
-  summarize(mean(guessed_category == drawn_category))
+humans <- d %>%
+  rename(category = drawn_category) %>%
+  # get site and unique ids from filenanme
+  mutate(unique_ids = str_split_fixed(imageName, '_',6)[,6]) %>%
+  mutate(unique_ids = str_split_fixed(unique_ids, '.png',2)[,1]) %>%
+  mutate(site = case_when( is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
+                           !is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "CDM")) %>%
+  mutate(unique_ids = case_when(site == "CDM" ~ str_split_fixed(unique_ids, '_',2)[,2],
+                                site == "THU" ~ unique_ids)) %>%
+  mutate(guessed_category = as.character(guessed_category)) %>%
+  # clean up two guesses that somehow overrode drop down menU?
+  mutate(guessed_category = case_when(guessed_category == "carn" ~ "car",
+                                guessed_category == "hatb" ~ "hat",
+                                TRUE ~ guessed_category)) %>%
+  # make factors
+  mutate(guessed_category = as.factor(guessed_category)) %>%
+  mutate(unique_ids = as.factor(unique_ids)) %>%
+  # calculate whether a guess was correct or not
+  mutate(correct_or_not = guessed_category == category) %>%
+  select(-subID)
+
 ```
+
+```{r}
+write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))
+```

### 2021-06-17 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
updated main analysis script

@@
 date: "6/16/2021"
-output: html_document
+output:
+  html_document:
+    toc: true
+    theme: united
 ---
@@
 
+```{r}
+by_category <- humans_merged %>%
+  group_by(category) %>%
+  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))
+
+ggplot(by_category, aes(x=model_pc, y=humans_pc, label=category)) +
+  geom_point() +
+  geom_smooth(method='lm') +
+  ylab('human recognition') +
+  xlab('model recognition') +
+  theme_few() +
+  ggrepel::geom_label_repel()
+```
+
 ### Correlates humans vs vgg classifications 
@@
 
-## Remove 3-way interaction
+### Remove 3-way interaction
 No interactions with site are significant, removing from main effects structure
@@
 
+### Add back site*condition
 ```{r}
-summary(full_model_no_int)
+with_site_condition <- glmer(correct_or_not ~ condition*scale(age_numeric)+condition*site +
+                        (1 | unique_ids) +
+                        (condition*scale(age_numeric) | category),
+      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+
+summary(with_site_condition)
+
+```
+
+### Add back age*site
+```{r}
+with_age_site <- glmer(correct_or_not ~ condition*scale(age_numeric)+scale(age_numeric)*site +
+                        (1 | unique_ids) +
+                        (condition*scale(age_numeric) | category),
+      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+
+summary(with_age_site)
+
+```
+
+## Add back both
+```{r}
+
+with_site_condition_and_site_age <- glmer(correct_or_not ~ condition*scale(age_numeric)+condition*site+scale(age_numeric)*site+
+                        (1 | unique_ids) +
+                        (condition*scale(age_numeric) | category),
+      data = d, family="binomial", control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+
+summary(with_site_condition_and_site_age)
 ```

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 8 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_7_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_8_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch7_production_june2021'
+    this_version = 'batch8_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 9 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_8_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_9_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch8_production_june2021'
+    this_version = 'batch9_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 10 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_9_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_10_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch9_production_june2021'
+    this_version = 'batch10_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 11 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_10_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_11_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch10_production_june2021'
+    this_version = 'batch11_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-17 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 12 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_11_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_12_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch11_production_june2021'
+    this_version = 'batch12_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 13 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_12_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_13_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch12_production_june2021'
+    this_version = 'batch13_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 14 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_13_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_14_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch13_production_june2021'
+    this_version = 'batch14_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 15 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_14_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_15_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch14_production_june2021'
+    this_version = 'batch15_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 16 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_15_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_16_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch15_production_june2021'
+    this_version = 'batch16_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 17 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_16_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_17_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch16_production_june2021'
+    this_version = 'batch17_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
check images

@@ -180,7 +180,7 @@ var experiment = {
         var response_logged = false;
         var input = document.getElementById("recognitionInput");
         var response = input.value;
-        var testing = false
+        var testing = true
 
         // if there is something in the response, log it
         if (input && response) {

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 18 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_17_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_18_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch17_production_june2021'
+    this_version = 'batch18_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
fix

@@ -180,7 +180,7 @@ var experiment = {
         var response_logged = false;
         var input = document.getElementById("recognitionInput");
         var response = input.value;
-        var testing = true
+        var testing = false
 
         // if there is something in the response, log it
         if (input && response) {

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 19 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_18_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_19_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch18_production_june2021'
+    this_version = 'batch19_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
batch 20 production

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_19_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_20_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch19_production_june2021'
+    this_version = 'batch20_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-18 experiments/Recognition_ratings/experiment/sketchRecognize_12AFC.js
final batch

@@ -83,7 +83,7 @@ $(document).ready(function() {
 
 $.ajax({
         type: "GET",
-        url: "recognition_rating_chunks/chunk_20_compiled_dataset.csv",
+        url: "recognition_rating_chunks/chunk_21_compiled_dataset.csv",
         dataType: "text",
         success: function(data) {
             results = Papa.parse(data);
@@ -99,7 +99,7 @@ $.ajax({
                
     
     //global variable 
-    this_version = 'batch20_production_june2021'
+    this_version = 'batch21_production_june2021'
     //
     trials = []
     numTrialsExperiment = imgArray.length;    

### 2021-06-19 analysis/step4b_download_recognition_data/preprocess_recognition_data.Rmd
update data compilation and main analysis files

@@
 ```{r}
-for (batch in 1:4){
+for (batch in 1:21){
   this_batch = read.csv(paste0("csv_out/",'batch',  batch, '_production_june2021.csv')) 
@@
   summarize(num_drawings = length(unique(image_name_short))) %>%
-  filter(num_drawings > 140)
+  filter(num_drawings > 50)
 
@@
   mutate(unique_ids = str_split_fixed(unique_ids, '.png',2)[,1]) %>%
-  mutate(site = case_when( is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
+  mutate(site = case_when(is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "THU", 
                            !is.na(str_locate(unique_ids,'photodraw_e2')[,1]) ~ "CDM")) %>%
@@
 ```{r}
-write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))
+write.csv(humans, here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))
 ```

### 2021-06-19 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
update data compilation and main analysis files

@@
 ```{r}
-humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_data_test.csv'))
+humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))
 
@@
   summarize(num_correct = mean(correct_or_not)) %>%
-  left_join(d, by=c('unique_ids','category')) # join with classification data
-
+  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
+  filter(!is.na(age))
 ```
@@
 cor_by_age_by_site_by_cond <- d %>%  
-  group_by(session_id,category,condition,age_numeric, site) %>%
+  group_by(unique_ids,category,condition,age_numeric, site) %>%
   summarize(avg_cor = mean(correct_or_not)) %>%
   group_by(age_numeric,condition, site) %>%
-  multi_boot_standard(col = "avg_cor") 
+  multi_boot_standard(col = "avg_cor") %>%
+  mutate(who = "model")
+
+cor_by_age_by_site_by_cond_humans <- humans_merged %>%  
+  group_by(unique_ids,category,condition,age_numeric, site) %>%
+  summarize(avg_cor = mean(num_correct)) %>%
+  group_by(age_numeric,condition, site) %>%
+  multi_boot_standard(col = "avg_cor") %>%
+  mutate(who = 'humans')
+
+humans_and_models <- cor_by_age_by_site_by_cond %>%
+  full_join(cor_by_age_by_site_by_cond_humans)
 ```
@@
 base_size_chosen=12; smooth_alpha=.2
-ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = condition)) +
+ggplot(humans_and_models, aes(age_numeric,mean, col = condition)) +
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
@@
   geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
-  facet_grid(~site)
+  facet_grid(who~site)
 ```
@@
 
+```{r}
+full_model_humans <- lmer(num_correct ~ condition*scale(age_numeric)*site +
+                        (1 | unique_ids) +
+                        (condition | category),
+      data = humans_merged)
+summary(full_model_humans)
+```
+
 ### Remove 3-way interaction
@@
 summary(full_model_no_int)
+
+```
+
+```{r}
+full_model_no_int_humans <- lmer(num_correct ~ condition*scale(age_numeric)+site +
+                        (1 | unique_ids) +
+                        (condition | category),
+      data = humans_merged)
+
+summary(full_model_no_int_humans)
 
@@
 ```{r}
-full_model_with_effort <- glmer(correct_or_not ~ condition*scale(age_numeric)+site +
+full_model_with_effort <- glmer(correct_or_not ~ condition*scale(age_numeric)*site +
                       scale(avg_tracing_score) +
@@
 
+## Repeat with human classificatinos
+```{r}
+full_model_with_effort <- lmer(num_correct ~ condition*scale(age_numeric)*site +
+                      scale(avg_tracing_score) +
+                      scale(mean_intensity) +
+                      scale(draw_duration) +
+                      scale(num_strokes) + 
+                      (1 | unique_ids) +
+                      (condition |category), data = humans_merged)
+
+# condition*age slopes on categories won't converge
+summary(full_model_with_effort)
+```
+
 ## No difference in tracing abilities across sites; only across age

### 2021-06-24 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
add rmarkdown manuscript file to repo

@@
 humans_merged <- humans %>%
-  group_by(unique_ids, category) %>% # group by each drawing of each category
+  group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
   summarize(num_correct = mean(correct_or_not)) %>%
@@
 
+```{r}
+
+category_age_cond <- humans_merged %>%
+  group_by(category, condition) %>%
+  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))
+
+```
+
+```{r}
+ggplot(category_age_cond, aes(x=model_pc, y=humans_pc, color=condition))+
+  geom_point() +
+  ylim(0,1) +
+  xlim(0,1) +
+  theme_few() +
+  theme(aspect.ratio = 1) +
+  facet_wrap(~category) +
+  geom_abline(color='grey')
+
+```
+```{r}
+ggplot(category_age_cond, aes(x=model_pc, y=humans_pc, label=category))+
+  geom_point() +
+  ylim(0,1) +
+  xlim(0,1) +
+  theme_few() +
+  theme(aspect.ratio = 1) +
+  facet_wrap(~condition) +
+  geom_abline(xintercept=0, color='grey') +
+  ggrepel::geom_label_repel() 
+```
 ## Main descriptive anlayses 
@@
 
+```{r descriptives-across-age}
+cor_by_age_by_cond <- d %>%  
+  group_by(unique_ids,category,condition,age_numeric) %>%
+  summarize(avg_cor = mean(correct_or_not)) %>%
+  group_by(age_numeric,condition) %>%
+  multi_boot_standard(col = "avg_cor") %>%
+  mutate(who = "model")
+
+cor_by_age_by_cond_humans <- humans_merged %>%  
+  group_by(unique_ids,category,condition,age_numeric) %>%
+  summarize(avg_cor = mean(num_correct)) %>%
+  group_by(age_numeric,condition) %>%
+  multi_boot_standard(col = "avg_cor") %>%
+  mutate(who = 'humans')
+
+humans_and_models_no_site <- cor_by_age_by_cond_humans %>%
+  full_join(cor_by_age_by_cond)
+```
+
 ### Plot accuracy by age, condition, site 
@@
 ```
+```{r}
+base_size_chosen=12; smooth_alpha=.2
+ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = conditionf)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
+  theme_few(base_size = base_size_chosen) + 
+  labs(x='Age', y='Classification accuracy') +
+  ylim(0,1) + 
+  geom_smooth(span=10, alpha=.2) +
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  facet_grid(~who)
+
+```
+```{r}
+disagreements <- humans_merged %>%
+  filter(num_correct>.8) %>%
+  filter(correct_or_not==0) %>%
+  filter(condition=='S')
+
+disagreements <- disagreements %>%
+  mutate(image_path = here::here('data/compiled/drawings/object_drawings', image_name_short)) %>%
+  mutate(new_image_path = here::here('data/compiled/drawings/disagreements', image_name_short))
+
+dir.create(here::here('data/compiled/drawings/disagreements'))
+
+file.copy(disagreements$image_path, disagreements$new_image_path)
+
+```
+
+```{r}
+machine_p_advantage <- humans_merged %>%
+  filter(num_correct<.5) %>%
+  filter(correct_or_not==1) %>%
+  filter(condition=='P')
+
+machine_p_advantage <- machine_p_advantage %>%
+  mutate(image_path = here::here('data/compiled/drawings/object_drawings', image_name_short)) %>%
+  mutate(new_image_path = here::here('data/compiled/drawings/machine_p_advantage', image_name_short))
+
+dir.create(here::here('data/compiled/drawings/machine_p_advantage'))
+
+file.copy(machine_p_advantage$image_path, machine_p_advantage$new_image_path)
+
+```
+
 ### Compute effort/tracing by age, condition, site 
@@
 ggplot(item_effects, aes(x=CDM, y=THU, color=age_numeric)) +
+  geom_point() + 
+  theme_few(base_size = base_size_chosen) + 
+  ylim(0,1) + 
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  facet_wrap(~category)
+```
+
+```{r}
+item_effects <- humans_merged %>%
+  group_by(session_id,age_numeric,category, site) %>%
+  summarize(avg_sub_cor = mean(num_correct)) %>%
+  group_by(age_numeric,category, site) %>%
+  summarize(avg_cor = mean(avg_sub_cor)) %>%
+  spread(key=site, value=avg_cor)
+
+ggplot(item_effects, aes(x=CDM, y=THU, color=age_numeric)) +
+  geom_point() + 
+  theme_few(base_size = base_size_chosen) + 
+  ylim(0,1) + 
+  xlim(0,1) +
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  geom_abline(color = 'grey', intercept=0) + 
+  facet_wrap(~category)
+```
+
+```{r}
+item_effects_not_spread <- humans_merged %>%
+  group_by(session_id,age_numeric,category, site) %>%
+  summarize(avg_sub_cor = mean(num_correct)) %>%
+  group_by(age_numeric,category, site) %>%
+  multi_boot_standard(col = "avg_sub_cor")
+
+ggplot(item_effects_not_spread, aes(x=as.numeric(age_numeric), y=mean, color=site)) +
+  geom_point() +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
+  theme_few(base_size = base_size_chosen) + 
+  ylim(0,1) + 
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  ylab('Proportion correct') +
+  xlab('Age (in years)') +
+  geom_abline(color = 'grey', intercept=0) +
+  geom_smooth(span=20, alpha=.1) +
+  facet_wrap(~category)
+```
+
+```{r}
+item_effects <- humans_merged %>%
+  group_by(age_numeric,category) %>%
+  summarize(model_pc = mean(correct_or_not), human_pc = mean(num_correct))
+
+ggplot(item_effects, aes(x=model_pc, y=human_pc, color=age_numeric)) +
   geom_point() + 

### 2021-06-24 writing/Manuscript_June2021.Rmd
add rmarkdown manuscript file to repo

---
title             : "Consistency and variability in the development of children's drawings between two countries"
shorttitle        : "Development of drawing"

author: 
  - name          : "Bria Long"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "450 Jane Stanford Way, Stanford CA 94305"
    email         : "bria@stanford.edu"
  - name          : "Ying Wang"
    affiliation   : "2"
  - name          : "Stella Christie"
    affiliation   : "2"
  - name          : "Michael C. Frank"
    affiliation   : "1"
  - name          : "Judith E. Fan"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Stanford University"
  - id            : "2"
    institution   : "Tsinghua University"
  - id            : "3"
    institution   : "University of California, San Diego"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
 Childen's drawings of common object categories become dramatically more recognziable across development. What are the major factors that explain these developmental changes? Here, we examined the degree to which these changes in recognzibility vary across different drawing tasks (i.e. drawing from observation vs. from memory), geographical locations,  and children's tracing abilities. To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253) who were recruited near San Jose, USA and Beijing, China. Overall, we show broad consistency in these developmental trajectories across object categories, drawing tasks, and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce. In addition, we find that children recruited near Beijing, China produced overal more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.  Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.

keywords          : "children's drawings, visual production, tracing, object recognition, visuomotor control"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)
library(xtable)
```

As humans, we have many powerful tools to externalize what we know, including language and gesture. 
One tool that has been transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format. 
Drawing is an important case study in graphical representation, being a technique that dates back 60,000 years [@hoffmann2018u], well before the emergence of symbolic writing systems, and is practiced in many cultures.

In modern times, drawings are produced prolifically by children from an early age. 
Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities [@minsky1972artificial], and accordingly a long history of work has examined changes in children's drawings across development [@piaget1929child; @kellogg1969analyzing; @karmiloff1990constraints; @fury1997children].
Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs. \textit{child}) than older children, who enrich their drawings with more diagnostic part [@sitton1992drawing] and relational [@light1983effects] information. 
Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict [@long2018drawings].

What drives these dramatic changes in children's drawings across development? 
A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements [@freeman1987current; @rehrig2018does]. 
While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
% how recognizable drawing is a complex skill that integrates many different aspects of cognition. 
% For example, in order to "draw a [rabbit]", a child has to access their mental representation of a rabbit, choose the particular visual features needed to convey this visual concept, and then maintain this representation and goal in mind as they plan and produce a series of motor movements. 
Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].

One idea is that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like. 
On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2020relating]. 
However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.  
For example, when asked to draw from observation, younger children tend to include features that are not visible from their vantage point, yet are diagnostic of category membership (e.g., a handle on a \textit{mug}) [@bremmer1984prior; @barrett1976symbolism], and only omit these features later in development. 
Similarly, young children will insist that their nearly identical drawings of different concepts (e.g., balloon and person) unambiguously refer to different things [@bloom1998intention]. 
Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories. 
On this account, changes in children's drawings from memory across age may be largely due to other factors beyond changes in memory -- for example, changes in how children represent the diagnostic visual features of each category [@long2018drawings].

To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when asked to draw from memory ("Can you draw a [rabbit]?) and when asked to draw a canonical exemplar from observation ("Can you draw this [rabbit] as it looks in the picture?") across two different geographical sites (San Jose, USA and Beijing, China).
To do so, we gathered digital drawings from a large sample of children 4-9 years of age in a controlled experimental setting.
While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making], most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities [@la2001children; @winner1989can; @huntsinger2011cultural].
To assess the degree to which visuomotor development accounts for any observed variation, we also measured each child's shape tracing abilities.

We had several predictions about the nature of the effects that we would observe. First, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, in keeping with accounts of naïve realism and contra a strong account of working memory limitations.
Second, we predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
Finally, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at https://osf.io/qymjr/.

Overall, we replicated prior work, showing strong and consistent developmental changes in the recognizability of children's drawings across development.

# Methods

```{r plotting-params}
base_size_chosen=12; smooth_alpha=.2
```

```{r load-classifications}
classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
  as_tibble() %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  dplyr::select(-X, -X.1, -index) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site)) 
```

```{r load-metadata}
# load and clean up "category" for tracing trials
all_meta <- read.csv(here::here('data/compiled/metadata/final_merged_metadata.csv')) %>%
    mutate(category = as.character(category)) %>%
    mutate(category = case_when(category == 'this square' ~ 'square',
                                category == 'this shape' ~ 'shape',                                
                                TRUE ~ as.character(category)))

# subIDs are unique identifier in recognition data for THU, session_ids in CDM data
meta_thu <- all_meta %>%
  filter(site=='THU') %>%
  mutate(unique_ids = subID) %>%
  mutate(draw_duration = draw_duration / 1000) # in ms for thu, whoops

meta_cdm <- all_meta %>%
  filter(site=='CDM') %>%
  mutate(unique_ids = session_id)

## unique IDs are now the identifier which will be used to join with machine/human recognition data
all_meta_cleaned <- meta_cdm %>%
  full_join(meta_thu) 
```

\
```{r load-tracing}
# import, standardized spliced session_ids, and join back together
# tracing IDs are read in by session_ids, so need these to join with metadata
tracing_thu <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  mutate(session_id =  paste0('Tsinghua_photodraw_',session_id)) %>%
  filter(site=='Tsinghua') %>%
  left_join(meta_thu, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

tracing_cdm <- read.csv(here::here('data/compiled/tracing_outputs/transformed_tracings.csv'))  %>%
  filter(site=='CDM') %>%
  mutate(session_id = paste0('photodraw_',session_id)) %>%
  left_join(meta_cdm, by=c('session_id','category')) %>%
  dplyr::select(-X.1, -X, -site.x, -filename.y) %>%
  rename(site = site.y, filename = filename.x)

# for modeling tracing scores for each shape (square/shape) separately for each participant
all_tracing <- tracing_thu %>%
  full_join(tracing_cdm)

# for per-subject tracing estimates
tracing_by_sub <- all_tracing %>%
  group_by(unique_ids) %>%
  summarize(avg_tracing_score = mean(rating))
```

```{r join-data}
model_classifications <- classification_data %>%
  mutate(unique_ids = session_id) %>%
  left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
  left_join(tracing_by_sub)

# bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
# this was checked directly in mongodb database -- no idea why, assuming bad internet.
tech_error_drawings <- model_classifications %>%
  filter(is.na(num_strokes))
# filter out tech error drawings from dataset (24)
model_classifications <- model_classifications%>%
  filter(!is.na(num_strokes))

```

```{r load-human-recognition}
humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))

```

```{r join-human-rec-with-meta}
d <- humans %>%
  group_by(unique_ids, category, image_name_short, site, age) %>% # group by each drawing of each category
  summarize(prop_correct = mean(correct_or_not))  %>%
   left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>%
  mutate(age_numeric = age) %>%
  mutate(age_numeric = as.double(age_numeric)) %>%
  mutate(age_numeric = case_when(age_numeric == 10 ~ 9, # merge 2 10-year-olds into THU data for 9-year-olds
                                 TRUE ~ age_numeric)) %>%
  left_join(tracing_by_sub) %>%
  mutate(site = fct_recode(site, "San Jose" = "CDM", "Beijing" = "THU"))%>%
  mutate(condition = fct_recode(condition, "From perception" = "P", "From memory" = "S"))

humans_and_models_merged <- humans %>%
  group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
  summarize(prop_correct = mean(correct_or_not)) %>%
  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
  filter(!is.na(age))
```

```{r count-participants}
participant_counts <- d %>%
  group_by(age_numeric, site) %>%
  summarize(num_participants = length(unique(unique_ids)))

count_by_site <- d %>%
  group_by(site) %>%
  summarize(num_participants = length(unique(unique_ids)))

count_by_category <- d %>%
  group_by(category) %>%
  summarize(num_drawings = length(unique(unique_ids)))

count_by_id <- d %>%
  group_by(unique_ids) %>%
  summarize(num_drawings = length(unique(category))) 
```

## Participants
265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e. 20 4-year-olds, 20 5-year-olds, etc.). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children. In the China based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database. Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification. On average, each child contributed `r mean(count_by_id$num_drawings)` to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).

## Task Procedure
Before beginning, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw. So, please draw so that someone else could try what you were trying to draw.” Children then completed a series of tracing trials designed to both familiarize them with the tablet interface and to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure X). Children used their fingers to draw and had a maximum of 30 seconds to produce their tracings/drawings on all trials; strokes could not be deleted once drawn.

The primary experimental manipulation was the type of cue used to prompt children to produce a drawing. Specifically, there were two cue types: (1) a verbal cue provided by the experimenter in a 5s video clip (2) an photo cue which remained on screen continuously while children drew. In the verbal-cue condition, children heard “What about a [x]? Can you draw a [x]?” In the image-cue condition, children heard audio of the same experimenter said,  “What about this [x]? Can you draw the [x] as it looks in the picture?”. Children completed 12 drawing trials, with six categories each randomly assigned to each condition and displayed in a random order. For photo-cues trials, one of three possible exemplars was randomly chosen (see Appendix, Figure X for all stimuli). Children completed drawing trials were blocked by these two conditions; the condition order counterbalanced across subjects in each age group. All instructions were translated into Mandarin by a native speaker; see Appendix, Table X for exact translations.

## Measuring Tracing Accuracy
As in [@long2018drawings], we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality. We decomposed tracing accuracy into two components: a shape error component and a spatial error component. Shape error reflects how closely the participant’s tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant’s tracing matched the target shape.

To compute these error components, we applied an image registration algorithm, AirLab [@sandkuhler2018], to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, $T$, and the target shape, $S$: $Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}$, where $N$ is the number of pixels in both images.  The shape error was defined by the final correlation distance between the aligned tracing and the target shape. The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively. In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).

We used the same tracing quality ratings to obtained in [@long2018drawings] to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale. An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs. star) as predictors, with random intercepts for rater.  This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes within session to yield a single tracing score for each participant.

## Measuring effort covariates
For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers. We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke — start time of first stroke). As a second measure of effort, we also counted the number of strokes that children put into a given drawing. Finally, we estimated the proportion of the drawing canvas that was filled (e.g., 'ink used') by computing the proportion of each final drawing that were non-white pixels.

## Measuring drawing recognizability

### Human recognition scores
We assessed the recognizability of each drawing via a recognition experiment. Adult participants were recruited via Prolific for a 15 minute experiment and compensated at $14/hour. Participants were shown a random subset of the drawings and asked "What does this look like?" and then selected an answer from the twelve categories that children were prompted to draw. Participants were encouraged to guess.

### Automated recognition scores
We used a combination of neural neural activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol. To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification. We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6). Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization across all filtered drawings in the dataset.  Next, we used these features to train object category decoders. We then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories. No additional metadata about the age of the child who produced each sketch was provided to the decoder. This procedure was repeated for each drawing in the dataset, yielding both a binary a recognition score and the softmax probability assigned to each target class in the dataset.

## Statistical models
Two mixed effects models were fit to assess the factors that influenced the recognizability of the drawings that children produced. A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs. Beijing), and drawing task (photo-cue vs. label-cue), and the three way interaction between these key variables. We initially attempted to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category. However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge following @Barr2013. We then ran a second model predicting the human recognition scores for each drawing with the same fixed and random effect structure.

In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings. We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see above), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e. percentage of non-white pixels), and the number of strokes children used. All predictors were scaled to have a mean of 0 and a standard deviation of 1. Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with random intercepts for each participant.

```{r}
full_model <- lmer(prop_correct ~ condition*scale(age_numeric)*site +
                        (1 | unique_ids) +
                        (condition | category),
      data = d)

full_model_out = summary(full_model)

```

```{r}
full_model_with_effort <- lmer(prop_correct ~ condition*scale(age_numeric)*site +
                      scale(avg_tracing_score) +
                      scale(mean_intensity) +
                      scale(draw_duration) +
                      scale(num_strokes) + 
                      (1 | unique_ids) +
                      (condition | category),
      data = d)

# frustratingly can't get anything with random slopes to converge!
full_model_with_effort_out = summary(full_model_with_effort)

```

# Results
Overall, we found relative consistency in the developmental trajectory of children's drawings. Figure \ref{fig:main_results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in. We found no difference in the recognizability of children's drawings according to the task they were asked to do: drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" and they were simply asked "What about a rabbit? Can you draw a rabbit." While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do some adults when presented with canonical photographs of object categories [@photodrawcogsci] -- this was not the case. All model coefficients can be found in Table 1.

However, we did observe a main effect of geographical site: Children who were recruited outside of Beijing, China tended to produce more recognizable drawings than children who were recruited in San Jose, USA. In a second set of analyses, we aimed to understand the nature of this difference. We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. To test this hypothesis, we thus included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into the same linear mixed-effects model. If these effort covariates explained the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability. Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.

```{r}
cor_by_age_by_site_by_cond <- d %>%  
  group_by(unique_ids,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(prop_correct)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

```{r main-results, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs. Beijing), and the type of drawing task they completed. Error bars show bootstrapped 95 percent cofnidence intervals."}
ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age (in years)', y='Proportion recognized') +
  ylim(0,1) + 
  geom_smooth(span=20, alpha=.1) +
  scale_color_discrete(name="") +
  theme(legend.position = 'bottom') +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(~site)

```

```{r}
cleaned_names_full_model = c("Intercept","Task","Age","Site","Task*Age","Task*Site","Age*Site","Task*Age*Site")
rownames(full_model_out$coefficients)<-cleaned_names_full_model

# xtable(full_model_out$coefficients, digits=c(2,2,2,2,2,3),"Model coefficients from a  linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")
```

```{r}
cleaned_names_full_model_with_effort = c("Intercept","Task","Age","Site","Est. tracing score","Avg. intensity", "Draw duration", "Number of strokes","Task*Age","Task&Site", "Age*Site","Task*Age*Site")

rownames(full_model_with_effort_out$coefficients)<-cleaned_names_full_model_with_effort

# xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,2,3),"Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
```

```{r get-descriptives-across-age}
draw_duration <- d %>%
  group_by(unique_ids,condition,age_numeric, site) %>%
  summarize(avg_draw_duration = mean(draw_duration)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_draw_duration")

num_strokes <- d %>%
  group_by(unique_ids,condition,age_numeric,site) %>%
  summarize(avg_num_strokes = mean(num_strokes)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_num_strokes")

avg_intensity <- d %>%
  group_by(unique_ids,condition,age_numeric,site) %>%
  summarize(avg_intensity = mean(mean_intensity)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_intensity")
```

```{r plot-effort}
## Make compiled plot of descriptives
base_size_chosen=14 # size of text in plots
smooth_alpha=.2

p1=ggplot(draw_duration, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Draw duration (s)') +
  theme(legend.position = "none") + 
  ylim(0,30) +
  facet_grid(~site)

p2=ggplot(avg_intensity, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Ink used (mean intensity)') +
  theme(legend.position = "none") + 
  ylim(.02,.08) +
  facet_grid(~site)

p3=ggplot(num_strokes, aes(age_numeric,mean, color=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Number of strokes') +
  theme(legend.position = "none") +
  ylim(0,15) +
  facet_grid(~site)
```

```{r effort-covariates, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Effort covariates measured during the drawing task -- amount of time spent drawing, amount of 'ink' used, and number of strokes used -- as function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs. Beijing), and the type of drawing task they completed. Error bars show bootstrapped 95 percent cofnidence intervals."}
cowplot::plot_grid(p1,p2,p3,nrow=1)
```

```{r}
tracing_scores_indiv <- d %>%
  ungroup() %>%
  distinct(unique_ids, avg_tracing_score, site, age_numeric)

tracing_scores <- tracing_scores_indiv %>%
  group_by(age_numeric, site) %>%
  multi_boot_standard(col = 'avg_tracing_score')
```

```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals."} 
ggplot(tracing_scores, aes(age_numeric,mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.05, alpha=.5) +
  theme_few(base_size = base_size_chosen) +
  labs(x='Age', y='Tracing score') +
  theme(legend.position = "none") +
  geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
  facet_grid(~site) +
  ylim(0,4)
```

# Discussion

# Acknowledgements  
We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible. We also gratefully acknowledge the San Jose Children's Discovery Museum for their collaboration. We are also thankful to all of the parents at XX and XX preschool whose children participated. We also thank the members of the Stanford Language and Cognition lab for their feedback. This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.

\newpage

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-06-24 writing/Manuscript_June2021.tex
add rmarkdown manuscript file to repo

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Consistency and variability in the development of children's drawings between two countries},
  pdflang={en-EN},
  pdfkeywords={children's drawings, visual production, tracing, object recognition, visuomotor control},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Development of drawing}
\author{Bria Long\textsuperscript{1}, Ying Wang\textsuperscript{2}, Stella Christie\textsuperscript{2}, Michael C. Frank\textsuperscript{1}, \& Judith E. Fan\textsuperscript{3}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Stanford University\\\textsuperscript{2} Tsinghua University\\\textsuperscript{3} University of California, San Diego}
\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Bria Long, 450 Jane Stanford Way, Stanford CA 94305. E-mail: bria@stanford.edu}
\keywords{children's drawings, visual production, tracing, object recognition, visuomotor control\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Consistency and variability in the development of children's drawings between two countries}

\date{}

\abstract{
Childen's drawings of common object categories become dramatically more recognziable across development. What are the major factors that explain these developmental changes? Here, we examined the degree to which these changes in recognzibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations, and children's tracing abilities. To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253) who were recruited near San Jose, USA and Beijing, China. Overall, we show broad consistency in these developmental trajectories across object categories, drawing tasks, and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce. In addition, we find that children recruited near Beijing, China produced overal more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA. Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.
}

\begin{document}
\maketitle

As humans, we have many powerful tools to externalize what we know, including language and gesture.
One tool that has been transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format.
Drawing is an important case study in graphical representation, being a technique that dates back 60,000 years (Hoffmann et al., 2018), well before the emergence of symbolic writing systems, and is practiced in many cultures.

In modern times, drawings are produced prolifically by children from an early age.
Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities (Minsky \& Papert, 1972), and accordingly a long history of work has examined changes in children's drawings across development (Fury, Carlson, \& Sroufe, 1997; Karmiloff-Smith, 1990; Kellogg, 1969; Piaget, 1929).
Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict (Long, Fan, \& Frank, 2018).

What drives these dramatic changes in children's drawings across development?
A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements (Freeman, 1987; Rehrig \& Stromswold, 2018).
While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
\% how recognizable drawing is a complex skill that integrates many different aspects of cognition.
\% For example, in order to \enquote{draw a {[}rabbit{]}}, a child has to access their mental representation of a rabbit, choose the particular visual features needed to convey this visual concept, and then maintain this representation and goal in mind as they plan and produce a series of motor movements.
Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations (Dekker, Mareschal, Sereno, \& Johnson, 2011; Long et al., 2018; Natu et al., 2016) as well as their increasing working memory capacity (Pailian, Libertus, Feigenson, \& Halberda, 2016).

One idea is that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan et al., 2020).
However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.\\
For example, when asked to draw from observation, younger children tend to include features that are not visible from their vantage point, yet are diagnostic of category membership (e.g., a handle on a \textit{mug}) (Barrett \& Light, 1976; Bremner \& Moore, 1984), and only omit these features later in development.
Similarly, young children will insist that their nearly identical drawings of different concepts (e.g., balloon and person) unambiguously refer to different things (Bloom \& Markson, 1998).
Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories.
On this account, changes in children's drawings from memory across age may be largely due to other factors beyond changes in memory -- for example, changes in how children represent the diagnostic visual features of each category (Long et al., 2018).

To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when asked to draw from memory (\enquote{Can you draw a {[}rabbit{]}?) and when asked to draw a canonical exemplar from observation (}Can you draw this {[}rabbit{]} as it looks in the picture?") across two different geographical sites (San Jose, USA and Beijing, China).
To do so, we gathered digital drawings from a large sample of children 4-9 years of age in a controlled experimental setting.
While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006), most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
To assess the degree to which visuomotor development accounts for any observed variation, we also measured each child's shape tracing abilities.

We had several predictions about the nature of the effects that we would observe. First, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, in keeping with accounts of naïve realism and contra a strong account of working memory limitations.
Second, we predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
Finally, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at \url{https://osf.io/qymjr/}.

Overall, we replicated prior work, showing strong and consistent developmental changes in the recognizability of children's drawings across development.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

265 participants were recruited from the San Jose Children's Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children. In the China based sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database. Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification. On average, each child contributed 11.46 to analysis (min 6, max = 12).

\hypertarget{task-procedure}{%
\subsection{Task Procedure}\label{task-procedure}}

Before beginning, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw. So, please draw so that someone else could try what you were trying to draw.} Children then completed a series of tracing trials designed to both familiarize them with the tablet interface and to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure X). Children used their fingers to draw and had a maximum of 30 seconds to produce their tracings/drawings on all trials; strokes could not be deleted once drawn.

The primary experimental manipulation was the type of cue used to prompt children to produce a drawing. Specifically, there were two cue types: (1) a verbal cue provided by the experimenter in a 5s video clip (2) an photo cue which remained on screen continuously while children drew. In the verbal-cue condition, children heard \enquote{What about a {[}x{]}? Can you draw a {[}x{]}?} In the image-cue condition, children heard audio of the same experimenter said, \enquote{What about this {[}x{]}? Can you draw the {[}x{]} as it looks in the picture?}. Children completed 12 drawing trials, with six categories each randomly assigned to each condition and displayed in a random order. For photo-cues trials, one of three possible exemplars was randomly chosen (see Appendix, Figure X for all stimuli). Children completed drawing trials were blocked by these two conditions; the condition order counterbalanced across subjects in each age group. All instructions were translated into Mandarin by a native speaker; see Appendix, Table X for exact translations.

\hypertarget{measuring-tracing-accuracy}{%
\subsection{Measuring Tracing Accuracy}\label{measuring-tracing-accuracy}}

As in (Long et al., 2018), we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality. We decomposed tracing accuracy into two components: a shape error component and a spatial error component. Shape error reflects how closely the participant's tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant's tracing matched the target shape.

To compute these error components, we applied an image registration algorithm, AirLab (Sandkühler, Jud, Andermatt, \& Cattin, 2018), to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, \(T\), and the target shape, \(S\): \(Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}\), where \(N\) is the number of pixels in both images. The shape error was defined by the final correlation distance between the aligned tracing and the target shape. The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively. In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).

We used the same tracing quality ratings to obtained in (Long et al., 2018) to assign weights to each of their error terms; adult observers (\(N\)=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated \enquote{how well the tracing matches the target shape and is aligned to the position of the target shape} on a 5-point scale. An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs.~star) as predictors, with random intercepts for rater. This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes within session to yield a single tracing score for each participant.

\hypertarget{measuring-effort-covariates}{%
\subsection{Measuring effort covariates}\label{measuring-effort-covariates}}

For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers. We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke --- start time of first stroke). As a second measure of effort, we also counted the number of strokes that children put into a given drawing. Finally, we estimated the proportion of the drawing canvas that was filled (e.g., \enquote{ink used}) by computing the proportion of each final drawing that were non-white pixels.

\hypertarget{measuring-drawing-recognizability}{%
\subsection{Measuring drawing recognizability}\label{measuring-drawing-recognizability}}

\hypertarget{human-recognition-scores}{%
\subsubsection{Human recognition scores}\label{human-recognition-scores}}

We assessed the recognizability of each drawing via a recognition experiment. Adult participants were recruited via Prolific for a 15 minute experiment and compensated at \$14/hour. Participants were shown a random subset of the drawings and asked \enquote{What does this look like?} and then selected an answer from the twelve categories that children were prompted to draw. Participants were encouraged to guess.

\hypertarget{automated-recognition-scores}{%
\subsubsection{Automated recognition scores}\label{automated-recognition-scores}}

We used a combination of neural neural activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol. To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification. We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6). Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization across all filtered drawings in the dataset. Next, we used these features to train object category decoders. We then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories. No additional metadata about the age of the child who produced each sketch was provided to the decoder. This procedure was repeated for each drawing in the dataset, yielding both a binary a recognition score and the softmax probability assigned to each target class in the dataset.

\hypertarget{statistical-models}{%
\subsection{Statistical models}\label{statistical-models}}

Two mixed effects models were fit to assess the factors that influenced the recognizability of the drawings that children produced. A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (photo-cue vs.~label-cue), and the three way interaction between these key variables. We initially attempted to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category. However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge following ({\textbf{???}}). We then ran a second model predicting the human recognition scores for each drawing with the same fixed and random effect structure.

In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings. We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see above), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.~percentage of non-white pixels), and the number of strokes children used. All predictors were scaled to have a mean of 0 and a standard deviation of 1. Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with random intercepts for each participant.

\hypertarget{results}{%
\section{Results}\label{results}}

Overall, we found relative consistency in the developmental trajectory of children's drawings. Figure \ref{fig:main_results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in. We found no difference in the recognizability of children's drawings according to the task they were asked to do: drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} and they were simply asked \enquote{What about a rabbit? Can you draw a rabbit.} While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do some adults when presented with canonical photographs of object categories ({\textbf{???}}) -- this was not the case. All model coefficients can be found in Table 1.

However, we did observe a main effect of geographical site: Children who were recruited outside of Beijing, China tended to produce more recognizable drawings than children who were recruited in San Jose, USA. In a second set of analyses, we aimed to understand the nature of this difference. We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. To test this hypothesis, we thus included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into the same linear mixed-effects model. If these effort covariates explained the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability. Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.

\begin{figure}[H]

{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/main-results-1}

}

\caption{Proportion of drawings recognized as a function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs. Beijing), and the type of drawing task they completed. Error bars show bootstrapped 95 percent cofnidence intervals.}\label{fig:main-results}
\end{figure}

\begin{verbatim}
## % latex table generated in R 3.6.1 by xtable 1.8-4 package
## % Wed Jun 23 21:21:29 2021
## \begin{table}[ht]
## \centering
## \begin{tabular}{rrrrrr}
##   \hline
##  & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
##   \hline
## Intercept & 0.73 & 0.02 & 31.62 & 34.74 & 0.000 \\ 
##   Task & -0.02 & 0.02 & 17.29 & -0.87 & 0.397 \\ 
##   Age & 0.17 & 0.02 & 373.04 & 11.21 & 0.000 \\ 
##   Site & 0.05 & 0.02 & 385.12 & 2.39 & 0.017 \\ 
##   Task*Age & -0.02 & 0.01 & 2622.52 & -1.47 & 0.141 \\ 
##   Task*Site & -0.00 & 0.02 & 2631.48 & -0.20 & 0.842 \\ 
##   Age*Site & -0.00 & 0.02 & 388.66 & -0.06 & 0.951 \\ 
##   Task*Age*Site & 0.00 & 0.02 & 2639.46 & 0.21 & 0.834 \\ 
##    \hline
## \end{tabular}
## \caption{Model coefficients from a  linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.} 
## \end{table}
\end{verbatim}

\begin{verbatim}
## % latex table generated in R 3.6.1 by xtable 1.8-4 package
## % Wed Jun 23 21:21:29 2021
## \begin{table}[ht]
## \centering
## \begin{tabular}{rrrrrr}
##   \hline
##  & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
##   \hline
## Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\ 
##   Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\ 
##   Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\ 
##   Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\ 
##   Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\ 
##   Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\ 
##   Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\ 
##   Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\ 
##   Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\ 
##   Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\ 
##   Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\ 
##   Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\ 
##    \hline
## \end{tabular}
## \caption{Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.} 
## \end{table}
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/effort-covariates-1}

}

\caption{Effort covariates measured during the drawing task -- amount of time spent drawing, amount of 'ink' used, and number of strokes used -- as function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs. Beijing), and the type of drawing task they completed. Error bars show bootstrapped 95 percent cofnidence intervals.}\label{fig:effort-covariates}
\end{figure}

\begin{verbatim}
## Warning: Removed 18 rows containing missing values (geom_point).
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/tracing-1}

}

\caption{Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered. Error bars represent bootstrapped 95 percent confidence intervals.}\label{fig:tracing}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible. We also gratefully acknowledge the San Jose Children's Discovery Museum for their collaboration. We are also thankful to all of the parents at XX and XX preschool whose children participated. We also thank the members of the Stanford Language and Cognition lab for their feedback. This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-barrett1976symbolism}{}%
Barrett, M., \& Light, P. (1976). Symbolism and intellectual realism in children's drawings. \emph{British Journal of Educational Psychology}, \emph{46}(2), 198--202.

\leavevmode\hypertarget{ref-bloom1998intention}{}%
Bloom, P., \& Markson, L. (1998). Intention and analogy in children's naming of pictorial representations. \emph{Psychological Science}, \emph{9}(3), 200--204.

\leavevmode\hypertarget{ref-bremmer1984prior}{}%
Bremner, J. G., \& Moore, S. (1984). Prior visual inspection and object naming: Two factors that enhance hidden feature inclusion in young children's drawings. \emph{British Journal of Developmental Psychology}, \emph{2}(4), 371--376.

\leavevmode\hypertarget{ref-cohn2012explaining}{}%
Cohn, N. (2012). Explaining ``i can't draw'': Parallels between the structure and development of language and drawing. \emph{Human Development}, \emph{55}(4), 167--192.

\leavevmode\hypertarget{ref-dekker2011dorsal}{}%
Dekker, T., Mareschal, D., Sereno, M. I., \& Johnson, M. H. (2011). Dorsal and ventral stream activation and object recognition performance in school-age children. \emph{NeuroImage}, \emph{57}(3), 659--670.

\leavevmode\hypertarget{ref-fan2020relating}{}%
Fan, J. E., Wammes, J. D., Gunn, J. B., Yamins, D. L., Norman, K. A., \& Turk-Browne, N. B. (2020). Relating visual production and recognition of objects in human visual cortex. \emph{Journal of Neuroscience}, \emph{40}(8), 1710--1721.

\leavevmode\hypertarget{ref-freeman1987current}{}%
Freeman, N. H. (1987). Current problems in the development of representational picture-production. \emph{Archives de Psychologie}.

\leavevmode\hypertarget{ref-fury1997children}{}%
Fury, G., Carlson, E. A., \& Sroufe, A. (1997). Children's representations of attachment relationships in family drawings. \emph{Child Development}, \emph{68}(6), 1154--1164.

\leavevmode\hypertarget{ref-hoffmann2018u}{}%
Hoffmann, D. L., Standish, C. D., Garcia-Diez, M., Pettitt, P. B., Milton, J., Zilhão, J., \ldots{} others. (2018). U-th dating of carbonate crusts reveals neandertal origin of iberian cave art. \emph{Science}, \emph{359}(6378), 912--915.

\leavevmode\hypertarget{ref-huntsinger2011cultural}{}%
Huntsinger, C. S., Jose, P. E., Krieg, D. B., \& Luo, Z. (2011). Cultural differences in chinese american and european american children's drawing skills over time. \emph{Early Childhood Research Quarterly}, \emph{26}(1), 134--145.

\leavevmode\hypertarget{ref-karmiloff1990constraints}{}%
Karmiloff-Smith, A. (1990). Constraints on representational change: Evidence from children's drawing. \emph{Cognition}, \emph{34}(1), 57--83.

\leavevmode\hypertarget{ref-kellogg1969analyzing}{}%
Kellogg, R. (1969). \emph{Analyzing children's art}. National Press Books Palo Alto, CA.

\leavevmode\hypertarget{ref-la2001children}{}%
La Voy, S. K., Pedersen, W. C., Reitz, J. M., Brauch, A. A., Luxenberg, T. M., \& Nofsinger, C. C. (2001). Children's drawings: A cross-cultural analysis from japan and the united states. \emph{School Psychology International}, \emph{22}(1), 53--63.

\leavevmode\hypertarget{ref-light1983effects}{}%
Light, P., \& Simmons, B. (1983). The effects of a communication task upon the representation of depth relationships in young children's drawings. \emph{Journal of Experimental Child Psychology}, \emph{35}(1), 81--92.

\leavevmode\hypertarget{ref-long2018drawings}{}%
Long, B., Fan, J., \& Frank, M. C. (2018). Drawings as a window into developmental changes in object representations. In \emph{Proceedings of the 40th annual meeting of the cognitive science society}.

\leavevmode\hypertarget{ref-minsky1972artificial}{}%
Minsky, M., \& Papert, S. (1972). \emph{Artificial intelligence progress report}. Cambridge, MA, USA: Massachusetts Institute of Technology.

\leavevmode\hypertarget{ref-natu2016development}{}%
Natu, V. S., Barnett, M. A., Hartley, J., Gomez, J., Stigliani, A., \& Grill-Spector, K. (2016). Development of neural sensitivity to face identity correlates with perceptual discriminability. \emph{Journal of Neuroscience}, \emph{36}(42), 10893--10907.

\leavevmode\hypertarget{ref-pailian2016visual}{}%
Pailian, H., Libertus, M. E., Feigenson, L., \& Halberda, J. (2016). Visual working memory capacity increases between ages 3 and 8 years, controlling for gains in attention, perception, and executive control. \emph{Attention, Perception, \& Psychophysics}, \emph{78}(6), 1556--1573.

\leavevmode\hypertarget{ref-piaget1929child}{}%
Piaget, J. (1929). The child's concept of the world. \emph{Londres, Routldge \& Kegan Paul}.

\leavevmode\hypertarget{ref-rehrig2018does}{}%
Rehrig, G., \& Stromswold, K. (2018). What does the dap: IQ measure?: Drawing comparisons between drawing performance and developmental assessments. \emph{The Journal of Genetic Psychology}, \emph{179}(1), 9--18.

\leavevmode\hypertarget{ref-sandkuhler2018}{}%
Sandkühler, R., Jud, C., Andermatt, S., \& Cattin, P. C. (2018). AirLab: Autograd image registration laboratory. \emph{arXiv Preprint arXiv:1806.09907}.

\leavevmode\hypertarget{ref-sitton1992drawing}{}%
Sitton, R., \& Light, P. (1992). Drawing to differentiate: Flexibility in young children's human figure drawings. \emph{British Journal of Developmental Psychology}, \emph{10}(1), 25--33.

\leavevmode\hypertarget{ref-willats2006making}{}%
Willats, J. (2006). \emph{Making sense of children's drawings}. Psychology Press.

\leavevmode\hypertarget{ref-winner1989can}{}%
Winner, E. (1989). How can chinese children draw so well? \emph{Journal of Aesthetic Education}, \emph{23}(1), 41--63.

\endgroup

\end{document}

### 2021-06-25 writing/Manuscript_June2021.Rmd
Latest draft of manuscript, all sections complete

@@
 ---
-title             : "Consistency and variability in the development of children's drawings between two countries"
+title             : "Consistency and variability in the development of children's drawings of object categories"
 shorttitle        : "Development of drawing"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
 
@@
  Childen's drawings of common object categories become dramatically more recognziable across development.
-What are the major factors that explain these developmental changes?
-Here, we examined the degree to which these changes in recognzibility vary across different drawing tasks (i.e.
+What are the major factors that explain this developmental change?
+Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.
 drawing from observation vs.
-from memory), geographical locations,  and children's tracing abilities.
-To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253) who were recruited near San Jose, USA and Beijing, China.
-Overall, we show broad consistency in these developmental trajectories across object categories, drawing tasks, and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children recruited near Beijing, China produced overal more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
+from memory), geographical locations (San Jose, US vs.
+Beijing, China),and with children's tracing abilities.
+To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
+Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
+In addition, we find that children recruited near Beijing, China producedmore recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
 Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.
@@
 library(xtable)
+library(viridis)
 ```
@@
 \textit{child}) than older children, who enrich their drawings with more diagnostic part [@sitton1992drawing] and relational [@light1983effects] information.
-Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict [@long2018drawings].
+Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel].
 
@@
 While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
-% how recognizable drawing is a complex skill that integrates many different aspects of cognition. 
-% For example, in order to "draw a [rabbit]", a child has to access their mental representation of a rabbit, choose the particular visual features needed to convey this visual concept, and then maintain this representation and goal in mind as they plan and produce a series of motor movements.
 Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].
@@
 While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making], most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities [@la2001children; @winner1989can; @huntsinger2011cultural].
-To assess the degree to which visuomotor development accounts for any observed variation, we also measured each child's shape tracing abilities.
+In addition, we assessed the degree to which visuomotor development accounts for developmental changes in drawing recognizability by measuring each child's shape tracing abilities.
 
@@
 
-Overall, we replicated prior work, showing strong and consistent developmental changes in the recognizability of children's drawings across development.
+<!-- Overall, we replicated prior work [@long2021parallel], showing strong and consistent developmental changes in the recognizability of children's drawings across development across both geographical sites.
+In addition, children of all ages produced equally recognizable drawings across both drawing tasks, suggesting that working memory limitations are not amoung the primary factors that influence the recognizability of children's drawings.
+Finally, we found that children recruited  -->
 
 # Methods
-
 ```{r plotting-params}
@@
   summarize(prop_correct = mean(correct_or_not)) %>%
-  left_join(d, by=c('unique_ids','category')) %>% # join with classification data 
+  left_join(model_classifications, by=c('unique_ids','category')) %>% # join with classification data 
   filter(!is.na(age))
@@
 265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
-We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e.
-20 4-year-olds, 20 5-year-olds, etc.).
-In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children.
-In the China based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.
+20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
+In the San Jose based sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
+Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of `r count_by_site$num_participants[1]` children.
+In the Beijing based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
-A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.
-
-Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification.
 On average, each child contributed `r mean(count_by_id$num_drawings)` to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).
+No additional demographic data was recorded about the participants.
+This protocol was approved by both the Institutional Review Board at [blinded] (43992, Development of Children's Drawing Abilities) and the Department of Psychology Ethics Committee at [blinded] in Beijing, China.
 
@@
 Before beginning, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
-So, please draw so that someone else could try what you were trying to draw.” Children then completed a series of tracing trials designed to both familiarize them with the tablet interface and to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure X).
-Children used their fingers to draw and had a maximum of 30 seconds to produce their tracings/drawings on all trials; strokes could not be deleted once drawn.
+So, please draw so that someone else could try what you were trying to draw.” A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
+The rest of the instructions were given via audio and video cues of native English/Mandarin speakers, respectively; all experimental code, videos, and stimuli are available on the public repository for this project.
+All children used their fingers to draw on an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case.
+All experimental code, videos, and data are available on the public repository for this project.
 
-The primary experimental manipulation was the type of cue used to prompt children to produce a drawing.
-Specifically, there were two cue types: (1) a verbal cue provided by the experimenter in a 5s video clip (2) an photo cue which remained on screen continuously while children drew.
-In the verbal-cue condition, children heard “What about a [x]?
-Can you draw a [x]?” In the image-cue condition, children heard audio of the same experimenter said,  “What about this [x]?
-Can you draw the [x] as it looks in the picture?”.
-Children completed 12 drawing trials, with six categories each randomly assigned to each condition and displayed in a random order.
-For photo-cues trials, one of three possible exemplars was randomly chosen (see Appendix, Figure X for all stimuli).
-Children completed drawing trials were blocked by these two conditions; the condition order counterbalanced across subjects in each age group.
-All instructions were translated into Mandarin by a native speaker; see Appendix, Table X for exact translations.
+Children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
+Children had maximum of 30 seconds to produce their tracings/drawings on all trials, and strokes could not be deleted once drawn; stroke-by-stroke data for each drawing was stored on a remote server.
+
+The primary experimental manipulation was the drawing task that children participated in; each child completed both tasks and the order of tasks was counterbalanced across participants.
+To elicit drawings from memory, children saw a short video clip where an experimenter said,  “What about a [cat]?
+Can you draw a [cat]?” (exact Mandarin translation has trouble in latex).
+To elicit drawings from observation, children heard audio of the same experimenter who said,  “What about this [cat]?
+Can you draw the [cat] as it looks in the picture?”  (Mandarin translation) while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
+This photograph was randomly sampled from one of three possible exemplars.
+Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
+Task examples are shown in Figure \ref{fig:example-tasks}.
+
+```{r example-tasks, fig.env = "figure", out.width="100%", fig.pos = "H", fig.cap = "Example trials from the tracing assessment and two drawing tasks."}
+knitr::include_graphics("figs/task_examples.png")
+```
+
+## Measuring effort covariates
+For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
+We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke — start time of first stroke).
+As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
+Finally, we estimated the proportion of the drawing canvas that was filled (e.g., 'ink used') by computing the proportion of each final drawing that were non-white pixels.
 
@@
 
-## Measuring effort covariates
-For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
-We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke — start time of first stroke).
-As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
-Finally, we estimated the proportion of the drawing canvas that was filled (e.g., 'ink used') by computing the proportion of each final drawing that were non-white pixels.
-
 ## Measuring drawing recognizability
@@
 ### Human recognition scores
-We assessed the recognizability of each drawing via a recognition experiment.
-Adult participants were recruited via Prolific for a 15 minute experiment and compensated at $14/hour.
-Participants were shown a random subset of the drawings and asked "What does this look like?" and then selected an answer from the twelve categories that children were prompted to draw.
-Participants were encouraged to guess.
+We assessed the recognizability of each drawing via an online recognition experiment.
+Adult participants based in the U.S.
+were recruited via Prolific for a 15 minute experiment,compensated at $14/hour, and recognized a random subset of around 140 drawings that were balanced with respect to age, category, and site.
+Each drawing was recognized by 10 participants.
+Participants were shown a were shown these drawings in a random order and asked "What does this look like?".
+Participants selected an answer from the twelve categories that children were prompted to draw and were were encouraged to guess.
+No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
+These binary recognition scores were then averaged across participants to yield a recognition score (e.g., recognized by 80% of participants) for each drawing.
 
 ### Automated recognition scores
-We used a combination of neural neural activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
+We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
 To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification.
@@
 No additional metadata about the age of the child who produced each sketch was provided to the decoder.
-This procedure was repeated for each drawing in the dataset, yielding both a binary a recognition score and the softmax probability assigned to each target class in the dataset.
+This procedure was repeated for each drawing in the dataset, yielding a binary a recognition score for each drawing.
 
 ## Statistical models
-Two mixed effects models were fit to assess the factors that influenced the recognizability of the drawings that children produced.
+```{r}
+human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)
+```
+
+To assess our main hypotheses, we fit linear mixed effects models to the human recogniton scores to assess the factors that influenced the recognizability of the drawings that children produced.
 A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
-Beijing), and drawing task (photo-cue vs.
-label-cue), and the three way interaction between these key variables.
-We initially attempted to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge following @Barr2013.
-We then ran a second model predicting the human recognition scores for each drawing with the same fixed and random effect structure.
+Beijing), and drawing task (drawing from perception vs.
+memory) and the three way interaction between these key variables.
+We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
+However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge.
 
@@
 Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with random intercepts for each participant.
+
+This anlaysis plan was pre-registered at https://osf.io/qymjr/; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel]; however, we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$estimate,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future researcs.
 
@@
 Overall, we found relative consistency in the developmental trajectory of children's drawings.
-Figure \ref{fig:main_results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in.
-We found no difference in the recognizability of children's drawings according to the task they were asked to do: drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" and they were simply asked "What about a rabbit?
-Can you draw a rabbit." While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do some adults when presented with canonical photographs of object categories [@photodrawcogsci] -- this was not the case.
-All model coefficients can be found in Table 1.
+Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in; All model coefficients can be found in Table 1.
+First, we found consistent and steady changes in the recognizability of children's drawings across this age range, replicating prior work with observational datasets collected at a free-standing kiosk [@long2021parallel].
+Critically, these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" and they were simply asked "What about a rabbit?
+Can you draw a rabbit." While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
 
-However, we did observe a main effect of geographical site: Children who were recruited outside of Beijing, China tended to produce more recognizable drawings than children who were recruited in San Jose, USA.
-In a second set of analyses, we aimed to understand the nature of this difference.
+However, we did observe a main effect of geographical site: Children who were recruited near Beijing, China tended to produce more recognizable drawings than children who were recruited near San Jose, USA.
+In a second set of analyses, we aimed to understand the nature of this difference in recognizability.
 We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
-To test this hypothesis, we thus included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into the same linear mixed-effects model.
-If these effort covariates explained the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
+We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
+Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site: effort covariates measured for each drawing; children tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children recruited outside Beijing tended to spend more time drawing overall.
+In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
+While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children recruited at both sites produced equally good shape tracings.
+
+Next, we included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model with the same fixed and random effects structure as used above.
+If these effort covariates accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
 Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
+In addition, the amount of time a child spent drawing  was a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
 
-```{r}
+Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not esaily explainable by effort covariates or tracing abilities, contra previous accounts.
+In a third set of analyses, we examined how the developmental trajectory of the recognizability of children's drawings may differ for different object categories.
+Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
+However, we had no strong hypotheses about how these trajectories might additionally vary with geographical locations.
+
+Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.
+For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
+In addition,  children recruited near Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children recruited near San Jose produced more recognizable drawings of bikes.
+Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
+
+```{r render-drawings, include=FALSE}
+# set.seed(123)
+# set.seed(234)
+# sample_drawings <- d %>%
+#   filter(prop_correct>.8) %>%
+#   filter(age_numeric==6) %>%
+#   group_by(category, condition, site) %>%
+#   sample_n(1)
+#   
+# sample_drawings <- sample_drawings %>%
+#   mutate(image_path = here::here('data/compiled/drawings/object_drawings', image_name_short)) %>%
+#   mutate(new_image_path = here::here('data/compiled/drawings/sample_drawings2', image_name_short)) 
+# 
+# dir.create(here::here('data/compiled/drawings/sample_drawings2'))
+# 
+# file.copy(sample_drawings$image_path, sample_drawings$new_image_path)
+
+```
+
+```{r check-drawing-time}
+# drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
+#                       (1 | unique_ids) +
+#                       (1 | category),
+#       data = d)
+# 
+# # frustratingly can't get anything with random slopes to converge!
+# drawing_time_out = summary(drawing_time)
+
+```
+
+```{r compile-main-results}
 cor_by_age_by_site_by_cond <- d %>%  
@@
   multi_boot_standard(col = "avg_cor")
+
+cor_by_age_by_site_by_cond_indiv <- d %>%  
+  group_by(unique_ids,category,condition,age_numeric, site) %>%
+  summarize(avg_cor = mean(prop_correct))
 ```
 
-```{r main-results, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs.
+```{r main-results, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=5, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs.
 Beijing), and the type of drawing task they completed.
+Individual data points represent drawings within each condition by an individual participant and are slightly jittered.
 Error bars show bootstrapped 95 percent cofnidence intervals."}
@@
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
+  geom_point(data = cor_by_age_by_site_by_cond_indiv, aes(x=age_numeric, y=avg_cor), position=position_jitterdodge(jitter.width = NULL,
+  jitter.height = .001,
+  dodge.width = 0.2,
+  seed = 123), alpha=.2) +
   theme_few(base_size = base_size_chosen) + 
-  labs(x='Age (in years)', y='Proportion recognized') +
-  ylim(0,1) + 
+  labs(x='Age (in years)', y='Proportion drawings recognized') +
+  ylim(-.01,1.1) + 
   geom_smooth(span=20, alpha=.1) +
@@
 
-```{r}
+```{r output-models-1}
 cleaned_names_full_model = c("Intercept","Task","Age","Site","Task*Age","Task*Site","Age*Site","Task*Age*Site")
@@
 
-```{r}
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+  \hline
+Intercept & 0.73 & 0.02 & 31.62 & 34.74 & 0.000 \\
+  Task & -0.02 & 0.02 & 17.29 & -0.87 & 0.397 \\
+  Age & 0.17 & 0.02 & 373.04 & 11.21 & 0.000 \\
+  Site & 0.05 & 0.02 & 385.12 & 2.39 & 0.017 \\
+  Task*Age & -0.02 & 0.01 & 2622.52 & -1.47 & 0.141 \\
+  Task*Site & -0.00 & 0.02 & 2631.48 & -0.20 & 0.842 \\
+  Age*Site & -0.00 & 0.02 & 388.66 & -0.06 & 0.951 \\
+  Task*Age*Site & 0.00 & 0.02 & 2639.46 & 0.21 & 0.834 \\
+   \hline
+\end{tabular}
+\caption{Table 1. Model coefficients from a linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}
+\end{table}
+
+```{r output-models-2}
 cleaned_names_full_model_with_effort = c("Intercept","Task","Age","Site","Est. tracing score","Avg. intensity", "Draw duration", "Number of strokes","Task*Age","Task&Site", "Age*Site","Task*Age*Site")
@@
 ```
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+  \hline
+Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\
+  Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\
+  Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\
+  Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\
+  Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\
+  Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\
+  Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\
+  Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\
+  Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\
+  Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
+  Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\
+  Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\
+   \hline
+\end{tabular}
+\caption{Table 2.
+Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
+\end{table}
 
@@
 
-```{r effort-covariates, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Effort covariates measured during the drawing task -- amount of time spent drawing, amount of 'ink' used, and number of strokes used -- as function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs.
+```{r effort-covariates, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=3, fig.cap = "Effort covariates measured during the drawing task -- amount of time spent drawing, amount of 'ink' used, and number of strokes used -- as function of the age of the child who completed each drawing, the geographical site they were tested at (San Jose vs.
 Beijing), and the type of drawing task they completed.
@@
 Error bars represent bootstrapped 95 percent confidence intervals."}
-ggplot(tracing_scores, aes(age_numeric,mean)) +
+ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
@@
   facet_grid(~site) +
-  ylim(0,4)
+  ylim(0,4) +
+  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
+```
+```{r example-drawings, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Randomly sampled, highly recognized drawings for each task, category, and geographical site made by 6-year-old children."}
+knitr::include_graphics("figs/example_drawings.png")
+```
+
+```{r}
+item_effects_not_spread <- d %>%
+  group_by(unique_ids,age_numeric,category, site) %>%
+  summarize(avg_sub_cor = mean(prop_correct)) %>%
+  group_by(age_numeric,category, site) %>%
+  multi_boot_standard(col = "avg_sub_cor")
+```
+
+```{r item-effects, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=8, fig.cap = "Developmental trajectory of drawing recognizability for each category and for each geographical site.
+Error bars represent 95 percent bootstrapped confidence intervals."}
+ggplot(item_effects_not_spread, aes(x=as.numeric(age_numeric), y=mean, color=site)) +
+  geom_point(alpha=.8) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2), alpha=.8) +
+  theme_few(base_size = base_size_chosen) + 
+  ylim(0,1) + 
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  ylab('Proportion drawings recognized') +
+  xlab('Age (in years)') +
+  geom_abline(color = 'grey', intercept=0) +
+  geom_smooth(span=20, alpha=.1) +
+  facet_wrap(~category) +
+  theme(legend.position = 'bottom') +
+  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
 ```
@@
 # Discussion
+Here, we examined the consistency and variability in the developmental trajectory of children's drawings across two different drawing tasks and geographical locations.
+First, we found that asking children to draw from memory ("Can you draw a [cat]?") vs.
+from perception ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
+While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bruner1984], this did not seem to change how recognizable their drawings were to outside observers.
+Overall, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
+
+Instead, we found that the recogniability of children's drawings differed considerably across  between geographical locations.
+Why might this be the case?
+Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would show perhaps exhibit greater dexterity in our tracing assessment task.
+However, children across the two sites showed equivalent tracing abilites -- despite the fact that children's individual tracing abilities were strong predictors of the recognizability of the drawings that they produced.
+A second possibility is that children recruited at preschools near Beijing were more engaged with the task than children recruited at museums near San Jose, USA: this more academic context could have created conditions in which children were incentivized to spend more effort on their drawings.
+However, our measures of children's effort (e.g., amount of time spent drawing) did not account for differences in recognizability across sites, providing evidence against this account.
+A final possibility is that children across these two sites may differ in the amount of practice they have drawing common object categories.
+If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories.
+In future work, surveys that assesses the amount of time that children spend drawing outside of these experimental contexts could address this hypothesis.
+
+A natural question for future concerns the relationship between the degree to which children across these different geographical sites show differences in their ability to recognize drawings of object categories.
+In a U.S.
+based population, prior work has found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings.
+Thus, if children in different contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and explicitely identifying the distinctive visual features of these categories.
+
+Furthermore, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Finer-grained measurements of these drawings could reveal interesting differences with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
+Furthermore, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the genera population.
+These developmental trajectories may thus vary in many ways that are not captured by the slice of experience captured by the present dataset.
+
+Overall, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development across two different tasks and geographical locations.
+[more here].
 

### 2021-06-25 writing/Manuscript_June2021.tex
Latest draft of manuscript, all sections complete

@@
 \hypersetup{
-  pdftitle={Consistency and variability in the development of children's drawings between two countries},
+  pdftitle={Consistency and variability in the development of children's drawings of object categories},
   pdflang={en-EN},
@@
 \textsuperscript{1} Stanford University\\\textsuperscript{2} Tsinghua University\\\textsuperscript{3} University of California, San Diego}
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+\authornote{
 
@@
 
-\title{Consistency and variability in the development of children's drawings between two countries}
+\title{Consistency and variability in the development of children's drawings of object categories}
 
@@
 Childen's drawings of common object categories become dramatically more recognziable across development.
-What are the major factors that explain these developmental changes?
-Here, we examined the degree to which these changes in recognzibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations, and children's tracing abilities.
-To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253) who were recruited near San Jose, USA and Beijing, China.
-Overall, we show broad consistency in these developmental trajectories across object categories, drawing tasks, and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children recruited near Beijing, China produced overal more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
+What are the major factors that explain this developmental change?
+Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China),and with children's tracing abilities.
+To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
+Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
+In addition, we find that children recruited near Beijing, China producedmore recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
 Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.
@@
 Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
-Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict (Long, Fan, \& Frank, 2018).
+Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018).
 
@@
 While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
-\% how recognizable drawing is a complex skill that integrates many different aspects of cognition.
-\% For example, in order to \enquote{draw a {[}rabbit{]}}, a child has to access their mental representation of a rabbit, choose the particular visual features needed to convey this visual concept, and then maintain this representation and goal in mind as they plan and produce a series of motor movements.
 Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations (Dekker, Mareschal, Sereno, \& Johnson, 2011; Long et al., 2018; Natu et al., 2016) as well as their increasing working memory capacity (Pailian, Libertus, Feigenson, \& Halberda, 2016).
@@
 While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006), most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
-To assess the degree to which visuomotor development accounts for any observed variation, we also measured each child's shape tracing abilities.
+In addition, we assessed the degree to which visuomotor development accounts for developmental changes in drawing recognizability by measuring each child's shape tracing abilities.
 
@@
 Finally, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at \url{https://osf.io/qymjr/}.
-
-Overall, we replicated prior work, showing strong and consistent developmental changes in the recognizability of children's drawings across development.
 
@@
 265 participants were recruited from the San Jose Children's Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
-We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.).
-In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children.
-In the China based sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
+In the San Jose based sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
+Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of 121 children.
+In the Beijing based sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
-A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.
-
-Blank drawings were excluded from analysis, and drawings were randomly undersampled to have an equal number of drawings for each leave-one-out-classification.
 On average, each child contributed 11.46 to analysis (min 6, max = 12).
+No additional demographic data was recorded about the participants.
+This protocol was approved by both the Institutional Review Board at {[}blinded{]} (43992, Development of Children's Drawing Abilities) and the Department of Psychology Ethics Committee at {[}blinded{]} in Beijing, China.
 
@@
 Before beginning, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
-So, please draw so that someone else could try what you were trying to draw.} Children then completed a series of tracing trials designed to both familiarize them with the tablet interface and to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure X).
-Children used their fingers to draw and had a maximum of 30 seconds to produce their tracings/drawings on all trials; strokes could not be deleted once drawn.
+So, please draw so that someone else could try what you were trying to draw.} A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
+The rest of the instructions were given via audio and video cues of native English/Mandarin speakers, respectively; all experimental code, videos, and stimuli are available on the public repository for this project.
+All children used their fingers to draw on an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case.
+All experimental code, videos, and data are available on the public repository for this project.
 
-The primary experimental manipulation was the type of cue used to prompt children to produce a drawing.
-Specifically, there were two cue types: (1) a verbal cue provided by the experimenter in a 5s video clip (2) an photo cue which remained on screen continuously while children drew.
-In the verbal-cue condition, children heard \enquote{What about a {[}x{]}?
-Can you draw a {[}x{]}?} In the image-cue condition, children heard audio of the same experimenter said, \enquote{What about this {[}x{]}?
-Can you draw the {[}x{]} as it looks in the picture?}.
-Children completed 12 drawing trials, with six categories each randomly assigned to each condition and displayed in a random order.
-For photo-cues trials, one of three possible exemplars was randomly chosen (see Appendix, Figure X for all stimuli).
-Children completed drawing trials were blocked by these two conditions; the condition order counterbalanced across subjects in each age group.
-All instructions were translated into Mandarin by a native speaker; see Appendix, Table X for exact translations.
+Children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
+Children had maximum of 30 seconds to produce their tracings/drawings on all trials, and strokes could not be deleted once drawn; stroke-by-stroke data for each drawing was stored on a remote server.
+
+The primary experimental manipulation was the drawing task that children participated in; each child completed both tasks and the order of tasks was counterbalanced across participants.
+To elicit drawings from memory, children saw a short video clip where an experimenter said, \enquote{What about a {[}cat{]}?
+Can you draw a {[}cat{]}?} (exact Mandarin translation has trouble in latex).
+To elicit drawings from observation, children heard audio of the same experimenter who said, \enquote{What about this {[}cat{]}?
+Can you draw the {[}cat{]} as it looks in the picture?} (Mandarin translation) while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
+This photograph was randomly sampled from one of three possible exemplars.
+Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
+Task examples are shown in Figure \ref{fig:example-tasks}.
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{figs/task_examples} \caption{Example trials from the tracing assessment and two drawing tasks.}\label{fig:example-tasks}
+\end{figure}
+
+\hypertarget{measuring-effort-covariates}{%
+\subsection{Measuring effort covariates}\label{measuring-effort-covariates}}
+
+For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
+We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke --- start time of first stroke).
+As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
+Finally, we estimated the proportion of the drawing canvas that was filled (e.g., \enquote{ink used}) by computing the proportion of each final drawing that were non-white pixels.
 
@@
 
-\hypertarget{measuring-effort-covariates}{%
-\subsection{Measuring effort covariates}\label{measuring-effort-covariates}}
-
-For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
-We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke --- start time of first stroke).
-As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
-Finally, we estimated the proportion of the drawing canvas that was filled (e.g., \enquote{ink used}) by computing the proportion of each final drawing that were non-white pixels.
-
 \hypertarget{measuring-drawing-recognizability}{%
@@
 
-We assessed the recognizability of each drawing via a recognition experiment.
-Adult participants were recruited via Prolific for a 15 minute experiment and compensated at \$14/hour.
-Participants were shown a random subset of the drawings and asked \enquote{What does this look like?} and then selected an answer from the twelve categories that children were prompted to draw.
-Participants were encouraged to guess.
+We assessed the recognizability of each drawing via an online recognition experiment.
+Adult participants based in the U.S.
+were recruited via Prolific for a 15 minute experiment,compensated at \$14/hour, and recognized a random subset of around 140 drawings that were balanced with respect to age, category, and site.
+Each drawing was recognized by 10 participants.
+Participants were shown a were shown these drawings in a random order and asked \enquote{What does this look like?}.
+Participants selected an answer from the twelve categories that children were prompted to draw and were were encouraged to guess.
+No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
+These binary recognition scores were then averaged across participants to yield a recognition score (e.g., recognized by 80\% of participants) for each drawing.
 
@@
 
-We used a combination of neural neural activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
+We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
 To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification.
@@
 No additional metadata about the age of the child who produced each sketch was provided to the decoder.
-This procedure was repeated for each drawing in the dataset, yielding both a binary a recognition score and the softmax probability assigned to each target class in the dataset.
+This procedure was repeated for each drawing in the dataset, yielding a binary a recognition score for each drawing.
 
@@
 
-Two mixed effects models were fit to assess the factors that influenced the recognizability of the drawings that children produced.
-A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (photo-cue vs.~label-cue), and the three way interaction between these key variables.
-We initially attempted to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge following ({\textbf{???}}).
-We then ran a second model predicting the human recognition scores for each drawing with the same fixed and random effect structure.
+To assess our main hypotheses, we fit linear mixed effects models to the human recogniton scores to assess the factors that influenced the recognizability of the drawings that children produced.
+A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (drawing from perception vs.~memory) and the three way interaction between these key variables.
+We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
+However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge.
 
@@
 
+This anlaysis plan was pre-registered at \url{https://osf.io/qymjr/}; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work (Long et al., 2021); however, we found that these automated recognition scores were only modestly correlated with human recognition scores (\(r\) = 0.40, \(t\) = 0.40, p \textless{} .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future researcs.
+
 \hypertarget{results}{%
@@
 Overall, we found relative consistency in the developmental trajectory of children's drawings.
-Figure \ref{fig:main_results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in.
-We found no difference in the recognizability of children's drawings according to the task they were asked to do: drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} and they were simply asked \enquote{What about a rabbit?
-Can you draw a rabbit.} While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do some adults when presented with canonical photographs of object categories ({\textbf{???}}) -- this was not the case.
-All model coefficients can be found in Table 1.
+Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in; All model coefficients can be found in Table 1.
+First, we found consistent and steady changes in the recognizability of children's drawings across this age range, replicating prior work with observational datasets collected at a free-standing kiosk (Long et al., 2021).
+Critically, these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} and they were simply asked \enquote{What about a rabbit?
+Can you draw a rabbit.} While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do adults when presented with canonical photographs of object categories (Yang \& Fan, 2021) -- this was not the case.
 
-However, we did observe a main effect of geographical site: Children who were recruited outside of Beijing, China tended to produce more recognizable drawings than children who were recruited in San Jose, USA.
-In a second set of analyses, we aimed to understand the nature of this difference.
+However, we did observe a main effect of geographical site: Children who were recruited near Beijing, China tended to produce more recognizable drawings than children who were recruited near San Jose, USA.
+In a second set of analyses, we aimed to understand the nature of this difference in recognizability.
 We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
-To test this hypothesis, we thus included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into the same linear mixed-effects model.
-If these effort covariates explained the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
+We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
+Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site: effort covariates measured for each drawing; children tended to spend more time drawing when asked to draw \enquote{the {[}rabbit{]} as it looks in the picture}, and children recruited outside Beijing tended to spend more time drawing overall.
+In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
+While children's tracing abilities increased steadily with age, as in prior work (Long et al., 2021), children recruited at both sites produced equally good shape tracings.
+
+Next, we included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model with the same fixed and random effects structure as used above.
+If these effort covariates accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
 Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
+In addition, the amount of time a child spent drawing was a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
+
+Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not esaily explainable by effort covariates or tracing abilities, contra previous accounts.
+In a third set of analyses, we examined how the developmental trajectory of the recognizability of children's drawings may differ for different object categories.
+Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
+However, we had no strong hypotheses about how these trajectories might additionally vary with geographical locations.
+
+Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.
+For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
+In addition, children recruited near Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children recruited near San Jose produced more recognizable drawings of bikes.
+Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
+
+\begin{verbatim}
+## Warning: Removed 690 rows containing missing values (geom_point).
+\end{verbatim}
 
@@
 Beijing), and the type of drawing task they completed.
+Individual data points represent drawings within each condition by an individual participant and are slightly jittered.
 Error bars show bootstrapped 95 percent cofnidence intervals.}\label{fig:main-results}
@@
 
-\begin{verbatim}
-## % latex table generated in R 3.6.1 by xtable 1.8-4 package
-## % Wed Jun 23 21:21:29 2021
-## \begin{table}[ht]
-## \centering
-## \begin{tabular}{rrrrrr}
-##   \hline
-##  & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
-##   \hline
-## Intercept & 0.73 & 0.02 & 31.62 & 34.74 & 0.000 \\ 
-##   Task & -0.02 & 0.02 & 17.29 & -0.87 & 0.397 \\ 
-##   Age & 0.17 & 0.02 & 373.04 & 11.21 & 0.000 \\ 
-##   Site & 0.05 & 0.02 & 385.12 & 2.39 & 0.017 \\ 
-##   Task*Age & -0.02 & 0.01 & 2622.52 & -1.47 & 0.141 \\ 
-##   Task*Site & -0.00 & 0.02 & 2631.48 & -0.20 & 0.842 \\ 
-##   Age*Site & -0.00 & 0.02 & 388.66 & -0.06 & 0.951 \\ 
-##   Task*Age*Site & 0.00 & 0.02 & 2639.46 & 0.21 & 0.834 \\ 
-##    \hline
-## \end{tabular}
-## \caption{Model coefficients from a  linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.} 
-## \end{table}
-\end{verbatim}
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+  \hline
+Intercept & 0.73 & 0.02 & 31.62 & 34.74 & 0.000 \\
+  Task & -0.02 & 0.02 & 17.29 & -0.87 & 0.397 \\
+  Age & 0.17 & 0.02 & 373.04 & 11.21 & 0.000 \\
+  Site & 0.05 & 0.02 & 385.12 & 2.39 & 0.017 \\
+  Task*Age & -0.02 & 0.01 & 2622.52 & -1.47 & 0.141 \\
+  Task*Site & -0.00 & 0.02 & 2631.48 & -0.20 & 0.842 \\
+  Age*Site & -0.00 & 0.02 & 388.66 & -0.06 & 0.951 \\
+  Task*Age*Site & 0.00 & 0.02 & 2639.46 & 0.21 & 0.834 \\
+   \hline
+\end{tabular}
+\caption{Table 1. Model coefficients from a linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}
+\end{table}
 
-\begin{verbatim}
-## % latex table generated in R 3.6.1 by xtable 1.8-4 package
-## % Wed Jun 23 21:21:29 2021
-## \begin{table}[ht]
-## \centering
-## \begin{tabular}{rrrrrr}
-##   \hline
-##  & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\ 
-##   \hline
-## Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\ 
-##   Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\ 
-##   Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\ 
-##   Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\ 
-##   Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\ 
-##   Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\ 
-##   Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\ 
-##   Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\ 
-##   Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\ 
-##   Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\ 
-##   Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\ 
-##   Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\ 
-##    \hline
-## \end{tabular}
-## \caption{Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
-## \end{table}
-\end{verbatim}
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+  \hline
+Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\
+  Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\
+  Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\
+  Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\
+  Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\
+  Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\
+  Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\
+  Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\
+  Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\
+  Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
+  Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\
+  Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\
+   \hline
+\end{tabular}
+\caption{Table 2.
+Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
+\end{table}
 
@@
 \begin{verbatim}
-## Warning: Removed 18 rows containing missing values (geom_point).
+## Warning: Removed 12 rows containing missing values (geom_point).
 \end{verbatim}
@@
 \end{figure}
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{figs/example_drawings} \caption{Randomly sampled, highly recognized drawings for each task, category, and geographical site made by 6-year-old children.}\label{fig:example-drawings}
+\end{figure}
+
+\begin{verbatim}
+## Warning: Removed 16 rows containing missing values (geom_smooth).
+\end{verbatim}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/item-effects-1}
+
+}
+
+\caption{Developmental trajectory of drawing recognizability for each category and for each geographical site.
+Error bars represent 95 percent bootstrapped confidence intervals.}\label{fig:item-effects}
+\end{figure}
 
@@
 \section{Discussion}\label{discussion}}
+
+Here, we examined the consistency and variability in the devleopmental trajectory of children's drawings across two different drawing tasks and geographical locations. We
 
@@
 
+\leavevmode\hypertarget{ref-long2021parallel}{}%
+Long, B., Fan, J., Chai, Z., \& Frank, M. C. (2021). Parallel developmental changes in children's drawing and recognition of visual concepts.
+
 \leavevmode\hypertarget{ref-long2018drawings}{}%
@@
 
+\leavevmode\hypertarget{ref-yang2021visual}{}%
+Yang, J., \& Fan, J. E. (2021). Visual communication of object concepts at different levels of abstraction. \emph{arXiv Preprint arXiv:2106.02775}.
+
 \endgroup

### 2021-06-25 writing/Manuscript_June2021.Rmd
latest edits

@@
 We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
-To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification.
+To encode the high-level visual features of each sketch, we used the VGG-19 architecture [@simonyan2014very] a deep convolutional neural network pre-trained on Imagenet classification.
 We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6).
@@
 
-This anlaysis plan was pre-registered at https://osf.io/qymjr/; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel]; however, we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$estimate,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
+This analysis plan was pre-registered at https://osf.io/qymjr/; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel]; however, we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
 To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future researcs.
@@
 from perception ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
-While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bruner1984], this did not seem to change how recognizable their drawings were to outside observers.
+While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
 Overall, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.

### 2021-06-26 writing/Manuscript_June2021.Rmd
discussion edits

@@
 While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
-Overall, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
+Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
 
-Instead, we found that the recogniability of children's drawings differed considerably across  between geographical locations.
-Why might this be the case?
-Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would show perhaps exhibit greater dexterity in our tracing assessment task.
-However, children across the two sites showed equivalent tracing abilites -- despite the fact that children's individual tracing abilities were strong predictors of the recognizability of the drawings that they produced.
-A second possibility is that children recruited at preschools near Beijing were more engaged with the task than children recruited at museums near San Jose, USA: this more academic context could have created conditions in which children were incentivized to spend more effort on their drawings.
-However, our measures of children's effort (e.g., amount of time spent drawing) did not account for differences in recognizability across sites, providing evidence against this account.
-A final possibility is that children across these two sites may differ in the amount of practice they have drawing common object categories.
+Instead, we found that the recognizability of children's drawings differed between our two different geographical sites -- Beijing, China and San Jose, USA  Why might this be the case?
+Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recogizable their drawings were.
+However, children across the two sites showed equivalent tracing abilities -- despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
+Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the drawings they produce yet further suggests that it is far from the only factor that does so.
+
+A second possibility that recognizability may have differed across sites is that children recruited at preschools near Beijing were simply more engaged with the task than children recruited at museums near San Jose, USA.
+A more academic context could have created an environment in which children felt incentivized to spend more effort on their drawings.
+However, our measures of children's effort (e.g., amount of time spent drawing) did not account for differences in recognizability across sites.
+Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
+A final possibility is that children across these two sites could differ in the amount of practice they have drawing common object categories.
 If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories.
-In future work, surveys that assesses the amount of time that children spend drawing outside of these experimental contexts could address this hypothesis.
+In future work, surveys that assesses the amount of time that children at these two sites -- as well as many others -- spend drawing outside of these experimental contexts could address this hypothesis.
 
-A natural question for future concerns the relationship between the degree to which children across these different geographical sites show differences in their ability to recognize drawings of object categories.
+A natural question for future work concerns the relationship between the degree to which children across different geographical sites might also show differences in their ability to recognize drawings of object categories.
 In a U.S.
-based population, prior work has found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings.
-Thus, if children in different contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and explicitely identifying the distinctive visual features of these categories.
+based population, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
+Thus, if children in different environmentsand contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
 
-Furthermore, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
-Finer-grained measurements of these drawings could reveal interesting differences with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
-Furthermore, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the genera population.
-These developmental trajectories may thus vary in many ways that are not captured by the slice of experience captured by the present dataset.
+However, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Finer-grained measurements of these drawings could reveal differences with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
+We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
 
-Overall, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development across two different tasks and geographical locations.
-[more here].
+More broadly, however, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the genera population.
+Many children within the same country or area code may differ in the very same ways children's drawings differ in this dataset.
+At the same time, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the slice of experience represented in the the present dataset.
+
+Nonetheless, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development  two different tasks and geographical locations.
+We propose that the systematic collection of digital drawings across many different populations, ages, and tasks has potential to shed light on the processes that result in the development of children's drawing abilities.
 

### 2021-06-26 writing/Manuscript_June2021.Rmd
smoothing edits

@@
 from memory), geographical locations (San Jose, US vs.
-Beijing, China),and with children's tracing abilities.
+Beijing, China), and with children's tracing abilities.
 To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
 Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children recruited near Beijing, China producedmore recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.
+In addition, we find that children recruited near Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control or working memory capacity.
 
@@
 ## Measuring Tracing Accuracy
-As in [@long2018drawings], we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
+As in @long2021parallel, we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
 We decomposed tracing accuracy into two components: a shape error component and a spatial error component.
@@
 
-We used the same tracing quality ratings to obtained in [@long2018drawings] to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale.
+We used the tracing quality ratings to obtained in @long2021parallel to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale.
 An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs.
 star) as predictors, with random intercepts for rater.
-This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes within session to yield a single tracing score for each participant.
+This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes to yield a single tracing score for each participant.
 
@@
 Adult participants based in the U.S.
-were recruited via Prolific for a 15 minute experiment,compensated at $14/hour, and recognized a random subset of around 140 drawings that were balanced with respect to age, category, and site.
+were recruited via Prolific for a 15 minute experiment, compensated at $14/hour, and asked to recognize a random subset of around 140 drawings that were balanced with respect to age, category, and site.
 Each drawing was recognized by 10 participants.
-Participants were shown a were shown these drawings in a random order and asked "What does this look like?".
-Participants selected an answer from the twelve categories that children were prompted to draw and were were encouraged to guess.
+Participants were shown these drawings in a random order and asked "What does this look like?".
+Participants selected an answer from the twelve categories that children were prompted to draw and were encouraged to guess.
 No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
-These binary recognition scores were then averaged across participants to yield a recognition score (e.g., recognized by 80% of participants) for each drawing.
+These binary recognition scores were then averaged across participants to yield a recognition score for each drawing.
+(e.g., recognized by 80% of participants).
 
@@
 
-To assess our main hypotheses, we fit linear mixed effects models to the human recogniton scores to assess the factors that influenced the recognizability of the drawings that children produced.
-A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
+To assess our main hypotheses, we fit linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
+A first linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
 Beijing), and drawing task (drawing from perception vs.
@@
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge.
+However, all models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge (see corresponding codebase).
 
 In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings.
-We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see above), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.
+We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see Measuring Tracing Abilities), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.
 percentage of non-white pixels), and the number of strokes children used.
@@
 
-This analysis plan was pre-registered at https://osf.io/qymjr/; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel]; however, we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
-To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future researcs.
+This analysis plan was pre-registered at https://osf.io/qymjr.
+While we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel],  we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a overall difference between the two drawing tasks that was not evident in the human recognition data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future research.
 
@@
 Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in; All model coefficients can be found in Table 1.
-First, we found consistent and steady changes in the recognizability of children's drawings across this age range, replicating prior work with observational datasets collected at a free-standing kiosk [@long2021parallel].
+First, we found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
 Critically, these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" and they were simply asked "What about a rabbit?
@@
 We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
-Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site: effort covariates measured for each drawing; children tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children recruited outside Beijing tended to spend more time drawing overall.
+Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
+Cchildren tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children recruited outside Beijing tended to spend more time drawing overall.
 In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
-While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children recruited at both sites produced equally good shape tracings.
+While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children recruited at both sites produced equally good tracings.
 
-Next, we included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model with the same fixed and random effects structure as used above.
-If these effort covariates accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
+We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model (described in Statistical Models).
+If the amount of effort spent or children's tracing abilities accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
 Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
-In addition, the amount of time a child spent drawing  was a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
+In addition, the amount of time a child spent drawing was in fact a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
 
-Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not esaily explainable by effort covariates or tracing abilities, contra previous accounts.
-In a third set of analyses, we examined how the developmental trajectory of the recognizability of children's drawings may differ for different object categories.
+Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
+In a third set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
 Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
@@
 Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
+These exploratory analyses thus reveal systematic differences between object categories and geographical site that do not seem easily attributable to differences in effort.
 
@@
 Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recogizable their drawings were.
-However, children across the two sites showed equivalent tracing abilities -- despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
+However, children across the two sites showed equivalent shape tracing abilities -- despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
 Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the drawings they produce yet further suggests that it is far from the only factor that does so.

### 2021-07-07 writing/Manuscript_June2021.Rmd
Latest edits to intro following MCF's comments

@@
 ---
-title             : "Consistency and variability in the development of children's drawings of object categories"
+title             : "Developmental consistency in children’s drawings of object categories across two countries"
 shorttitle        : "Development of drawing"
@@
 \textit{child}) than older children, who enrich their drawings with more diagnostic part [@sitton1992drawing] and relational [@light1983effects] information.
-Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel].
 
@@
 While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
+In our prior work, we found some evidence that these changes in children's drawings are accompanied by changes in children's ability to recognize drawings of object categories: in a correlational study, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel] and tended to rely more on these diagnostic visual features during recognition.
 Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].
 
-One idea is that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
 On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2020relating].
@@
 
-To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when asked to draw from memory ("Can you draw a [rabbit]?) and when asked to draw a canonical exemplar from observation ("Can you draw this [rabbit] as it looks in the picture?") across two different geographical sites (San Jose, USA and Beijing, China).
-To do so, we gathered digital drawings from a large sample of children 4-9 years of age in a controlled experimental setting.
-While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making], most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities [@la2001children; @winner1989can; @huntsinger2011cultural].
-In addition, we assessed the degree to which visuomotor development accounts for developmental changes in drawing recognizability by measuring each child's shape tracing abilities.
+To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when children were provided with a verbal cue ("Can you draw a [rabbit]?) versus when provided with a picture cue ("Can you draw this [rabbit] as it looks in the picture?").
+On verbal-cue trials, children thus must access their mental representation of a "rabbit" and choose the features necessary to convey that object's identity.
+Conversely, on picture-cue trials, children are explicitly asked to rely on the visual features provided in a canonical photograph of each object category.
 
-We had several predictions about the nature of the effects that we would observe.
-First, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, in keeping with accounts of naïve realism and contra a strong account of working memory limitations.
-Second, we predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
-Finally, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at https://osf.io/qymjr/.
+Second, we tested the generalizability of our findings across different populations by recruiting children from two different sites in different countries — San Jose, USA and Beijing, China.
+Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
+Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making].
+While some prior work has focused on differences in children's drawings across these two countries, most of this descriptive work has focused on differences in educational practices that may account for any observed differences [@la2001children; @winner1989can; @huntsinger2011cultural].
+Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
+
+Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
+While it is clear that visuomotor control influences how and what we can draw, little work has directly related meausres of visuomotor control to drawing outcomes.
+To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
+
+In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in two different countries using both picture cues and verbal cues.
+In doing so, we make three major contributions to our understanding of the development of children's drawings.
+First, we replicate our prior findings  [@long2021parallel] that the recognizability of children's drawings increases steadily throughout this age range (4-9 years).
+Second, we test the degree to which working memory constraints might account for these developmental changes.
+In keeping with accounts of naïve realism and contra a strong account of working memory limitations, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, Third, we test the generalizability of our findings across two different countries.
+We predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
+In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at https://osf.io/qymjr/.
 
@@
 ## Participants
-265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in [BLINDED] and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.
@@
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
-On average, each child contributed `r mean(count_by_id$num_drawings)` to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).
+On average, each child contributed `r mean(count_by_id$num_drawings)` drawings to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).
 No additional demographic data was recorded about the participants.
@@
 The primary experimental manipulation was the drawing task that children participated in; each child completed both tasks and the order of tasks was counterbalanced across participants.
-To elicit drawings from memory, children saw a short video clip where an experimenter said,  “What about a [cat]?
+Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
+on verbal-cue trials, children saw a short video clip where an experimenter said,  “What about a [cat]?
 Can you draw a [cat]?” (exact Mandarin translation has trouble in latex).
-To elicit drawings from observation, children heard audio of the same experimenter who said,  “What about this [cat]?
+On picture-cue trials, children heard audio of the same experimenter who said,  “What about this [cat]?
 Can you draw the [cat] as it looks in the picture?”  (Mandarin translation) while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
 This photograph was randomly sampled from one of three possible exemplars.
-Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
 Task examples are shown in Figure \ref{fig:example-tasks}.
@@
 # Results
+### Confirmatory Analyses
 Overall, we found relative consistency in the developmental trajectory of children's drawings.
@@
 
-However, we did observe a main effect of geographical site: Children who were recruited near Beijing, China tended to produce more recognizable drawings than children who were recruited near San Jose, USA.
+However, we did observe a main effect of geographical site: Children from Beijing, China tended to produce more recognizable drawings than children from San Jose, USA.
+Figure \ref{fig:main-results} suggests that this may be because children from Beijing, China tended to reach
 In a second set of analyses, we aimed to understand the nature of this difference in recognizability.
@@
 
+### Exploratory Analyses
 Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.

### 2021-07-07 writing/Manuscript_June2021.Rmd
revised .rmd and .pdf

@@
 Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children recruited near Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, USA.
+In addition, we find that children from Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
 Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control or working memory capacity.
@@
   mutate(site = fct_recode(site, "San Jose" = "CDM", "Beijing" = "THU"))%>%
-  mutate(condition = fct_recode(condition, "From perception" = "P", "From memory" = "S"))
+  mutate(condition = fct_recode(condition, "Picture cue" = "P", "Verbal cue" = "S"))
 
@@
 A first linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
-Beijing), and drawing task (drawing from perception vs.
-memory) and the three way interaction between these key variables.
+Beijing), and drawing task (verbal cue vs.
+picture cue) and the three way interaction between these key variables.
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
@@
 
+```{r}
+site_difference <- lmer(prop_correct ~ scale(age_numeric)^2*site +
+                      (1 | unique_ids) +
+                      (1 | category),
+      data = d)
+
+# frustratingly can't get anything with random slopes to converge!
+site_difference_out = summary(site_difference)
+
+```
+
 # Results
@@
 Can you draw a rabbit." While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
+However, we did observe a main effect of geographical site: overall, we found that children from Beijing, China tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
+A closer look directly comparing the recognizability of the drawings made at children at each site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
 
-However, we did observe a main effect of geographical site: Children from Beijing, China tended to produce more recognizable drawings than children from San Jose, USA.
-Figure \ref{fig:main-results} suggests that this may be because children from Beijing, China tended to reach
-In a second set of analyses, we aimed to understand the nature of this difference in recognizability.
+In a second set of analyses, we aimed to understand the nature of this difference in recognizability across sites.
 We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
@@
 Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
-Cchildren tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children recruited outside Beijing tended to spend more time drawing overall.
+Children tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children from Beijing tended to spend more time drawing overall.
 In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
-While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children recruited at both sites produced equally good tracings.
+While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.
 
@@
 For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
-In addition, children recruited near Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children recruited near San Jose produced more recognizable drawings of bikes.
+In addition, children from Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children from San Jose produced more recognizable drawings of bikes.
 Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
@@
 Error bars show bootstrapped 95 percent cofnidence intervals."}
-ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = condition)) +
+ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = site)) +
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
@@
   dodge.width = 0.2,
-  seed = 123), alpha=.2) +
+  seed = 123), alpha=.05) +
   theme_few(base_size = base_size_chosen) + 
@@
   geom_smooth(span=20, alpha=.1) +
-  scale_color_discrete(name="") +
+  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4) +
   theme(legend.position = 'bottom') +
   geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
-  facet_grid(~site)
+  facet_grid(~condition)
+```
+
+```{r site-difference, include=FALSE, eval=FALSE, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=4, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing and the geographical site they were tested at (San Jose vs.
+Beijing).
+Individual data points represent drawings within each condition by an individual participant and are slightly jittered.
+Error bars show bootstrapped 95 percent confidence intervals."}
+cor_by_age_by_site <- d %>%
+  group_by(unique_ids,category,age_numeric, site) %>%
+  summarize(avg_cor = mean(prop_correct)) %>%
+  group_by(age_numeric, site) %>%
+  multi_boot_standard(col = "avg_cor")
+
+cor_by_age_by_site_by_indiv <- d %>%
+  group_by(unique_ids,category,age_numeric, site) %>%
+  summarize(avg_cor = mean(prop_correct))
+
+ggplot(cor_by_age_by_site, aes(age_numeric,mean, col = site)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
+  geom_point(data = cor_by_age_by_site_by_indiv, aes(x=age_numeric, y=avg_cor), position=position_jitterdodge(jitter.width = NULL,
+  jitter.height = .001,
+  dodge.width = 0.2,
+  seed = 123), alpha=.05) +
+  theme_few(base_size = base_size_chosen) +
+  labs(x='Age (in years)', y='Proportion drawings recognized') +
+  ylim(-.01,1.1) +
+  geom_smooth(span=1, alpha=.1) +
+  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4) +
+  theme(legend.position = 'bottom') +
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey")
 
@@
 ```{r output-models-2}
-cleaned_names_full_model_with_effort = c("Intercept","Task","Age","Site","Est. tracing score","Avg. intensity", "Draw duration", "Number of strokes","Task*Age","Task&Site", "Age*Site","Task*Age*Site")
+cleaned_names_full_model_with_effort = c("Intercept","Task","Age","Site","Est. tracing score","Avg. intensity", "Draw duration", "Number of strokes","Task*Age","Task*Site", "Age*Site","Task*Age*Site")
 
@@
   Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\
-  Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
+  Task*Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
   Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\
@@
 Here, we examined the consistency and variability in the developmental trajectory of children's drawings across two different drawing tasks and geographical locations.
-First, we found that asking children to draw from memory ("Can you draw a [cat]?") vs.
-from perception ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
+First, we found that asking children from a verbal cue("Can you draw a [cat]?") vs.
+from a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
 While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
@@
 Instead, we found that the recognizability of children's drawings differed between our two different geographical sites -- Beijing, China and San Jose, USA  Why might this be the case?
-Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recogizable their drawings were.
+Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recognizable their drawings were.
 However, children across the two sites showed equivalent shape tracing abilities -- despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
@@
 Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-A final possibility is that children across these two sites could differ in the amount of practice they have drawing common object categories.
+
+While a long literature has sought to examine variation in cognitive abilities across cultural contexts, we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured.
+Drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differ in this dataset.
+For example,  children across could reasonably differ in the amount of practice they have drawing common object categories.
 If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories.
 In future work, surveys that assesses the amount of time that children at these two sites -- as well as many others -- spend drawing outside of these experimental contexts could address this hypothesis.
-
-A natural question for future work concerns the relationship between the degree to which children across different geographical sites might also show differences in their ability to recognize drawings of object categories.
-In a U.S.
-based population, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
-Thus, if children in different environmentsand contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
 
@@
 We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+A natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to recognize drawings of object categories.
+In a U.S.
+based population, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
+Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
 
-More broadly, however, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the genera population.
-Many children within the same country or area code may differ in the very same ways children's drawings differ in this dataset.
-At the same time, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Furthermore, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
 Thus, these developmental trajectories could thus vary in several ways that are not captured by the slice of experience represented in the the present dataset.

### 2021-07-08 writing/Manuscript_June2021.Rmd
Redo models as glmers on proportions, add some x-cultural refs to GD, render

@@
   group_by(unique_ids, category, image_name_short, site, age) %>% # group by each drawing of each category
-  summarize(prop_correct = mean(correct_or_not))  %>%
+  summarize(num_correct = sum(correct_or_not==TRUE), num_incorrect = sum(correct_or_not==FALSE), prop_correct = mean(correct_or_not))  %>%
    left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>%
@@
 
-To assess our main hypotheses, we fit linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
-A first linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
+To assess our main hypotheses, we fit generalized linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
+A first generalized linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
 Beijing), and drawing task (verbal cue vs.
@@
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, all models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge (see corresponding codebase).
+However, models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge -- which included random sloops for the two-way interaction between task and age on each category.
 
@@
 All predictors were scaled to have a mean of 0 and a standard deviation of 1.
-Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with random intercepts for each participant.
+Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random effects structure as the first model.
 
@@
 ```{r}
-full_model <- lmer(prop_correct ~ condition*scale(age_numeric)*site +
-                        (1 | unique_ids) +
-                        (condition | category),
-      data = d)
+full_model <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
+                        (condition | unique_ids) +
+                        (condition*scale(age_numeric) | category),
+      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
 
@@
 ```{r}
-full_model_with_effort <- lmer(prop_correct ~ condition*scale(age_numeric)*site +
+full_model_with_effort <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
                       scale(avg_tracing_score) +
@@
                       scale(num_strokes) + 
-                      (1 | unique_ids) +
-                      (condition | category),
-      data = d)
+                      (condition | unique_ids) +
+                      (condition*scale(age_numeric) | category),
+      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
 
@@
 ```{r}
-site_difference <- lmer(prop_correct ~ scale(age_numeric)^2*site +
+site_difference <- glmer(cbind(num_correct, num_incorrect) ~ poly(scale(age_numeric),2)*site +
                       (1 | unique_ids) +
                       (1 | category),
-      data = d)
+      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
 
-# frustratingly can't get anything with random slopes to converge!
 site_difference_out = summary(site_difference)
@@
 ### Confirmatory Analyses
-Overall, we found relative consistency in the developmental trajectory of children's drawings.
-Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in; All model coefficients can be found in Table 1.
-First, we found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
-Critically, these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" and they were simply asked "What about a rabbit?
-Can you draw a rabbit." While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
-However, we did observe a main effect of geographical site: overall, we found that children from Beijing, China tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
-A closer look directly comparing the recognizability of the drawings made at children at each site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
+Overall, we found relative consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in (all model coefficients can be found in Table 1).
+We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
+Further, we found that these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" versus they were simply asked "Can you draw a rabbit?".
+While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
+However, we did observe a main effect of geographical site: we found that children from Beijing, China overall tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
+A closer look comparing the recognizability of the drawings made at children at each age and site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
 
 In a second set of analyses, we aimed to understand the nature of this difference in recognizability across sites.
-We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
+We initially hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
 We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
 Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
-Children tended to spend more time drawing when asked to draw "the [rabbit] as it looks in the picture", and children from Beijing tended to spend more time drawing overall.
+Children tended to spend more time drawing provided with a picture cue and asked to draw "the [rabbit] as it looks in the picture", and children from Beijing tended to spend more time drawing overall.
 In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
@@
 
-We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model (described in Statistical Models).
+We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models).
 If the amount of effort spent or children's tracing abilities accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
@@
 In addition, the amount of time a child spent drawing was in fact a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
+Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
 
-Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
+### Exploratory Analyses
 In a third set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
@@
 
-### Exploratory Analyses
 Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.
@@
 
-# xtable(full_model_out$coefficients, digits=c(2,2,2,2,2,3),"Model coefficients from a  linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")
+# xtable(full_model_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")
 ```
@@
 \centering
-\begin{tabular}{rrrrrr}
+\begin{tabular}{rrrrr}
   \hline
- & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+ & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
   \hline
-Intercept & 0.73 & 0.02 & 31.62 & 34.74 & 0.000 \\
-  Task & -0.02 & 0.02 & 17.29 & -0.87 & 0.397 \\
-  Age & 0.17 & 0.02 & 373.04 & 11.21 & 0.000 \\
-  Site & 0.05 & 0.02 & 385.12 & 2.39 & 0.017 \\
-  Task*Age & -0.02 & 0.01 & 2622.52 & -1.47 & 0.141 \\
-  Task*Site & -0.00 & 0.02 & 2631.48 & -0.20 & 0.842 \\
-  Age*Site & -0.00 & 0.02 & 388.66 & -0.06 & 0.951 \\
-  Task*Age*Site & 0.00 & 0.02 & 2639.46 & 0.21 & 0.834 \\
+Intercept & 1.39 & 0.16 & 8.51 & 0.000 \\ 
+  Task & 0.02 & 0.26 & 0.08 & 0.936 \\ 
+  Age & 1.16 & 0.14 & 8.59 & 0.000 \\ 
+  Site & 0.60 & 0.16 & 3.71 & 0.000 \\ 
+  Task*Age & -0.14 & 0.19 & -0.73 & 0.467 \\ 
+  Task*Site & -0.19 & 0.16 & -1.17 & 0.244 \\ 
+  Age*Site & 0.15 & 0.16 & 0.91 & 0.361 \\ 
+  Task*Age*Site & 0.06 & 0.16 & 0.38 & 0.706 \\ 
    \hline
 \end{tabular}
-\caption{Table 1. Model coefficients from a linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}
+\caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.} 
 \end{table}
@@
 
-# xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,2,3),"Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
+# xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
 ```
@@
 \centering
-\begin{tabular}{rrrrrr}
+\begin{tabular}{rrrrr}
   \hline
- & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+ & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
   \hline
-Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\
-  Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\
-  Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\
-  Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\
-  Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\
-  Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\
-  Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\
-  Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\
-  Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\
-  Task*Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
-  Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\
-  Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\
+Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\ 
+  Task & -0.04 & 0.26 & -0.16 & 0.873 \\ 
+  Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 
+  Site & 0.80 & 0.16 & 5.04 & 0.000 \\ 
+  Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\ 
+  Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\ 
+  Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\ 
+  Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\ 
+  Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\ 
+  Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\ 
+  Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\ 
+  Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\ 
    \hline
 \end{tabular}
-\caption{Table 2.
-Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
+\caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
 \end{table}
@@
 # Discussion
-Here, we examined the consistency and variability in the developmental trajectory of children's drawings across two different drawing tasks and geographical locations.
-First, we found that asking children from a verbal cue("Can you draw a [cat]?") vs.
-from a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
+Here, we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
+Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel] In addition, we found that asking children to draw categories when provided witha verbal cue ("Can you draw a [cat]?") vs.a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
 While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
@@
 Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recognizable their drawings were.
-However, children across the two sites showed equivalent shape tracing abilities -- despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
+However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
 Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the drawings they produce yet further suggests that it is far from the only factor that does so.
@@
 
-While a long literature has sought to examine variation in cognitive abilities across cultural contexts, we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured.
-Drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differ in this dataset.
+These results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Indeed, some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail [@gernhardt2015cultural] and place a horizon line in systematically different locations when drawing scenes [@senzaki2014holistic].
+Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
+We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+
+However, while many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].
+Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021].
+For example, some work has suggested that the distinction between wheat vs.
+rice farming traditions explains substantial variation in cultural practices within China [@talhelm2014large].
+We are caution against a strong interpretation of the observed site differences, and we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
 For example, children across could reasonably differ in the amount of practice they have drawing common object categories.
 If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories.
-In future work, surveys that assesses the amount of time that children at these two sites -- as well as many others -- spend drawing outside of these experimental contexts could address this hypothesis.
+In future work, surveys that assesses the amount of time that children in many different communities spend drawing outside could address this hypothesis.
 
-However, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
-Finer-grained measurements of these drawings could reveal differences with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
-We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
-A natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to recognize drawings of object categories.
+Instead, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to recognize drawings of object categories.
 In a U.S.
-based population, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
+based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
 Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
 
-Furthermore, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+Finally, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
 For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the slice of experience represented in the the present dataset.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
 
-Nonetheless, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development  two different tasks and geographical locations.
+Nonetheless, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development, two different tasks, and geographical locations.
 We propose that the systematic collection of digital drawings across many different populations, ages, and tasks has potential to shed light on the processes that result in the development of children's drawing abilities.

### 2021-07-09 writing/Manuscript_June2021.Rmd
minor edits

@@
 library(viridis)
+
+knitr::opts_chunk$set(fig.crop = FALSE, 
+                      fig.path='figs/', echo=FALSE, warning = FALSE, 
+                      cache=FALSE, message = FALSE, sanitize = TRUE)
 ```
@@
 
-<!-- Overall, we replicated prior work [@long2021parallel], showing strong and consistent developmental changes in the recognizability of children's drawings across development across both geographical sites.
-In addition, children of all ages produced equally recognizable drawings across both drawing tasks, suggesting that working memory limitations are not amoung the primary factors that influence the recognizability of children's drawings.
-Finally, we found that children recruited  -->
-
 # Methods
@@
 
-\
 ```{r load-tracing}
@@
 #       data = d)
-# 
-# # frustratingly can't get anything with random slopes to converge!
 # drawing_time_out = summary(drawing_time)
-
 ```
@@
   facet_grid(~condition)
-```
-
-```{r site-difference, include=FALSE, eval=FALSE, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=4, fig.cap = "Proportion of drawings recognized as a function of the age of the child who completed each drawing and the geographical site they were tested at (San Jose vs.
-Beijing).
-Individual data points represent drawings within each condition by an individual participant and are slightly jittered.
-Error bars show bootstrapped 95 percent confidence intervals."}
-cor_by_age_by_site <- d %>%
-  group_by(unique_ids,category,age_numeric, site) %>%
-  summarize(avg_cor = mean(prop_correct)) %>%
-  group_by(age_numeric, site) %>%
-  multi_boot_standard(col = "avg_cor")
-
-cor_by_age_by_site_by_indiv <- d %>%
-  group_by(unique_ids,category,age_numeric, site) %>%
-  summarize(avg_cor = mean(prop_correct))
-
-ggplot(cor_by_age_by_site, aes(age_numeric,mean, col = site)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
-  geom_point(data = cor_by_age_by_site_by_indiv, aes(x=age_numeric, y=avg_cor), position=position_jitterdodge(jitter.width = NULL,
-  jitter.height = .001,
-  dodge.width = 0.2,
-  seed = 123), alpha=.05) +
-  theme_few(base_size = base_size_chosen) +
-  labs(x='Age (in years)', y='Proportion drawings recognized') +
-  ylim(-.01,1.1) +
-  geom_smooth(span=1, alpha=.1) +
-  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4) +
-  theme(legend.position = 'bottom') +
-  geom_hline(yintercept = 1/12, linetype="dashed", color="grey")
-
 ```
@@
 
-```{r plot-effort}
+```{r plot-effort, include=FALSE}
 ## Make compiled plot of descriptives
@@
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.05, alpha=.5) +
+  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5) +
   theme_few(base_size = base_size_chosen) +
@@
   facet_grid(~site) +
-  ylim(0,4) +
+  ylim(-.1,4.1) +
   scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
 ```
+
 ```{r example-drawings, fig.env = "figure", out.width="100%", fig.pos = "H", fig.label="exampledetections", fig.cap = "Randomly sampled, highly recognized drawings for each task, category, and geographical site made by 6-year-old children."}
@@
 rice farming traditions explains substantial variation in cultural practices within China [@talhelm2014large].
-We are caution against a strong interpretation of the observed site differences, and we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
+We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
 For example, children across could reasonably differ in the amount of practice they have drawing common object categories.

### 2021-11-09 writing/Manuscript_June2021.Rmd
Updates to ms post MCF edits

@@
 ---
-title             : "Developmental consistency in children’s drawings of object categories across two countries"
+title             : "Developmental consistency in children’s drawings of object categories"
 shorttitle        : "Development of drawing"
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements [@freeman1987current; @rehrig2018does]. 
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
-In our prior work, we found some evidence that these changes in children's drawings are accompanied by changes in children's ability to recognize drawings of object categories: in a correlational study, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel] and tended to rely more on these diagnostic visual features during recognition.
-Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints — including how children represent different visual concepts and how well children are able to access these visual concepts when producing drawings.
 
+In our prior work, we found that evidence that changes in children's drawings partly reflect changes in children's visual representations of common object categories.
+In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel], even when accounting for differences across age in basic shape tracing abilities and the amount of effort children expended on individual drawings.
+Furthermore, older children tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal representations may drive parallel changes in hildren's production and recognition of drawings.
+Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving perceptual category representations [@natu2016development; @dekker2011dorsal].
+
+<!-- Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].
+-->
+
+However, this work leaves open the contribution of children's evolving memory: children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood [@pailian2016visual].
 Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
@@
 Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
-While it is clear that visuomotor control influences how and what we can draw, little work has directly related meausres of visuomotor control to drawing outcomes.
+While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes [[@long2021parallel].
 To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
@@
 ## Task Procedure
-Before beginning, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
+
+Children participated in a drawing game using their fingers to draw, completing 2 shape tracing trials and 12 object category drawing trials.
+Children drew using an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case, and had maximum of 30 seconds to produce their tracings and drawings.
+Strokes could not be deleted once drawn, and stroke-by-stroke data for each drawing was stored on a remote server.
+
+Before beginning the game, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
 So, please draw so that someone else could try what you were trying to draw.” A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
-The rest of the instructions were given via audio and video cues of native English/Mandarin speakers, respectively; all experimental code, videos, and stimuli are available on the public repository for this project.
-All children used their fingers to draw on an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case.
-All experimental code, videos, and data are available on the public repository for this project.
 
-Children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-Children had maximum of 30 seconds to produce their tracings/drawings on all trials, and strokes could not be deleted once drawn; stroke-by-stroke data for each drawing was stored on a remote server.
-
-The primary experimental manipulation was the drawing task that children participated in; each child completed both tasks and the order of tasks was counterbalanced across participants.
-Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
-on verbal-cue trials, children saw a short video clip where an experimenter said,  “What about a [cat]?
-Can you draw a [cat]?” (exact Mandarin translation has trouble in latex).
+After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
+The primary experimental manipulation was the drawing cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
+Children completed six trials with the same cue type (verbal or picture) before switching; cue order was counterbalanced across participants.
+On verbal cue trials, children saw a short video clip where an experimenter said,  “What about a [cat]?
+Can you draw a [cat]?”.
 On picture-cue trials, children heard audio of the same experimenter who said,  “What about this [cat]?
-Can you draw the [cat] as it looks in the picture?”  (Mandarin translation) while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
-This photograph was randomly sampled from one of three possible exemplars.
-Task examples are shown in Figure \ref{fig:example-tasks}.
+Can you draw the [cat] as it looks in the picture?”  while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
+This photograph was randomly sampled from one of three possible exemplar (see Appendix).
+All experimental code, videos, translations, and stimuli are available on the public repository for this project.
 
@@
 Shape error reflects how closely the participant’s tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant’s tracing matched the target shape.
-
-To compute these error components, we applied an image registration algorithm, AirLab [@sandkuhler2018], to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, $T$, and the target shape, $S$: $Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}$, where $N$ is the number of pixels in both images.
-The shape error was defined by the final correlation distance between the aligned tracing and the target shape.
-The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively.
-In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).
-
-We used the tracing quality ratings to obtained in @long2021parallel to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale.
-An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs.
-star) as predictors, with random intercepts for rater.
-This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes to yield a single tracing score for each participant.
+See Appendix for details on how these error components were computed and translated into a tracing score.
 
@@
 ## Make compiled plot of descriptives
-base_size_chosen=14 # size of text in plots
+base_size_chosen=12 # size of text in plots
 smooth_alpha=.2
@@
   labs(x='Age', y='Draw duration (s)') +
-  theme(legend.position = "none") + 
+  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
+  theme(legend.position = "bottom") + 
   ylim(0,30) +
@@
   labs(x='Age', y='Ink used (mean intensity)') +
-  theme(legend.position = "none") + 
+  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
+  theme(legend.position = "bottom") + 
   ylim(.02,.08) +
@@
   labs(x='Age', y='Number of strokes') +
-  theme(legend.position = "none") +
+  theme(legend.position = "bottom") +
+  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
   ylim(0,15) +
@@
 
-# Discussion
+# General Discussion
 Here, we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
-Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel] In addition, we found that asking children to draw categories when provided witha verbal cue ("Can you draw a [cat]?") vs.a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
+Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel].
+We found that asking children to draw categories when provided with a verbal cue ("Can you draw a [cat]?") vs.
+a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
 While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
@@
 However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
-Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the drawings they produce yet further suggests that it is far from the only factor that does so.
-
-A second possibility that recognizability may have differed across sites is that children recruited at preschools near Beijing were simply more engaged with the task than children recruited at museums near San Jose, USA.
-A more academic context could have created an environment in which children felt incentivized to spend more effort on their drawings.
-However, our measures of children's effort (e.g., amount of time spent drawing) did not account for differences in recognizability across sites.
+A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularily incentivized to spend more effort on their drawings.
+Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
 Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-
-These results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
-Indeed, some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail [@gernhardt2015cultural] and place a horizon line in systematically different locations when drawing scenes [@senzaki2014holistic].
-Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
-We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence th recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
 
 However, while many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].
-Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021].
+Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021investigating].
 For example, some work has suggested that the distinction between wheat vs.
@@
 We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
-For example, children across could reasonably differ in the amount of practice they have drawing common object categories.
-If so, then children who spend more time drawing may simply have more practice communicating about the diagnostic features of different object categories.
-In future work, surveys that assesses the amount of time that children in many different communities spend drawing outside could address this hypothesis.
+For example, the children we recruited from Beijing vs.
+San Jose could differ widely in the amount of time they spending practicing drawing.
+If so, then children who spend more time drawing may simply have more experience communicating about the diagnostic features of different object categories.
 
-Instead, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to recognize drawings of object categories.
+Furthermore, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
+
+Indeed, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to produce or recognize drawings of object categories.
 In a U.S.
@@
 
-Finally, while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
-For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
+Of course, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail [@gernhardt2015cultural] and place a horizon line in systematically different locations when drawing scenes [@senzaki2014holistic].
+Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
+We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
 
-Nonetheless, these results take a first step towards characterizing the consistency and variability in the developmental trajectory of children's drawings across development, two different tasks, and geographical locations.
-We propose that the systematic collection of digital drawings across many different populations, ages, and tasks has potential to shed light on the processes that result in the development of children's drawing abilities.
+Nonetheless, these results take a first step towards characterizing the consistency in the developmental trajectory of children's drawings.
+We propose that the systematic collection of digital drawings from children with a wide variety of experiences will help uncover the myriad factors that drive the developmental changes in children's drawings -- and in turn help us understand how different cognitive systems coordinate to produce this complex behavior.
 
 # Acknowledgements  
-We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible.
+[BLINDED]
+<!-- We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible.
 We also gratefully acknowledge the San Jose Children's Discovery Museum for their collaboration.
@@
 This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.
+-->
+
+```{r appendix, include = FALSE}
+render_appendix("appendix.Rmd")
+```
 

### 2021-11-09 writing/Manuscript_June2021.tex
Updates to ms post MCF edits

@@
 \hypersetup{
-  pdftitle={Consistency and variability in the development of children's drawings of object categories},
+  pdftitle={Developmental consistency in children's drawings of object categories},
   pdflang={en-EN},
@@
 
-\title{Consistency and variability in the development of children's drawings of object categories}
+\title{Developmental consistency in children's drawings of object categories}
 
@@
 What are the major factors that explain this developmental change?
-Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China),and with children's tracing abilities.
+Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China), and with children's tracing abilities.
 To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
 Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children recruited near Beijing, China producedmore recognizable drawings but showed similar tracing abilities to childen recruited near San Jose, CA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control.
+In addition, we find that children from Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control or working memory capacity.
 }
@@
 Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
-Overall, younger children produce drawings of object categories that are less diagnostic of the categories they are trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018).
 
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements (Freeman, 1987; Rehrig \& Stromswold, 2018).
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints, such as how well children are able to access previously acquired semantic knowledge about each target concept and maintain this information in working memory during drawing production.
-Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations (Dekker, Mareschal, Sereno, \& Johnson, 2011; Long et al., 2018; Natu et al., 2016) as well as their increasing working memory capacity (Pailian, Libertus, Feigenson, \& Halberda, 2016).
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints --- including how children represent different visual concepts and how well children are able to access these visual concepts when producing drawings.
 
-One idea is that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
+In our prior work, we found that evidence that changes in children's drawings partly reflect changes in children's visual representations of common object categories.
+In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018), even when accounting for differences across age in basic shape tracing abilities and the amount of effort children expended on individual drawings.
+Furthermore, older children tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal representations may drive parallel changes in hildren's production and recognition of drawings.
+Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving perceptual category representations (Dekker, Mareschal, Sereno, \& Johnson, 2011; Natu et al., 2016).
+
+However, this work leaves open the contribution of children's evolving memory: children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood (Pailian, Libertus, Feigenson, \& Halberda, 2016).\\
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
 On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan et al., 2020).
@@
 
-To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when asked to draw from memory (\enquote{Can you draw a {[}rabbit{]}?) and when asked to draw a canonical exemplar from observation (}Can you draw this {[}rabbit{]} as it looks in the picture?") across two different geographical sites (San Jose, USA and Beijing, China).
-To do so, we gathered digital drawings from a large sample of children 4-9 years of age in a controlled experimental setting.
-While children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006), most empirical studies on children's drawings have been conducted exclusively on children from the United States -- or focused on differences in educational practices between communities (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
-In addition, we assessed the degree to which visuomotor development accounts for developmental changes in drawing recognizability by measuring each child's shape tracing abilities.
+To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when children were provided with a verbal cue (\enquote{Can you draw a {[}rabbit{]}?) versus when provided with a picture cue (}Can you draw this {[}rabbit{]} as it looks in the picture?\enquote{).
+On verbal-cue trials, children thus must access their mental representation of a}rabbit" and choose the features necessary to convey that object's identity.
+Conversely, on picture-cue trials, children are explicitly asked to rely on the visual features provided in a canonical photograph of each object category.
 
-We had several predictions about the nature of the effects that we would observe.
-First, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, in keeping with accounts of naïve realism and contra a strong account of working memory limitations.
-Second, we predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
-Finally, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at \url{https://osf.io/qymjr/}.
+Second, we tested the generalizability of our findings across different populations by recruiting children from two different sites in different countries --- San Jose, USA and Beijing, China.
+Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
+Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006).
+While some prior work has focused on differences in children's drawings across these two countries, most of this descriptive work has focused on differences in educational practices that may account for any observed differences (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
+Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
+
+Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
+While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes {[}(Long et al., 2021).
+To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
+
+In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in two different countries using both picture cues and verbal cues.
+In doing so, we make three major contributions to our understanding of the development of children's drawings.
+First, we replicate our prior findings (Long et al., 2021) that the recognizability of children's drawings increases steadily throughout this age range (4-9 years).
+Second, we test the degree to which working memory constraints might account for these developmental changes.
+In keeping with accounts of naïve realism and contra a strong account of working memory limitations, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, Third, we test the generalizability of our findings across two different countries.
+We predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
+In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at \url{https://osf.io/qymjr/}.
 
@@
 
-265 participants were recruited from the San Jose Children's Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in {[}BLINDED{]} and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
@@
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
-On average, each child contributed 11.46 to analysis (min 6, max = 12).
+On average, each child contributed 11.46 drawings to analysis (min 6, max = 12).
 No additional demographic data was recorded about the participants.
@@
 
-Before beginning, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
+Children participated in a drawing game using their fingers to draw, completing 2 shape tracing trials and 12 object category drawing trials.
+Children drew using an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case, and had maximum of 30 seconds to produce their tracings and drawings.
+Strokes could not be deleted once drawn, and stroke-by-stroke data for each drawing was stored on a remote server.
+
+Before beginning the game, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
 So, please draw so that someone else could try what you were trying to draw.} A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
-The rest of the instructions were given via audio and video cues of native English/Mandarin speakers, respectively; all experimental code, videos, and stimuli are available on the public repository for this project.
-All children used their fingers to draw on an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case.
-All experimental code, videos, and data are available on the public repository for this project.
 
-Children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-Children had maximum of 30 seconds to produce their tracings/drawings on all trials, and strokes could not be deleted once drawn; stroke-by-stroke data for each drawing was stored on a remote server.
-
-The primary experimental manipulation was the drawing task that children participated in; each child completed both tasks and the order of tasks was counterbalanced across participants.
-To elicit drawings from memory, children saw a short video clip where an experimenter said, \enquote{What about a {[}cat{]}?
-Can you draw a {[}cat{]}?} (exact Mandarin translation has trouble in latex).
-To elicit drawings from observation, children heard audio of the same experimenter who said, \enquote{What about this {[}cat{]}?
-Can you draw the {[}cat{]} as it looks in the picture?} (Mandarin translation) while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
-This photograph was randomly sampled from one of three possible exemplars.
-Overall, each child completed 2 tracing trials and 12 drawing trials, with six categories randomly assigned to each condition and displayed in a random order.
-Task examples are shown in Figure \ref{fig:example-tasks}.
+After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
+The primary experimental manipulation was the drawing cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
+Children completed six trials with the same cue type (verbal or picture) before switching; cue order was counterbalanced across participants.
+On verbal cue trials, children saw a short video clip where an experimenter said, \enquote{What about a {[}cat{]}?
+Can you draw a {[}cat{]}?}.
+On picture-cue trials, children heard audio of the same experimenter who said, \enquote{What about this {[}cat{]}?
+Can you draw the {[}cat{]} as it looks in the picture?} while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
+This photograph was randomly sampled from one of three possible exemplar (see Appendix).
+All experimental code, videos, translations, and stimuli are available on the public repository for this project.
 
@@
 
-As in (Long et al., 2018), we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
+As in Long et al.
+(2021), we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
 We decomposed tracing accuracy into two components: a shape error component and a spatial error component.
 Shape error reflects how closely the participant's tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant's tracing matched the target shape.
-
-To compute these error components, we applied an image registration algorithm, AirLab (Sandkühler, Jud, Andermatt, \& Cattin, 2018), to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, \(T\), and the target shape, \(S\): \(Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}\), where \(N\) is the number of pixels in both images.
-The shape error was defined by the final correlation distance between the aligned tracing and the target shape.
-The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively.
-In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).
-
-We used the same tracing quality ratings to obtained in (Long et al., 2018) to assign weights to each of their error terms; adult observers (\(N\)=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated \enquote{how well the tracing matches the target shape and is aligned to the position of the target shape} on a 5-point scale.
-An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs.~star) as predictors, with random intercepts for rater.
-This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes within session to yield a single tracing score for each participant.
+See Appendix for details on how these error components were computed and translated into a tracing score.
 
@@
 Adult participants based in the U.S.
-were recruited via Prolific for a 15 minute experiment,compensated at \$14/hour, and recognized a random subset of around 140 drawings that were balanced with respect to age, category, and site.
+were recruited via Prolific for a 15 minute experiment, compensated at \$14/hour, and asked to recognize a random subset of around 140 drawings that were balanced with respect to age, category, and site.
 Each drawing was recognized by 10 participants.
-Participants were shown a were shown these drawings in a random order and asked \enquote{What does this look like?}.
-Participants selected an answer from the twelve categories that children were prompted to draw and were were encouraged to guess.
+Participants were shown these drawings in a random order and asked \enquote{What does this look like?}.
+Participants selected an answer from the twelve categories that children were prompted to draw and were encouraged to guess.
 No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
-These binary recognition scores were then averaged across participants to yield a recognition score (e.g., recognized by 80\% of participants) for each drawing.
+These binary recognition scores were then averaged across participants to yield a recognition score for each drawing.
+(e.g., recognized by 80\% of participants).
 
@@
 We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
-To encode the high-level visual features of each sketch, we used the VGG-19 architecture \cite{simonyan2014very}, a deep convolutional neural network pre-trained on Imagenet classification.
+To encode the high-level visual features of each sketch, we used the VGG-19 architecture (Simonyan \& Zisserman, 2014) a deep convolutional neural network pre-trained on Imagenet classification.
 We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6).
@@
 
-To assess our main hypotheses, we fit linear mixed effects models to the human recogniton scores to assess the factors that influenced the recognizability of the drawings that children produced.
-A first linear mixed effect model was fit to the recognizability scores assigned to each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (drawing from perception vs.~memory) and the three way interaction between these key variables.
+To assess our main hypotheses, we fit generalized linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
+A first generalized linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (verbal cue vs.~picture cue) and the three way interaction between these key variables.
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, all models with this complicated random effects structure failed to converge, and the reported models the maximal random effects structure that did converge.
+However, models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge -- which included random sloops for the two-way interaction between task and age on each category.
 
 In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings.
-We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see above), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.~percentage of non-white pixels), and the number of strokes children used.
+We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see Measuring Tracing Abilities), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.~percentage of non-white pixels), and the number of strokes children used.
 All predictors were scaled to have a mean of 0 and a standard deviation of 1.
-Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with random intercepts for each participant.
+Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random effects structure as the first model.
 
-This anlaysis plan was pre-registered at \url{https://osf.io/qymjr/}; however, we had initially planned to use automated recognition scores as our main dependent variable, following prior work (Long et al., 2021); however, we found that these automated recognition scores were only modestly correlated with human recognition scores (\(r\) = 0.40, \(t\) = 0.40, p \textless{} .001); furthermore, descriptive plots of the automated recognition scores revealed a difference between the two drawing tasks that was not evident in the human data.
-To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future researcs.
+This analysis plan was pre-registered at \url{https://osf.io/qymjr}.
+While we had initially planned to use automated recognition scores as our main dependent variable, following prior work (Long et al., 2021), we found that these automated recognition scores were only modestly correlated with human recognition scores (\(r\) = 0.40, \(t\) = 22.78, p \textless{} .001); furthermore, descriptive plots of the automated recognition scores revealed a overall difference between the two drawing tasks that was not evident in the human recognition data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future research.
 
@@
 
-Overall, we found relative consistency in the developmental trajectory of children's drawings.
-Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in; All model coefficients can be found in Table 1.
-First, we found consistent and steady changes in the recognizability of children's drawings across this age range, replicating prior work with observational datasets collected at a free-standing kiosk (Long et al., 2021).
-Critically, these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} and they were simply asked \enquote{What about a rabbit?
-Can you draw a rabbit.} While we anticipated that older children might produce more recognizable drawings when drawing from observation -- as do adults when presented with canonical photographs of object categories (Yang \& Fan, 2021) -- this was not the case.
+\hypertarget{confirmatory-analyses}{%
+\subsubsection{Confirmatory Analyses}\label{confirmatory-analyses}}
 
-However, we did observe a main effect of geographical site: Children who were recruited near Beijing, China tended to produce more recognizable drawings than children who were recruited near San Jose, USA.
-In a second set of analyses, we aimed to understand the nature of this difference in recognizability.
-We hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
+Overall, we found relative consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in (all model coefficients can be found in Table 1).
+We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk (Long et al., 2021).
+Further, we found that these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} versus they were simply asked \enquote{Can you draw a rabbit?}.
+While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories (Yang \& Fan, 2021) -- this was not the case.
+However, we did observe a main effect of geographical site: we found that children from Beijing, China overall tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
+A closer look comparing the recognizability of the drawings made at children at each age and site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
+
+In a second set of analyses, we aimed to understand the nature of this difference in recognizability across sites.
+We initially hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
 We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
-Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site: effort covariates measured for each drawing; children tended to spend more time drawing when asked to draw \enquote{the {[}rabbit{]} as it looks in the picture}, and children recruited outside Beijing tended to spend more time drawing overall.
+Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
+Children tended to spend more time drawing provided with a picture cue and asked to draw \enquote{the {[}rabbit{]} as it looks in the picture}, and children from Beijing tended to spend more time drawing overall.
 In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
-While children's tracing abilities increased steadily with age, as in prior work (Long et al., 2021), children recruited at both sites produced equally good shape tracings.
+While children's tracing abilities increased steadily with age, as in prior work (Long et al., 2021), children from both sites produced equally good tracings.
 
-Next, we included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second linear mixed-effects model with the same fixed and random effects structure as used above.
-If these effort covariates accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
+We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models).
+If the amount of effort spent or children's tracing abilities accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
 Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
-In addition, the amount of time a child spent drawing was a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
+In addition, the amount of time a child spent drawing was in fact a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
+Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
 
-Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not esaily explainable by effort covariates or tracing abilities, contra previous accounts.
-In a third set of analyses, we examined how the developmental trajectory of the recognizability of children's drawings may differ for different object categories.
+\hypertarget{exploratory-analyses}{%
+\subsubsection{Exploratory Analyses}\label{exploratory-analyses}}
+
+In a third set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
 Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
@@
 For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
-In addition, children recruited near Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children recruited near San Jose produced more recognizable drawings of bikes.
+In addition, children from Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children from San Jose produced more recognizable drawings of bikes.
 Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
-
-\begin{verbatim}
-## Warning: Removed 690 rows containing missing values (geom_point).
-\end{verbatim}
+These exploratory analyses thus reveal systematic differences between object categories and geographical site that do not seem easily attributable to differences in effort.
 
@@
 
-{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/main-results-1}
+{\centering \includegraphics[width=\textwidth]{figs/main-results-1}
 
@@
 \centering
-\begin{tabular}{rrrrrr}
+\begin{tabular}{rrrrr}
   \hline
- & Estimate & Std. Error & df & t value & Pr($>$$|$t$|$) \\
+ & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
   \hline
-Intercept & 0.72 & 0.02 & 34.02 & 37.49 & 0.000 \\
-  Task & -0.02 & 0.02 & 17.55 & -1.19 & 0.249 \\
-  Age & 0.14 & 0.02 & 376.68 & 9.30 & 0.000 \\
-  Site & 0.07 & 0.02 & 459.46 & 3.58 & 0.000 \\
-  Est. tracing score & 0.06 & 0.01 & 249.21 & 5.71 & 0.000 \\
-  Avg. intensity & 0.01 & 0.01 & 2839.40 & 1.90 & 0.058 \\
-  Draw duration & -0.03 & 0.01 & 1692.69 & -3.42 & 0.001 \\
-  Number of strokes & 0.03 & 0.01 & 2655.21 & 4.67 & 0.000 \\
-  Task*Age & -0.02 & 0.01 & 2623.63 & -1.72 & 0.086 \\
-  Task\&Site & -0.01 & 0.02 & 2630.59 & -0.45 & 0.655 \\
-  Age*Site & -0.01 & 0.02 & 415.59 & -0.74 & 0.462 \\
-  Task*Age*Site & 0.00 & 0.02 & 2638.72 & 0.18 & 0.858 \\
+Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\ 
+  Task & -0.04 & 0.26 & -0.16 & 0.873 \\ 
+  Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 
+  Site & 0.80 & 0.16 & 5.04 & 0.000 \\ 
+  Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\ 
+  Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\ 
+  Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\ 
+  Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\ 
+  Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\ 
+  Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\ 
+  Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\ 
+  Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\ 
    \hline
 \end{tabular}
-\caption{Table 2.
-Model coefficients from a linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
+\caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
 \end{table}
@@
 
-{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/effort-covariates-1}
+{\centering \includegraphics[width=\textwidth]{figs/effort-covariates-1}
 
@@
 
-\begin{verbatim}
-## Warning: Removed 12 rows containing missing values (geom_point).
-\end{verbatim}
-
 \begin{figure}[H]
 
-{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/tracing-1}
+{\centering \includegraphics[width=\textwidth]{figs/tracing-1}
 
@@
 \end{figure}
+
 \begin{figure}[H]
@@
 
-\begin{verbatim}
-## Warning: Removed 16 rows containing missing values (geom_smooth).
-\end{verbatim}
-
 \begin{figure}[H]
 
-{\centering \includegraphics[width=\textwidth]{Manuscript_June2021_files/figure-latex/item-effects-1}
+{\centering \includegraphics[width=\textwidth]{figs/item-effects-1}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
-Here, we examined the consistency and variability in the devleopmental trajectory of children's drawings across two different drawing tasks and geographical locations. We
+Here, we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
+Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets (Long et al., 2021).
+We found that asking children to draw categories when provided with a verbal cue (\enquote{Can you draw a {[}cat{]}?}) vs.~a picture cue (\enquote{Can you draw this {[}cat{]} as it looks in the picture?}) had little effect on the recognizability of the drawings that children produced.
+While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work (Bremner \& Moore, 1984), this did not seem to change how recognizable their drawings were to outside observers.
+Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
+
+Instead, we found that the recognizability of children's drawings differed between our two different geographical sites -- Beijing, China and San Jose, USA Why might this be the case?
+Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recognizable their drawings were.
+However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
+A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularily incentivized to spend more effort on their drawings.
+Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
+Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
+Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence th recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
+
+However, while many have sought to examine variation across different cultural contexts in children's drawings (Winner, 1989) or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition (Kuwabara \& Smith, 2016) -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured (Amir \& McAuliffe, 2020).
+Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings (Carstensen, Cao, Gao, \& Frank, 2021).
+For example, some work has suggested that the distinction between wheat vs.~rice farming traditions explains substantial variation in cultural practices within China (Talhelm et al., 2014).
+We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code -- may differ in the very same ways children's drawings differed in this dataset.
+For example, the children we recruited from Beijing vs.~San Jose could differ widely in the amount of time they spending practicing drawing.
+If so, then children who spend more time drawing may simply have more experience communicating about the diagnostic features of different object categories.
+
+Furthermore, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
+
+Indeed, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to produce or recognize drawings of object categories.
+In a U.S.
+based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings (Long et al., 2021).
+Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
+
+Of course, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail (Gernhardt, Rübeling, \& Keller, 2015) and place a horizon line in systematically different locations when drawing scenes (Senzaki, Masuda, \& Nand, 2014).
+Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
+We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+
+Nonetheless, these results take a first step towards characterizing the consistency in the developmental trajectory of children's drawings.
+We propose that the systematic collection of digital drawings from children with a wide variety of experiences will help uncover the myriad factors that drive the developmental changes in children's drawings -- and in turn help us understand how different cognitive systems coordinate to produce this complex behavior.
 
@@
 
-We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible.
-We also gratefully acknowledge the San Jose Children's Discovery Museum for their collaboration.
-We are also thankful to all of the parents at XX and XX preschool whose children participated.
-We also thank the members of the Stanford Language and Cognition lab for their feedback.
-This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.
+{[}BLINDED{]}
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-amir2020cross}{}%
+Amir, D., \& McAuliffe, K. (2020). Cross-cultural, developmental psychology: Integrating approaches and key insights. \emph{Evolution and Human Behavior}, \emph{41}(5), 430--444.
+
 \leavevmode\hypertarget{ref-barrett1976symbolism}{}%
@@
 \emph{British Journal of Developmental Psychology}, \emph{2}(4), 371--376.
+
+\leavevmode\hypertarget{ref-carstensen2021investigating}{}%
+Carstensen, A., Cao, A., Gao, S., \& Frank, M.
+C.
+(2021).
+Investigating cross-cultural differences in reasoning, vision, and social cognition through replication.
+In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol.
+43).
 
@@
 
+\leavevmode\hypertarget{ref-gernhardt2015cultural}{}%
+Gernhardt, A., Rübeling, H., \& Keller, H.
+(2015).
+Cultural perspectives on children's tadpole drawings: At the interface between representation and production.
+\emph{Frontiers in Psychology}, \emph{6}, 812.
+
 \leavevmode\hypertarget{ref-hoffmann2018u}{}%
@@
 Kellogg, R. (1969). \emph{Analyzing children's art}. National Press Books Palo Alto, CA.
+
+\leavevmode\hypertarget{ref-kuwabara2016cultural}{}%
+Kuwabara, M., \& Smith, L. B. (2016). Cultural differences in visual object recognition in 3-year-old children. \emph{Journal of Experimental Child Psychology}, \emph{147}, 22--38.
 
@@
 
-\leavevmode\hypertarget{ref-sandkuhler2018}{}%
-Sandkühler, R., Jud, C., Andermatt, S., \& Cattin, P. C. (2018). AirLab: Autograd image registration laboratory. \emph{arXiv Preprint arXiv:1806.09907}.
+\leavevmode\hypertarget{ref-senzaki2014holistic}{}%
+Senzaki, S., Masuda, T., \& Nand, K.
+(2014).
+Holistic versus analytic expressions in artworks: Cross-cultural differences and similarities in drawings and collages by canadian and japanese school-age children.
+\emph{Journal of Cross-Cultural Psychology}, \emph{45}(8), 1297--1316.
+
+\leavevmode\hypertarget{ref-simonyan2014very}{}%
+Simonyan, K., \& Zisserman, A. (2014). Very deep convolutional networks for large-scale image recognition. \emph{arXiv Preprint arXiv:1409.1556}.
 
@@
 Sitton, R., \& Light, P. (1992). Drawing to differentiate: Flexibility in young children's human figure drawings. \emph{British Journal of Developmental Psychology}, \emph{10}(1), 25--33.
+
+\leavevmode\hypertarget{ref-talhelm2014large}{}%
+Talhelm, T., Zhang, X., Oishi, S., Shimin, C., Duan, D., Lan, X., \& Kitayama, S.
+(2014).
+Large-scale psychological differences within china explained by rice versus wheat agriculture.
+\emph{Science}, \emph{344}(6184), 603--608.
 

### 2021-11-09 writing/appendix.Rmd
Updates to ms post MCF edits

---
title: Appendix 
date: "`r Sys.Date()`"
output:
  pdf_document: default
---

```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
```

# Tracing Scores
To compute these error components, we applied an image registration algorithm, AirLab [@sandkuhler2018], to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, $T$, and the target shape, $S$: $Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}$, where $N$ is the number of pixels in both images.  The shape error was defined by the final correlation distance between the aligned tracing and the target shape. The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively. In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).

We used the tracing quality ratings to obtained in @long2021parallel to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale. An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs. star) as predictors, with random intercepts for rater. This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes to yield a single tracing score for each participant.

### 2021-11-09 writing/appendix.tex
Updates to ms post MCF edits

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\hypertarget{tracing-scores}{%
\section{Tracing Scores}\label{tracing-scores}}

To compute these error components, we applied an image registration
algorithm, AirLab (Sandkühler, Jud, Andermatt, \& Cattin, 2018), to
align each tracing to the target shape, yielding an affine
transformation matrix that minimized the pixel-wise correlation distance
between the aligned tracing, \(T\), and the target shape, \(S\):
\(Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}\),
where \(N\) is the number of pixels in both images. The shape error was
defined by the final correlation distance between the aligned tracing
and the target shape. The spatial error was defined by the magnitude of
three distinct error terms: location, orientation, and size error,
derived by decomposing the affine transformation matrix above into
translation, rotation, and scaling components, respectively. In sum,
this procedure yielded four error values for each tracing: one value
representing the shape error (i.e., the pixel-wise correlation distance)
and three values representing the spatial error (i.e., magnitude of
translation, rotation, scaling components).

We used the tracing quality ratings to obtained in Long, Fan, Chai, \&
Frank (2021) to assign weights to each of their error terms; adult
observers (\(N\)=70) rated 1325 tracings (i.e., 50-80 tracings per shape
per age) and evaluated ``how well the tracing matches the target shape
and is aligned to the position of the target shape'' on a 5-point scale.
An ordinal regression mixed-effects model to predict these 5-point
ratings, which contained correlation distance, translation, rotation,
scaling, and shape identity (square vs.~star) as predictors, with random
intercepts for rater. This model yielded parameter estimates that could
then be used to score each tracing in the dataset; we averaged scores
for both shapes to yield a single tracing score for each participant.

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-long2021parallel}{}%
Long, B., Fan, J., Chai, Z., \& Frank, M. C. (2021). Parallel
developmental changes in children's drawing and recognition of visual
concepts.

\leavevmode\hypertarget{ref-sandkuhler2018}{}%
Sandkühler, R., Jud, C., Andermatt, S., \& Cattin, P. C. (2018). AirLab:
Autograd image registration laboratory. \emph{arXiv Preprint
arXiv:1806.09907}.
\end{appendix}

### 2021-11-10 writing/Manuscript_June2021.Rmd
minor updates to manuscript throughout

@@
 library(viridis)
+```
+
+```{r}
 
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements [@freeman1987current; @rehrig2018does]. 
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints — including how children represent different visual concepts and how well children are able to access these visual concepts when producing drawings.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings — including how children represent a given visual concept and how well children are able to access these concepts when producing drawings.
 
-In our prior work, we found that evidence that changes in children's drawings partly reflect changes in children's visual representations of common object categories.
-In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict [@long2018drawings; @long2021parallel], even when accounting for differences across age in basic shape tracing abilities and the amount of effort children expended on individual drawings.
-Furthermore, older children tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal representations may drive parallel changes in hildren's production and recognition of drawings.
-Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving perceptual category representations [@natu2016development; @dekker2011dorsal].
+Prior work provides evidence that changes in children's drawings partly reflect changes in children's representations of visual concepts.
+In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they were trying to depict [@long2018drawings; @long2021parallel].
+This result held even when accounting for differences in basic shape tracing abilities and the amount of effort children expended on individual drawings.
+FUrthermore, older children also tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal visual representations drive parallel changes in children's production and recognition of drawings.
+Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving visual concepts [@natu2016development; @dekker2011dorsal].
 
-<!-- Thus, drawing is a skill that likely also relies on children's evolving perceptual category representations [@long2018drawings; @natu2016development; @dekker2011dorsal] as well as their increasing working memory capacity [@pailian2016visual].
--->
+However, this work leaves open the contribution of children's evolving memory.
+Children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood [@pailian2016visual].
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
+On this account, providing children with additional perceptual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2020relating].
 
-However, this work leaves open the contribution of children's evolving memory: children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood [@pailian2016visual].
-Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
-On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2020relating].
 However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.
@@
 Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories. 
-On this account, changes in children's drawings from memory across age may be largely due to other factors beyond changes in memory -- for example, changes in how children represent the diagnostic visual features of each category [@long2018drawings].
+On this account, working memory constraints are not a major factor that drives developmental changes in children's drawings.
 
@@
 
-Second, we tested the generalizability of our findings across different populations by recruiting children from two different sites in different countries — San Jose, USA and Beijing, China.
+To test the generality of our findings, we recruited children from two different sites in different countries — San Jose, USA and Beijing, China.
 Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
 Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making].
-While some prior work has focused on differences in children's drawings across these two countries, most of this descriptive work has focused on differences in educational practices that may account for any observed differences [@la2001children; @winner1989can; @huntsinger2011cultural].
+While some prior work has focused on differences in children's drawings across different countries, most of this descriptive work has focused on differences in educational practices that may manifest in children's drawings [@la2001children; @winner1989can; @huntsinger2011cultural].
 Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
@@
 Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
-While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes [[@long2021parallel].
+While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes [@long2021parallel].
 To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
 
-In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in two different countries using both picture cues and verbal cues.
+In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
 In doing so, we make three major contributions to our understanding of the development of children's drawings.
@@
 ## Participants
-265 participants were recruited from two local children's museum in [BLINDED] and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in [BLINDED] and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.
@@
 
-Before beginning the game, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
+Before beginning the drawing game, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
 So, please draw so that someone else could try what you were trying to draw.” A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
@@
 After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-The primary experimental manipulation was the drawing cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
-Children completed six trials with the same cue type (verbal or picture) before switching; cue order was counterbalanced across participants.
+The primary experimental manipulation was the type of cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
+Children completed six trials with the same cue type (verbal or picture cue) before switching cue types; this order was counterbalanced across participants.
 On verbal cue trials, children saw a short video clip where an experimenter said,  “What about a [cat]?
@@
 On picture-cue trials, children heard audio of the same experimenter who said,  “What about this [cat]?
-Can you draw the [cat] as it looks in the picture?”  while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
-This photograph was randomly sampled from one of three possible exemplar (see Appendix).
+Can you draw the [cat] as it looks in the picture?”  while seeing a canonical photograph of each category.
+This photograph was randomly sampled from one of three possible exemplars and remained on the screen for the duration of the drawing trial.
 All experimental code, videos, translations, and stimuli are available on the public repository for this project.
@@
 
-## Measuring effort covariates
+## Measuring drawing effort covariates
 For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
@@
 ## Measuring Tracing Accuracy
-As in @long2021parallel, we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
-We decomposed tracing accuracy into two components: a shape error component and a spatial error component.
+As in prior work [@long2021parallel], we used a semi-automated procedure for evaluating how accurately each child performed the tracing task that was validated against empirical judgments of tracing quality.
+In brief, we decomposed tracing accuracy into two components: a shape error component and a spatial error component.
 Shape error reflects how closely the participant’s tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant’s tracing matched the target shape.
-See Appendix for details on how these error components were computed and translated into a tracing score.
+These two error components were computed automatically for each tracing and used to yield a "tracing score" for each tracing that mirrors adult human judgements of tracing quality (see Appendix for details).
 
@@
 To encode the high-level visual features of each sketch, we used the VGG-19 architecture [@simonyan2014very] a deep convolutional neural network pre-trained on Imagenet classification.
-We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6).
-Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization across all filtered drawings in the dataset.
-Next, we used these features to train object category decoders.
-We then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
+We used model activations in the second-to-last layer of this network (FC6).
+Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.
+Next, we used these features to train object category decoders; we then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
 No additional metadata about the age of the child who produced each sketch was provided to the decoder.
@@
 We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
-Further, we found that these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" versus they were simply asked "Can you draw a rabbit?".
+Further, we found that these changes in recognizability did not depend on the drawing task children completed: Children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" versus they were simply asked "Can you draw a rabbit?".
 While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
@@
 We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
-Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
+Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
 Children tended to spend more time drawing provided with a picture cue and asked to draw "the [rabbit] as it looks in the picture", and children from Beijing tended to spend more time drawing overall.
@@
 However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
-A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularily incentivized to spend more effort on their drawings.
+A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularly incentivized to spend more effort on their drawings.
 Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
 Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence th recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
+Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
 
-However, while many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].
+While many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].
 Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021investigating].
 For example, some work has suggested that the distinction between wheat vs.
-rice farming traditions explains substantial variation in cultural practices within China [@talhelm2014large].
+rice farming traditions explains  variation in cultural practices within China [@talhelm2014large].
 We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
-For example, the children we recruited from Beijing vs.
+For example, a final possibility is that the children we recruited from Beijing vs.
 San Jose could differ widely in the amount of time they spending practicing drawing.
@@
 
-Furthermore, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
-For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
-
-Indeed, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to produce or recognize drawings of object categories.
-In a U.S.
-based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel].
-Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
-
-Of course, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Of course, these results of course do not preclude the possibility that children's drawings differed across these two drawing tasks or geographical sites in other interesting ways beyond their recognizability.
 Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail [@gernhardt2015cultural] and place a horizon line in systematically different locations when drawing scenes [@senzaki2014holistic].
@@
 We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+
+However, we think a natural question for future work concerns the relationship between the degree to which  difference kinds of developmental experience drawing or learning about visual concepts changes how children draw and recognize them.
+In a U.S.
+based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel], hinting at a relationship between production and recognition.
+Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
+
+Finally, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
 
@@
 
+\newpage
+
 ```{r appendix, include = FALSE}
@@
 ```
-
-\newpage
 
@@
 
-<div id="refs" custom-style="Bibliography"></div>
 \endgroup

### 2021-11-10 writing/Manuscript_June2021.tex
minor updates to manuscript throughout

@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements (Freeman, 1987; Rehrig \& Stromswold, 2018).
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints --- including how children represent different visual concepts and how well children are able to access these visual concepts when producing drawings.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings --- including how children represent a given visual concept and how well children are able to access these concepts when producing drawings.
 
-In our prior work, we found that evidence that changes in children's drawings partly reflect changes in children's visual representations of common object categories.
-In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they are trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018), even when accounting for differences across age in basic shape tracing abilities and the amount of effort children expended on individual drawings.
-Furthermore, older children tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal representations may drive parallel changes in hildren's production and recognition of drawings.
-Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving perceptual category representations (Dekker, Mareschal, Sereno, \& Johnson, 2011; Natu et al., 2016).
+Prior work provides evidence that changes in children's drawings partly reflect changes in children's representations of visual concepts.
+In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they were trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018).
+This result held even when accounting for differences in basic shape tracing abilities and the amount of effort children expended on individual drawings.
+FUrthermore, older children also tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal visual representations drive parallel changes in children's production and recognition of drawings.
+Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving visual concepts (Dekker, Mareschal, Sereno, \& Johnson, 2011; Natu et al., 2016).
 
-However, this work leaves open the contribution of children's evolving memory: children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood (Pailian, Libertus, Feigenson, \& Halberda, 2016).\\
+However, this work leaves open the contribution of children's evolving memory.
+Children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood (Pailian, Libertus, Feigenson, \& Halberda, 2016).
 Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
-On this account, providing children with additional perceptual information about different categories -- for example, canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan et al., 2020).
-However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.\\
+On this account, providing children with additional perceptual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan et al., 2020).
+
+However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.
 For example, when asked to draw from observation, younger children tend to include features that are not visible from their vantage point, yet are diagnostic of category membership (e.g., a handle on a \textit{mug}) (Barrett \& Light, 1976; Bremner \& Moore, 1984), and only omit these features later in development.
@@
 Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories.
-On this account, changes in children's drawings from memory across age may be largely due to other factors beyond changes in memory -- for example, changes in how children represent the diagnostic visual features of each category (Long et al., 2018).
+On this account, working memory constraints are not a major factor that drives developmental changes in children's drawings.
 
@@
 
-Second, we tested the generalizability of our findings across different populations by recruiting children from two different sites in different countries --- San Jose, USA and Beijing, China.
+To test the generality of our findings, we recruited children from two different sites in different countries --- San Jose, USA and Beijing, China.
 Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
 Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006).
-While some prior work has focused on differences in children's drawings across these two countries, most of this descriptive work has focused on differences in educational practices that may account for any observed differences (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
+While some prior work has focused on differences in children's drawings across different countries, most of this descriptive work has focused on differences in educational practices that may manifest in children's drawings (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
 Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
@@
 Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
-While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes {[}(Long et al., 2021).
+While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes (Long et al., 2021).
 To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
 
-In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in two different countries using both picture cues and verbal cues.
+In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
 In doing so, we make three major contributions to our understanding of the development of children's drawings.
@@
 
-265 participants were recruited from two local children's museum in {[}BLINDED{]} and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in {[}BLINDED{]} and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
@@
 
-Before beginning the game, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
+Before beginning the drawing game, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
 So, please draw so that someone else could try what you were trying to draw.} A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
@@
 After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-The primary experimental manipulation was the drawing cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
-Children completed six trials with the same cue type (verbal or picture) before switching; cue order was counterbalanced across participants.
+The primary experimental manipulation was the type of cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
+Children completed six trials with the same cue type (verbal or picture cue) before switching cue types; this order was counterbalanced across participants.
 On verbal cue trials, children saw a short video clip where an experimenter said, \enquote{What about a {[}cat{]}?
@@
 On picture-cue trials, children heard audio of the same experimenter who said, \enquote{What about this {[}cat{]}?
-Can you draw the {[}cat{]} as it looks in the picture?} while seeing a canonical photograph of each category; this photograph then remained on the screen for the duration of the drawing trial.
-This photograph was randomly sampled from one of three possible exemplar (see Appendix).
+Can you draw the {[}cat{]} as it looks in the picture?} while seeing a canonical photograph of each category.
+This photograph was randomly sampled from one of three possible exemplars and remained on the screen for the duration of the drawing trial.
 All experimental code, videos, translations, and stimuli are available on the public repository for this project.
@@
 
-\hypertarget{measuring-effort-covariates}{%
-\subsection{Measuring effort covariates}\label{measuring-effort-covariates}}
+\hypertarget{measuring-drawing-effort-covariates}{%
+\subsection{Measuring drawing effort covariates}\label{measuring-drawing-effort-covariates}}
 
@@
 
-As in Long et al.
-(2021), we used an automated procedure for evaluating how accurately participants performed the tracing task, validated against empirical judgments of tracing quality.
-We decomposed tracing accuracy into two components: a shape error component and a spatial error component.
+As in prior work (Long et al., 2021), we used a semi-automated procedure for evaluating how accurately each child performed the tracing task that was validated against empirical judgments of tracing quality.
+In brief, we decomposed tracing accuracy into two components: a shape error component and a spatial error component.
 Shape error reflects how closely the participant's tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant's tracing matched the target shape.
-See Appendix for details on how these error components were computed and translated into a tracing score.
+These two error components were computed automatically for each tracing and used to yield a \enquote{tracing score} for each tracing that mirrors adult human judgements of tracing quality (see Appendix for details).
 
@@
 To encode the high-level visual features of each sketch, we used the VGG-19 architecture (Simonyan \& Zisserman, 2014) a deep convolutional neural network pre-trained on Imagenet classification.
-We used model activations in the second-to-last layer of this network, which is the first fully connected layer of the network (FC6).
-Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization across all filtered drawings in the dataset.
-Next, we used these features to train object category decoders.
-We then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
+We used model activations in the second-to-last layer of this network (FC6).
+Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.
+Next, we used these features to train object category decoders; we then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
 No additional metadata about the age of the child who produced each sketch was provided to the decoder.
@@
 We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk (Long et al., 2021).
-Further, we found that these changes in recognizability did not depend on the drawing task children completed: children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} versus they were simply asked \enquote{Can you draw a rabbit?}.
+Further, we found that these changes in recognizability did not depend on the drawing task children completed: Children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} versus they were simply asked \enquote{Can you draw a rabbit?}.
 While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories (Yang \& Fan, 2021) -- this was not the case.
@@
 We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
-Figure \ref{fig:effort-covariates} shows three effort covariates - average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
+Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
 Children tended to spend more time drawing provided with a picture cue and asked to draw \enquote{the {[}rabbit{]} as it looks in the picture}, and children from Beijing tended to spend more time drawing overall.
@@
 However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
-A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularily incentivized to spend more effort on their drawings.
+A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularly incentivized to spend more effort on their drawings.
 Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
 Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence th recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
+Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
 
-However, while many have sought to examine variation across different cultural contexts in children's drawings (Winner, 1989) or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition (Kuwabara \& Smith, 2016) -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured (Amir \& McAuliffe, 2020).
+While many have sought to examine variation across different cultural contexts in children's drawings (Winner, 1989) or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition (Kuwabara \& Smith, 2016) -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured (Amir \& McAuliffe, 2020).
 Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings (Carstensen, Cao, Gao, \& Frank, 2021).
-For example, some work has suggested that the distinction between wheat vs.~rice farming traditions explains substantial variation in cultural practices within China (Talhelm et al., 2014).
+For example, some work has suggested that the distinction between wheat vs.~rice farming traditions explains variation in cultural practices within China (Talhelm et al., 2014).
 We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code -- may differ in the very same ways children's drawings differed in this dataset.
-For example, the children we recruited from Beijing vs.~San Jose could differ widely in the amount of time they spending practicing drawing.
+For example, a final possibility is that the children we recruited from Beijing vs.~San Jose could differ widely in the amount of time they spending practicing drawing.
 If so, then children who spend more time drawing may simply have more experience communicating about the diagnostic features of different object categories.
 
-Furthermore, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
-For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
-
-Indeed, a natural question for future work concerns the relationship between the degree to which children with difference kinds of experience might also show differences in their ability to produce or recognize drawings of object categories.
-In a U.S.
-based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings (Long et al., 2021).
-Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
-
-Of course, these results of course do not preclude the possibility that children's drawings differed across these two conditions or geographical sites in other interesting ways beyond their recognizability.
+Of course, these results of course do not preclude the possibility that children's drawings differed across these two drawing tasks or geographical sites in other interesting ways beyond their recognizability.
 Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail (Gernhardt, Rübeling, \& Keller, 2015) and place a horizon line in systematically different locations when drawing scenes (Senzaki, Masuda, \& Nand, 2014).
@@
 We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+
+However, we think a natural question for future work concerns the relationship between the degree to which difference kinds of developmental experience drawing or learning about visual concepts changes how children draw and recognize them.
+In a U.S.
+based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings (Long et al., 2021), hinting at a relationship between production and recognition.
+Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
+
+Finally, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
+For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
+Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
 
@@
 \setlength{\leftskip}{0.5in}
+
+\endgroup
 
@@
 
-\endgroup
-
 \end{document}

### 2021-11-10 writing/appendix.Rmd
minor updates to manuscript throughout

@@
 title: Appendix 
-date: "`r Sys.Date()`"
 output:
@@
 library(tidyverse)
-library(ggplot2)
-library(ggthemes)
 ```
 
-# Tracing Scores
+Tracing Scores
+
 To compute these error components, we applied an image registration algorithm, AirLab [@sandkuhler2018], to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, $T$, and the target shape, $S$: $Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}$, where $N$ is the number of pixels in both images.

### 2021-11-11 writing/Manuscript_June2021.Rmd
minor edits through intro

@@
 What are the major factors that explain this developmental change?
-Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.
+Here we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.
 drawing from observation vs.
@@
 To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
-Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children from Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control or working memory capacity.
+Overall, we show broad consistency in these developmental trajectories across both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
+In addition, we find that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in visuomotor control or working memory capacity.
 
@@
 
-As humans, we have many powerful tools to externalize what we know, including language and gesture.
-One tool that has been transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format. 
+As humans, we have many powerful tools to externalize what we perceive and know, including language and gesture.
+One tool that has been especially transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format. 
 Drawing is an important case study in graphical representation, being a technique that dates back 60,000 years [@hoffmann2018u], well before the emergence of symbolic writing systems, and is practiced in many cultures.
@@
 In modern times, drawings are produced prolifically by children from an early age. 
-Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities [@minsky1972artificial], and accordingly a long history of work has examined changes in children's drawings across development [@piaget1929child; @kellogg1969analyzing; @karmiloff1990constraints; @fury1997children].
-Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.
+Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities [@minsky1972artificial], and accordingly a long history of work has examined changes in how children draw objects across development [@piaget1929child; @kellogg1969analyzing; @karmiloff1990constraints; @fury1997children].
+Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.
 \textit{child}) than older children, who enrich their drawings with more diagnostic part [@sitton1992drawing] and relational [@light1983effects] information.
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements [@freeman1987current; @rehrig2018does]. 
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings — including how children represent a given visual concept and how well children are able to access these concepts when producing drawings.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings — including what children know about a given target object and how well children are able to access this conceptual knowledge when producing a drawing.
 
-Prior work provides evidence that changes in children's drawings partly reflect changes in children's representations of visual concepts.
+Prior work has provided evidence that changes in children's drawings partly reflect changes in children's mental representations of visual concepts.
 In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they were trying to depict [@long2018drawings; @long2021parallel].
 This result held even when accounting for differences in basic shape tracing abilities and the amount of effort children expended on individual drawings.
-FUrthermore, older children also tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal visual representations drive parallel changes in children's production and recognition of drawings.
-Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving visual concepts [@natu2016development; @dekker2011dorsal].
+Furthermore, older children also relied more on these same diagnostic visual features when recognizing other children's drawings.
+Together, these results suggest that developmental change in these underlying conceptual representations drive parallel changes in both children's production and recognition of drawings, and thus that change in how well children can produce recognizable drawings do not only reflect improvements in motor control [@natu2016development; @dekker2011dorsal].
 
-However, this work leaves open the contribution of children's evolving memory.
+However, this work leaves open the contribution of children's evolving abilities to retrieve and maintain relevant information in memory.
 Children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood [@pailian2016visual].
-Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
-On this account, providing children with additional perceptual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2020relating].
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant visual features of different categories: that is, when asked to "draw a [rabbit]", they may struggle to conjure up the relevant visual details and then hold in mind what rabbits tend to look like.
+On this account, providing children with additional visual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults [@fan2018common].
 
-However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.
+However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate information in their immediate perceptual experience [@luquet1927dessin].
 For example, when asked to draw from observation, younger children tend to include features that are not visible from their vantage point, yet are diagnostic of category membership (e.g., a handle on a \textit{mug}) [@bremmer1984prior; @barrett1976symbolism], and only omit these features later in development.
@@
 Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories. 
-On this account, working memory constraints are not a major factor that drives developmental changes in children's drawings.
+On this account, memory constraints are not a major factor that drives developmental changes in children's drawings.
 
@@
 
-To test the generality of our findings, we recruited children from two different sites in different countries — San Jose, USA and Beijing, China.
+To test the generality of our findings, we recruited children from two sites in different countries — San Jose, USA and Beijing, China.
 Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
 Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw [@cohn2012explaining; @willats2006making].
-While some prior work has focused on differences in children's drawings across different countries, most of this descriptive work has focused on differences in educational practices that may manifest in children's drawings [@la2001children; @winner1989can; @huntsinger2011cultural].
-Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
+While some prior work has focused on differences in children's drawings across different countries, most of this work has focused on differences in educational practices that are thought to manifest in children's drawings [@la2001children; @winner1989can; @huntsinger2011cultural].
+Leaving aside questions about potential causes of differences between sites, here we focus on measuring the degree to which drawing abilities vary between children at these two sites using the same experimental protocol.
 
 Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
-While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes [@long2021parallel].
-To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
+While it is uncontroversial that visuomotor control can constrain how and what we can draw, little work has directly related measures of visuomotor control to measures of drawing recognizability [@long2021parallel].
+To do so, we measured each child's visuomotor control via a shape tracing task and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
 
-In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
-In doing so, we make three major contributions to our understanding of the development of children's drawings.
+In sum, in the current study we collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
+In doing so, we make three key contributions to our understanding of the development of children's drawings.
 First, we replicate our prior findings  [@long2021parallel] that the recognizability of children's drawings increases steadily throughout this age range (4-9 years).
-Second, we test the degree to which working memory constraints might account for these developmental changes.
-In keeping with accounts of naïve realism and contra a strong account of working memory limitations, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, Third, we test the generalizability of our findings across two different countries.
+Second, we test the degree to which memory constraints might account for these developmental changes.
+In keeping with accounts of naïve realism and against a large role of limitations on memory, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings.
+Third, we test the generalizability of our findings across two sites in different countries.
 We predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
-In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at https://osf.io/qymjr/.
+In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at: https://osf.io/qymjr/.
 
@@
 # General Discussion
-Here, we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
+Here we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
 Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel].

### 2021-11-13 writing/Manuscript_June2021.Rmd
up to end of methods!

@@
 20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
-In the San Jose based sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
+In the San Jose sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
 Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of `r count_by_site$num_participants[1]` children.
-In the Beijing based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+In the Beijing sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
@@
 
-## Task Procedure
+## Stimuli and Task Procedure
 
-Children participated in a drawing game using their fingers to draw, completing 2 shape tracing trials and 12 object category drawing trials.
-Children drew using an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case, and had maximum of 30 seconds to produce their tracings and drawings.
-Strokes could not be deleted once drawn, and stroke-by-stroke data for each drawing was stored on a remote server.
-
-Before beginning the drawing game, a trained experimenter first told each child “After this game is over, someone is going to try to recognize what you were trying to draw.
-So, please draw so that someone else could try what you were trying to draw.” A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
-
-After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-The primary experimental manipulation was the type of cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
-Children completed six trials with the same cue type (verbal or picture cue) before switching cue types; this order was counterbalanced across participants.
-On verbal cue trials, children saw a short video clip where an experimenter said,  “What about a [cat]?
-Can you draw a [cat]?”.
-On picture-cue trials, children heard audio of the same experimenter who said,  “What about this [cat]?
-Can you draw the [cat] as it looks in the picture?”  while seeing a canonical photograph of each category.
-This photograph was randomly sampled from one of three possible exemplars and remained on the screen for the duration of the drawing trial.
+Children were seated in front of a touchscreen tablet (Ipad Pro 12.9") during each drawing session.
+At the beginning of the session, a trained experimenter first told each child, “After this game is over, someone is going to try to recognize what you were trying to draw.
+So, please draw so that someone else could guess what you were trying to draw.”
+A native English speaker gave these instructions to the San Jose sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing sample. 
+Following these instructions, children completed 2 shape-tracing trials, providing a baseline measure of visuomotor control in the absence of memory demands.
+All children first traced a square, then a more complex shape (see Figure \ref{fig:example-tasks}).
+After these tracing trials, children produced drawings of 12 familiar object categories (airplane, bike, bird, car, cat, chair, cup, hat, house, rabbit, tree, watch).
+Strokes could not be deleted once drawn, and children had to complete each trial within 30 seconds.
+Across trials, we manipulated the type of cue (verbal vs.
+picture) children received before producing each drawing (Fig.
+\ref{fig:example-tasks}), providing a measure of the impact of reminding children of what typical exemplars of each category looked like.
+Specifically, children first completed six trials with one cue type, then switched to the other cue type. 
+The order in which each cue type was used was counterbalanced across children.
+On verbal-cue trials, children viewed a short video clip in which an experimenter named the target category: “What about a [cat]? Can you draw a [cat]?”.  
+On picture-cue trials, children viewed a photograph of a typical exemplar of the target category while listening to an audio clip of the same experimenter who said, “What about this [cat]?
+Can you draw the [cat] as it looks in the picture?”
+The photograph remained on the screen for the duration of the drawing trial.
+There were three different exemplars of each category used in this study, one of which was randomly sampled on each picture-cue trial.
 All experimental code, videos, translations, and stimuli are available on the public repository for this project.
@@
 ## Measuring drawing effort covariates
-For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
-We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke — start time of first stroke).
-As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
-Finally, we estimated the proportion of the drawing canvas that was filled (e.g., 'ink used') by computing the proportion of each final drawing that were non-white pixels.
+We recorded both the final drawings and the location of each stroke in a digital format, allowing us to precisely measure several different variables that provided proxies for the amount of effort children invested in producing each drawing.
+Specifically, we measured: (1) the amount of time spent (i.e., end time of last stroke — start time of first stroke), (2) the number of individual strokes drawn, and (3) the amount of "ink" used (i.e., proportion of drawing canvas that was filled).
 
@@
 Shape error reflects how closely the participant’s tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant’s tracing matched the target shape.
-These two error components were computed automatically for each tracing and used to yield a "tracing score" for each tracing that mirrors adult human judgements of tracing quality (see Appendix for details).
+These two error components were computed automatically for each tracing and used to yield a "tracing score" for each tracing that mirrors adult human judgments of tracing quality (see Appendix for details).
 
@@
 ### Human recognition scores
-We assessed the recognizability of each drawing via an online recognition experiment.
+We measured the recognizability of each drawing via an online recognition experiment. 
 Adult participants based in the U.S.
-were recruited via Prolific for a 15 minute experiment, compensated at $14/hour, and asked to recognize a random subset of around 140 drawings that were balanced with respect to age, category, and site.
-Each drawing was recognized by 10 participants.
-Participants were shown these drawings in a random order and asked "What does this look like?".
-Participants selected an answer from the twelve categories that children were prompted to draw and were encouraged to guess.
-No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
-These binary recognition scores were then averaged across participants to yield a recognition score for each drawing.
-(e.g., recognized by 80% of participants).
+were recruited via Prolific for a 15-minute experiment, compensated at $14/hour, and asked to identify the category depicted in a random subset of approximately 140 drawings.
+Each subset of drawings was balanced with respect to age, category, and site, and each drawing was shown to 10 participants. 
+Participants were shown these drawings in a random sequence and asked "What does this look like?"
+Participants selected their responses from the set of 12 categories and were encouraged to provide their best guess if they were unsure. 
+No participants were excluded from analysis for missing the catch trial, which was included to verify that participants could accurately describe their goal in this task. 
+We then computed a recognition score for each drawing, reflecting the proportion of participants who correctly identified the target category.
 
 ### Automated recognition scores
-We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
-To encode the high-level visual features of each sketch, we used the VGG-19 architecture [@simonyan2014very] a deep convolutional neural network pre-trained on Imagenet classification.
-We used model activations in the second-to-last layer of this network (FC6).
-Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.
-Next, we used these features to train object category decoders; we then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
-No additional metadata about the age of the child who produced each sketch was provided to the decoder.
-This procedure was repeated for each drawing in the dataset, yielding a binary a recognition score for each drawing.
+We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol. 
+To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 [@simonyan2014very], a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch [@paszke2017automatic].
+We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6). 
+Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization. 
+Next, we used these features to train a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
+To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
+\textbf{jefan query: Here we describe the training data distribution, but not the test set? What kind of train/test splitting procedure did we use here (LOO? 80/20 CV?)}
+No additional metadata about the age of the child who produced each sketch was provided to the model. 
+This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing.
 
@@
 
-To assess our main hypotheses, we fit generalized linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
+To evaluate our main hypotheses, we fit generalized linear mixed-effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
 A first generalized linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.
 Beijing), and drawing task (verbal cue vs.
-picture cue) and the three way interaction between these key variables.
+picture cue) and the three-way interaction between these key variables.
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge -- which included random sloops for the two-way interaction between task and age on each category.
+However, models with this random-effects structure failed to converge, and the reported models use the maximal random effects structure that did converge, which included random slopes for the two-way interaction between task and age on each category.
 
-In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings.
-We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see Measuring Tracing Abilities), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.
-percentage of non-white pixels), and the number of strokes children used.
-All predictors were scaled to have a mean of 0 and a standard deviation of 1.
-Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random effects structure as the first model.
+In a secondary analysis, we investigated the degree to which any of the above effects were mediated by children's tracing abilities or the amount of effort that children expended while drawings. 
+We thus fit the same model above, with the addition of fixed-effect terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of "ink" used (i.e.
+percentage of non-white pixels in the drawn image), and the number of strokes.
+These additional predictors were first z-scored before being included in the model.
+Finally, we also assessed the degree to which tracing ability development differed across geographical sites, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random-effects structure as the first model.
 
 This analysis plan was pre-registered at https://osf.io/qymjr.
-While we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel],  we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed a overall difference between the two drawing tasks that was not evident in the human recognition data.
-To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future research.
+While we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel], we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed an overall difference between the two drawing tasks that was not evident in the human recognition data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model predictions available to facilitate future research.
 

### 2021-11-15 writing/Manuscript_June2021.Rmd
add classifier details in response to jefan query

@@
 Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization. 
-Next, we used these features to train a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
+Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
 To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
-\textbf{jefan query: Here we describe the training data distribution, but not the test set? What kind of train/test splitting procedure did we use here (LOO? 80/20 CV?)}
 No additional metadata about the age of the child who produced each sketch was provided to the model. 

### 2021-11-29 writing/Manuscript_June2021.Rmd
minor

--- 2021-11-13 writing/Manuscript_June2021.Rmd
@@
 In a secondary analysis, we investigated the degree to which any of the above effects were mediated by children's tracing abilities or the amount of effort that children expended while drawings. 
-We thus fit the same model above, with the addition of fixed-effect terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of "ink" used (i.e.
-percentage of non-white pixels in the drawn image), and the number of strokes.
+We fit the same model above with additional fixed-effects terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of "ink" used (i.e.
+percentage of non-white pixels in the drawn image), and the number of strokes produced.
 These additional predictors were first z-scored before being included in the model.
@@
 ### Confirmatory Analyses
-Overall, we found relative consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in (all model coefficients can be found in Table 1).
+Overall, we found general consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of cue type (picture, verbal) and geographical site (San Jose, Beijing; all model coefficients can be found in Table 1).
 We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].

### 2021-11-29 writing/Manuscript_June2021.Rmd
editing pass through results

@@
 ### Confirmatory Analyses
-Overall, we found general consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of cue type (picture, verbal) and geographical site (San Jose, Beijing; all model coefficients can be found in Table 1).
-We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
-Further, we found that these changes in recognizability did not depend on the drawing task children completed: Children's drawings were equally recognizable when they were asked to "Draw this rabbit as it looks in the picture" versus they were simply asked "Can you draw a rabbit?".
-While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories [@yang2021visual] -- this was not the case.
-However, we did observe a main effect of geographical site: we found that children from Beijing, China overall tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
-A closer look comparing the recognizability of the drawings made at children at each age and site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
 
-In a second set of analyses, we aimed to understand the nature of this difference in recognizability across sites.
-We initially hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
-We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
+We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
+Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph ("Draw this rabbit as it looks in the picture") as when they were cued with the category label ("Can you draw a rabbit?").
+While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar based on prior work with adult participants [@yang2021visual], we did not find evidence of an interaction between age and cue type.
+However, we did observe a main effect of geographical site: children in Beijing, China producde more recognizable drawings than children in San Jose, USA (Table 1).
+A closer look comparing the recognizability of the drawings made by children at each age and site hints that the children in the Beijing group produced more recognizable drawings earlier in development.
+
+In follow-up analyses, we aimed to understand the nature of this difference in recognizability across sites. 
+We initially hypothesized that any differences in drawing recognizability between sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. 
 Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
-Children tended to spend more time drawing provided with a picture cue and asked to draw "the [rabbit] as it looks in the picture", and children from Beijing tended to spend more time drawing overall.
-In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
+We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.
+By contrast, children's tracing abilities did not vary across geographical sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
 While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.
@@
 We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models).
-If the amount of effort spent or children's tracing abilities accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
-Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
-In addition, the amount of time a child spent drawing was in fact a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
-Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
+If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
+Contra this hypothesis, we still observed a significant effect of geographical site (see Table 2), even having accounted for the effect of individual differences in tracing ability.
+We also found that the amount of time a child spent drawing negatively predicted recognizability -- indicating that spending more time on a drawing did not necessarily result in a more recognizable drawing.
+Together, these results suggest that these site differences in the ability to produce recognizable drawings are not explained by differences in effort or tracing ability.
 
 ### Exploratory Analyses
-In a third set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
+In a set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
 Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
-However, we had no strong hypotheses about how these trajectories might additionally vary with geographical locations.
+However, we did not have strong hypotheses about how these trajectories might additionally vary with geographical locations.
 
-Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.
-For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
-In addition, children from Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children from San Jose produced more recognizable drawings of bikes.
+Figure \ref{fig:item-effects} shows considerable variation in drawing recognizability across the 12 categories as a function of geographical site and age.
+For example, certain distinctions between similar categories (e.g., cats and rabbits) were more difficult to make, especially for younger children.
+In addition, children in the Beijing group produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children in San Jose produced more recognizable drawings of bikes.
 Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
-These exploratory analyses thus reveal systematic differences between object categories and geographical site that do not seem easily attributable to differences in effort.
+As a whole, these exploratory analyses provide converging evidence for systematic differences between object categories and geographical site that are not easily attributable to differences in effort.
 

### 2021-11-29 writing/Manuscript_June2021.Rmd
work in progress, second pass through results/start of discussion

@@
 
-We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel].
+We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work using the verbal-cue paradigm under less controlled settings [@long2021parallel].
 Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph ("Draw this rabbit as it looks in the picture") as when they were cued with the category label ("Can you draw a rabbit?").
-While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar based on prior work with adult participants [@yang2021visual], we did not find evidence of an interaction between age and cue type.
-However, we did observe a main effect of geographical site: children in Beijing, China producde more recognizable drawings than children in San Jose, USA (Table 1).
-A closer look comparing the recognizability of the drawings made by children at each age and site hints that the children in the Beijing group produced more recognizable drawings earlier in development.
+While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar, as adult participants do [@yang2021visual], we did not find evidence of an interaction between age and cue type.
+However, we did observe a main effect of geographical site: children in Beijing, China produced drawings that were more recognizable than children in San Jose, USA (Table 1), reflecting steeper age-related gains earlier in development.
 
-In follow-up analyses, we aimed to understand the nature of this difference in recognizability across sites. 
+In follow-up analyses, we investigated potential sources of variation that might explain these site-related differences. 
 We initially hypothesized that any differences in drawing recognizability between sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. 
@@
 # General Discussion
-Here we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
-Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel].
+Here we examined developmental change in children's ability to produce recognizable drawings of familiar object concepts and potential variation in task performance due to demands on memory. 
+We found steady improvement from 4-9 years of age in two groups of children tested in different sites, replicating prior work [@long2021parallel].
+
 We found that asking children to draw categories when provided with a verbal cue ("Can you draw a [cat]?") vs.
@@
 While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
-Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
+Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
 

### 2021-12-04 writing/Manuscript_June2021.Rmd
edits through discussion

@@
 While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar, as adult participants do [@yang2021visual], we did not find evidence of an interaction between age and cue type.
-However, we did observe a main effect of geographical site: children in Beijing, China produced drawings that were more recognizable than children in San Jose, USA (Table 1), reflecting steeper age-related gains earlier in development.
+However, we did observe a main effect of geographical site: children in Beijing, China produced drawings that were more recognizable than did children in San Jose, USA (Table 1), reflecting steeper age-related gains earlier in development.
 
 In follow-up analyses, we investigated potential sources of variation that might explain these site-related differences. 
-We initially hypothesized that any differences in drawing recognizability between sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. 
+We initially hypothesized that any differences in drawing recognizability between sites could be mediated by the amount of effort children expended while drawing or their tracing abilities. 
 Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
 We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.
-By contrast, children's tracing abilities did not vary across geographical sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
+By contrast, children's tracing abilities did not vary across sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
 While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.
@@
 
+**JEFAN QUERY: I noticed that while draw duration was a negative predictor of recognizability, number of strokes was a positive predictor.
+We comment on the former, but not the latter.
+Could it be potentially confusing to a reader if we do not mention the latter?**
+
 ### Exploratory Analyses
-In a set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
+In a set of exploratory analyses, we examined how the developmental trajectory for drawing recognizability varied across object categories.
 Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
@@
 # General Discussion
-Here we examined developmental change in children's ability to produce recognizable drawings of familiar object concepts and potential variation in task performance due to demands on memory. 
-We found steady improvement from 4-9 years of age in two groups of children tested in different sites, replicating prior work [@long2021parallel].
+Here we examined developmental change in children's ability to produce recognizable drawings of familiar visual concepts, and the degree to which this ability is constrained by retrieval of diagnostic attributes from memory.
+We manipulated memory demands by either cueing children with a category label ("Can you draw a [cat]?") or a color photo ("Can you draw this [cat] as it looks in the picture?"), and measured the recognizability of each drawing to adult observers.
+To evaluate the generality of our findings, we recruited two groups of children in different sites: San Jose, USA and Beijing, China. 
+We found steady improvement from 4-9 years of age in both groups of children, replicating prior work conducted in a field setting [@long2021parallel].
+We did not find an effect of cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
+On the other hand, we discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group.
 
-We found that asking children to draw categories when provided with a verbal cue ("Can you draw a [cat]?") vs.
-a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced.
-While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers.
-Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
+To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort. 
+Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
+Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average, although individual tracing scores were strong predictors of the recognizablity of their own drawings.
+Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
+However, we also found that these effort measures could not account for differences in drawing recognizability between groups. 
+In exploratory analyses, we also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+**JEFAN QUERY: The previous six sentences were edited for clarity but are redundant with similar sentences in the results section.
+Perhaps it would be more effective to consolidate them (in Results?) and summarize them more concisely here?**
+While such group differences are intriguing, they are consistent with a number of other potential explanations.
+Further systematic investigation within and between geographical, socioeconomic, and cultural contexts will be crucial for producing more precise characterization of developmental variability in drawing behavior, itself critical to strongly evaluate causal theories of such variation [@amir2020cross, @carstensen2021investigating, @winner1989can, @kuwabara2016cultural].
+We have made our drawing dataset publicly available to contribute to this more cumulative effort and to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural, @senzaki2014holistic].
 
-Instead, we found that the recognizability of children's drawings differed between our two different geographical sites -- Beijing, China and San Jose, USA  Why might this be the case?
-Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recognizable their drawings were.
-However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
-A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularly incentivized to spend more effort on their drawings.
-Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
-Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
+Another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them. 
+For example, if some children are exposed to a wide variety of illustrations of some concepts but not others (e.g., in books or other media), they may also be able to produce more recognizable drawings of those concepts.
+Conversely, if some children spend more time drawing certain visual concepts but not others (e.g., in school or at home), they may also be better at recognizing graphical representations of them in other contexts, and perhaps explicitly identifying their diagnostic features.
+Prior work has found that older children not only produce more recognizable drawings of object categories, but also tend to be better at recognizing other children's drawings [@long2021parallel], providing evidence that visual production and recognition abilities are related throughout childhood at the group level.
+However, further investigation will be necessary for understanding what kinds of experience are responsible for concurrent developmental changes in these two behaviors at the individual level.
 
-While many have sought to examine variation across different cultural contexts in children's drawings [@winner1989can] or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition [@kuwabara2016cultural] -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured [@amir2020cross].
-Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings [@carstensen2021investigating].
-For example, some work has suggested that the distinction between wheat vs.
-rice farming traditions explains  variation in cultural practices within China [@talhelm2014large].
-We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code --  may differ in the very same ways children's drawings differed in this dataset.
-For example, a final possibility is that the children we recruited from Beijing vs.
-San Jose could differ widely in the amount of time they spending practicing drawing.
-If so, then children who spend more time drawing may simply have more experience communicating about the diagnostic features of different object categories.
+**JEFAN QUERY: We currently do not have a paragraph that expands on the null effect of cue type. Though perhaps we could, for "balance?"**
 
-Of course, these results of course do not preclude the possibility that children's drawings differed across these two drawing tasks or geographical sites in other interesting ways beyond their recognizability.
-Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail [@gernhardt2015cultural] and place a horizon line in systematically different locations when drawing scenes [@senzaki2014holistic].
-Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
-We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+In sum, our findings advance our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
+More broadly, we believe our approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
 
-However, we think a natural question for future work concerns the relationship between the degree to which  difference kinds of developmental experience drawing or learning about visual concepts changes how children draw and recognize them.
-In a U.S.
-based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings [@long2021parallel], hinting at a relationship between production and recognition.
-Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
-
-Finally, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
-For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
-
-Nonetheless, these results take a first step towards characterizing the consistency in the developmental trajectory of children's drawings.
-We propose that the systematic collection of digital drawings from children with a wide variety of experiences will help uncover the myriad factors that drive the developmental changes in children's drawings -- and in turn help us understand how different cognitive systems coordinate to produce this complex behavior.
+**JEFAN QUERY: Is there any way to hijack this APA template to force figures/tables to appear in the text close to where they are mentioned, rather than all the way at the end?**
 
@@
 [BLINDED]
-<!-- We thank Yi Feng and Megan Merrick for assistance with data collection, with whom this project would have not been possible.
-We also gratefully acknowledge the San Jose Children's Discovery Museum for their collaboration.
-We are also thankful to all of the parents at XX and XX preschool whose children participated.
-We also thank the members of the Stanford Language and Cognition lab for their feedback.
+<!-- We thank Yi Feng and Megan Merrick for assistance with data collection.
+We also thank the San Jose Children's Discovery Museum for their collaboration, as well as the parents at XX and XX preschool whose children participated.
+Thanks to members of the Stanford Language and Cognition lab for their feedback.
 This work was funded by an NSF SPRF-FR Grant \#1714726 to BLL and a Jacobs Foundation Fellowship to MCF.

### 2021-12-04 writing/Manuscript_June2021.Rmd
address one of the queries while fresh

@@
 
-In follow-up analyses, we investigated potential sources of variation that might explain these site-related differences. 
-We initially hypothesized that any differences in drawing recognizability between sites could be mediated by the amount of effort children expended while drawing or their tracing abilities. 
+To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort. 
+Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
+Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizablity of their own drawings, as in prior work [@long2021parallel].
+Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
 Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
 We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.
-By contrast, children's tracing abilities did not vary across sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
-While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.
 
@@
 If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
-Contra this hypothesis, we still observed a significant effect of geographical site (see Table 2), even having accounted for the effect of individual differences in tracing ability.
+Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability.
 We also found that the amount of time a child spent drawing negatively predicted recognizability -- indicating that spending more time on a drawing did not necessarily result in a more recognizable drawing.
@@
 In a set of exploratory analyses, we examined how the developmental trajectory for drawing recognizability varied across object categories.
-Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
+For example, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
 However, we did not have strong hypotheses about how these trajectories might additionally vary with geographical locations.
@@
 
-To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort. 
-Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
-Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average, although individual tracing scores were strong predictors of the recognizablity of their own drawings.
-Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
-However, we also found that these effort measures could not account for differences in drawing recognizability between groups. 
+To follow up on this effect of site, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
 In exploratory analyses, we also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
-**JEFAN QUERY: The previous six sentences were edited for clarity but are redundant with similar sentences in the results section.
-Perhaps it would be more effective to consolidate them (in Results?) and summarize them more concisely here?**
-While such group differences are intriguing, they are consistent with a number of other potential explanations.
+While these group-level differences are intriguing, they remain consistent with a number of other potential explanations.
 Further systematic investigation within and between geographical, socioeconomic, and cultural contexts will be crucial for producing more precise characterization of developmental variability in drawing behavior, itself critical to strongly evaluate causal theories of such variation [@amir2020cross, @carstensen2021investigating, @winner1989can, @kuwabara2016cultural].

### 2021-12-04 writing/Manuscript_June2021.Rmd
add a bit of teeth back to bit in discussion on culture

@@
 We did not find an effect of cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
+
 On the other hand, we discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group. 
-
-To follow up on this effect of site, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
-In exploratory analyses, we also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
-While these group-level differences are intriguing, they remain consistent with a number of other potential explanations.
-Further systematic investigation within and between geographical, socioeconomic, and cultural contexts will be crucial for producing more precise characterization of developmental variability in drawing behavior, itself critical to strongly evaluate causal theories of such variation [@amir2020cross, @carstensen2021investigating, @winner1989can, @kuwabara2016cultural].
-We have made our drawing dataset publicly available to contribute to this more cumulative effort and to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural, @senzaki2014holistic].
+In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
+We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
+Further systematic investigation of drawing behavior within and between geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, itself critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @winner1989can; @kuwabara2016cultural].
+On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of certain demographic variables (e.g., nationality).
+We have made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].
 

### 2021-12-04 writing/Manuscript_June2021.Rmd
ok one more tweak to that thorny discussion para

@@
 While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
-Further systematic investigation of drawing behavior within and between geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, itself critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @winner1989can; @kuwabara2016cultural].
-On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of certain demographic variables (e.g., nationality).
-We have made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].
+Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @frank2021variability].
+On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality [@winner1989can; @kuwabara2016cultural].
+We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].
 

### 2022-02-12 writing/Manuscript_2022.Rmd
latest ms draft edits

--- 2021-12-04 writing/Manuscript_June2021.Rmd
@@
 Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
-Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizablity of their own drawings, as in prior work [@long2021parallel].
+Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizability of their own drawings, as in prior work [@long2021parallel].
 Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
@@
 If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
-Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability.
-We also found that the amount of time a child spent drawing negatively predicted recognizability -- indicating that spending more time on a drawing did not necessarily result in a more recognizable drawing.
+Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability as well as effort covariates for each drawing that was produced.
+Nonetheless, children's tracing abilities were clearly related to the degree they were able to produce recognizable drawings.
 Together, these results suggest that these site differences in the ability to produce recognizable drawings are not explained by differences in effort or tracing ability.
-
-**JEFAN QUERY: I noticed that while draw duration was a negative predictor of recognizability, number of strokes was a positive predictor.
-We comment on the former, but not the latter.
-Could it be potentially confusing to a reader if we do not mention the latter?**
 
@@
 
-On the other hand, we discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group. 
+<!-- Why might we have not observed an effect of cue type?
+In related work with adults, @yang2021 found that providing adults with photograph cues of these same categories led to more recognizable drawings of object categories.
+Thus, one possibility is that children have yet to develop the skill -->
+
+We also discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group.
 In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
 We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+
 While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
@@
 
-**JEFAN QUERY: We currently do not have a paragraph that expands on the null effect of cue type. Though perhaps we could, for "balance?"**
-
 In sum, our findings advance our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
 More broadly, we believe our approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
-
-**JEFAN QUERY: Is there any way to hijack this APA template to force figures/tables to appear in the text close to where they are mentioned, rather than all the way at the end?**
 

### 2022-02-12 writing/Manuscript_2022.tex
latest ms draft edits

--- 2021-11-10 writing/Manuscript_June2021.tex
@@
 What are the major factors that explain this developmental change?
-Here, we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China), and with children's tracing abilities.
+Here we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China), and with children's tracing abilities.
 To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
-Overall, we show broad consistency in these developmental trajectories acros both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that children from Beijing, China produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in their visuomotor control or working memory capacity.
+Overall, we show broad consistency in these developmental trajectories across both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
+In addition, we find that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in visuomotor control or working memory capacity.
 }
@@
 
-As humans, we have many powerful tools to externalize what we know, including language and gesture.
-One tool that has been transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format.
+As humans, we have many powerful tools to externalize what we perceive and know, including language and gesture.
+One tool that has been especially transformative for human cognition and culture is graphical representation, which allows people to encode their thoughts in a visible, durable format.
 Drawing is an important case study in graphical representation, being a technique that dates back 60,000 years (Hoffmann et al., 2018), well before the emergence of symbolic writing systems, and is practiced in many cultures.
@@
 In modern times, drawings are produced prolifically by children from an early age.
-Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities (Minsky \& Papert, 1972), and accordingly a long history of work has examined changes in children's drawings across development (Fury, Carlson, \& Sroufe, 1997; Karmiloff-Smith, 1990; Kellogg, 1969; Piaget, 1929).
-Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age; younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
+Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities (Minsky \& Papert, 1972), and accordingly a long history of work has examined changes in how children draw objects across development (Fury, Carlson, \& Sroufe, 1997; Karmiloff-Smith, 1990; Kellogg, 1969; Piaget, 1929).
+Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
 
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements (Freeman, 1987; Rehrig \& Stromswold, 2018).
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings --- including how children represent a given visual concept and how well children are able to access these concepts when producing drawings.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings --- including what children know about a given target object and how well children are able to access this conceptual knowledge when producing a drawing.
 
-Prior work provides evidence that changes in children's drawings partly reflect changes in children's representations of visual concepts.
+Prior work has provided evidence that changes in children's drawings partly reflect changes in children's mental representations of visual concepts.
 In a large observational dataset, older children produced drawings of object categories that were more diagnostic of the categories they were trying to depict (Long, Fan, Chai, \& Frank, 2021; Long, Fan, \& Frank, 2018).
 This result held even when accounting for differences in basic shape tracing abilities and the amount of effort children expended on individual drawings.
-FUrthermore, older children also tended to rely more on these same diagnostic visual features when recognizing each other's drawings, suggesting that changes in children's internal visual representations drive parallel changes in children's production and recognition of drawings.
-Thus, the drawings that children produce likely not only reflect their increasing motor abilities but their evolving visual concepts (Dekker, Mareschal, Sereno, \& Johnson, 2011; Natu et al., 2016).
+Furthermore, older children also relied more on these same diagnostic visual features when recognizing other children's drawings.
+Together, these results suggest that developmental change in these underlying conceptual representations drive parallel changes in both children's production and recognition of drawings, and thus that change in how well children can produce recognizable drawings do not only reflect improvements in motor control (Dekker, Mareschal, Sereno, \& Johnson, 2011; Natu et al., 2016).
 
-However, this work leaves open the contribution of children's evolving memory.
+However, this work leaves open the contribution of children's evolving abilities to retrieve and maintain relevant information in memory.
 Children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood (Pailian, Libertus, Feigenson, \& Halberda, 2016).
-Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant perceptual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant perceptual details and then hold in mind what rabbits tend to look like.
-On this account, providing children with additional perceptual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan et al., 2020).
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant visual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant visual details and then hold in mind what rabbits tend to look like.
+On this account, providing children with additional visual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan, Yamins, \& Turk-Browne, 2018).
 
-However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate the information in their immediate perceptual experience.
+However, prior work also suggests that younger children tend to draw what they know about objects rather than integrate information in their immediate perceptual experience (Luquet, 1927).
 For example, when asked to draw from observation, younger children tend to include features that are not visible from their vantage point, yet are diagnostic of category membership (e.g., a handle on a \textit{mug}) (Barrett \& Light, 1976; Bremner \& Moore, 1984), and only omit these features later in development.
@@
 Thus, an alternative possibility is that only older children may be able to produce more recognizable drawings when provided with canonical exemplars of different categories.
-On this account, working memory constraints are not a major factor that drives developmental changes in children's drawings.
+On this account, memory constraints are not a major factor that drives developmental changes in children's drawings.
 
@@
 
-To test the generality of our findings, we recruited children from two different sites in different countries --- San Jose, USA and Beijing, China.
+To test the generality of our findings, we recruited children from two sites in different countries --- San Jose, USA and Beijing, China.
 Most empirical studies on children's drawings have been conducted exclusively on small samples of children from the United States or Western Europe, limiting their generalizability.
 Further, children in different communities may spend more or less time practicing drawing or use different visual conventions to draw (Cohn, 2012; Willats, 2006).
-While some prior work has focused on differences in children's drawings across different countries, most of this descriptive work has focused on differences in educational practices that may manifest in children's drawings (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
-Instead, here we focus on the degree to which the overall developmental trajectory of drawing abilities are similar between children at these two sites.
+While some prior work has focused on differences in children's drawings across different countries, most of this work has focused on differences in educational practices that are thought to manifest in children's drawings (Huntsinger, Jose, Krieg, \& Luo, 2011; La Voy et al., 2001; Winner, 1989).
+Leaving aside questions about potential causes of differences between sites, here we focus on measuring the degree to which drawing abilities vary between children at these two sites using the same experimental protocol.
 
 Finally, we assessed the degree to which visuomotor development accounts for observed developmental changes in drawing recognizability.
-While it is clear that visuomotor control influences how and what we can draw, little work has directly related measures of visuomotor control to drawing outcomes (Long et al., 2021).
-To do so, we measured each child's visuomotor control via a shape tracing task on a table and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
+While it is uncontroversial that visuomotor control can constrain how and what we can draw, little work has directly related measures of visuomotor control to measures of drawing recognizability (Long et al., 2021).
+To do so, we measured each child's visuomotor control via a shape tracing task and related these measurements of tracing accuracy to the recognizability of the drawings that each child produced.
 
-In the present study, we thus collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
-In doing so, we make three major contributions to our understanding of the development of children's drawings.
+In sum, in the current study we collect shape tracings and digital drawings of visual concepts from 4-9 year-old children in Beijing, China and San Jose, USA using both picture cues and verbal cues.
+In doing so, we make three key contributions to our understanding of the development of children's drawings.
 First, we replicate our prior findings (Long et al., 2021) that the recognizability of children's drawings increases steadily throughout this age range (4-9 years).
-Second, we test the degree to which working memory constraints might account for these developmental changes.
-In keeping with accounts of naïve realism and contra a strong account of working memory limitations, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings, Third, we test the generalizability of our findings across two different countries.
+Second, we test the degree to which memory constraints might account for these developmental changes.
+In keeping with accounts of naïve realism and against a large role of limitations on memory, we predicted that only older children would be able to use the visual information present in the canonical photographs to improve their drawings.
+Third, we test the generalizability of our findings across two sites in different countries.
 We predicted that we would see convergence in the development of drawing abilities across both geographical sites, with older children becoming progressively better at producing recognizable drawings.
-In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at \url{https://osf.io/qymjr/}.
+In addition, we predicted that most of the variance across geographical sites in drawing ability would be explainable by differences in visuomotor control, operationalized as performance on a shape tracing task; these primary analyses were pre-registered at: \url{https://osf.io/qymjr/}.
 
@@
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
-In the San Jose based sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
+In the San Jose sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
 Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of 121 children.
-In the Beijing based sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+In the Beijing sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
@@
 
-\hypertarget{task-procedure}{%
-\subsection{Task Procedure}\label{task-procedure}}
+\hypertarget{stimuli-and-task-procedure}{%
+\subsection{Stimuli and Task Procedure}\label{stimuli-and-task-procedure}}
 
-Children participated in a drawing game using their fingers to draw, completing 2 shape tracing trials and 12 object category drawing trials.
-Children drew using an Ipad Pro (12.9") that was set at a slight angle on a table via a tablet case, and had maximum of 30 seconds to produce their tracings and drawings.
-Strokes could not be deleted once drawn, and stroke-by-stroke data for each drawing was stored on a remote server.
-
-Before beginning the drawing game, a trained experimenter first told each child \enquote{After this game is over, someone is going to try to recognize what you were trying to draw.
-So, please draw so that someone else could try what you were trying to draw.} A native English speaker gave these instructions to the San Jose based sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing based sample.
-
-After these instructions, children first completed two series of tracing trials to obtain an estimate of their tracing abilities; children were first asked to trace a square and then a complex shape (see Figure \ref{fig:example-tasks}).
-The primary experimental manipulation was the type of cue that children heard on the subsequent drawing trials (see task examples in Figure \ref{fig:example-tasks}).
-Children completed six trials with the same cue type (verbal or picture cue) before switching cue types; this order was counterbalanced across participants.
-On verbal cue trials, children saw a short video clip where an experimenter said, \enquote{What about a {[}cat{]}?
-Can you draw a {[}cat{]}?}.
-On picture-cue trials, children heard audio of the same experimenter who said, \enquote{What about this {[}cat{]}?
-Can you draw the {[}cat{]} as it looks in the picture?} while seeing a canonical photograph of each category.
-This photograph was randomly sampled from one of three possible exemplars and remained on the screen for the duration of the drawing trial.
+Children were seated in front of a touchscreen tablet (Ipad Pro 12.9\enquote{) during each drawing session.
+At the beginning of the session, a trained experimenter first told each child, ``After this game is over, someone is going to try to recognize what you were trying to draw.
+So, please draw so that someone else could guess what you were trying to draw.}
+A native English speaker gave these instructions to the San Jose sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing sample.
+Following these instructions, children completed 2 shape-tracing trials, providing a baseline measure of visuomotor control in the absence of memory demands.
+All children first traced a square, then a more complex shape (see Figure \ref{fig:example-tasks}).
+After these tracing trials, children produced drawings of 12 familiar object categories (airplane, bike, bird, car, cat, chair, cup, hat, house, rabbit, tree, watch).
+Strokes could not be deleted once drawn, and children had to complete each trial within 30 seconds.
+Across trials, we manipulated the type of cue (verbal vs.~picture) children received before producing each drawing (Fig.
+\ref{fig:example-tasks}), providing a measure of the impact of reminding children of what typical exemplars of each category looked like.
+Specifically, children first completed six trials with one cue type, then switched to the other cue type.
+The order in which each cue type was used was counterbalanced across children.
+On verbal-cue trials, children viewed a short video clip in which an experimenter named the target category: \enquote{What about a {[}cat{]}? Can you draw a {[}cat{]}?}.\\
+On picture-cue trials, children viewed a photograph of a typical exemplar of the target category while listening to an audio clip of the same experimenter who said, \enquote{What about this {[}cat{]}?
+Can you draw the {[}cat{]} as it looks in the picture?}
+The photograph remained on the screen for the duration of the drawing trial.
+There were three different exemplars of each category used in this study, one of which was randomly sampled on each picture-cue trial.
 All experimental code, videos, translations, and stimuli are available on the public repository for this project.
@@
 
-For each drawing trial, children had up to 30 seconds to complete their drawings with their fingers.
-We recorded both the final drawings and the parameters of each stroke produced by children, allowing us to estimate the amount of time children put into their drawings (e.g., end time of last stroke --- start time of first stroke).
-As a second measure of effort, we also counted the number of strokes that children put into a given drawing.
-Finally, we estimated the proportion of the drawing canvas that was filled (e.g., \enquote{ink used}) by computing the proportion of each final drawing that were non-white pixels.
+We recorded both the final drawings and the location of each stroke in a digital format, allowing us to precisely measure several different variables that provided proxies for the amount of effort children invested in producing each drawing.
+Specifically, we measured: (1) the amount of time spent (i.e., end time of last stroke --- start time of first stroke), (2) the number of individual strokes drawn, and (3) the amount of \enquote{ink} used (i.e., proportion of drawing canvas that was filled).
 
@@
 Shape error reflects how closely the participant's tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant's tracing matched the target shape.
-These two error components were computed automatically for each tracing and used to yield a \enquote{tracing score} for each tracing that mirrors adult human judgements of tracing quality (see Appendix for details).
+These two error components were computed automatically for each tracing and used to yield a \enquote{tracing score} for each tracing that mirrors adult human judgments of tracing quality (see Appendix for details).
 
@@
 
-We assessed the recognizability of each drawing via an online recognition experiment.
+We measured the recognizability of each drawing via an online recognition experiment.
 Adult participants based in the U.S.
-were recruited via Prolific for a 15 minute experiment, compensated at \$14/hour, and asked to recognize a random subset of around 140 drawings that were balanced with respect to age, category, and site.
-Each drawing was recognized by 10 participants.
-Participants were shown these drawings in a random order and asked \enquote{What does this look like?}.
-Participants selected an answer from the twelve categories that children were prompted to draw and were encouraged to guess.
-No participants were excluded from analysis for missing a catch trial (a free response describing the task that were completing).
-These binary recognition scores were then averaged across participants to yield a recognition score for each drawing.
-(e.g., recognized by 80\% of participants).
+were recruited via Prolific for a 15-minute experiment, compensated at \$14/hour, and asked to identify the category depicted in a random subset of approximately 140 drawings.
+Each subset of drawings was balanced with respect to age, category, and site, and each drawing was shown to 10 participants.
+Participants were shown these drawings in a random sequence and asked \enquote{What does this look like?}
+Participants selected their responses from the set of 12 categories and were encouraged to provide their best guess if they were unsure.
+No participants were excluded from analysis for missing the catch trial, which was included to verify that participants could accurately describe their goal in this task.
+We then computed a recognition score for each drawing, reflecting the proportion of participants who correctly identified the target category.
 
@@
 
-We used a combination of deep CNN activations and logistic regressions to obtain automated recognition scores, as per our pre-registered protocol.
-To encode the high-level visual features of each sketch, we used the VGG-19 architecture (Simonyan \& Zisserman, 2014) a deep convolutional neural network pre-trained on Imagenet classification.
-We used model activations in the second-to-last layer of this network (FC6).
-Raw feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.
-Next, we used these features to train object category decoders; we then trained a 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to estimate the category label for each drawing in the dataset.To avoid any bias due to imbalance in the distribution of drawings over categories, we randomly under sampled such that there were an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
-No additional metadata about the age of the child who produced each sketch was provided to the decoder.
-This procedure was repeated for each drawing in the dataset, yielding a binary a recognition score for each drawing.
+We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol.
+To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 (Simonyan \& Zisserman, 2014), a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch (Paszke et al., 2017).
+We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6).
+Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.
+Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
+To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
+No additional metadata about the age of the child who produced each sketch was provided to the model.
+This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing.
 
@@
 
-To assess our main hypotheses, we fit generalized linear mixed effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
-A first generalized linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (verbal cue vs.~picture cue) and the three way interaction between these key variables.
+To evaluate our main hypotheses, we fit generalized linear mixed-effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
+A first generalized linear mixed effect model was fit to the recognizability scores for each drawing, including fixed effects of children's age (in years), geographical site (San Jose vs.~Beijing), and drawing task (verbal cue vs.~picture cue) and the three-way interaction between these key variables.
 We initially planned to include random slopes for the effect of drawing task on each child (as this varied within-subjects), and random slopes for the effect the full three-way interactions between task, age, and site on each category.
-However, models with this complicated random effects structure failed to converge, and the reported models use the maximal random effects structure that did converge -- which included random sloops for the two-way interaction between task and age on each category.
+However, models with this random-effects structure failed to converge, and the reported models use the maximal random effects structure that did converge, which included random slopes for the two-way interaction between task and age on each category.
 
-In a secondary analysis, we aimed to understand the degree to which any of the above effects were mediated by (1) children's tracing abilities and (2) the amount of effort that children expended while drawings.
-We thus ran the same main model while also now including fixed effects of children's estimated tracing score (see Measuring Tracing Abilities), the time children spent drawing (in seconds), the mean intensity of the drawing (i.e.~percentage of non-white pixels), and the number of strokes children used.
-All predictors were scaled to have a mean of 0 and a standard deviation of 1.
-Finally, we also assessed the degree to which tracing ability development differed by geographical site, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random effects structure as the first model.
+In a secondary analysis, we investigated the degree to which any of the above effects were mediated by children's tracing abilities or the amount of effort that children expended while drawings.
+We fit the same model above with additional fixed-effects terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of \enquote{ink} used (i.e.~percentage of non-white pixels in the drawn image), and the number of strokes produced.
+These additional predictors were first z-scored before being included in the model.
+Finally, we also assessed the degree to which tracing ability development differed across geographical sites, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random-effects structure as the first model.
 
 This analysis plan was pre-registered at \url{https://osf.io/qymjr}.
-While we had initially planned to use automated recognition scores as our main dependent variable, following prior work (Long et al., 2021), we found that these automated recognition scores were only modestly correlated with human recognition scores (\(r\) = 0.40, \(t\) = 22.78, p \textless{} .001); furthermore, descriptive plots of the automated recognition scores revealed a overall difference between the two drawing tasks that was not evident in the human recognition data.
-To be conservative, we thus fit all of our models to the human recognition data but have made all model classifications available for future research.
+While we had initially planned to use automated recognition scores as our main dependent variable, following prior work (Long et al., 2021), we found that these automated recognition scores were only modestly correlated with human recognition scores (\(r\) = 0.40, \(t\) = 22.78, p \textless{} .001); furthermore, descriptive plots of the automated recognition scores revealed an overall difference between the two drawing tasks that was not evident in the human recognition data.
+To be conservative, we thus fit all of our models to the human recognition data but have made all model predictions available to facilitate future research.
 
@@
 
-Overall, we found relative consistency in the developmental trajectory of children's drawings: Figure \ref{fig:main-results} shows the recognizability of children's drawings at each age as a function of the drawing task and the geographical site that they were located in (all model coefficients can be found in Table 1).
-We found steady changes in the recognizability of children's drawings across this age range, replicating prior work with an observational dataset collected at a free-standing kiosk (Long et al., 2021).
-Further, we found that these changes in recognizability did not depend on the drawing task children completed: Children's drawings were equally recognizable when they were asked to \enquote{Draw this rabbit as it looks in the picture} versus they were simply asked \enquote{Can you draw a rabbit?}.
-While we anticipated that older children might produce more recognizable drawings when provided with a picture cue -- as do adults when presented with canonical photographs of object categories (Yang \& Fan, 2021) -- this was not the case.
-However, we did observe a main effect of geographical site: we found that children from Beijing, China overall tended to produce more recognizable drawings than children from San Jose, USA (see coefficients in Table 1).
-A closer look comparing the recognizability of the drawings made at children at each age and site hints that the children from Beijing, China may tend to produce more recognizable drawings earlier in development.
+We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work using the verbal-cue paradigm under less controlled settings (Long et al., 2021).
+Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph (\enquote{Draw this rabbit as it looks in the picture}) as when they were cued with the category label (\enquote{Can you draw a rabbit?}).\\
+While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar, as adult participants do (Yang \& Fan, 2021), we did not find evidence of an interaction between age and cue type.
+However, we did observe a main effect of geographical site: children in Beijing, China produced drawings that were more recognizable than did children in San Jose, USA (Table 1), reflecting steeper age-related gains earlier in development.
 
-In a second set of analyses, we aimed to understand the nature of this difference in recognizability across sites.
-We initially hypothesized that any differences in the recognizability of children's drawings across sites would be mediated by the amount of effort children expended while drawing or their tracing abilities.
-We thus first examined how effort and tracing abilities varied across task, age, and geographical location.
-Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.
-Children tended to spend more time drawing provided with a picture cue and asked to draw \enquote{the {[}rabbit{]} as it looks in the picture}, and children from Beijing tended to spend more time drawing overall.
-In contrast, children's tracing abilities did not vary across geographical site: Figure \ref{fig:tracing} shows the average tracing score at each age at each site.
-While children's tracing abilities increased steadily with age, as in prior work (Long et al., 2021), children from both sites produced equally good tracings.
+To follow up on this effect of site, we tested two potential sources of variation: visuomotor control and effort.
+Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
+Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizablity of their own drawings, as in prior work (Long et al., 2021).
+Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
+Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.\\
+We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose.
 
 We then included children's average tracing scores and effort covariates measured for each drawing (average intensity, number of strokes used, and time spent drawing) as fixed effects into a second generalized linear mixed-effects model (see Statistical Models).
-If the amount of effort spent or children's tracing abilities accounted the differences between sites that we observed, we reasoned that we should no longer observe a main effect of geographical location on drawing recognizability.
-Contra this hypothesis, however, we still observed a significant effect of geographical site (see Table 2), despite the fact that individual children's tracing abilities were strong predictors of how recognizable their drawings were.
-In addition, the amount of time a child spent drawing was in fact a significant negative predictor of recognizability -- indicating that the amount of effort that children expended did not necessarily result in a drawing that was more recognizable to others.
-Thus, these results suggest that these two groups of children differ in their ability to produce recognizable drawings of object categories in a way that is not easily explainable by effort covariates or tracing abilities.
+If effort and/or tracing ability is sufficient to account for the differences between sites, we reasoned that we should no longer observe a main effect of geographical site on drawing recognizability in this expanded statistical model.
+Instead, we observed a significant effect of geographical site (see Table 2), even after having accounted for the effect of individual differences in tracing ability as well as effort covariates for each drawing that was produced.
+Nonetheless, children's tracing abilities were clearly related to the degree they were able to produce recognizable drawings.
+Together, these results suggest that these site differences in the ability to produce recognizable drawings are not explained by differences in effort or tracing ability.
 
@@
 
-In a third set of exploratory analyses, we examined how the developmental trajectory of the recognizability of children's drawings differ for different object categories.
-Intuitively, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
-However, we had no strong hypotheses about how these trajectories might additionally vary with geographical locations.
+In a set of exploratory analyses, we examined how the developmental trajectory for drawing recognizability varied across object categories.
+For example, some object categories (e.g., cat) may be easier to draw than others (e.g., watch), resulting in shallower or steeper changes in recognizability over age.
+However, we did not have strong hypotheses about how these trajectories might additionally vary with geographical locations.
 
-Figure \ref{fig:item-effects} shows the recognizability of children's drawings for each of the 12 categories a function of geographical location and children's age and reveal considerable variability.
-For example, certain categories (e.g., cats and rabbits) were overall more difficult for children to depict such that they were distinct from one another, particularly for younger children.
-In addition, children from Beijing produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children from San Jose produced more recognizable drawings of bikes.
+Figure \ref{fig:item-effects} shows considerable variation in drawing recognizability across the 12 categories as a function of geographical site and age.
+For example, certain distinctions between similar categories (e.g., cats and rabbits) were more difficult to make, especially for younger children.
+In addition, children in the Beijing group produced more recognizable drawings of certain categories at all ages -- including airplanes, birds, and rabbits -- while older children in San Jose produced more recognizable drawings of bikes.
 Figure \ref{fig:example-drawings} shows recognizable, randomly sampled example drawings from 6-year-olds at each category, site, and condition.
-These exploratory analyses thus reveal systematic differences between object categories and geographical site that do not seem easily attributable to differences in effort.
+As a whole, these exploratory analyses provide converging evidence for systematic differences between object categories and geographical site that are not easily attributable to differences in effort.
 
@@
 
-Here, we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations.
-Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets (Long et al., 2021).
-We found that asking children to draw categories when provided with a verbal cue (\enquote{Can you draw a {[}cat{]}?}) vs.~a picture cue (\enquote{Can you draw this {[}cat{]} as it looks in the picture?}) had little effect on the recognizability of the drawings that children produced.
-While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work (Bremner \& Moore, 1984), this did not seem to change how recognizable their drawings were to outside observers.
-Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.
+Here we examined developmental change in children's ability to produce recognizable drawings of familiar visual concepts, and the degree to which this ability is constrained by retrieval of diagnostic attributes from memory.
+We manipulated memory demands by either cueing children with a category label (\enquote{Can you draw a {[}cat{]}?}) or a color photo (\enquote{Can you draw this {[}cat{]} as it looks in the picture?}), and measured the recognizability of each drawing to adult observers.
+To evaluate the generality of our findings, we recruited two groups of children in different sites: San Jose, USA and Beijing, China.
+We found steady improvement from 4-9 years of age in both groups of children, replicating prior work conducted in a field setting (Long et al., 2021).
+We did not find an effect of cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
 
-Instead, we found that the recognizability of children's drawings differed between our two different geographical sites -- Beijing, China and San Jose, USA Why might this be the case?
-Our initial hypothesis was that children who had daily practice with a non-orthographic, complex writing system would exhibit greater dexterity in our tracing assessment task -- and that this dexterity could be a factor in how recognizable their drawings were.
-However, children across the two sites showed equivalent shape tracing abilities, despite the fact that children's individual tracing scores were strong predictors of the recognizability of the drawings that they produced.
-A second possibility is that children from preschools near Beijing were simply more engaged with the task than children recruited at a children's museum outside San Jose, USA: A more academic context could have created an environment in which children felt particularly incentivized to spend more effort on their drawings.
-Nonetheless, our measures of drawing's effort (e.g., amount of time spent drawing, number of strokes made) did not account for differences in recognizability across sites.
-Furthermore, we saw systematic differences in the object categories that were more or less recognizable across sites, which is not well-explained by this account.
-Thus, this finding both confirms the idea that children's visuomotor abilities strongly influence the recognizability of the drawings they produce, yet further suggests that it is far from the only factor that does so.
+We also discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group.
+In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
+We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
 
-While many have sought to examine variation across different cultural contexts in children's drawings (Winner, 1989) or cognitive abilities that may be relevant to children's drawing abilities -- including object recognition (Kuwabara \& Smith, 2016) -- we note that this is there is substantial variation within different geographical locations and countries that often goes unmeasured (Amir \& McAuliffe, 2020).
-Indeed, this unmeasured variation within sites may lead to the low replicability of some cross-cultural findings (Carstensen, Cao, Gao, \& Frank, 2021).
-For example, some work has suggested that the distinction between wheat vs.~rice farming traditions explains variation in cultural practices within China (Talhelm et al., 2014).
-We thus caution against a strong interpretation of the observed site differences, as we believe that drawings from children within the same country -- or even area code -- may differ in the very same ways children's drawings differed in this dataset.
-For example, a final possibility is that the children we recruited from Beijing vs.~San Jose could differ widely in the amount of time they spending practicing drawing.
-If so, then children who spend more time drawing may simply have more experience communicating about the diagnostic features of different object categories.
+While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
+Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation ({\textbf{???}}; Amir \& McAuliffe, 2020; Carstensen, Cao, Gao, \& Frank, 2021).
+On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality (Kuwabara \& Smith, 2016; Winner, 1989).
+We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style (Gernhardt, Rübeling, \& Keller, 2015; Senzaki, Masuda, \& Nand, 2014).
 
-Of course, these results of course do not preclude the possibility that children's drawings differed across these two drawing tasks or geographical sites in other interesting ways beyond their recognizability.
-Some work has shown that young children across different cultural contexts tend to produce different tadpole drawings of varying heights and with different amounts of detail (Gernhardt, Rübeling, \& Keller, 2015) and place a horizon line in systematically different locations when drawing scenes (Senzaki, Masuda, \& Nand, 2014).
-Thus, finer-grained measurements of these drawings could reveal differences -- with respect to the exact visual features that children chose to include, the strategies they employed while drawing, or the order in which they chose to draw certain elements of these categories.
-We have thus made this dataset and the resulting code publicly available for these exploratory analyses.
+Another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them.
+For example, if some children are exposed to a wide variety of illustrations of some concepts but not others (e.g., in books or other media), they may also be able to produce more recognizable drawings of those concepts.
+Conversely, if some children spend more time drawing certain visual concepts but not others (e.g., in school or at home), they may also be better at recognizing graphical representations of them in other contexts, and perhaps explicitly identifying their diagnostic features.
+Prior work has found that older children not only produce more recognizable drawings of object categories, but also tend to be better at recognizing other children's drawings (Long et al., 2021), providing evidence that visual production and recognition abilities are related throughout childhood at the group level.
+However, further investigation will be necessary for understanding what kinds of experience are responsible for concurrent developmental changes in these two behaviors at the individual level.
 
-However, we think a natural question for future work concerns the relationship between the degree to which difference kinds of developmental experience drawing or learning about visual concepts changes how children draw and recognize them.
-In a U.S.
-based sample, prior work found that older children not only produce more recognizable drawings of object categories but tend to be better skilled at recognizing other children's drawings (Long et al., 2021), hinting at a relationship between production and recognition.
-Thus, if children in different environmental contexts tend to spend more time practicing drawing, these children may also be more skilled at recognizing drawings of object categories and perhaps explicitly identifying the distinctive visual features of these categories.
-
-Finally, we note that while this work moves beyond investigating the drawings of children at a single geographical location, these children are still in many ways non-representative of the general population.
-For example, children in more rural populations may spend considerably less time both consuming and producing drawings of object categories.
-Thus, these developmental trajectories could thus vary in several ways that are not captured by the populations represented in the the present dataset.
-
-Nonetheless, these results take a first step towards characterizing the consistency in the developmental trajectory of children's drawings.
-We propose that the systematic collection of digital drawings from children with a wide variety of experiences will help uncover the myriad factors that drive the developmental changes in children's drawings -- and in turn help us understand how different cognitive systems coordinate to produce this complex behavior.
+In sum, our findings advance our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
+More broadly, we believe our approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
 
@@
 
-\leavevmode\hypertarget{ref-fan2020relating}{}%
-Fan, J.
-E., Wammes, J.
-D., Gunn, J.
-B., Yamins, D.
-L., Norman, K.
-A., \& Turk-Browne, N.
-B.
-(2020).
-Relating visual production and recognition of objects in human visual cortex.
-\emph{Journal of Neuroscience}, \emph{40}(8), 1710--1721.
+\leavevmode\hypertarget{ref-fan2018common}{}%
+Fan, J. E., Yamins, D. L., \& Turk-Browne, N. B. (2018). Common object representations for visual production and recognition. \emph{Cognitive Science}, \emph{42}(8), 2670--2698.
 
@@
 
+\leavevmode\hypertarget{ref-luquet1927dessin}{}%
+Luquet, G.-H. (1927). Le dessin enfantin.(Bibliothèque de psychologie de l" enfant et de pédagogie.).
+
 \leavevmode\hypertarget{ref-minsky1972artificial}{}%
@@
 \emph{Attention, Perception, \& Psychophysics}, \emph{78}(6), 1556--1573.
+
+\leavevmode\hypertarget{ref-paszke2017automatic}{}%
+Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., \ldots{} Lerer, A. (2017). Automatic differentiation in pytorch.
 
@@
 
-\leavevmode\hypertarget{ref-talhelm2014large}{}%
-Talhelm, T., Zhang, X., Oishi, S., Shimin, C., Duan, D., Lan, X., \& Kitayama, S.
-(2014).
-Large-scale psychological differences within china explained by rice versus wheat agriculture.
-\emph{Science}, \emph{344}(6184), 603--608.
-
 \leavevmode\hypertarget{ref-willats2006making}{}%

### 2022-07-21 writing/Manuscript_2022.Rmd
update latest version of manuscript and appendix

@@
 abstract: |
- Childen's drawings of common object categories become dramatically more recognziable across development.
+ Children's drawings of common object categories become dramatically more recognziable across development.
 What are the major factors that explain this developmental change?
-Here we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.
+Here we examined the degree to which these developmental changes in recognizability vary across different drawing tasks (i.e.
 drawing from observation vs.
@@
 Beijing, China), and with children's tracing abilities.
-To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
-Overall, we show broad consistency in these developmental trajectories across both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in visuomotor control or working memory capacity.
+To do so, we collected digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
+We found that the developmental trajectory of drawing recognizability was remarkably similar when children were asked to draw from observation vs.
+memory and across these two geographical locations.
+In addition, we found that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to children from San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings is remarkably consistent and not easily explainable by changes in domain general changes in visuomotor control or working memory.
 
@@
 
-documentclass     : "apa6"
+documentclass     : "docx"
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_doc
 ---
@@
 library(viridis)
+library(papaja)
 ```
@@
 ```{r}
-
 knitr::opts_chunk$set(fig.crop = FALSE, 
@@
 Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities [@minsky1972artificial], and accordingly a long history of work has examined changes in how children draw objects across development [@piaget1929child; @kellogg1969analyzing; @karmiloff1990constraints; @fury1997children].
-Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.
+Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between categories (e.g., \textit{adult} vs.
 \textit{child}) than older children, who enrich their drawings with more diagnostic part [@sitton1992drawing] and relational [@light1983effects] information.
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements [@freeman1987current; @rehrig2018does]. 
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings — including what children know about a given target object and how well children are able to access this conceptual knowledge when producing a drawing.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings — including what children know about a given visual concept and how well children are able to access this conceptual knowledge when producing a drawing.
 
@@
 ```{r load-classifications}
-classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
-  as_tibble() %>%
-  mutate(age_numeric = age) %>%
-  mutate(age = paste('age',age,sep="")) %>%
-  mutate(age = as.factor(age)) %>%
-  mutate(category = target_label) %>% 
-  dplyr::select(-X, -X.1, -index) %>%
-  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
-                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
-  mutate(site = as.factor(site)) 
+# classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
+#   as_tibble() %>%
+#   mutate(age_numeric = age) %>%
+#   mutate(age = paste('age',age,sep="")) %>%
+#   mutate(age = as.factor(age)) %>%
+#   mutate(category = target_label) %>% 
+#   dplyr::select(-X, -X.1, -index) %>%
+#   mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
+#                            !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
+#   mutate(site = as.factor(site)) 
 ```
@@
 ```{r join-data}
-model_classifications <- classification_data %>%
-  mutate(unique_ids = session_id) %>%
-  left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
-  left_join(tracing_by_sub)
-
-# bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
-# this was checked directly in mongodb database -- no idea why, assuming bad internet.
-tech_error_drawings <- model_classifications %>%
-  filter(is.na(num_strokes))
-# filter out tech error drawings from dataset (24)
-model_classifications <- model_classifications%>%
-  filter(!is.na(num_strokes))
+# model_classifications <- classification_data %>%
+#   mutate(unique_ids = session_id) %>%
+#   left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
+#   left_join(tracing_by_sub)
+#   
+# 
+# # bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
+# # this was checked directly in mongodb database -- no idea why, assuming bad internet.
+# tech_error_drawings <- model_classifications %>%
+#   filter(is.na(num_strokes))
+# # filter out tech error drawings from dataset (24)
+# model_classifications <- model_classifications%>%
+#   filter(!is.na(num_strokes))
 
@@
   left_join(tracing_by_sub) %>%
+  mutate(site = as.factor(site), condition = as.factor(condition)) %>%
   mutate(site = fct_recode(site, "San Jose" = "CDM", "Beijing" = "THU"))%>%
@@
 
-humans_and_models_merged <- humans %>%
-  group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
-  summarize(prop_correct = mean(correct_or_not)) %>%
-  left_join(model_classifications, by=c('unique_ids','category')) %>% # join with classification data 
-  filter(!is.na(age))
+# humans_and_models_merged <- humans %>%
+#   group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
+#   summarize(prop_correct = mean(correct_or_not)) %>%
+#   left_join(model_classifications, by=c('unique_ids','category')) %>% # join with classification data 
+#   filter(!is.na(age))
 ```
@@
 ## Participants
-265 participants were recruited from two local children's museum in [BLINDED] and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in San Jose and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.
@@
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
-On average, each child contributed `r mean(count_by_id$num_drawings)` drawings to analysis (min `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).
+On average, each child contributed `r mean(count_by_id$num_drawings)` drawings to analysis (min = `r min(count_by_id$num_drawings)`, max = `r max(count_by_id$num_drawings)`).
 No additional demographic data was recorded about the participants.
@@
 ```{r example-tasks, fig.env = "figure", out.width="100%", fig.pos = "H", fig.cap = "Example trials from the tracing assessment and two drawing tasks."}
-knitr::include_graphics("figs/task_examples.png")
+knitr::include_graphics("figs/task_examples_updated.png")
 ```
@@
 ## Measuring drawing recognizability 
+```{r}
+# note: hard coding footnote so we don't have to load and join all model classificaitons on each render..
 
-### Human recognition scores
+# human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)
+
+```
+
 We measured the recognizability of each drawing via an online recognition experiment. 
@@
 We then computed a recognition score for each drawing, reflecting the proportion of participants who correctly identified the target category. 
+^[While in our pre-registration we planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel], we found that automated recognition scores were only modestly correlated with human recognition ($r$ = .4, p < .001) and that descriptive plots of the automated recognition scores revealed an overall difference between the two drawing tasks that was not evident in the human recognition data.
+To be conservative, we thus fit all of our models to the human recognition data.]
 
-### Automated recognition scores
-We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol. 
-To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 [@simonyan2014very], a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch [@paszke2017automatic].
-We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6). 
-Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization. 
-Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
-To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
-No additional metadata about the age of the child who produced each sketch was provided to the model. 
-This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing.
+<!-- ### Automated recognition scores -->
+<!-- We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol.  -->
+<!-- To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 [@simonyan2014very], a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch [@paszke2017automatic].
+-->
+<!-- We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6).  -->
+<!-- Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.  -->
+<!-- Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
+-->
+<!-- To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
+-->
+<!-- No additional metadata about the age of the child who produced each sketch was provided to the model. -->
+<!-- This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing. -->
 
 ## Statistical models
-```{r}
-human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)
-```
-
 To evaluate our main hypotheses, we fit generalized linear mixed-effects models to the human recognition scores to assess the factors that influenced the recognizability of the drawings that children produced.
@@
 Finally, we also assessed the degree to which tracing ability development differed across geographical sites, where tracing scores were modeled as a function of age (in years), site, and their interaction, with the same random-effects structure as the first model.
-
 This analysis plan was pre-registered at https://osf.io/qymjr.
-While we had initially planned to use automated recognition scores as our main dependent variable, following prior work [@long2021parallel], we found that these automated recognition scores were only modestly correlated with human recognition scores ($r$ = `r round(human_v_model$estimate,2)`, $t$ = `r round(human_v_model$statistic,2)`, p < .001); furthermore, descriptive plots of the automated recognition scores revealed an overall difference between the two drawing tasks that was not evident in the human recognition data.
-To be conservative, we thus fit all of our models to the human recognition data but have made all model predictions available to facilitate future research.
 
@@
 
-# frustratingly can't get anything with random slopes to converge!
 full_model_with_effort_out = summary(full_model_with_effort)
@@
 ```{r}
-site_difference <- glmer(cbind(num_correct, num_incorrect) ~ poly(scale(age_numeric),2)*site +
-                      (1 | unique_ids) +
-                      (1 | category),
-      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
-
-site_difference_out = summary(site_difference)
-
+# site_difference <- glmer(cbind(num_correct, num_incorrect) ~ poly(scale(age_numeric),2)*site +
+#                       (1 | unique_ids) +
+#                       (1 | category),
+#       data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+# 
+# 
+# site_difference_out = summary(site_difference)
 ```
@@
   group_by(age_numeric,condition, site) %>%
-  multi_boot_standard(col = "avg_cor")
+  multi_boot_standard(col = "avg_cor")  %>%
+  mutate(cond_by_site = as.factor(paste0(condition,', ',site)))
 
@@
   group_by(unique_ids,category,condition,age_numeric, site) %>%
-  summarize(avg_cor = mean(prop_correct))
+  summarize(avg_cor = mean(prop_correct)) %>%
+  mutate(cond_by_site = as.factor(paste0(condition,', ',site)))
 ```
@@
 Error bars show bootstrapped 95 percent cofnidence intervals."}
-ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = site)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
+ggplot(cor_by_age_by_site_by_cond, aes(age_numeric,mean, col = cond_by_site)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.4),size=.5) +
   geom_point(data = cor_by_age_by_site_by_cond_indiv, aes(x=age_numeric, y=avg_cor), position=position_jitterdodge(jitter.width = NULL,
   jitter.height = .001,
-  dodge.width = 0.2,
-  seed = 123), alpha=.05) +
-  theme_few(base_size = base_size_chosen) + 
+  dodge.width = 0.4,
+  seed = 123), alpha=.03, size=.5) +
+  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
+  theme_few(base_size = base_size_chosen, base_family = "Helvetica") + 
   labs(x='Age (in years)', y='Proportion drawings recognized') +
-  ylim(-.01,1.1) + 
-  geom_smooth(span=20, alpha=.1) +
-  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4) +
-  theme(legend.position = 'bottom') +
+  ylim(-.01,1.01) + 
+  geom_smooth(span=10, alpha=.1) +
+  # scale_color_viridis(discrete=TRUE, name="", option='B', begin=.2, end=.4) +
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(1,9,3,7)], name="") +
+    # scale_color_manual(values = natparks.pals("Banff", 7)[c(1,4,2,5)], name="") +
+  theme(legend.position = 'none', aspect.ratio=1.3) +
   geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
-  facet_grid(~condition)
+  facet_grid(~site)
+
+ggsave('figures_pdf/figure3_main_results.pdf',width=7.2, height=3, units='in')
 ```
@@
 # xtable(full_model_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")
+
+papaja::apa_table(full_model_out$coefficients, caption='"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.')
+
 ```
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
-  \hline
-Intercept & 1.39 & 0.16 & 8.51 & 0.000 \\ 
-  Task & 0.02 & 0.26 & 0.08 & 0.936 \\ 
-  Age & 1.16 & 0.14 & 8.59 & 0.000 \\ 
-  Site & 0.60 & 0.16 & 3.71 & 0.000 \\ 
-  Task*Age & -0.14 & 0.19 & -0.73 & 0.467 \\ 
-  Task*Site & -0.19 & 0.16 & -1.17 & 0.244 \\ 
-  Age*Site & 0.15 & 0.16 & 0.91 & 0.361 \\ 
-  Task*Age*Site & 0.06 & 0.16 & 0.38 & 0.706 \\ 
-   \hline
-\end{tabular}
-\caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.} 
-\end{table}
+<!-- \begin{table}[ht] -->
+<!-- \centering -->
+<!-- \begin{tabular}{rrrrr} -->
+<!--   \hline -->
+<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
+<!--   \hline -->
+<!-- Intercept & 1.39 & 0.16 & 8.51 & 0.000 \\  -->
+<!--   Task & 0.02 & 0.26 & 0.08 & 0.936 \\  -->
+<!--   Age & 1.16 & 0.14 & 8.59 & 0.000 \\  -->
+<!--   Site & 0.60 & 0.16 & 3.71 & 0.000 \\  -->
+<!--   Task*Age & -0.14 & 0.19 & -0.73 & 0.467 \\  -->
+<!--   Task*Site & -0.19 & 0.16 & -1.17 & 0.244 \\  -->
+<!--   Age*Site & 0.15 & 0.16 & 0.91 & 0.361 \\  -->
+<!--   Task*Age*Site & 0.06 & 0.16 & 0.38 & 0.706 \\  -->
+<!--    \hline -->
+<!-- \end{tabular} -->
+<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}  -->
+<!-- \end{table} -->
 
@@
 
+apa_table(full_model_with_effort_out$coefficients, caption='Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and estimates of children\'s tracing abilities.')
+
 # xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
@@
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
-  \hline
-Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\ 
-  Task & -0.04 & 0.26 & -0.16 & 0.873 \\ 
-  Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 
-  Site & 0.80 & 0.16 & 5.04 & 0.000 \\ 
-  Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\ 
-  Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\ 
-  Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\ 
-  Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\ 
-  Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\ 
-  Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\ 
-  Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\ 
-  Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\ 
-   \hline
-\end{tabular}
-\caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}
-\end{table}
+<!-- \begin{table}[ht] -->
+<!-- \centering -->
+<!-- \begin{tabular}{rrrrr} -->
+<!--   \hline -->
+<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
+<!--   \hline -->
+<!-- Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\  -->
+<!--   Task & -0.04 & 0.26 & -0.16 & 0.873 \\  -->
+<!--   Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 24 -->
+<!--   Site & 0.80 & 0.16 & 5.04 & 0.000 \\  -->
+<!--   Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\  -->
+<!--   Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\  -->
+<!--   Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\  -->
+<!--   Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\  -->
+<!--   Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\  -->
+<!--   Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\  -->
+<!--   Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\  -->
+<!--   Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\  -->
+<!--    \hline -->
+<!-- \end{tabular} -->
+<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}  -->
+<!-- \end{table} -->
 
@@
   group_by(age_numeric,condition, site) %>%
-  multi_boot_standard(col = "avg_draw_duration")
+  multi_boot_standard(col = "avg_draw_duration") %>%
+  mutate(cond_site = as.factor(paste0(condition,', ',site)))
 
@@
   group_by(age_numeric,condition, site) %>%
-  multi_boot_standard(col = "avg_num_strokes")
+  multi_boot_standard(col = "avg_num_strokes") %>%
+  mutate(cond_site = as.factor(paste0(condition,', ',site)))
 
@@
   group_by(age_numeric,condition, site) %>%
-  multi_boot_standard(col = "avg_intensity")
+  multi_boot_standard(col = "avg_intensity") %>%
+  mutate(cond_site = as.factor(paste0(condition,', ',site)))
 ```
@@
 ## Make compiled plot of descriptives
-base_size_chosen=12 # size of text in plots
+base_size_chosen=10 # size of text in plots
 smooth_alpha=.2
 
-p1=ggplot(draw_duration, aes(age_numeric,mean, color=condition)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
+p1=ggplot(draw_duration, aes(age_numeric,mean, color=cond_site)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5), size=.3) +
   theme_few(base_size = base_size_chosen) +
   labs(x='Age', y='Draw duration (s)') +
-  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
-  theme(legend.position = "bottom") + 
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(1,9,3,7)], name="") +
+  theme(legend.position = "none") + 
   ylim(0,30) +
+  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
   facet_grid(~site)
 
-p2=ggplot(avg_intensity, aes(age_numeric,mean, color=condition)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
+p2=ggplot(avg_intensity, aes(age_numeric,mean, color=cond_site)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5), size=.3) +
   theme_few(base_size = base_size_chosen) +
   labs(x='Age', y='Ink used (mean intensity)') +
-  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
-  theme(legend.position = "bottom") + 
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(1,9,3,7)], name="") +
+  theme(legend.position = "none") + 
+  scale_x_continuous(breaks=c(4,5,6,7,8,9))+
   ylim(.02,.08) +
@@
 
-p3=ggplot(num_strokes, aes(age_numeric,mean, color=condition)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5)) +
+p3=ggplot(num_strokes, aes(age_numeric,mean, color=cond_site)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = 0.5), size=.3) +
   theme_few(base_size = base_size_chosen) +
   labs(x='Age', y='Number of strokes') +
-  theme(legend.position = "bottom") +
-  scale_color_viridis(name="", discrete=TRUE, option='D', begin=.2, end=.8) +
+  theme(legend.position = "none") +
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(1,9,3,7)], name="") +
+  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
   ylim(0,15) +
@@
 cowplot::plot_grid(p1,p2,p3,nrow=1)
+ggsave('figures_pdf/figure5_efforts.pdf', width=7.2, units='in', height=2.4)
 ```
@@
 ggplot(tracing_scores, aes(x=age_numeric,y=mean, col=site)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
-  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=.1) +
+  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5, size=.3) +
   theme_few(base_size = base_size_chosen) +
   labs(x='Age', y='Tracing score') +
-  theme(legend.position = "none") +
-  geom_smooth(col='grey', span = 10,alpha=smooth_alpha)  +
+  theme(legend.position = "none", aspect.ratio=1.3) +
+  geom_smooth(span = 10,alpha=smooth_alpha, aes(group =site), size=.5)  +
+  scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
   facet_grid(~site) +
   ylim(-.1,4.1) +
-  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(2,8)])
+  # scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
+
+ggsave('figures_pdf/figure4_tracingscores.pdf',width=3, height=2.4, units='in')
 ```
@@
   multi_boot_standard(col = "avg_sub_cor")
+
+item_effects_with_condition<- d %>%
+  group_by(unique_ids,age_numeric,category,condition, site) %>%
+  summarize(avg_sub_cor = mean(prop_correct)) %>%
+  group_by(age_numeric,category, condition, site) %>%
+  multi_boot_standard(col = "avg_sub_cor") %>%
+  mutate(cond_by_site = as.factor(paste0(condition, ', ', site)))
 ```
 
-```{r item-effects, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=8, fig.cap = "Developmental trajectory of drawing recognizability for each category and for each geographical site.
-Error bars represent 95 percent bootstrapped confidence intervals."}
-ggplot(item_effects_not_spread, aes(x=as.numeric(age_numeric), y=mean, color=site)) +
+```{R}
+ggplot(item_effects_with_condition
+       , aes(x=as.numeric(age_numeric), y=mean, color=cond_by_site)) +
   geom_point(alpha=.8) +
@@
   theme(legend.position = 'bottom') +
-  scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
+    scale_color_manual(values = natparks.pals("Acadia", 9)[c(1,3,9,7)], name="") 
+```
+
+```{r item-effects, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=8, fig.cap = "Developmental trajectory of drawing recognizability for each category and for each geographical site.
+Error bars represent 95 percent bootstrapped confidence intervals."}
+ggplot(item_effects_not_spread, aes(x=as.numeric(age_numeric), y=mean, color=site)) +
+  geom_point(alpha=.6) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2), alpha=.8) +
+  theme_few(base_size = base_size_chosen) + 
+  ylim(0,1.01) + 
+  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
+  ylab('Proportion drawings recognized') +
+  xlab('Age (in years)') +
+  geom_abline(color = 'grey', intercept=0) +
+  geom_smooth(span=20, alpha=.1) +
+  facet_wrap(~category, nrow=2) +
+  theme(legend.position = 'none') +
+  scale_color_manual(values = natparks.pals("Acadia", 9)[c(2,8)])
+
+    # scale_color_manual(values = natparks.pals("Acadia", 9)[c(2,8)], name="") 
+  # scale_color_viridis(discrete=TRUE, name="", option='B', begin=0, end=.4)
+
+ggsave('figures_pdf/figure6_item_effects.pdf',width=7.2, height=2.6, units='in')
 ```
@@
 We found steady improvement from 4-9 years of age in both groups of children, replicating prior work conducted in a field setting [@long2021parallel].
-We did not find an effect of cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
+We did not find an effect of drawing cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
 
-<!-- Why might we have not observed an effect of cue type?
-In related work with adults, @yang2021 found that providing adults with photograph cues of these same categories led to more recognizable drawings of object categories.
-Thus, one possibility is that children have yet to develop the skill -->
+We also discovered that drawing recognizability differed between sites: children in the Beijing group produced more recognizable drawings than those in the San Jose group.
+While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.One idea is that children in the Beijing group drew at their preschool and elementary schools, whereas children in the San Jose group drew in a room at a children's science museum; these two testing environments could have created motivational differences that affected how much effort children put into their drawings.
+However, contra a strong version of this account, we found that the substantial individual variation in basic shape tracing ability and effort (as assessed via ink, time, and strokes spent while drwaing) was insufficient to account for differences in drawing recognizability between groups.
 
-We also discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group.
-In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
-We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+A second possibility is that the children who are learning to produce the complex, visually-demanding characters in the Chinese language that have meaningful subparts [@mcbride2016chinese; @mcbride2015learning] may develop more sophisticated visuomotor skills that are recruited while drawing.
+For example, the skills necessary to generate, combine, and arrange multiple shape parts in specific locations may be well-practiced by children learning to produce Chinese characters, and not well captured by the relatively simple shape tracing assessment that we used.
+Future work that relates writing, tracing, and drawing abilities within individual children learning to write different languages will be useful for understanding the degree to children's writing and drawing abilities inform each other more generally.
 
-While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
-Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @frank2021variability].
-On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality [@winner1989can; @kuwabara2016cultural].
-We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].
-
-Another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them.
+Finally, we also found that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+Indeed, another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them.
 For example, if some children are exposed to a wide variety of illustrations of some concepts but not others (e.g., in books or other media), they may also be able to produce more recognizable drawings of those concepts.
@@
 
-In sum, our findings advance our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
-More broadly, we believe our approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
+Thus, further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation [@amir2020cross; @carstensen2021investigating; @frank2021variability].
+On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality [@winner1989can; @kuwabara2016cultural].
+We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style [@gernhardt2015cultural; @senzaki2014holistic].
+
+Overall our result thus support a domain-specific account of the development of drawing abilities: children's ability to convey their knowledge about familiar visual concepts does not seem to be influenced by how they are cued to draw a given visual concept, and changes systematically across age in two different geographical contexts.
+We propose that further investigation into the factors that influence how children learn to identify and combine the relevant diagonstic features of different visual concepts will further explain individual and age-related variation in drawing abilities.
+More broadly, we believe that this approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
+
+<!-- further our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
+-->
 
@@
 
-\newpage
-
-```{r appendix, include = FALSE}
-render_appendix("appendix.Rmd")
-```
-
 # References
@@
 ```
+
+<!-- # Appendix A: Tracing Score Calculation -->
+
+<!-- To compute these error components, we applied an image registration algorithm, AirLab [@sandkuhler2018], to align each tracing to the target shape, yielding an affine transformation matrix that minimized the pixel-wise correlation distance between the aligned tracing, $T$, and the target shape, $S$: $Loss_{NCC} = - \frac{\sum S \cdot T - \sum E(S) E(T)}{N \sum Var(S) Var(T)}$, where $N$ is the number of pixels in both images.
+The shape error was defined by the final correlation distance between the aligned tracing and the target shape.
+The spatial error was defined by the magnitude of three distinct error terms: location, orientation, and size error, derived by decomposing the affine transformation matrix above into translation, rotation, and scaling components, respectively.
+In sum, this procedure yielded four error values for each tracing: one value representing the shape error (i.e., the pixel-wise correlation distance) and three values representing the spatial error (i.e., magnitude of translation, rotation, scaling components).
+-->
+
+<!-- We used the tracing quality ratings to obtained in @long2021parallel to assign weights to each of their error terms; adult observers ($N$=70) rated 1325 tracings (i.e., 50-80 tracings per shape per age) and evaluated “how well the tracing matches the target shape and is aligned to the position of the target shape” on a 5-point scale.
+An ordinal regression mixed-effects model to predict these 5-point ratings, which contained correlation distance, translation, rotation, scaling, and shape identity (square vs.
+star) as predictors, with random intercepts for rater.
+This model yielded parameter estimates that could then be used to score each tracing in the dataset; we averaged scores for both shapes to yield a single tracing score for each participant.
+-->
 

### 2022-07-21 writing/Manuscript_2022.tex
update latest version of manuscript and appendix

@@
 \documentclass[
-  english,
   man]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   pdftitle={Developmental consistency in children's drawings of object categories},
+  pdfauthor={Bria Long1, Ying Wang2, Stella Christie2, Michael C. Frank1, \& Judith E. Fan3},
   pdflang={en-EN},
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
   {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
 \makeatother
-\shorttitle{Development of drawing}
-\author{Bria Long\textsuperscript{1}, Ying Wang\textsuperscript{2}, Stella Christie\textsuperscript{2}, Michael C. Frank\textsuperscript{1}, \& Judith E. Fan\textsuperscript{3}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Stanford University\\\textsuperscript{2} Tsinghua University\\\textsuperscript{3} University of California, San Diego}
-\authornote{
 
-Correspondence concerning this article should be addressed to Bria Long, 450 Jane Stanford Way, Stanford CA 94305. E-mail: bria@stanford.edu}
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{children's drawings, visual production, tracing, object recognition, visuomotor control\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[shorthands=off,main=english]{babel}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
@@
 \title{Developmental consistency in children's drawings of object categories}
-
+\author{Bria Long\textsuperscript{1}, Ying Wang\textsuperscript{2}, Stella Christie\textsuperscript{2}, Michael C. Frank\textsuperscript{1}, \& Judith E. Fan\textsuperscript{3}}
 \date{}
 
-\abstract{
-Childen's drawings of common object categories become dramatically more recognziable across development.
+\shorttitle{Development of drawing}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Bria Long, 450 Jane Stanford Way, Stanford CA 94305. E-mail: \href{mailto:bria@stanford.edu}{\nolinkurl{bria@stanford.edu}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Stanford University\\\textsuperscript{2} Tsinghua University\\\textsuperscript{3} University of California, San Diego}
+
+\abstract{%
+Children's drawings of common object categories become dramatically more recognziable across development.
 What are the major factors that explain this developmental change?
-Here we examined the degree to which these developmental changes in recognizibility vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China), and with children's tracing abilities.
-To do so, we collecting digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
-Overall, we show broad consistency in these developmental trajectories across both drawing tasks and these two geographical locations, and we find that children's tracings abilites are good predictors of the recognizability of the drawings that they produce.
-In addition, we find that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to childen from San Jose, USA.
-Overall, this work suggests that the developmental trajectory of children's drawings are remarkably consistent and not easily explainable by changes in visuomotor control or working memory capacity.
+Here we examined the degree to which these developmental changes in recognizability vary across different drawing tasks (i.e.~drawing from observation vs.~from memory), geographical locations (San Jose, US vs.~Beijing, China), and with children's tracing abilities.
+To do so, we collected digital drawings of object categories (e.g., cat, airplane) from 4-9 year-olds (N=253).
+We found that the developmental trajectory of drawing recognizability was remarkably similar when children were asked to draw from observation vs.~memory and across these two geographical locations.
+In addition, we found that our Beijing sample produced more recognizable drawings but showed similar tracing abilities to children from San Jose, USA.
+Overall, this work suggests that the developmental trajectory of children's drawings is remarkably consistent and not easily explainable by changes in domain general changes in visuomotor control or working memory.
 }
@@
 Figurative drawings have long provided inspiration for scientists investigating children's emerging cognitive abilities (Minsky \& Papert, 1972), and accordingly a long history of work has examined changes in how children draw objects across development (Fury, Carlson, \& Sroufe, 1997; Karmiloff-Smith, 1990; Kellogg, 1969; Piaget, 1929).
-Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between target concepts (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
+Indeed, there appear to be dramatic changes in how children encode diagnostic visual information in their drawings across age: younger children (4-5 years) tend to include fewer cues in their drawings to differentiate between categories (e.g., \textit{adult} vs.~\textit{child}) than older children, who enrich their drawings with more diagnostic part (Sitton \& Light, 1992) and relational (Light \& Simmons, 1983) information.
 
@@
 A common view is that these changes are driven primarily by children's increasing ability to plan and control their motor movements (Freeman, 1987; Rehrig \& Stromswold, 2018).
-While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings --- including what children know about a given target object and how well children are able to access this conceptual knowledge when producing a drawing.
+While such changes in visuomotor control are clearly important, this view fails to account for other important constraints on children's drawings --- including what children know about a given visual concept and how well children are able to access this conceptual knowledge when producing a drawing.
 
@@
 Children's ability to access semantic knowledge about categories and to maintain this information in mind when producing a drawing likely changes across childhood (Pailian, Libertus, Feigenson, \& Halberda, 2016).
-Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant visual features of different categories: that is, when asked to \enquote{draw a {[}rabbit{]}}, they may struggle to conjure up the relevant visual details and then hold in mind what rabbits tend to look like.
+Here, we directly test the idea that a principal reason younger children produce less recognizable drawings is because they simply have more difficulty recalling the relevant visual features of different categories: that is, when asked to ``draw a {[}rabbit{]}'', they may struggle to conjure up the relevant visual details and then hold in mind what rabbits tend to look like.
 On this account, providing children with additional visual information about different categories -- for example, via canonical photographs of typical exemplars -- could help them improve their drawings of these categories, as it does with adults (Fan, Yamins, \& Turk-Browne, 2018).
@@
 
-To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when children were provided with a verbal cue (\enquote{Can you draw a {[}rabbit{]}?) versus when provided with a picture cue (}Can you draw this {[}rabbit{]} as it looks in the picture?\enquote{).
-On verbal-cue trials, children thus must access their mental representation of a}rabbit" and choose the features necessary to convey that object's identity.
+To tease apart these alternatives, we investigated the development of children's ability to produce recognizable drawings of visual concepts when children were provided with a verbal cue (``Can you draw a {[}rabbit{]}?) versus when provided with a picture cue (''Can you draw this {[}rabbit{]} as it looks in the picture?``).
+On verbal-cue trials, children thus must access their mental representation of a''rabbit'' and choose the features necessary to convey that object's identity.
 Conversely, on picture-cue trials, children are explicitly asked to rely on the visual features provided in a canonical photograph of each object category.
@@
 
-265 participants were recruited from two local children's museum in {[}BLINDED{]} and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
+265 participants were recruited from two local children's museum in San Jose and at preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area.
 Our goal was to recruit 120 children between 4-9 years of age after exclusions (i.e.~20 4-year-olds, 20 5-year-olds, etc.) at each geographical site.
 In the San Jose sample, 135 children participated in the experiment; 6 participants were excluded, (3) for skipping more than 6 drawing trials and (3) for scribbling three or more times in a row.
-Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of 121 children.
-In the Beijing sample, 132 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
+Six additional participants were tested but their data was not recorded due to a technical error, and two participants never advanced past the practice trials, leading to a final sample of 132 children.
+In the Beijing sample, 121 children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database.
 Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group.
@@
 
-Children were seated in front of a touchscreen tablet (Ipad Pro 12.9\enquote{) during each drawing session.
+Children were seated in front of a touchscreen tablet (Ipad Pro 12.9'') during each drawing session.
 At the beginning of the session, a trained experimenter first told each child, ``After this game is over, someone is going to try to recognize what you were trying to draw.
-So, please draw so that someone else could guess what you were trying to draw.}
+So, please draw so that someone else could guess what you were trying to draw.''
 A native English speaker gave these instructions to the San Jose sample, and a native Mandarin speaker gave a translation of these instructions to the Beijing sample.
@@
 The order in which each cue type was used was counterbalanced across children.
-On verbal-cue trials, children viewed a short video clip in which an experimenter named the target category: \enquote{What about a {[}cat{]}? Can you draw a {[}cat{]}?}.\\
-On picture-cue trials, children viewed a photograph of a typical exemplar of the target category while listening to an audio clip of the same experimenter who said, \enquote{What about this {[}cat{]}?
-Can you draw the {[}cat{]} as it looks in the picture?}
+On verbal-cue trials, children viewed a short video clip in which an experimenter named the target category: ``What about a {[}cat{]}? Can you draw a {[}cat{]}?''.\\
+On picture-cue trials, children viewed a photograph of a typical exemplar of the target category while listening to an audio clip of the same experimenter who said, ``What about this {[}cat{]}?
+Can you draw the {[}cat{]} as it looks in the picture?''
 The photograph remained on the screen for the duration of the drawing trial.
@@
 We recorded both the final drawings and the location of each stroke in a digital format, allowing us to precisely measure several different variables that provided proxies for the amount of effort children invested in producing each drawing.
-Specifically, we measured: (1) the amount of time spent (i.e., end time of last stroke --- start time of first stroke), (2) the number of individual strokes drawn, and (3) the amount of \enquote{ink} used (i.e., proportion of drawing canvas that was filled).
+Specifically, we measured: (1) the amount of time spent (i.e., end time of last stroke --- start time of first stroke), (2) the number of individual strokes drawn, and (3) the amount of ``ink'' used (i.e., proportion of drawing canvas that was filled).
 
@@
 Shape error reflects how closely the participant's tracing matched the contours of the target shape; the spatial error reflects how closely the location, size, and orientation of the participant's tracing matched the target shape.
-These two error components were computed automatically for each tracing and used to yield a \enquote{tracing score} for each tracing that mirrors adult human judgments of tracing quality (see Appendix for details).
+These two error components were computed automatically for each tracing and used to yield a ``tracing score'' for each tracing that mirrors adult human judgments of tracing quality (see Appendix for details).
 
@@
 Each subset of drawings was balanced with respect to age, category, and site, and each drawing was shown to 10 participants.
-Participants were shown these drawings in a random sequence and asked \enquote{What does this look like?}
+Participants were shown these drawings in a random sequence and asked ``What does this look like?''
 Participants selected their responses from the set of 12 categories and were encouraged to provide their best guess if they were unsure.
@@
 In a secondary analysis, we investigated the degree to which any of the above effects were mediated by children's tracing abilities or the amount of effort that children expended while drawings.
-We fit the same model above with additional fixed-effects terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of \enquote{ink} used (i.e.~percentage of non-white pixels in the drawn image), and the number of strokes produced.
+We fit the same model above with additional fixed-effects terms for each child's estimated tracing score (see Measuring Tracing Abilities), the time that child spent drawing (in seconds), the amount of ``ink'' used (i.e.~percentage of non-white pixels in the drawn image), and the number of strokes produced.
 These additional predictors were first z-scored before being included in the model.
@@
 We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work using the verbal-cue paradigm under less controlled settings (Long et al., 2021).
-Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph (\enquote{Draw this rabbit as it looks in the picture}) as when they were cued with the category label (\enquote{Can you draw a rabbit?}).\\
+Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph (``Draw this rabbit as it looks in the picture'') as when they were cued with the category label (``Can you draw a rabbit?'').\\
 While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar, as adult participants do (Yang \& Fan, 2021), we did not find evidence of an interaction between age and cue type.
@@
 Insofar as differences in visuomotor control could explain differences between groups, we reasoned that this would manifest as a difference in tracing ability that predicts variation in drawing recognizability.
-Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizablity of their own drawings, as in prior work (Long et al., 2021).
+Instead, we found that children across the two sites were indistinguishable with respect to tracing ability on average (Figure \ref{fig:tracing}), although individual tracing scores were strong predictors of the recognizability of their own drawings, as in prior work (Long et al., 2021).
 Next, we evaluated whether there were systematic differences in effort between the two groups, as measured by the amount of time each child spent producing their drawings and the number of strokes drawn.
@@
   Task & -0.04 & 0.26 & -0.16 & 0.873 \\ 
-  Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 
+  Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 24
   Site & 0.80 & 0.16 & 5.04 & 0.000 \\ 
@@
 Here we examined developmental change in children's ability to produce recognizable drawings of familiar visual concepts, and the degree to which this ability is constrained by retrieval of diagnostic attributes from memory.
-We manipulated memory demands by either cueing children with a category label (\enquote{Can you draw a {[}cat{]}?}) or a color photo (\enquote{Can you draw this {[}cat{]} as it looks in the picture?}), and measured the recognizability of each drawing to adult observers.
+We manipulated memory demands by either cueing children with a category label (``Can you draw a {[}cat{]}?'') or a color photo (``Can you draw this {[}cat{]} as it looks in the picture?''), and measured the recognizability of each drawing to adult observers.
 To evaluate the generality of our findings, we recruited two groups of children in different sites: San Jose, USA and Beijing, China.
 We found steady improvement from 4-9 years of age in both groups of children, replicating prior work conducted in a field setting (Long et al., 2021).
-We did not find an effect of cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
+We did not find an effect of drawing cue type, however, suggesting that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
 
-We also discovered that drawing recognizability differed between sites, with children in the Beijing group having produced more recognizable drawings than those in the San Jose group.
-In follow-up analyses, we found that while there was substantial individual variation in tracing ability and effort, these covariates were insufficient to account for differences in drawing recognizability between groups.
-We also discovered that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+We also discovered that drawing recognizability differed between sites: children in the Beijing group produced more recognizable drawings than those in the San Jose group.
+While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.One idea is that children in the Beijing group drew at their preschool and elementary schools, whereas children in the San Jose group drew in a room at a children's science museum; these two testing environments could have created motivational differences that affected how much effort children put into their drawings.
+However, contra a strong version of this account, we found that the substantial individual variation in basic shape tracing ability and effort (as assessed via ink, time, and strokes spent while drwaing) was insufficient to account for differences in drawing recognizability between groups.
 
-While these group-level differences are intriguing, they remain consistent with wide variety of potential explanations.
-Further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation ({\textbf{???}}; Amir \& McAuliffe, 2020; Carstensen, Cao, Gao, \& Frank, 2021).
-On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality (Kuwabara \& Smith, 2016; Winner, 1989).
-We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style (Gernhardt, Rübeling, \& Keller, 2015; Senzaki, Masuda, \& Nand, 2014).
+A second possibility is that the children who are learning to produce the complex, visually-demanding characters in the Chinese language that have meaningful subparts C.
+McBride \& Wang (2015) may develop more sophisticated visuomotor skills that are recruited while drawing.
+For example, the skills necessary to generate, combine, and arrange multiple shape parts in specific locations may be well-practiced by children learning to produce Chinese characters, and not well captured by the relatively simple shape tracing assessment that we used.
+Future work that relates writing, tracing, and drawing abilities within individual children learning to write different languages will be useful for understanding the degree to children's writing and drawing abilities inform eachother more generally.
 
-Another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them.
+Finally, we also found that the groups differed with respect to which visual concepts were easier for children to convey in their drawings, perhaps reflecting different patterns of exposure to these concepts.
+Indeed, another natural question for future work concerns the relationship between the kind of experience children have with these visual concepts and the way they produce drawings of them.
 For example, if some children are exposed to a wide variety of illustrations of some concepts but not others (e.g., in books or other media), they may also be able to produce more recognizable drawings of those concepts.
@@
 
-In sum, our findings advance our understanding of the relative impact of age, task settings, and geographical context on the ability of children to communicate their knowledge about familiar visual concepts by drawing.
-More broadly, we believe our approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
+Thus, further systematic measurement of drawing behavior across a wider variety of geographical, socioeconomic, and cultural contexts will be crucial for producing more robust and precise estimates of developmental variability, critical to strongly evaluate causal theories of such variation (Amir \& McAuliffe, 2020; Carstensen, Cao, Gao, \& Frank, 2021; Frank, Braginsky, Yurovsky, \& Marchman, 2021).
+On the other hand, without such datasets it can be tempting to draw unwarranted causal inferences about the impact of single demographic covariates, such as nationality (Kuwabara \& Smith, 2016; Winner, 1989).
+We have thus made our drawing dataset publicly available to contribute to this more cumulative effort and also to reduce barriers to investigation of other aspects of these drawings other than their recognizability, such as which visual features children prioritized in their drawings, the order in which they drew them, as well as variation in visual style (Gernhardt, Rübeling, \& Keller, 2015; Senzaki, Masuda, \& Nand, 2014).
+
+Overall our result thus support a domain-specific account of the development of drawing abilities: children's ability to convey their knowledge about familiar visual concepts does not seem to be influenced by how they are cued to draw a given visual concept, and changes systematically across age in two different geographical contexts.
+We propose that further investigation into the factors that influence how children learn to identify and combine the relevant diagonstic features of different visual concepts will further explain individual and age-related variation in drawing abilities.
+More broadly, we believe that this approach to concurrently quantifying multiple sources of variation in the context of rich, naturalistic behaviors will lead to more robust and unified theories of cognitive development.
 
@@
 {[}BLINDED{]}
-
-\newpage
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-amir2020cross}{}%
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-amir2020cross}{}}%
 Amir, D., \& McAuliffe, K. (2020). Cross-cultural, developmental psychology: Integrating approaches and key insights. \emph{Evolution and Human Behavior}, \emph{41}(5), 430--444.
 
-\leavevmode\hypertarget{ref-barrett1976symbolism}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-barrett1976symbolism}{}}%
 Barrett, M., \& Light, P. (1976). Symbolism and intellectual realism in children's drawings. \emph{British Journal of Educational Psychology}, \emph{46}(2), 198--202.
 
-\leavevmode\hypertarget{ref-bloom1998intention}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bloom1998intention}{}}%
 Bloom, P., \& Markson, L. (1998). Intention and analogy in children's naming of pictorial representations. \emph{Psychological Science}, \emph{9}(3), 200--204.
 
-\leavevmode\hypertarget{ref-bremmer1984prior}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bremmer1984prior}{}}%
 Bremner, J.
@@
 
-\leavevmode\hypertarget{ref-carstensen2021investigating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-carstensen2021investigating}{}}%
 Carstensen, A., Cao, A., Gao, S., \& Frank, M.
@@
 Investigating cross-cultural differences in reasoning, vision, and social cognition through replication.
-In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol.
-43).
+\emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{43}.
 
-\leavevmode\hypertarget{ref-cohn2012explaining}{}%
-Cohn, N. (2012). Explaining ``i can't draw'': Parallels between the structure and development of language and drawing. \emph{Human Development}, \emph{55}(4), 167--192.
+\leavevmode\vadjust pre{\hypertarget{ref-cohn2012explaining}{}}%
+Cohn, N. (2012). Explaining {``i can't draw''}: Parallels between the structure and development of language and drawing. \emph{Human Development}, \emph{55}(4), 167--192.
 
-\leavevmode\hypertarget{ref-dekker2011dorsal}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-dekker2011dorsal}{}}%
 Dekker, T., Mareschal, D., Sereno, M.
@@
 
-\leavevmode\hypertarget{ref-fan2018common}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-fan2018common}{}}%
 Fan, J. E., Yamins, D. L., \& Turk-Browne, N. B. (2018). Common object representations for visual production and recognition. \emph{Cognitive Science}, \emph{42}(8), 2670--2698.
 
-\leavevmode\hypertarget{ref-freeman1987current}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-frank2021variability}{}}%
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2021). \emph{Variability and consistency in early language learning: The wordbank project}. MIT Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-freeman1987current}{}}%
 Freeman, N. H. (1987). Current problems in the development of representational picture-production. \emph{Archives de Psychologie}.
 
-\leavevmode\hypertarget{ref-fury1997children}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-fury1997children}{}}%
 Fury, G., Carlson, E. A., \& Sroufe, A. (1997). Children's representations of attachment relationships in family drawings. \emph{Child Development}, \emph{68}(6), 1154--1164.
 
-\leavevmode\hypertarget{ref-gernhardt2015cultural}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gernhardt2015cultural}{}}%
 Gernhardt, A., Rübeling, H., \& Keller, H.
@@
 
-\leavevmode\hypertarget{ref-hoffmann2018u}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hoffmann2018u}{}}%
 Hoffmann, D.
@@
 
-\leavevmode\hypertarget{ref-huntsinger2011cultural}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-huntsinger2011cultural}{}}%
 Huntsinger, C.
@@
 
-\leavevmode\hypertarget{ref-karmiloff1990constraints}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-karmiloff1990constraints}{}}%
 Karmiloff-Smith, A. (1990). Constraints on representational change: Evidence from children's drawing. \emph{Cognition}, \emph{34}(1), 57--83.
 
-\leavevmode\hypertarget{ref-kellogg1969analyzing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kellogg1969analyzing}{}}%
 Kellogg, R. (1969). \emph{Analyzing children's art}. National Press Books Palo Alto, CA.
 
-\leavevmode\hypertarget{ref-kuwabara2016cultural}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kuwabara2016cultural}{}}%
 Kuwabara, M., \& Smith, L. B. (2016). Cultural differences in visual object recognition in 3-year-old children. \emph{Journal of Experimental Child Psychology}, \emph{147}, 22--38.
 
-\leavevmode\hypertarget{ref-la2001children}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-la2001children}{}}%
 La Voy, S.
@@
 
-\leavevmode\hypertarget{ref-light1983effects}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-light1983effects}{}}%
 Light, P., \& Simmons, B.
@@
 
-\leavevmode\hypertarget{ref-long2021parallel}{}%
-Long, B., Fan, J., Chai, Z., \& Frank, M. C. (2021). Parallel developmental changes in children's drawing and recognition of visual concepts.
+\leavevmode\vadjust pre{\hypertarget{ref-long2021parallel}{}}%
+Long, B., Fan, J., Chai, Z., \& Frank, M. C. (2021). \emph{Parallel developmental changes in children's drawing and recognition of visual concepts}.
 
-\leavevmode\hypertarget{ref-long2018drawings}{}%
-Long, B., Fan, J., \& Frank, M. C. (2018). Drawings as a window into developmental changes in object representations. In \emph{Proceedings of the 40th annual meeting of the cognitive science society}.
+\leavevmode\vadjust pre{\hypertarget{ref-long2018drawings}{}}%
+Long, B., Fan, J., \& Frank, M. C. (2018). Drawings as a window into developmental changes in object representations. \emph{Proceedings of the 40th Annual Meeting of the Cognitive Science Society}.
 
-\leavevmode\hypertarget{ref-luquet1927dessin}{}%
-Luquet, G.-H. (1927). Le dessin enfantin.(Bibliothèque de psychologie de l" enfant et de pédagogie.).
+\leavevmode\vadjust pre{\hypertarget{ref-luquet1927dessin}{}}%
+Luquet, G.-H. (1927). \emph{Le dessin enfantin.(biblioth{è}que de psychologie de l" enfant et de p{é}dagogie.).}
 
-\leavevmode\hypertarget{ref-minsky1972artificial}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mcbride2016chinese}{}}%
+McBride, C.
+A.
+(2016).
+Is chinese special?
+Four aspects of chinese literacy acquisition that might distinguish learning chinese from learning alphabetic orthographies.
+\emph{Educational Psychology Review}, \emph{28}(3), 523--549.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcbride2015learning}{}}%
+McBride, C., \& Wang, Y. (2015). Learning to read chinese: Universal and unique cognitive cores. \emph{Child Development Perspectives}, \emph{9}(3), 196--200.
+
+\leavevmode\vadjust pre{\hypertarget{ref-minsky1972artificial}{}}%
 Minsky, M., \& Papert, S. (1972). \emph{Artificial intelligence progress report}. Cambridge, MA, USA: Massachusetts Institute of Technology.
 
-\leavevmode\hypertarget{ref-natu2016development}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-natu2016development}{}}%
 Natu, V.
@@
 
-\leavevmode\hypertarget{ref-pailian2016visual}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pailian2016visual}{}}%
 Pailian, H., Libertus, M.
@@
 
-\leavevmode\hypertarget{ref-paszke2017automatic}{}%
-Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., \ldots{} Lerer, A. (2017). Automatic differentiation in pytorch.
+\leavevmode\vadjust pre{\hypertarget{ref-paszke2017automatic}{}}%
+Paszke, A., Gross, S., Chintala, S., Chanan, G., Yang, E., DeVito, Z., \ldots{} Lerer, A. (2017). \emph{Automatic differentiation in PyTorch}.
 
-\leavevmode\hypertarget{ref-piaget1929child}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-piaget1929child}{}}%
 Piaget, J. (1929). The child's concept of the world. \emph{Londres, Routldge \& Kegan Paul}.
 
-\leavevmode\hypertarget{ref-rehrig2018does}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rehrig2018does}{}}%
 Rehrig, G., \& Stromswold, K.
 (2018).
-What does the dap: IQ measure?: Drawing comparisons between drawing performance and developmental assessments.
+What does the DAP: IQ measure?: Drawing comparisons between drawing performance and developmental assessments.
 \emph{The Journal of Genetic Psychology}, \emph{179}(1), 9--18.
 
-\leavevmode\hypertarget{ref-senzaki2014holistic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-senzaki2014holistic}{}}%
 Senzaki, S., Masuda, T., \& Nand, K.
@@
 
-\leavevmode\hypertarget{ref-simonyan2014very}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-simonyan2014very}{}}%
 Simonyan, K., \& Zisserman, A. (2014). Very deep convolutional networks for large-scale image recognition. \emph{arXiv Preprint arXiv:1409.1556}.
 
-\leavevmode\hypertarget{ref-sitton1992drawing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sitton1992drawing}{}}%
 Sitton, R., \& Light, P. (1992). Drawing to differentiate: Flexibility in young children's human figure drawings. \emph{British Journal of Developmental Psychology}, \emph{10}(1), 25--33.
 
-\leavevmode\hypertarget{ref-willats2006making}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-willats2006making}{}}%
 Willats, J. (2006). \emph{Making sense of children's drawings}. Psychology Press.
 
-\leavevmode\hypertarget{ref-winner1989can}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-winner1989can}{}}%
 Winner, E. (1989). How can chinese children draw so well? \emph{Journal of Aesthetic Education}, \emph{23}(1), 41--63.
 
-\leavevmode\hypertarget{ref-yang2021visual}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-yang2021visual}{}}%
 Yang, J., \& Fan, J. E. (2021). Visual communication of object concepts at different levels of abstraction. \emph{arXiv Preprint arXiv:2106.02775}.
 
+\end{CSLReferences}
+
 \end{document}

### 2022-07-21 writing/appendix_sep.Rmd
update latest version of manuscript and appendix

--- 2021-11-10 writing/appendix.Rmd
@@
 title: Appendix 
-output:
-  pdf_document: default
+author: 
+  - name          : "Blinded"
+documentclass     : "docx"
+classoption       : "man"
+output            : papaja::apa6_doc
+bibliography      : ["references.bib"]
+
 ---
@@
 ```{r}
+knitr::opts_chunk$set(fig.crop = FALSE, 
+                      fig.path='figs/', echo=FALSE, warning = FALSE, 
+                      cache=FALSE, message = FALSE, sanitize = TRUE)
+```
+
+```{r}
+library(papaja)
 library(tidyverse)
@@
 
-Tracing Scores
+# Tracing Scores
 

### 2022-07-21 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
reorg get drawings folder to add scripts to get svg strokes

@@
 ```{r}
+recopy=FALSE
+if (recopy){
 file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
+}
 ```
@@
 ```{r}
+if (recopy){
 file.copy(fs::path(drawing_path, tracings_to_include$fullPath), fs::path(compiled_tracing_dataset_path, tracings_to_include$better_filename))
+}
 ```

### 2022-07-21 analysis/step1_get_drawings/preprocess_sketches.Rmd
reorg get drawings folder to add scripts to get svg strokes

---
title: "preprocess_sketches CDM"
author: "Bria Long"
date: "9/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(assertthat)
library(knitr)
library(here)
library(lubridate)
```

```{r}
drawing_path = here::here('data/CDM/drawings/full_set/')
filtered_dataset_path =  here::here('data/CDM/drawings/object_drawings')
dir.create(filtered_dataset_path)

compiled_dataset_path = here::here('data/compiled/drawings/object_drawings')
# dir.create(filtered_dataset_path)
dir.create(compiled_dataset_path)
```

```{r}
all_drawings = list.files(path=drawing_path, pattern = ".png$", recursive = TRUE) %>%
    as_tibble()  %>%
    rename(fullPath = value)

practice_categories = c('triangle','this shape','this square','rectangle')

drawing_info = all_drawings %>%
    mutate(fileNameShort = str_split_fixed(fullPath,"/",2)[,2]) %>%
    mutate(condition = str_split_fixed(fileNameShort,"_",2)[,1]) %>%
    mutate(category = str_split_fixed(fileNameShort,"_",3)[,2]) %>%
    mutate(id = str_split_fixed(fileNameShort,"_",4)[,4]) %>%
   select(fileNameShort, fullPath, category, condition) %>%
  filter(!category %in% practice_categories)

```

# copy all drawings and rename
```{r}
file.copy(fs::path(drawing_path, drawing_info$fullPath), fs::path(filtered_dataset_path, drawing_info$fileNameShort))

file.copy(fs::path(drawing_path, drawing_info$fullPath), fs::path(compiled_dataset_path, drawing_info$fileNameShort))

```

### 2022-07-21 analysis/step2_clean_metadata/merge_metadata_and_svgs.Rmd
reorg get drawings folder to add scripts to get svg strokes

---
title: "merge_metadata_with_svgs"
author: "Bria Long"
date: '2022-05-25'
output: html_document
---

```{r, libraries}
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(langcog)
library(stringr)
library(here)
theme_set(theme_few())
```

```{r}
meta = read_csv(here::here('data/compiled/metadata/final_merged_metadata.csv'))
```
```{r}
practice_categories = c('triangle','this shape','this square','rectangle')
```

# And now merge with stroke data and resave cleaned versions
```{r}
cdm <- read_csv(here::here('data/CDM/strokes_raw/CDM_photodraw_e2_svg_output2022.csv'))
thu <- read_csv(here::here('data/THU/strokes_raw/THU_photodraw_e2_svg_output2022.csv'))
```

```{r}
all_svgs <- cdm %>%
  select(-'...1') %>%
  mutate(age = as.double(str_split_fixed(age,'age',2)[,2])) %>%
  full_join(thu %>% select(-'...1')) %>%
  select(-filename) %>%
  rename(age_numeric = age)
```

```{r}
missing_subs <- meta %>%
  filter(subID %in% all_svgs$subID) %>%
  distinct(subID)
```

```{r}
all_svgs_with_meta <- all_svgs %>%
  left_join(meta %>% select(-age))
```

### 2022-07-21 analysis/step2_clean_metadata/merge_svg_datasets.Rmd
reorg get drawings folder to add scripts to get svg strokes

---
title: "Examine_photodraw_classifications"
author: "Bria Long"
date: "4/2021"
output: html_document
---

```{r, libraries}
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(langcog)
library(stringr)
library(here)
theme_set(theme_few())
```

```{r}
cdm_strokes <- read_csv(here::here('data/CDM/strokes_raw/CDM_photodraw_e2_svg_output2022.csv')) %>%
  select(-filename, -`...1`) %>%
  mutate(session_id = str_split_fixed(session_id, 'CDM_', 2)[,2]) %>%
  mutate(unique_ids = session_id) %>%
  select(-session_id)
```

## Get THU strokes wtih cleaned subid as column
```{r}
thu_joined <- read_csv(here::here('data/THU/strokes_raw/THU_photodraw_e2_svg_output_May2022.csv')) %>%
  select(-filename, -`...1`, -subID) %>%
  rename(unique_ids = subID_cleaned)

length(unique(thu_joined$unique_ids))

```

### Weren't enough subs -- error in subid reading..
Discovered that the subid raw column had spaces that had gotten edited back out, so went through and rewrote stsrokes for those subs
```{r}
# issues <-read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
#   filter(!ID_Database %in% thu_strokes$subID)

```

```{r}
# what<-read_csv(here::here('data/THU/strokes_raw/THU_photodraw_e2_svg_output_May2022.csv'))
#   # filter(is.na(subID))
```

## Import extra strokes
```{r}
all_thu<-read_csv(here::here('data/THU/strokes_raw/THU_photodraw_e2_svg_output_June2022_spaces_added.csv')) %>%
  select(-filename, -`...1`, -subID) %>%
  rename(unique_ids = subID_cleaned) %>%
  full_join(thu_joined)
```
## check subjects
```{r}
length(unique(all_thu$unique_ids))
```

## Join processed thu and cdm data
```{r}
all_strokes <- all_thu %>%
  full_join(cdm_strokes %>% mutate(age = as.double(str_split_fixed(age,'age',2)[,2]))) %>%
  select(-subID) %>%
  filter(! category %in% c('this square','this shape','rectangle','triangle')) %>%
  # P_car_sketch_age5_IPAD3_THU5M7.png
  mutate(filename = paste0(condition,'_',category,'_sketch_age',floor(age),'_', unique_ids,'.png'))
```

## Save it out
```{r}
write_csv(all_strokes,here::here('data/compiled/strokes_preprocessed/all_strokes.csv'))
```

### Compare to metadata

```{r}
# load and clean up "category" for tracing trials
all_meta <- read.csv(here::here('data/compiled/metadata/final_merged_metadata.csv')) %>%
    mutate(category = as.character(category)) %>%
    mutate(category = case_when(category == 'this square' ~ 'square',
                                category == 'this shape' ~ 'shape',                                
                                TRUE ~ as.character(category)))

# subIDs are unique identifier in recognition data for THU, session_ids in CDM data
meta_thu <- all_meta %>%
  filter(site=='THU') %>%
  mutate(unique_ids = subID) %>%
  mutate(draw_duration = draw_duration / 1000) # in ms for thu, whoops

meta_cdm <- all_meta %>%
  filter(site=='CDM') %>%
  mutate(unique_ids = session_id)

## unique IDs are now the identifier which will be used to join with machine/human recognition data
all_meta_cleaned <- meta_cdm %>%
  full_join(meta_thu) 
```

```{r}
unique_ids_strokes = unique(all_strokes$unique_ids)
unique_ids_meta = unique(all_meta_cleaned$unique_ids)
sort(unique_ids_strokes) == sort(unique_ids_meta)
```

```{r}
# Make sure we have all the right filenames
meta_filenames= sort(unique(all_meta_cleaned$filename))
strokes_filenames= sort(unique(all_strokes$filename))
length(strokes_filenames)
length(meta_filenames)

missing <- all_meta_cleaned %>%
  filter(!category %in% c('square','shape','rectangle','triangle')) %>% # exclude shapes
  mutate(filename_check = paste0(condition,'_',category,'_sketch_age',floor(age_numeric),'_', unique_ids,'.png')) %>%
  filter(!filename_check %in% strokes_filenames)

# Draiwngs from the 2 10-year-olds -- have 'age9' so don't get the exact filename match with variables

```

```{r}
# missing_subs = unique(missing$subID)
# 
# missing_subs_demo <-read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
#   filter(ID_Database %in% missing_subs)

```

### 2022-07-21 analysis/step1_get_drawings/THU_Drawings/1_download_sketches/render_svgs.py

@@ -35,6 +35,7 @@ if not os.path.exists(sketch_dir):
 
 session_id = []
 subID=[]
+subID_cleaned=[]
 age=[]
 category = []
 condition=[] 
@@ -44,16 +45,19 @@ svg = []
 stroke_count = [] 
 
 ### read in valid sessions csv
-subject_log_csv= '/Users/brialong/Documents/GitHub/devphotodraw/data/THU/demographics/final_subject_info.csv'
+# subject_log_csv= '/Users/brialong/Documents/GitHub/devphotodraw/data/THU/demographics/final_subject_info.csv'
+subject_log_csv= '/Users/brialong/Documents/GitHub/d evphotodraw/data/THU/strokes_raw/to_add_space.csv'
 subject_log = pd.read_csv(subject_log_csv)
 total_sessions = subject_log['ID_Database_raw']
 age_data = subject_log['Age']
+cleaned_subids = subject_log['ID_Database'] 
 count_sub=0
 
 
 
 for s in total_sessions:
     sub_age = age_data[count_sub]
+    sub_cleaned_subids = cleaned_subids[count_sub]
     count_sub = count_sub + 1
     print 'rendering for {}, gone through {} of {} subs'.format(s, count_sub, np.size(total_sessions))
     img_recs_selector = {'selector': {'dataType':'finalImage', 'subID': s}}
@@ -61,6 +65,14 @@ for s in total_sessions:
     image_recs = sorted(img_recs_temp, key=lambda image: image['endTrialTime'])
     
     print 'found {} images for {}'.format(np.size(image_recs), s)
+    if np.size(image_recs)==0:
+        s=s + ' '
+        print('added space')
+        img_recs_selector = {'selector': {'dataType':'finalImage', 'subID': s}}
+        img_recs_temp = db.find(img_recs_selector)
+        image_recs = sorted(img_recs_temp, key=lambda image: image['endTrialTime'])
+        print 'found {} images for {}'.format(np.size(image_recs), s)
+
     for imrec in image_recs:  
         stroke_recs = {'selector': {'dataType':'stroke','category':imrec['category'], 'subID': s}}
         stroke_recs_temp = db.find(stroke_recs) 
@@ -83,6 +95,7 @@ for s in total_sessions:
                             svg.append(this_svg)
                             stroke_count.append(this_stroke)
                             subID.append(s)
+                            subID_cleaned.append(sub_cleaned_subids)
                             session_id.append(imrec['sessionId'])        
[…]

### 2022-07-21 analysis/step6_main_analyses/clip_classifications.Rmd
scripts for getting devphotodraw clip features

---
title: "clip_classifications"
author: "Bria Long"
date: '2022-05-17'
output: html_document
---

## Load libraries
```{r}
library(tidyverse)
library(here)
library(assertthat)
library(langcog)
library(ggthemes)
library(knitr)
library(lmerTest)
library(lme4)

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

## Load data
### Compiled classification data
```{r load-classifications}
# classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
#   as_tibble() %>%
#   mutate(age_numeric = age) %>%
#   mutate(age = paste('age',age,sep="")) %>%
#   mutate(age = as.factor(age)) %>%
#   mutate(category = target_label) %>% 
#   dplyr::select(-X, -X.1, -index) %>%
#   mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
#                            !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
#   mutate(site = as.factor(site)) 
```

### Load metadata
```{r}
# load and clean up "category" for tracing trials
all_meta <- read.csv(here::here('data/compiled/metadata/final_merged_metadata.csv')) %>%
    mutate(category = as.character(category)) %>%
    mutate(category = case_when(category == 'this square' ~ 'square',
                                category == 'this shape' ~ 'shape',                                
                                TRUE ~ as.character(category)))

# subIDs are unique identifier in recognition data for THU, session_ids in CDM data
meta_thu <- all_meta %>%
  filter(site=='THU') %>%
  mutate(unique_ids = subID) %>%
  mutate(draw_duration = draw_duration / 1000) # in ms for thu, whoops

meta_cdm <- all_meta %>%
  filter(site=='CDM') %>%
  mutate(unique_ids = session_id)

## unique IDs are now the identifier which will be used to join with machine/human recognition data
all_meta_cleaned <- meta_cdm %>%
  full_join(meta_thu)

```

```{r}
all_meta_cleaned <- all_meta_cleaned %>%
  select(-age) %>%
  rename(age = age_numeric)
```

### Load clip classifications
```{R}
clip_features <- read.csv(here::here('data/compiled/clip_classifications/CLIP_FEATURES_kid_photodraw_compiled_drawing_cue.csv'), header=TRUE) %>%
  as_tibble()

clip_meta <- read.csv(here::here('data/compiled/clip_classifications/CLIP_METADATA_batch32_kid.csv')) %>%
  as_tibble() %>%
  rename(category = label, session_id = session)

all_clip = clip_features %>%
  right_join(clip_meta, by=c('X')) 
```

#### Make long form clip data
```{r}
clip_long <- all_clip %>%
  rename(kid_age = age, site = condition, unique_ids = session_id) %>%
  select(-X) %>%
  pivot_longer(cols = cat:tree, names_to  = "guessed_category", values_to ="prob")  %>%
  mutate(guessed_category = factor(guessed_category)) %>%
  mutate(category = factor(category))
```

```{r}
# test_image = 'P_airplane_sketch_age8_IPAD2_THU8F12.png'
# test_session_id = 'IPAD2_THU8F12'

# test_image_clip <- all_clip %>%
  # filter(session_id == test_session_id & category=='airplane')
```

```{r}
clip_by_image <- clip_long %>%
  group_by(kid_age, unique_ids, category) %>%
  summarize(max_prob = max(prob), clip_category = guessed_category[prob == max_prob]) %>%
  mutate(correct_or_not = (category == clip_category)) %>%
  left_join(all_meta_cleaned)
```

```{r}
count_images <- clip_by_image %>% 
  group_by(kid_age, category) %>%
  summarize(count = n())

check <- clip_by_image %>% 
  filter(is.na(condition))

sum(count_images$count) # sanity
```

```{r}
clip_target_category_prob_by_age_by_category <- clip_long %>%
  filter(category == guessed_category) %>%
  group_by(category, kid_age) %>%
  multi_boot_standard(col = 'prob')

target_category_prob_by_age <- clip_target_category_prob_by_age_by_category %>%
  group_by(kid_age) %>%
  multi_boot_standard(col = 'mean')
```

```{r}
clip_correct_category_by_age <- clip_by_image %>%
   mutate(age_numeric = as.double(kid_age)) %>%
  mutate(age_numeric = case_when(age_numeric == 10 ~ 9, # merge 2 10-year-olds into THU data for 9-year-olds
                                 TRUE ~ age_numeric)) %>%
  group_by(category, age_numeric) %>%
  multi_boot_standard(col = 'correct_or_not') 
```

```{r}
ggplot(clip_correct_category_by_age, aes(x=age_numeric, y=mean, col=age_numeric)) +
  geom_pointrange(aes(y=mean, ymin = ci_lower, ymax = ci_upper), alpha=.3)+
  geom_point(alpha=.6) +
  # geom_line(data = clip_correct_category_by_age, alpha=.4, aes(group=category))+
  geom_smooth(alpha=.01, color='grey', span=2) +
  labs(x='Age of child drawing (yrs)', y='CLIP classification accuracy') +
  theme_few() + 
  scale_x_continuous(breaks = seq(2,10,1)) + 
  scale_color_viridis(option="D", breaks=seq(2,10,1)) +
  theme(legend.position= 'none') +
  facet_wrap(~category)

```

### Load human classification data
```{r}
humans <- read.csv(here::here('data/compiled/recognition_ratings/compiled_human_recognition.csv'))

humans_merged <- humans %>%
  group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
  summarize(num_correct = mean(correct_or_not)) %>%
  left_join(clip_by_image, by=c('unique_ids','category')) %>% # join with classification data 
  filter(!is.na(age))
```

```{r}
ggplot(humans_merged, aes(x=correct_or_not, y=num_correct)) +
  geom_jitter(alpha=.2, width=.1, height=.1) +
  geom_smooth(method='lm') +
  ylab('human recognition') +
  xlab('clip model recognition')+
  theme_few()
```

```{r}
by_category <- humans_merged %>%
  group_by(category) %>%
  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))

ggplot(by_category, aes(x=model_pc, y=humans_pc, label=category)) +
  geom_point() +
  geom_smooth(method='lm') +
  ylab('human recognition') +
  xlab('model recognition') +
  theme_few() +
  ggrepel::geom_label_repel()
```

### Correlates humans vs vgg classifications 
```{r}
# cor.test(humans_merged$num_correct, humans_merged$target_label_prob)
cor.test(humans_merged$num_correct, as.numeric(as.logical(humans_merged$correct_or_not)))
```

```{r}

category_by_age_by_cond <- humans_merged %>%
  group_by(category, age, condition) %>%
  summarize(humans_pc = mean(num_correct), model_pc = mean(correct_or_not, na.rm=TRUE))  %>%
  mutate(diff = (model_pc - humans_pc))

```

```{r}
ggplot(category_by_age_by_cond, aes(x=model_pc, y=humans_pc,color=age, label=category))+
  geom_point() +
  ylim(0,1) +
  xlim(0,1) +
  theme_few() +
  theme(aspect.ratio = 1) +
  facet_wrap(~category) +
  scale_color_viridis_c() +
  geom_abline(xintercept=0, color='grey')
  ggrepel::geom_label_repel(data = category_by_age_by_cond %>% filter(diff>.1), label.size=.1, max.overlaps=20) 
```

```{r}
cor_by_age_by_site_by_cond <- humans_merged %>%  
  group_by(unique_ids,category,condition,age, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = "model")

cor_by_age_by_site_by_cond_humans <- humans_merged %>%  
  group_by(unique_ids,category,condition,age, site) %>%
  summarize(avg_cor = mean(num_correct)) %>%
  group_by(age,condition, site) %>%
  multi_boot_standard(col = "avg_cor") %>%
  mutate(who = 'humans')

humans_and_models <- cor_by_age_by_site_by_cond %>%
  full_join(cor_by_age_by_site_by_cond_humans)

```

```{r}
summary(lmer(data=humans_merged, correct_or_not ~ condition*age + (1|unique_ids) + (1|category)))
```

```{r}
summary(lmer(data=humans_merged, num_correct ~ condition*age + (1|unique_ids) + (1|category)))

```

```{r}
base_size_chosen=12; smooth_alpha=.2
ggplot(humans_and_models, aes(age,mean, col = condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
  theme_few(base_size = base_size_chosen) + 
  labs(x='Age', y='Classification accuracy') +
  ylim(0,1) + 
  geom_smooth(span=10, alpha=.2) +
  geom_hline(yintercept = 1/12, linetype="dashed", color="grey") +
  facet_grid(who~site)
```

## How well does the model do on the images that humans unanimously recognize?
```{r}
easiest_to_recognize <- humans_merged %>%
  filter(num_correct == 1) %>%
  group_by(category) %>%
  summarize(model_correct = mean(correct_or_not), num_images= n()) %>%
  mutate(category = fct_reorder(category, -model_correct))
```

```{r}
clip_to_merge <- clip_by_image %>%
  select(-age) %>%
  rename(age = kid_age) %>% 
  select(age, unique_ids, category, correct_or_not) %>%
  mutate(model = 'clip')

vgg_vs_clip <- classification_data %>%
  select(-age) %>%
  rename(age = age_numeric, unique_ids = session_id) %>%
  mutate(model = 'vgg') %>%
  select(unique_ids, age, category, model, correct_or_not) %>%
  full_join(clip_to_merge)

```

```{r}
vgg_vs_clip_vs_humans <- vgg_vs_clip %>%
  left_join(humans_merged %>% select(unique_ids, category, num_correct) %>% rename(human_correct = num_correct))

```

```{r}
vgg_vs_clip_easy <- vgg_vs_clip_vs_humans %>%
  filter(human_correct == 1) %>%
  group_by(model, category) %>%
  summarize(model_correct = mean(correct_or_not), num_images = n()) %>%
  mutate(category = fct_reorder(category, -model_correct))
```
```{r}
vgg_vs_clip_easy_stats <- vgg_vs_clip_easy %>%
  summarize(avg_model_correct = mean(model_correct), sd_model_correct = sd(model_correct))

```

```{r}
summary(lmer(data = vgg_vs_clip_easy, model_correct ~ model + (1|category)))
```

```{r}
ggplot(vgg_vs_clip_easy, aes(x=category, y=model_correct, color=model)) +
  geom_point(aes(size = num_images)) +
  theme_few() +
  ylab('Model percent correct') +
  ylim(0,1) +
  ggtitle('CLIP vs VGG performance on very recognizable drawings')

```

```{r}

ggplot(easiest_to_recognize, aes(x=category, y=model_correct)) +
  geom_point(aes(size = num_images)) +
  theme_few() +
  ylab('CLIP percent correct') +
  ggtitle('CLIP performance on very recognizable drawings')

```

```{r}
ggplot(vgg_vs_clip_vs_humans, aes(x=correct_or_not, y=human_correct, color=model)) +
  theme_few() +
  geom_smooth(aes(group=model), method='lm') +
  geom_jitter(width=.2, height=.01, alpha=.2) +
  facet_grid(~model) +
  ylab('Average human recognition') +
  xlab('Model recognition') +
  scale_x_continuous(breaks = c(0,1))

```

```{r}
ggplot(vgg_vs_clip_vs_humans, aes(x=correct_or_not, y=human_correct, color=model)) +
  theme_few() +
  geom_smooth(aes(group=model), method='lm') +
  geom_jitter(width=.1, height=.01, alpha=.2) +
  facet_wrap(~category) +
  ylab('Average human recognition') +
  xlab('Model recognition')
```

### 2022-07-21 analysis/step4_get_features_and_classifications/1_extract_features/clip_embedding_devphotodraw.py

@@ -1,0 +1,231 @@
+from __future__ import division
+from __future__ import print_function
+from __future__ import absolute_import
+
+import copy
+import numpy as np
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from PIL import Image
+
+
+use_cuda = torch.cuda.is_available()
+        
+class FeatureExtractor():
+    
+    def __init__(self,paths, use_cuda=True, imsize=224, batch_size=32, cuda_device=0, cohort='kid',spatial_avg=True, dataset='rendered_111918'):
+        self.paths = paths
+        self.num_sketches = len(self.paths)
+        self.use_cuda = use_cuda
+        self.imsize = imsize
+        self.padding = 10
+        self.batch_size = batch_size
+        self.cuda_device = cuda_device
+        self.cohort = cohort ## 'kid' if analyzing kids' drawings; 'adult' if analyzing adults' drawings
+        self.spatial_avg = spatial_avg ## if true, collapse across spatial dimensions to just preserve channel activation
+        self.dataset = dataset ## if true, collapse across spatial dimensions to just preserve channel activation
+        
+    def extract_feature_matrix(self):
+        
+        def RGBA2RGB(image, color=(255, 255, 255)):
+            """Alpha composite an RGBA Image with a specified color.
+
+            Simpler, faster version than the solutions above.
+
+            Source: http://stackoverflow.com/a/9459208/284318
+
+            Keyword Arguments:
+            image -- PIL RGBA Image object
+            color -- Tuple r, g, b (default 255, 255, 255)
+
+            """
+            image.load()  # needed for split()
+            background = Image.new('RGB', image.size, color)
+            background.paste(image, mask=image.split()[3])  # 3 is the alpha channel
+            return background
+
+        def load_image(path, imsize=224, padding=self.padding, volatile=True, use_cuda=False):
+            im = Image.open(path)
+            
+            if self.cohort!='images':
+                im = RGBA2RGB(im)
+                
+                # crop to sketch only (reduce white space)
+                arr = np.asarray(im)
+                w,h,d = np.where(arr<255) # where the image is not white
+                if len(h)==0:
+                    print(path)  
+                try:
+                    xlb = min(h)
+                    xub = max(h)
+                    ylb = min(w)
+                    yub = max(w)
+                    lb = min([xlb,ylb])
[…]

### 2022-07-21 analysis/step4_get_features_and_classifications/1_extract_features/convert_to_csv.py

@@ -1,0 +1,15 @@
+import numpy as np
+import pandas as pd
+# categories = ["a bear", "a bed",  "a bee", "a bike", "a bird" , "a boat", "a book", "a bottle","a bowl","a cactus","a camel", "a car", "a cat","a chair", "a clock", "a couch", "a cow",  "a cup",   "a dog",   "a face",  "a fish",  "a frog",  "a hand",  "a hat", "a horse", "a house", "a key",   "a lamp",  "a mushroom",   "a person","a phone", "a piano", "a rabbit","a scissors","a sheep", "a snail", "a spider","a tiger", "a train", "a tree", "a TV",  "a watch", "a whale", "an airplane","an apple","an elephant" ,"an ice cream","an octopus"]
+categories = ["cat", "bird","rabbit", "house", "chair","bike","airplane","hat","car","watch","cup","tree"]
+
+
+data_32 = np.load('CLIP_FEATURES_batch32_kid_photodraw_compiled.npy')
+
+# data = np.load('CLIP_FEATURES_kid_photodraw_compiled.npy')
+X_out = pd.DataFrame(data_32)
+X_out.columns = categories
+X_out.to_csv('CLIP_FEATURES_kid_photodraw_compiled_drawing_cue.csv')
+
+# np.savetxt('CLIP_FEATURES_kid_photodraw_compiled.csv', data, delimiter=",")
+

### 2022-07-21 analysis/step4_get_features_and_classifications/1_extract_features/extract_features_clip_devphotodraw.py

@@ -1,0 +1,141 @@
+from __future__ import division
+
+import torch
+import torchvision.models as models
+import torch.nn as nn
+import torchvision.transforms as transforms
+import torch.nn.functional as F
+from torch.autograd import Variable
+
+from glob import glob
+import os
+
+import numpy as np
+import pandas as pd
+import json
+import re
+
+from PIL import Image
+import base64
+
+from clip_embedding_devphotodraw import *
+
+# retrieve sketch paths
+def list_files(path, ext='png'):
+    result = [y for x in os.walk(path) for y in glob(os.path.join(x[0], '*.%s' % ext))]
+    return result
+
+def check_invalid_sketch(filenames,invalids_path='images_to_exclude.txt'):    
+    if not os.path.exists(invalids_path):
+        print('No file containing invalid paths at {}'.format(invalids_path))
+        invalids = []        
+    else:
+        print('found invalids file...')
+        x = pd.read_csv(invalids_path, header=None)
+        x.columns = ['filenames']
+        invalids = list(x.filenames.values)
+    valids = []   
+    basenames = [f.split('/')[-1] for f in filenames]
+    for i,f in enumerate(basenames):
+        if f not in invalids:
+            valids.append(filenames[i])
+    return valids
+
+def make_dataframe(Labels,Ages,Sessions):    
+    Y = pd.DataFrame([Labels,Ages,Sessions])
+    Y = Y.transpose()
+    Y.columns = ['label','age','session']   
+    return Y
+
+def make_dataframe_photodraw(Labels,Ages,Sessions,Conditions):    
+    Y = pd.DataFrame([Labels,Ages,Sessions,Conditions])
+    Y = Y.transpose()
+    Y.columns = ['label','age','session','condition']   
+    return Y
+
+# def normalize(X):
+#     X = X - X.mean(0)
+#     X = X / np.maximum(X.std(0), 1e-5)
+#     return X
+
+def preprocess_features(Features, Y):
+    _Y = Y.sort_values(['label','age','session'])
+    inds = np.array(_Y.index)
+    _Features = Features[inds] # hack just to avoid redoing things, no normalizing here
+    # _Features = normalize(Features[inds]) # no normalizing for clip
+    _Y = _Y.reset_index(drop=True) # reset pandas dataframe index
+    return _Features, _Y
+
+def save_features(Features, Y, cohort, dataset):
+    if not os.path.exists('./features'):
[…]

### 2023-05-02 analysis/step6_main_analyses/devphotodraw_main_analysis.Rmd
fix typo

@@
 base_size_chosen=12; smooth_alpha=.2
-ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = conditionf)) +
+ggplot(humans_and_models_no_site, aes(age_numeric,mean, col = condition)) +
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), position=position_dodge(width=.2)) +
@@
 p3
+```
+
+##
+```{r}
+
 ```

### 2023-05-02 writing/Manuscript_2022.Rmd
updates to submission .rmd

@@
 library(papaja)
+library(NatParksPalettes)
 ```
@@
 
+## Extra models after peer-review
+
+### composite effort score
+```{r}
+
+d <- d %>%
+  ungroup %>%
+  mutate(avg_tracing_score_scaled = scale(avg_tracing_score),
+         mean_intensity_scaled = scale(mean_intensity),
+         draw_duration_scaled = scale(draw_duration)) %>%
+  mutate(effort_compiled = avg_tracing_score_scaled + mean_intensity_scaled + draw_duration_scaled)
+```
+
+```{r}
+
+full_model_with_effort_combined <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
+                      scale(avg_tracing_score) +
+                      scale(effort_compiled) + 
+                      (condition | unique_ids) +
+                      (condition*scale(age_numeric) | category),
+      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+
+full_model_with_effort_combined_out = summary(full_model_with_effort_combined)
+
+```
+
+```{R}
+tracing_score_by <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
+                      scale(avg_tracing_score) +
+                      scale(effort_compiled) + 
+                      (condition | unique_ids) +
+                      (condition*scale(age_numeric) | category),
+      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+```
+
 ```{r}
@@
 
+```{r}
+lmer(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site + (1|unique_ids))
+```
+
 ```{r tracing, fig.env="figure", out.width = "\\textwidth", fig.pos = "H", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "Average tracing scores across age and site; each dot represents an average tracing score obtained for each participant and are slightly jittered.

### 2023-05-02 writing/Manuscript_2023.Rmd
updates to revision .rmd

--- 2023-05-02 writing/Manuscript_2022.Rmd
@@
 
-```{r load-classifications}
-# classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2760.csv')) %>%
-#   as_tibble() %>%
-#   mutate(age_numeric = age) %>%
-#   mutate(age = paste('age',age,sep="")) %>%
-#   mutate(age = as.factor(age)) %>%
-#   mutate(category = target_label) %>% 
-#   dplyr::select(-X, -X.1, -index) %>%
-#   mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
-#                            !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
-#   mutate(site = as.factor(site)) 
-```
-
 ```{r load-metadata}
@@
 
-```{r join-data}
-# model_classifications <- classification_data %>%
-#   mutate(unique_ids = session_id) %>%
-#   left_join(all_meta_cleaned %>% dplyr::select(unique_ids, category, condition, num_strokes, draw_duration, mean_intensity)) %>% # need to select columns so we don't get join errors 
-#   left_join(tracing_by_sub)
-#   
-# 
-# # bizarrely, there are a few drawings from THU for which stroke data didn't save -- technical error.
-# # this was checked directly in mongodb database -- no idea why, assuming bad internet.
-# tech_error_drawings <- model_classifications %>%
-#   filter(is.na(num_strokes))
-# # filter out tech error drawings from dataset (24)
-# model_classifications <- model_classifications%>%
-#   filter(!is.na(num_strokes))
-
-```
-
 ```{r load-human-recognition}
@@
 
-# humans_and_models_merged <- humans %>%
-#   group_by(unique_ids, category, image_name_short) %>% # group by each drawing of each category
-#   summarize(prop_correct = mean(correct_or_not)) %>%
-#   left_join(model_classifications, by=c('unique_ids','category')) %>% # join with classification data 
-#   filter(!is.na(age))
 ```
@@
 # human_v_model = cor.test(humans_and_models_merged$prop_correct, humans_and_models_merged$correct_or_not)
+```
+
+```{r}
+edu = c(17,83,298,953,202,2018)
+edu_out <- edu %>%
+  as_tibble() %>%
+  rownames_to_column()
 
@@
 To be conservative, we thus fit all of our models to the human recognition data.]
-
-<!-- ### Automated recognition scores -->
-<!-- We used a combination of deep convolutional neural network (CNN) features and logistic regression to obtain automated recognition scores, per our preregistered protocol.  -->
-<!-- To encode the high-level visual features of each drawing, we passed each drawing into VGG-19 [@simonyan2014very], a deep CNN architecture that had been pre-trained on Imagenet classification and implemented in PyTorch [@paszke2017automatic].
--->
-<!-- We extracted the feature representation of this drawing in the second-to-last layer of this network (FC6).  -->
-<!-- Feature representations in this layer consist of flat 4096-dimensional vectors, to which we applied channel-wise normalization.  -->
-<!-- Next, we used these features to train a leave-one-out 12-way logistic classifier with L2 regularization (tolerance = .1, regularization = .1), and used this classifier to predict the category label for each drawing.
--->
-<!-- To ensure a balanced distribution of drawings appearing in the training set, we randomly undersampled such that there was an equal number of drawings for each combination of geographical site (San Jose, Beijing) and the 12 categories.
--->
-<!-- No additional metadata about the age of the child who produced each sketch was provided to the model. -->
-<!-- This procedure was repeated for each drawing in the dataset, yielding a binary recognition score for each drawing. -->
 
@@
 
+```{r}
 ## Extra models after peer-review
-
 ### composite effort score
-```{r}
 
@@
 ```{r}
-
 full_model_with_effort_combined <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
@@
 
-```{R}
-tracing_score_by <- glmer(cbind(num_correct, num_incorrect) ~ condition*scale(age_numeric)*site +
-                      scale(avg_tracing_score) +
-                      scale(effort_compiled) + 
-                      (condition | unique_ids) +
-                      (condition*scale(age_numeric) | category),
-      data = d, family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+```{r}
+# correct_by_effort_and_site <- glmer(cbind(num_correct, num_incorrect) ~ scale(draw_duration)*site + age_numeric + condition +
+#                       (1 | unique_ids) +
+#                       (scale(age_numeric) | category),
+#       data = d,family='binomial', control=glmerControl(optCtrl=list(maxfun=20000),optimizer=c("bobyqa")))
+# 
+# correct_by_effort_and_site_out = summary(correct_by_effort_and_site)
+```
+
+```{r}
+drawing_duration_by_site <- lmer(scale(draw_duration) ~ site*condition + 
+                      (1 | unique_ids) +
+                      (scale(age_numeric) | category),
+      data = d)
+
+drawing_duration_out = summary(drawing_duration_by_site)
+
+papaja::apa_table(drawing_duration_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the how long children spent on each drawing as a function of site (Beijing vs.
+San Jose) and drawing condition.')
+```
+```{r}
+num_strokes_by_site <- lmer(scale(num_strokes) ~ site*condition  + 
+                      (1 | unique_ids) +
+                      (scale(age_numeric) | category),
+      data = d)
+
+num_strokes_by_site_out = summary(num_strokes_by_site)
+papaja::apa_table(num_strokes_by_site_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the number of strokes children made on each drawing as a function of site (Beijing vs.
+San Jose) and drawing condition.')
+```
+
+```{r}
+intensity_by_site <- lmer(scale(mean_intensity) ~ site*condition  + 
+                      (1 | unique_ids) +
+                      (scale(age_numeric) | category),
+      data = d)
+
+intensity_by_site_out = summary(intensity_by_site)
+papaja::apa_table(intensity_by_site_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the amount of "ink" (i.e., average drawing intensity) children used on each drawing as a function of site (Beijing vs.
+San Jose) and drawing condition.')
+```
+
+```{r}
+effort_by_site <- lmer(scale(effort_compiled) ~ site*age_numeric  + 
+                      (1 | unique_ids) +
+                      (scale(age_numeric) | category),
+      data = d)
+
+effort_out = summary(effort_by_site)
+papaja::apa_table(effort_out$coefficients, caption='"Model coefficients from a linear mixed mode predicting the amount of overall effort children used on each drawing (sum of z-scored effort covariates -- ink, strokes, and time) as a function of site (Beijing vs.
+San Jose) and drawing condition.')
+```
+
+```{r}
+indiv_by_acc <- d %>%
+  group_by(unique_ids, avg_tracing_score_scaled) %>%
+  summarize(prop_correct = mean(prop_correct))
+
+cor.test(indiv_by_acc$avg_tracing_score_scaled, indiv_by_acc$prop_correct)
+```
+
+```{r}
+covariates <- d %>% select(num_strokes, draw_duration, mean_intensity, avg_tracing_score)
+
+covariates_cor_table = round(cor(covariates),3)
+rownames(covariates_cor_table)<-c('Number of strokes','Drawing duration (s)','Mean intensity','Average tracing score')
+colnames(covariates_cor_table)<-c('Number of strokes','Drawing duration (s)','Mean intensity','Average tracing score')
+
+papaja::apa_table(covariates_cor_table, caption="Pearsons corellation coefficients for all effort covariates (estimed for each drawing) and tracing scores (estimated by each participant).")
+
 ```
@@
 ```{r check-drawing-time}
-# drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
-#                       (1 | unique_ids) +
-#                       (1 | category),
-#       data = d)
-# drawing_time_out = summary(drawing_time)
+drawing_time <- lmer(draw_duration ~ condition*scale(age_numeric)*site +
+                      (1 | unique_ids) +
+                      (1 | category),
+      data = d)
+drawing_time_out = summary(drawing_time)
 ```
@@
 
-# xtable(full_model_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.")
-
 papaja::apa_table(full_model_out$coefficients, caption='"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.')
@@
 ```
-
-<!-- \begin{table}[ht] -->
-<!-- \centering -->
-<!-- \begin{tabular}{rrrrr} -->
-<!--   \hline -->
-<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
-<!--   \hline -->
-<!-- Intercept & 1.39 & 0.16 & 8.51 & 0.000 \\  -->
-<!--   Task & 0.02 & 0.26 & 0.08 & 0.936 \\  -->
-<!--   Age & 1.16 & 0.14 & 8.59 & 0.000 \\  -->
-<!--   Site & 0.60 & 0.16 & 3.71 & 0.000 \\  -->
-<!--   Task*Age & -0.14 & 0.19 & -0.73 & 0.467 \\  -->
-<!--   Task*Site & -0.19 & 0.16 & -1.17 & 0.244 \\  -->
-<!--   Age*Site & 0.15 & 0.16 & 0.91 & 0.361 \\  -->
-<!--   Task*Age*Site & 0.06 & 0.16 & 0.38 & 0.706 \\  -->
-<!--    \hline -->
-<!-- \end{tabular} -->
-<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing for the main experimental contrasts.}  -->
-<!-- \end{table} -->
 
@@
 
-# xtable(full_model_with_effort_out$coefficients, digits=c(2,2,2,2,3),"Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.")
 ```
-
-<!-- \begin{table}[ht] -->
-<!-- \centering -->
-<!-- \begin{tabular}{rrrrr} -->
-<!--   \hline -->
-<!--  & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\  -->
-<!--   \hline -->
-<!-- Intercept & 1.34 & 0.15 & 8.68 & 0.000 \\  -->
-<!--   Task & -0.04 & 0.26 & -0.16 & 0.873 \\  -->
-<!--   Age & 0.97 & 0.14 & 7.05 & 0.000 \\ 24 -->
-<!--   Site & 0.80 & 0.16 & 5.04 & 0.000 \\  -->
-<!--   Est. tracing score & 0.35 & 0.07 & 4.82 & 0.000 \\  -->
-<!--   Avg. intensity & 0.06 & 0.02 & 2.47 & 0.013 \\  -->
-<!--   Draw duration & -0.25 & 0.03 & -7.58 & 0.000 \\  -->
-<!--   Number of strokes & 0.33 & 0.03 & 10.99 & 0.000 \\  -->
-<!--   Task*Age & -0.17 & 0.19 & -0.90 & 0.370 \\  -->
-<!--   Task*Site & -0.22 & 0.16 & -1.38 & 0.168 \\  -->
-<!--   Age*Site & 0.04 & 0.16 & 0.22 & 0.823 \\  -->
-<!--   Task*Age*Site & 0.07 & 0.16 & 0.43 & 0.665 \\  -->
-<!--    \hline -->
-<!-- \end{tabular} -->
-<!-- \caption{Model coefficients from a generalized linear mixed mode predicting the recognizability of each drawing as a function the both the main experimental contrasts (task, site, and age) as well as several effort covariates and individual's estimates tracing abilities.}  -->
-<!-- \end{table} -->
 
@@
 ```{r}
-lmer(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site + (1|unique_ids))
+tracing_score_stats = summary((lm(data = tracing_scores_indiv, avg_tracing_score ~ scale(age_numeric)*site)))
+
+papaja::apa_table(tracing_score_stats$coefficients, caption='"Model coefficients from a  linear regression predicting the average tracing score of each child as a function of their age and the site at which they participated.')
+
 ```
@@
   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=.1) +
-  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5, size=.3) +
+  geom_jitter(data = tracing_scores_indiv, aes(x=age_numeric, y=avg_tracing_score), width=.2, height=.01, alpha=.5, size=.5) +
   theme_few(base_size = base_size_chosen) +
@@
   theme(legend.position = "none", aspect.ratio=1.3) +
-  geom_smooth(span = 10,alpha=smooth_alpha, aes(group =site), size=.5)  +
+  geom_smooth(span = 20,alpha=smooth_alpha, aes(group =site), size=.5)  +
   scale_x_continuous(breaks=c(4,5,6,7,8,9)) +
@@
 
-# Acknowledgements  
+# Acknowledgements  a
 [BLINDED]
@@
 ```
+
+<!-- # Appendix Table B1: drawing duration -->
+<!-- # Appendix Table B2: intensity -->
+<!-- # Appendix Table B3: strokes -->
+<!-- # Appendix Table B4: compiled effort -->
 
